### 2013-02-18 omrp.tex
Initial commit

\documentclass{article}

\usepackage{latexsym}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{enumerate}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}

\newtheorem{theorem}{Theorem}
\renewcommand{\thetheorem}{ \arabic{theorem}}
\newtheorem{corollary}[theorem]{Corollary}
\renewcommand{\thecorollary}{\arabic{corollary}}
\newtheorem{definition}{Definition}
\renewcommand{\thedefinition}{\arabic{definition}}
\newtheorem{lemma}{Lemma}
\renewcommand{\thelemma}{ \arabic{lemma}}
\newtheorem{proposition}{Proposition}
\renewcommand{\theproposition}{ \arabic{proposition}}
\newtheorem{remark}{Remark}
\renewcommand{\theremark}{ \arabic{remark}}

% Frequently used general mathematics
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\Rp}{\R^+}
\newcommand{\Z}{{\mathbb{Z}}}
\newcommand{\Zp}{\Z^+}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}

% Commands for probability
\newcommand{\p}[1]{\mathbb{P} \left\{ #1 \right\}}
\newcommand{\e}[1]{\mathbb{E} %\left[ 
#1 %\right]
}
\newcommand{\ee}[2]{\mathbb{E}_{#1} \left[ #2 \right]}
\newcommand{\var}[1]{\mathrm{Var} \left( #1 \right)}
\newcommand{\cov}[1]{\mathrm{Cov} \left( #1 \right)}
\newcommand{\cor}[1]{\mathrm{Corr} \left( #1 \right)}
\newcommand{\varh}[1]{\widehat{\mathrm{Var}} \left( #1 \right)}
\newcommand{\vart}[1]{\widetilde{\mathrm{Var}} \left( #1 \right)}
\newcommand{\vartg}[1]{\widetilde{\mathrm{Var}}_\gamma \left( #1 \right)}
\newcommand{\varhat}{\widehat{\mathrm{Var}}}

% Definitions of variables
\newcommand{\X}{X}
\newcommand{\x}{x} %% CHANGED THIS NOT TO BE MATHBF 
\newcommand{\xh}{{\hat{\x}}}
\newcommand{\xs}{\x^*}
\newcommand{\xit}{\xi}  %% CHANGED THIS TO BE WITHOUT TILDE! 
\newcommand{\xiti}{\xit^i}
\newcommand{\zs}{z^*}
\newcommand{\nb}{\left\lfloor\tfrac{n-m}{\gamma}\right\rfloor+1}
\newcommand{\nbl}{\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1}
\newcommand{\gammab}{\bar{\gamma}}
\newcommand{\ogb}{\tfrac{1}{\gammab}}
\newcommand{\cogb}{\left\lceil\ogb\right\rceil}

% Definitions for overlapping batches
\newcommand{\gb}{\bar{G}}
\newcommand{\gbb}{\bar{\gb}}
\newcommand{\db}{\bar{D}}
\newcommand{\dbb}{\bar{\db}}

% Used only for review of Meketon.  Should probably rewrite these.
%\newcommand{\xb}{\bar{x}}
%\newcommand{\xbb}{\bar{\xb}}
%\newcommand{\sx}{\{X_t, t \geq 0\}}
%\newcommand{\sxr}{\{X^n\}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\yb}{\bar{y}}
\newcommand{\ybb}{\bar{\yb}}

\DeclareMathOperator*{\argmin}{argmin}

\newcommand{\Keywords}[1]{\par\noindent 
{\small{\em Keywords\/}: #1}}

%#########################################################
%*
%*  The Document.
%*
\begin{document}

\title{Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}

% AUTHOR: Enter the authors of the article, see end of the example document for further examples
\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 520-621-2605. Fax:+1 520-621-6555}\\[6pt]
{\small
      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA, \texttt{dlove@math.arizona.edu}} \\
{\small 
      $^{b}$ Systems and Industrial Engineering, University of Arizona, Tucson, AZ 85721, USA, \texttt{guzinb@sie.arizona.edu}}}

%% ONE WAY: JUST NAMES ON TOP, EVERYTHING ELSE AS FOOTNOTE
%\author{David~Love%
%\thanks{D.\ Love: Interdisciplinary Graduate Program in Applied Mathematics,
%University of Arizona, Tucson, AZ 85721, USA. E-mail: \texttt{dlove@math.arizona.edu}}%
%\ \ and G\"{u}zin~Bayraksan%
%\thanks{G.\ Bayraksan: (corresponding author) Department of Systems and Industrial Engineering, University of Arizona, Tucson, AZ 85721, USA. E-mail: \texttt{guzinb@sie.arizona.edu}. Tel.: +1 520-621-2605. Fax:+1 520-621-6555}}

%%  ANOTHER WAY: ALL ON TOP, TWO DIFFERENT ONES SIDE BY SIDE
%\author{David Love \\ [6pt]
%       \texttt{dlove@math.arizona.edu} \\
%        Program in Applied Mathematics \\
%        University of Arizona \\
%        Tucson, AZ 85721, USA \\
% Multiple authors are entered as follows.
% You may also need to adjust the titlevbox size in the preamble - search for titlevboxsize
%\and
%        G\"{u}zin Bayraksan \\ [6pt]
%        \texttt{guzinb@sie.arizona.edu} \\
%        Department of Systems and Industrial Engineering \\
%        University of Arizona \\
%        Tucson, AZ 85721, USA
%}
\date{}

\maketitle

\begin{abstract}
We investigate the use of overlapping batches for assessing solution quality in stochastic programs. Motivated by the original use of overlapping batches in simulation, we present a variant of the multiple replications procedure that reuses data via variably overlapping batches to obtain alternative variance estimators.  These estimators have asymptotically lower variances, where the degree of variance reduction depends on the amount of overlap.  We provide several desired asymptotic properties and present computational results to examine small-sample behavior.\smallskip

	\Keywords{Sample average approximation; Optimality gap estimation; Overlapping batches; Stochastic programming}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}

We consider a stochastic program of the form
\begin{align} \tag{SP} \label{eq:sto_prog} 
	z^* & = \min_{\x \in X} \e{f(\x,\xit)},
\end{align}
where $\x$ is a vector of decision variables, $\xit$ is a vector of random variables, and $X$ is the feasible set, which is assumed to be independent of $\xit$.  Further, it is assumed that the distribution of $\xit$ is known and that we can sample from it.  Even though we will impose a more restrictive moment condition later, we assume that $\e{f(\x,\xit)}$ is well defined and finite for all $\x \in X$ and (\ref{eq:sto_prog}) has a finite optimal solution achieved on $X$.  Let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (iid) sample from the distribution of $\xit$.  A sampling approximation of (\ref{eq:sto_prog}) is given by
\begin{align} \tag{SP$_m$} \label{eq:sto_prog_m}
	z_m^* & = \min_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xiti).
\end{align}
We denote an optimal solution to (\ref{eq:sto_prog}) as $\xs$ and an optimal solution to (\ref{eq:sto_prog_m}) as $\xs_m$.

We are interested in assessing the quality of a candidate solution $\xh \in X$, which may have been found in any way, defined by its optimality gap $\e{f(\xh,\xit)} - \zs$.  This is important in practice since (\ref{eq:sto_prog}) typically cannot be solved exactly, so one only has an approximate solution $\xh$ without verification of its quality.  Assessing solution quality is also a critical component of stopping criteria in algorithms.  
In many fields of optimization, it is common to evaluate an upper bound on the optimality gap through relaxations such as integrality or Lagrangian relations.  In stochastic programming, given a sample size $m$, an upper bound on the optimality gap can be obtained by $\e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}$ due to the inequality $\e{\zs_m} \leq \zs$.  This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$ \cite{Mak1999,norkin_pflug_ruszczynski_98}.  For stochastic programs, one way to estimate an upper bound on optimality gaps is through Monte Carlo sampling. A straightforward estimate of $\e{f(\xh,\xit)}$ is the sample mean, $\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti)$. Instead of $\e{\zs_m}$, simply $\zs_m$ can be used.  The resulting point estimator is  $G_m(\xh) = \frac{1}{m} \sum_{i=1}^m f(\xh,\xiti) - \zs_m$.  Here, we assume the same observations $\xit^1, \dots, \xit^m$ are used in both terms of $G_m(\xh)$.

Computing $G_m(\xh)$ involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator $\zs_m$, which complicates the statistical analysis. To enable statistical inference, the \emph{Multiple Replications Procedure} (MRP) of Mak et.\ al.\ \cite{Mak1999} generates $k$ independent estimators of $G_m(\xh)$, each using sample size $m$ and averages them to obtain a point estimator.  To form confidence intervals, the sample variance of these estimators is calculated.  This is essentially a nonoverlapping batch means type estimator ($k$ batches of size $m$) commonly used in simulation \cite{law_07}. We further review MRP estimators in \S \ref{ssec:mrp}.

In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \cite{Meketon1984}. Suppose each batch contains $m$ observations and that there are a total of $2m$ observations.  In the nonoverlapping case, there are only two batches: the first batch contains observations $\xit^1, \xit^2, \dots, \xit^m$ and the second batch contains observations $\xit^{m+1}, \xit^{m+2}, \dots, \xit^{2m}$.   Meketon and Schmeiser \cite{Meketon1984} overlap the batches so that the first batch is as before, the second batch now consists of $\xit^2, \xit^3, \dots, \xit^{m+1}$, the third batch contains observations $\xit^3, \xit^4, \dots, \xit^{m+2}$ and so on. As a result, the corresponding batch means are no longer independent. However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual 
batch means variance estimator but the bias of the two 
estimators is approximately the same.  The idea 
of 
overlapping batches can be used for variance estimators of non-means \cite{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \cite{Alexopoulos01012007,Alexopoulos2007}. In this paper, we explore its use for assessing solution quality in stochastic programs.  Similar to Welch \cite{Welch1987} and Song and Schmeiser \cite{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting. We present conditions under which the point estimators are strongly consistent (that is, they converge almost surely (a.s.) as opposed in to in probability; referred to simply as consistent from this point on), the same variance reduction benefits are achieved, and the resulting confidence intervals are asymptotically valid.  We present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  Our experiments 
indicate that the asymptotic 
variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.

The rest of the paper is organized as follows.  In the next section, we review relevant background information.  We first discuss the overlapping batch means in \S \ref{ssec:obm} and then briefly go over the multiple replications procedure in \S \ref{ssec:mrp}.  In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with variable overlap.  In \S \ref{sec:theory}, we prove several asymptotic properties of the OMRP estimators and in \S \ref{sec:comp}, we test the performance of OMRP on three problems.  We end in \S \ref{sec:concl} with a summary and conclusions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\label{sec:background}

\subsection{Overlapping Batch Means} \label{ssec:obm}
Consider a covariance stationary stochastic process which has mean $\mu$ and variance $\sigma^2$.  The task is to estimate $\mu$ given some realization of the stochastic process $\y = (y^1, y^2, \dots, y^n)$.  Typically, this involves forming a confidence interval of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$.  The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \cite{law_07}.  We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.

Nonoverlapping batch means takes $n$ observations, $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume for now $n = mk$).  The sample mean of each batch is then computed as
$
	\yb_j = \frac{1}{m} \sum_{i=1}^{m} y^{m(j-1)+i}, j = 1,2, \dots, k,
$
and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  The sample variance of the batch means is calculated as
\begin{equation} \label{eq:var}
	\varhat(\ybb) = \frac{m}{n}\frac{1}{k-1} \sum_{j=1}^k \left( \yb_j - \ybb \right)^2,
\end{equation}
and the $(1-\alpha)$-level approximate confidence interval (CI) is formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.  Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$.

Overlapping batch means modifies this idea by taking batches given by $\yb_j(m) = \frac{1}{m} \sum_{i=1}^{m} y^{(j-1)+i}$, for $j = 1, \dots, n-m+1$.  This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  Given this, the sample variance estimator is updated to
\begin{equation} \label{eq:overlap_variance_def}
	\vart{\ybb} = \frac{1}{(\tfrac{n}{m}-1)(n - m + 1)}\sum_{j=1}^{n-m+1} (\yb_j(m) - \ybb)^2.
\end{equation}
Meketon and Schmeiser \cite{Meketon1984} show several attractive properties of the overlapping batches variance estimator, the two most important of which are: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.  That is, 
\begin{equation} \label{eq:asym_var}
	\frac{ \var{\vart{\ybb}} }{ \var{\varhat(\ybb)} } \rightarrow \frac{2}{3}
\end{equation}
in the limit as batch size $m$ and then the number of batches $(n/m)$ tend to infinity.  Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \cite{Meketon1984}.  The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for iid data for all finite $m$ and $n$ with the same asymptotic benefits \cite{Song1992}.  The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.

Welch \cite{Welch1987} established the relationship between OBM and spectral estimators and also considered partial overlap, see also \cite{Song1992}.  In our application to assessment of solution quality, we also consider varying the amount of overlap between neighboring batches.  We defer this discussion on variable overlap to \S \ref{ssec:overlap} and continue with a brief review of MRP.

\subsection{Multiple Replications Procedure} \label{ssec:mrp}

Given a candidate solution $\xh \in \X$ to (\ref{eq:sto_prog}), the task is to estimate its optimality gap $\e{f(\xh,\xit)} - \zs$.  Recall that MRP uses the upper bound on the optimality gap, $\e{f(\xh,\xit)} - \e{\zs_m}$ (for a given sample size $m$), to construct a point estimator and a CI using the nonoverlapping batches method described above.  Again, taking $n$ observations of the random variables and splitting them into $k$ batches of batch size $m$, define 
\begin{equation} \label{eq:mrp_gap}
	\gb_j = \frac{1}{m} \sum_{i = 1}^{m} f(\xh, \xit^{m(j-1)+i}) - \min_{\x \in X} \frac{1}{m} \sum_{i=1}^{m} f(\x, \xit^{m(j-1)+i}), \ \ \ \ j = 1,2, \dots, k.
\end{equation}
Since we are assessing the quality of a given solution $\xh \in \X$, we suppress it from the notation. $\gb_j$ is similar to $\yb_j$ except that the second term on the right-hand side of (\ref{eq:mrp_gap}) minimizes a sample mean.  As before, after $k$ estimates are obtained, the overall mean of these estimates $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  The sample variance is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in a one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$ that has a level of significance which is approximately $\alpha$.

Notice that the minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  Thus, we can expect that the true probability of the optimality gap residing within the confidence interval to be greater than the $1 - \alpha$ suggested by the above calculation.  This is shown empirically in Bayraksan and Morton \cite{Bayraksan2006}, which also suggests additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.  See also \cite{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.

An advantage of MRP is its applicability to a wide range of problems.  With iid sampling, (\ref{eq:sto_prog}) can be linear or nonlinear, $\X$ can include integrality constraints or not.  It is also easy to implement, thus, has been applied to a variety of problems, see e.g., \cite{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \cite{wang_ahmed_08} and stochastic dominance \cite{hu2010sample} constraints.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overlapping Multiple Replications Procedure} 
\label{sec:omrp}

Our aim is to apply the idea of overlapping batches to MRP.  We note several differences in this setting compared to the simulation setting.  In simulation, the point of interest is estimating the variance of the sample mean of a covariance stationary process.  We are interested in estimating the variance of an optimality gap estimator.  Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  First, minimization changes the statistical properties of sample means.  For instance, the central limit theorem may not hold for a minimized sample mean even though it holds for each $\x \in \X$.  We overcome this difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  The nonoptimized counterparts have the desired statistical properties and we establish convergence of the optimality gap estimators to their nonoptimized counterparts. Second, once the data 
is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  In our setting, due to the solution of a sampling problem (SP$_m$), the computational effort can increase with data reuse.  Fortunately, near-optimal variance reduction can be obtained by partially overlapping the batches.  Partial overlap results in a fewer number of batches, hence fewer number of optimization problems need to be solved.  Moreover, in many solution methods, warm-starting can be used to solve sampling approximations with overlapping samples, considerably reducing solution time.

We begin our discussion with variably overlapping batches and then define the estimators of OMRP.

\subsection{Variably Overlapping Batches} 
\label{ssec:overlap}

As before, let $m$ denote the batch size, $n$ the total sample size and $k = \lfloor \tfrac{n}{m} \rfloor$ be the number of nonoverlapping batches.  In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of Meketon and Schmeiser \cite{Meketon1984}.  The sample mean of each batch estimator is calculated similarly, 
$
\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, \nb, 
$
where $\nb$ is the number of batches used given $n$, $m$ and $\gamma$.  The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
\begin{equation} \label{eq:variance_gamma}
	\vartg{\ybb} = \frac{1}{\left( \tfrac{n}{m} - 1 \right) \left( \nb \right)}  \sum_{j=1}^{\nb} (\yb_j - \ybb)^2.
\end{equation}
Note that with $\gamma=1$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:overlap_variance_def}) and with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).

The amount of asymptotic variance reduction in this estimator depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$.  For example, when $\gamma = 1$ (or $\gammab=0$; the maximally overlapping case), the variance is reduced to two-thirds ($66.67\%$) of the original nonoverlapping case, as given in (\ref{eq:asym_var}).  When 75\% of observations overlap (i.e., when $\gamma = m/4$ or $\gammab = 1/4$), the variance is $33/48$th of the original ($68.75\%$), which is near-optimal.   When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  In general, from the spectral analysis given in Welch \cite{Welch1987}, the variance is reduced to
\begin{equation} \label{eq:var_reduct_formula}
	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right) = -\gammab\left( 1 - 2\gammab\cogb + \gammab^2\cogb^2 \right) + 2\gammab\cogb\left(1-\gammab\cogb\right) + \frac{2}{3}\gammab^3\cogb^3 + \frac{1}{3}\gammab^3\cogb
\end{equation}
of the nonoverlapping case.  If $\ogb$ is an integer, the terms in parentheses vanish and (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.

A $(1-\alpha)$-level approximate CI on the mean can be formed using variably overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \cite{Welch1987}.  If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$ and for maximally overlapping batches, $d_{\gamma} = \frac{3}{2}$.

\subsection{Definition of Estimators for OMRP}
In order to apply overlapping batches to MRP, we need to keep track of solutions to sampling problems (SP$_m$) for each batch of size $m$.  Toward this end, let $B(i)$ denote the set of batches $j \in \left\{1, 2, \dots, \nb \right\}$ observation $\xiti$ is used in, $i = 1, 2, \dots, n$.  See Figure \ref{fig:overlap_nonint} for an example with $n=18$, $m = 6$ and $\gamma = 2$.  Here, the first batch uses observations $\xit^1, \xit^2, \xit^3, \xit^4, \xit^5, \xit^6$, the second batch uses $\xit^3, \xit^4, \xit^5, \xit^6, \xit^7, \xit^8$, and so on.  So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  We use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch; $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.

\begin{figure}[htb!]
	\centering
	\begin{tabular}{*{18}{c}}
		$\xit^1$ & $\xit^2$ & $\xit^3$ & $\xit^4$ & $\xit^5$ & $\xit^6$ & $\xit^7$ & $\xit^8$ & $\xit^9$ & $\xit^{10}$ & $\xit^{11}$ & $\xit^{12}$ & $\xit^{13}$ & $\xit^{14}$ & $\xit^{15}$ & $\xit^{16}$ & $\xit^{17}$  & $\xit^{18}$ \\
% 		First Set of Batches
		\multicolumn{6}{l}{[---------------1-----------------]} &
		\multicolumn{6}{l}{[-----------------4------------------]} &
		\multicolumn{6}{l}{[------------------7--------------------]} \\
% 		Third set of Batches
		& & \multicolumn{6}{l}{[---------------2-----------------]} &
		\multicolumn{6}{l}{[------------------5--------------------]} \\
% 		Fifth set of Batches
		& & & & \multicolumn{6}{l}{[---------------3-----------------]} &
		\multicolumn{6}{l}{[------------------6--------------------]} \\
	\end{tabular}
	\caption{Visual representation of overlapping batches with $n = 18$, $m = 6$ and $\gamma = 2$.  The brackets show which observations are used in each batch, and the numbers inside each bracket show the batch number $j$.}
	\label{fig:overlap_nonint}
\end{figure}

The results on overlapping batch means occur in the limit as $n, m, k=n/m \rightarrow \infty$ \cite{damerdji1994strong,damerdji1995mean,Meketon1984,Song1992,Welch1987}.  Let $n_l, m_l$ and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$ as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  Now we are ready to define the estimators for OMRP.

\begin{align}
	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xh,\xit^{\gamma_l(j-1)+i}) - \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xs_j,\xit^{\gamma_l(j-1)+1}),\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
	VG_l & = \dfrac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
\end{align}

The optimality gap estimator for each batch $\gb_{lj}$ is defined like (\ref{eq:mrp_gap}) for general values of the nonoverlap parameter $\gamma_l$.  We just removed the minimization in (\ref{eq:mrp_gap}) and used directly an optimal solution of $\xs_j$ of batch $j$.  The overall mean, $\gbb_l$, is defined a little differently.  Here, $\gbb_l$ still uses each observation $i = 1, 2, \dots, n_l$ but also makes use of all the information collected throughout the batches.  That is, if observation $\xiti$ is used in $|B(i)|$ number of batches, all the optimal solutions $\xs_j$ corresponding to each batch $j \in B(i)$ are used for the lower bound estimator.  Then, $VG_l$ is defined in a similar fashion for the variably overlapping batches variance estimator (\ref{eq:variance_gamma}).

\section{Theoretical Results} 
\label{sec:theory}

In this section, we provide conditions under which several asymptotic properties hold. First, we show the consistency of the point estimators of optimality gap, $\gbb_l$, and variance, $n_l VG_l$. Then, we provide conditions under which the same benefits on variance reduction are observed in the stochastic programming setting by overlapping. Finally, we show the asymptotic validity of the OMRP interval estimator.

\subsection{Assumptions}
\label{subsec:assumptions}

We make the following assumptions:

\begin{description}
	\item[A1] Samples of the random variable $\xit$ are iid.
	\item[A2] $\sup_{\x \in X} \e{f(\x,\xi)^{4}} < \infty$.
	\item[A3] (\ref{eq:sto_prog}) has a unique optimal solution $\xs$ and $\p{\xs_m \neq \xs} \rightarrow 0$ exponentially fast as $m \rightarrow \infty$.  That is, there exists constants $M > 0$ and $c > 0$ such that $\log(\p{\xs_m \neq \xs}) \leq -cm$ for all $m > M$.
\end{description}

First, we restrict our attention to iid sampling by A1.
The classical variance-reduction results for overlapping batches show that $\var{n_l VG_l}$ is reduced by overlapping, thus requiring at least finite fourth moments. Finally, our proof relies on an exponential rate of convergence of sampled solution to the true solution of the problem.  Assumption A3 can be satisfied in several ways.  Shapiro and Homem-de-Mello \cite{shapiro2000rate} establish rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite and the optimal solution is unique.   Kleywegt, Shapiro,and Homem-de-Mello \cite{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition of a unique optimal solution $\xs$, and that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $x \in X \backslash \{\xs\}$ is finite valued on $\R$.  This class of problems includes stochastic integer programs with recourse.
  We present computational results on both stochastic linear and integer programs with recourse in \S \ref{sec:comp}.

% \begin{description}
% 	\item[A'1] (\ref{eq:sto_prog}) has a unique and sharp optimal solution, i.e., there is a constant $C$ such that $\e{f(\x,\xi)} \geq \e{f(\xs,\xi)} + C\Vert \x - \xs\Vert$ for all $\x \in X$
% 	\item[A'2] (\ref{eq:sto_prog}) is Lipschitz continuous almost surely, i.e., there is a constant $K$ such that $|f(\x_1,\xit) - f(\x_2,\xit)| \leq K \Vert \x_1 - \x_2 \Vert$ for all $\x_1,\x_2 \in X$.

% Some results require an additional assumption:
% \begin{description}
% 	\item[A4] (\ref{eq:sto_prog}) has a unique optimal solution.
% \end{description}

\subsection{Nonoptimimized Counterparts}
\label{subsec:nonO}

The internal optimization in the batches in (\ref{eq:gbar}) makes a straightforward statistical analysis of the behavior of the estimators difficult.  To overcome this problem, we introduce the following unbiased optimality gap estimators:
\begin{align}
	\db_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xh,\xit^{\gamma_l(j-1)+i}) - \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xs,\xit^{\gamma_l(j-1)+i}),\ \ \ j = 1, 2, \dots, \nbl, \label{eq:dbar} \\
	\dbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \left[ f(\xh,\xiti) - f(\xs,\xiti) \right], \label{eq:dbb} \\
	VD_l & = \frac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\db_{lj} - \dbb_l)^2. \label{eq:vd}
\end{align}
These are essentially the same as the variably overlapping batches estimators in \S \ref{ssec:overlap} with $y^i = f(\xh,\xiti) - f(\xs,\xiti)$.  These are also defined identically to the original estimators (\ref{eq:gbar})--(\ref{eq:vg}) with the exception that $\xs_j$ from (\ref{eq:gbar}) and (\ref{eq:gbb}) is replaced by an optimal solution $\xs$ in (\ref{eq:dbar}) and (\ref{eq:dbb}).  With $\xh$ and $\xs$ fixed, estimators (\ref{eq:dbar})--(\ref{eq:vd}) have the same statistical properties as variably overlapping batches estimators in \S \ref{ssec:overlap}.  Note that the optimal solution $\xs$ is not known. However, the estimators (\ref{eq:dbar})--(\ref{eq:vd}) are used only to show convergence of (\ref{eq:gbar})--(\ref{eq:vg}); they are not necessary for carrying out the OMRP algorithm.  Throughout the rest of this section, we assume that the optimality gap estimators (\ref{eq:gbar})--(\ref{eq:vg}) and their nonoptimized counterparts (\ref{eq:dbar})--(\ref{eq:vd}) use identical samples and values of $n_
l$, 
$m_l$, and $\gamma_l$.  \smallskip

\subsection{Consistency}
\label{subsec:conv}

\begin{lemma} \label{lem:gbb_prob}
	Under assumptions A1 and A3, $\p{\dbb_l - \gbb_l \neq 0} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
\end{lemma}

\begin{proof}
	\begin{align}
		\p{\dbb_l - \gbb_l \neq 0} & \leq \p{\left( \bigcap_{j=1}^{\nbl} \{\xs_{j} = \xs\} \right)^C} \notag \\
		& = \p{ \bigcup_{j=1}^{\nbl} \{\xs_{j} \neq \xs\}} \notag \\
% 		& \leq \sum_{j=1}^{\nbl} \p{ \xs_j \neq \xs } \notag \\
		& \leq \left( \nbl\right) \p{ \xs_{m_l} \neq \xs }. \notag
	\end{align}
	With a batching structure in which $m_l = \lfloor n_l^{r} \rfloor$ for some $0<r<1$,  $\gamma_l \geq 1$, and by A3, the desired result follows.
\end{proof}

\begin{lemma} \label{lem:gb_gbb_l4}
	Under assumptions A1--A3, both (i) $\e{(\db_{lj} - \gb_{lj})^4} \rightarrow 0$ and (ii) $\e{(\dbb_l - \gbb_l)^4} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
\end{lemma}

\begin{proof}
	For brevity, we drop the $lj$ subscripts from $\db_{lj}$ and $\gb_{lj}$ and $l$ from $\gbb_l$ and $\dbb_l$.
	(i) We can decompose the expectation as
	\begin{align*}
		\e{(\db - \gb)^4} & = \e{\left[ \left.(\db - \gb)^4 \right| \db - \gb \neq 0\right]} \p{\db - \gb \neq 0} + 0\\
		& \leq \e{\left[ \left.(\db - \gb)^4 \right| \db - \gb \neq 0 \right]} \p{ \xs_{m_l}  \neq \xs}.
	\end{align*}
	The expectation term on the right-hand side is bounded by assumption A2 for iid samples.  Assumption A3 states $\p{\xs_{m_l} \neq \xs} \rightarrow 0$ exponentially fast.  Thus $\e{(\db - \gb)^4} \rightarrow 0$ exponentially fast.
(ii) This expectation term can be decomposed in the same manner
	\begin{align*}
		\e{(\dbb - \gbb)^4} & = \e{\left[ \left. (\dbb - \gbb)^4 \right| \dbb - \gbb \neq 0\right]} \p{\dbb - \gbb \neq 0}.
	\end{align*}
	With the expectation term on the right-hand side again bounded by A2, and the probability term converges to zero exponentially fast by Lemma \ref{lem:gbb_prob}.
\end{proof}

\begin{theorem} \label{thm:strong_consistency}
	Under assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s, and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s. as $l \rightarrow \infty$.  Thus, $\gbb_l$ is a consistent estimator of $\mu_{\xh} = \e{\left[f(\xh,\xit) - f(\xs,\xit)\right]}$, and if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$, then $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$.
\end{theorem}

\begin{proof}
	(i) By Lemma \ref{lem:gbb_prob} we saw that $\p{\dbb_l - \gbb_l \neq 0} \rightarrow 0$ exponentially fast.  Thus $\sum_l \p{\dbb_l - \gbb_l \neq 0} < \infty$.  The desired result follows by the Borel-Cantelli Lemma.
%
(ii) This proof is nearly identical to above.  Note that
	\[
		\p{n_l VD_l -n_l VG_l \neq 0} \leq \p{\left( \bigcap_{j=1}^{\nbl} \{\xs_{j} = \xs\} \right)^C}
	\]
	and by the proof of Lemma \ref{lem:gbb_prob}, $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast, and thus $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$ if $n_l VD_l$ is, by the Borel-Cantelli Lemma.
\end{proof}

Part (i) of Theorem 1 provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$. Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s.

Strong consistency of the variance estimator $n_l VD_l$ have been studied in \cite{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  Under the additional moment assumption
\begin{description}
	\item[A2$^\prime$]  $\exists \epsilon > 0$ such that $\sup_{\x \in X} \e{f(\x,\xi)^{4+\epsilon}} < \infty$,
\end{description}
for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \cite{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.

\subsection{Variance Reduction}
\label{ssec:var_reduct}

Meketon and Schmeiser \cite{Meketon1984} show that $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha = \frac{4}{3}$ for maximally overlapping batches and $\alpha = 2$ for nonoverlapping batches, resulting in the decrease of variance for the maximally overlapping batches estimator.  Welch \cite{Welch1987} expands this result to variable amounts of overlap, showing that $\alpha$ is twice the value of (\ref{eq:var_reduct_formula}).  Damerdji \cite{damerdji1995mean} shows that convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\alpha \sigma^4_{\xh}$, and thus the mean-square consistency of $n_l VD_l$, is guaranteed for $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.  (With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.)

To prove the variance reduction results in our setting, we wish to show that $({n_l}/{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0$, for which it suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.

%To prove the variance reduction results in our setting, we wish to show that $\frac{\frac{n_l}{m_l} \var{n_lVG_l}}{\frac{n_l}{m_l} \var{n_lVD_l}} \rightarrow 1$.  We do this by showing that $({n_l}/{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0$, for which it suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.
%
%\begin{theorem} \label{thm:varvar_conv}
%	Suppose assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures $nVD_l$ converges in mean-square to $\sigma^2_\xh$.  Then $\dfrac{\frac{n_l}{m_l}\var{nVG_l}}{\frac{n_l}{m_l}\var{nVD_l}} \rightarrow 1$ as $l \rightarrow \infty$.
%\end{theorem}

\begin{theorem} \label{thm:varvar_conv}
	Suppose assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures  $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha$ is the twice the value of (\ref{eq:var_reduct_formula}). Then, $\frac{n_l}{m_l}\var{n_l VG_l} \rightarrow \alpha \sigma^4_{\xh}$ as $l \rightarrow \infty$ with the same $\alpha$. 
\end{theorem}

\begin{proof}
	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  Further, we use abbreviations $n_b = \nbl$ and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$.
	\begin{align}
		\e{(nVG - nVD)^2} & = \left( \frac{n}{df} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
		& \leq \left( \frac{n}{df} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
	\end{align}
	by the Cauchy-Schwartz inequality.  By examining the batch structure in Figure \ref{fig:overlap_nonint} and the definition of $\gbb$ in (\ref{eq:gbb}) one can see that the terms of the expectation are not identically distributed.  We will separate these into identically distributed ``center'' batches and ``fringe'' batches.  In Figure \ref{fig:overlap_nonint}, only batch 4 is a center batch, while the others are fringe batches.  Notice in Figure \ref{fig:overlap_nonint}, we see $\left\lceil \gammab^{-1} \right\rceil = 3$ sets of nonoverlapping batches, each of which has two fringe batches.  In general, there are $\left\lceil \gammab^{-1} \right\rceil$ sets of nonoverlapping batches, each of which will have two fringe batches, and $n_b - 2\left\lceil \gammab^{-1} \right\rceil$ center batches.

	The fringe batches will come in identically distributed pairs.  The first and last batch would be identically distributed, as would the second and second-to-last, etc.  We know this because we could reverse the order of the iid sample and perform the batching again to get the exact same batch structure.  Rewriting to take this into account, letting $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$, and continuing from (\ref{eq:vvar_conv_pf_1}),
	\begin{align*}
		\left( \frac{n}{df} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } & = \left( \frac{n}{df} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left[ A_j \right]^2 \right]\
		} \\
		& = \left( \frac{n}{df} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
		& = \left( \frac{n}{df} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
		+ \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
	\end{align*}	
	We have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{df}\right)^2n_b^2 < (2m)^2$.  So each expectation can be bounded by
	\begin{align}
		\left( 2m \right)^2 \e{ \left[ A_j \right]^2 } & = \left( 2m \right)^2 \e{ \left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^2 \left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^2 } \notag \\
		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{\e{\left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^4 }} \label{eq:var_reduct_cauchy2} \\
		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{8 \left(\e{(\gb_j - \gbb)^4} + \e{(\db_j - \dbb)^4} \right)}, \label{eq:var_reduct_holder2}
	\end{align}
	where equation (\ref{eq:var_reduct_cauchy2}) follows from the Cauchy-Schwartz inequality, and equation (\ref{eq:var_reduct_holder2}) follows from H\"{o}lder's inequality.  Since we can bound both expectation terms by A2, we can demonstrate $\sqrt{\frac{n}{m}}(nVG - nVD) \xrightarrow{L^2} 0$ by focusing on only one of the terms.  Focusing on the first expectation term and returning the $\tfrac{n}{m}$, by H\"{o}lder's inequality,
	\begin{align*}
		\frac{n}{m} 4m^2 \e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}	& \leq 32 \frac{n}{m} m^2\left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
	\end{align*}	
	By Lemma \ref{lem:gb_gbb_l4}, both expectation terms above converge to zero with exponential rates.  With a batching structure $m_l = \lfloor n_l^r \rfloor$ for some $0<r<1$, we see that $\frac{n_l}{m_l} \e{(n_l VG_l - n_l VD_l)^2} \rightarrow 0$.
\end{proof}

% END CHANGE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymptotic Validity of the Confidence Intervals}

The overlapping variance estimator for stochastic programs displays the same desirable properties as in simulation, but we must still check that it results in a valid confidence interval.  
Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided confidence interval generated by OMRP. The degrees of freedom $d_l$ is the inverse of (\ref{eq:var_reduct_formula}) using $\frac{\gamma_l}{m_l}$ instead of $\gammab$.

\begin{theorem} \label{thm:conf_int}
	Suppose assumptions A1--A3 hold and the batching structure ensures $n_l VD_l$ converges in probability to $\sigma^2_\xh$.  Then, for $\xh \neq \xs$, $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1 - \alpha$.
\end{theorem}

\begin{proof}
	Note that for $\xh = \xs$, $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.  With $\xh \neq \xs$, let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.  It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.  First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma. Next, since $X_l \Rightarrow N(0,1)$  by the central limit theorem and $|X_l - Y_l| \rightarrow 0$ in probability, $Y_l \Rightarrow N(0,1)$.  By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in 
probability.  Thus, 
by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
\end{proof}

The asymptotic validity of the OMRP confidence interval requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.

\section{Computational Results}
\label{sec:comp}

We empirically tested the effectiveness of OMRP on three problems. The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, and the final is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.  A description of CEP1 can be found in \cite{higle1996}, and a description of 10D is available in \cite{kleywegt2002sample}. . The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.  Both CEP1 and newsvendor can be written as two-stage stochastic linear programs with recourse. CEP1 was solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version 
of the 
algorithm implemented in C++ \cite{ruszczynski1997accelerating}. The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  In all three cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.

We used a total sample size of $n = 30 m$, with several values of the batch size $m$. Then, at each value of $m$, we formed OMRP estimators, with varying amounts of overlap. We also formed 90\% confidence intervals on the optimality gap using ORMP estimators. Results for the newsvendor problem were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs.  Summary of results from these experiments are depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.

\begin{figure}[htb!]
	\centering
	\subfloat[][Variance Reduction]{
	   \label{fig:nv_varvar}
	   \includegraphics[width=.32\textwidth]{images/nv_varvar_discrete}}
	\subfloat[][Expected Variance]{
	   \label{fig:nv_avgvar}
	   \includegraphics[width=.32\textwidth]{images/nv_avgvar_discrete}}
	\subfloat[][Coverage Probability]{
	   \label{fig:nv_cover}
	   \includegraphics[width=.32\textwidth]{images/nv_cover_discrete}}
	\caption{
		Summary of results for the newsvendor problem. 
		(a) Reduction in variance of $nVG$,
		(b) estimates of $\e{nVG}$, and 
		(c) coverage probability of the confidence intervals for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches).
	}
\label{fig:nv}
\end{figure}

\begin{figure}[htb!]
	\centering
	\subfloat[][CEP1]{
	   \label{fig:cep1_varvar}
	   \includegraphics[width=.32\textwidth]{images/cep1_varvar}}
	\subfloat[][10D]{
	   \label{fig:10d_varvar}
	   \includegraphics[width=.32\textwidth]{images/10D_varvar}}
		\caption{
		Variance Reduction for
		(a) CEP1 and 
		(b) 10D
		for various values of $\gamma / m$.
		}
\label{fig:varvar}
\end{figure}

Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). The solid lines in these figures show the theoretical variance reduction from \cite{Welch1987} given by (\ref{eq:var_reduct_formula}). Empirical results agree with the theoretical values well, with more variability observed in CEP1 and 10D, providing evidence that similar variance reduction can be achieved in stochastic programming by overlapping the batches even with small sample sizes.

Figure~\ref{fig:nv}(b) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and amount of overlap. We can see that the expectation of the variance estimator is not changed with increasing overlap. Although the estimate of $\e{nVG}$ looks large for $m=100$, the error from $\sigma^2_\xh$ is never more than 1\%.  Estimates for $\e{nVG}$ showed a similar pattern for CEP1 and 10D.  Those graphs are omitted for brevity.

Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of confidence intervals generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for newsvendor, and we observed the same for CEP1 and 10D.  The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \cite{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$. Coverage probability for 10D (not shown) was very high, more than $0.99$.  The bias from solving (\ref{eq:sto_prog_m}) for 10D seems to be much more significant than the variance.

Because variance reduction drops quickly as $\gammab$ drops below $1$, the authors recommend using an intermediate value of $\gammab$, such as $1/3$ or $1/4$, to gain the majority of the variance reduction, while reducing the number of optimization problems to be solved. Warm-starting the algorithm to solve the sampling problems, when such as scheme is available, can significantly reduce the solution times.

\section{Conclusion} \label{sec:concl}
We have extended previous work from simulation analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \cite{Meketon1984,Song1992,Welch1987} for Monte Carlo sampling-based estimators of optimality gaps in stochastic programs \cite{Mak1999}. We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid confidence intervals can be formed. Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.

\section*{Acknowledgments}
The authors thank Andrzej Ruszczy{\'{n}}ski and Artur {\'{S}}wietanowski for
access to their regularized decomposition code. This research is supported
in part by the National Science Foundation under Grants DMS-0602173 and
EFRI-0835930.  An earlier version of this paper appeared in \cite{love2011overlapping}.

% Please don't exchange the bibliographystyle style 
\bibliographystyle{plain}
% AUTHOR: Include your bib file here
\bibliography{omrp}

% \section*{AUTHOR BIOGRAPHIES}

% \noindent {\bf DAVID LOVE} is a graduate student in the Inderdisciplinary Program in Applied Mathematics at the University of Arizona.  His research focuses on Monte Carlo based quality assessment in stochastic programming.  His email address is \href{mailto://dlove@email.arizona.edu}{dlove@email.arizona.edu}.\\

% \noindent {\bf G\"{U}Z\.{I}N BAYRAKSAN} is an Assistant Professor in the Department of Systems and Industrial Engineering at the University of Arizona. Her research interests include stochastic optimization, particularly Monte Carlo sampling-based methods for stochastic programming, with applications to water resources management. Her email address is \href{mailto://guzinb@sie.arizona.edu}{guzinb@sie.arizona.edu} and her web page is \href{http://www.sie.arizona.edu/faculty/guzinb}{www.sie.arizona.edu/faculty/guzinb}.\\

\end{document}

### 2013-02-20 omrp.tex
Spaced omrp.tex so that each line corresponds to a sentence.  This way, Git will automatically keep track of how sentences change in the paper
Updated Guzin's contact information

@@
 % AUTHOR: Enter the authors of the article, see end of the example document for further examples
-\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 520-621-2605. Fax:+1 520-621-6555}\\[6pt]
+\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 520-621-2605. Fax:+1 614-292-7852}\\[6pt]
 {\small
@@
 {\small 
-      $^{b}$ Systems and Industrial Engineering, University of Arizona, Tucson, AZ 85721, USA, \texttt{guzinb@sie.arizona.edu}}}
+      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA, \texttt{bayraksan.1@osu.edu}}}
 
@@
 As a result, the corresponding batch means are no longer independent. 
-However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual
-batch means variance estimator but the bias of the two 
-estimators is approximately the same.  The idea 
-of 
-overlapping batches can be used for variance estimators of non-means \cite{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \cite{Alexopoulos01012007,Alexopoulos2007}.
+However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual batch means variance estimator but the bias of the two estimators is approximately the same.
+The idea of overlapping batches can be used for variance estimators of non-means \cite{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \cite{Alexopoulos01012007,Alexopoulos2007}.
 In this paper, we explore its use for assessing solution quality in stochastic programs.  
@@
 We present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  
-Our experiments
-indicate that the asymptotic 
-variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
+Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
 
@@
 $
-and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  The sample variance of the batch means is calculated as
+and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  
+The sample variance of the batch means is calculated as
 \begin{equation} \label{eq:var}
@@
 The nonoptimized counterparts have the desired statistical properties and we establish convergence of the optimality gap estimators to their nonoptimized counterparts. 
-Second, once the data
-is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.
+Second, once the data is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
 In our setting, due to the solution of a sampling problem (SP$_m$), the computational effort can increase with data reuse.  
@@
 $
-where $\nb$ is the number of batches used given $n$, $m$ and $\gamma$.  The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
+where $\nb$ is the number of batches used given $n$, $m$ and $\gamma$.  
+The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
 \begin{equation} \label{eq:variance_gamma}
@@
 \end{equation}
-of the nonoverlapping case.  If $\ogb$ is an integer, the terms in parentheses vanish and (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
+of the nonoverlapping case.  
+If $\ogb$ is an integer, the terms in parentheses vanish and (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
 
@@
 \begin{theorem} \label{thm:strong_consistency}
-	Under assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s, and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s.
-as $l \rightarrow \infty$.
+	Under assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s, and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s. as $l \rightarrow \infty$.  
         Thus, $\gbb_l$ is a consistent estimator of $\mu_{\xh} = \e{\left[f(\xh,\xit) - f(\xs,\xit)\right]}$, and if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$, then $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$.
@@
 %
-(ii) This proof is nearly identical to above.  Note that
+(ii) This proof is nearly identical to above.  
+Note that
 	\[
@@
 Part (i) of Theorem 1 provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$.
-Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s.
-by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s.
+Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s.
 
@@
         It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.  
-First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.
-Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.
+        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
         In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma.
         Next, since $X_l \Rightarrow N(0,1)$  by the central limit theorem and $|X_l - Y_l| \rightarrow 0$ in probability, $Y_l \Rightarrow N(0,1)$.  
-By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in
-probability.  Thus, 
-by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
+        By hypothesis and Theorem \ref{thm:strong_consistency}, $Z_l \rightarrow 1$ in probability.  
+        Thus, by Slutsky's theorem, $Y_lZ_l \Rightarrow N(0,1)$.
 \end{proof}
@@
 A description of CEP1 can be found in \cite{higle1996}, and a description of 10D is available in \cite{kleywegt2002sample}. 
-.
 The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.
 Both CEP1 and newsvendor can be written as two-stage stochastic linear programs with recourse. 
-CEP1 was solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version
-of the 
-algorithm implemented in C++ \cite{ruszczynski1997accelerating}.
+CEP1 was solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}.
 The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
@@
 Although the estimate of $\e{nVG}$ looks large for $m=100$, the error from $\sigma^2_\xh$ is never more than 1\%.  
-Estimates for $\e{nVG}$ showed a similar pattern for CEP1 and 10D.
-Those graphs are omitted for brevity.
+Estimates for $\e{nVG}$ showed a similar pattern for CEP1 and 10D.  Those graphs are omitted for brevity.
 
@@
 The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \cite{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
-Coverage probability for 10D (not shown) was very high, more than $0.99$.
-The bias from solving (\ref{eq:sto_prog_m}) for 10D seems to be much more significant than the variance.
+Coverage probability for 10D (not shown) was very high, more than $0.99$.  The bias from solving (\ref{eq:sto_prog_m}) for 10D seems to be much more significant than the variance.
 
@@
 The authors thank Andrzej Ruszczy{\'{n}}ski and Artur {\'{S}}wietanowski for
-access to their regularized decomposition code. This research is supported
+access to their regularized decomposition code. 
+This research is supported
 in part by the National Science Foundation under Grants DMS-0602173 and
-EFRI-0835930.  An earlier version of this paper appeared in \cite{love2011overlapping}.
+EFRI-0835930.  
+An earlier version of this paper appeared in \cite{love2011overlapping}.
 

### 2013-10-10 omrp.tex
Increased font size to 11 pt
Updated Guzin's phone number
Add test results from DB1
	new file:   images/db1_varvar.png
	modified:   omrp.bib
	modified:   omrp.tex

@@
-\documentclass{article}
+\documentclass[11pt]{article}
 
@@
 % AUTHOR: Enter the authors of the article, see end of the example document for further examples
-\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 520-621-2605. Fax:+1 614-292-7852}\\[6pt]
+\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 614-292-1695. Fax:+1 614-292-7852}\\[6pt]
 {\small
@@
 In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with variable overlap.  
-In \S \ref{sec:theory}, we prove several asymptotic properties of the OMRP estimators and in \S \ref{sec:comp}, we test the performance of OMRP on three problems.  
+In \S \ref{sec:theory}, we prove several asymptotic properties of the OMRP estimators and in \S \ref{sec:comp}, we test the performance of OMRP on four problems.  
 We end in \S \ref{sec:concl} with a summary and conclusions.
@@
 
-We empirically tested the effectiveness of OMRP on three problems. 
-The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, and the final is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.
-A description of CEP1 can be found in \cite{higle1996}, and a description of 10D is available in \cite{kleywegt2002sample}. 
+We empirically tested the effectiveness of OMRP on four problems.
+The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, the third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables, and the final is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
+Descriptions of CEP1, 10D, and DB1 can be found in \cite{higle1996}, \cite{kleywegt2002sample}, and \cite{donohue1995upper}, respectively.
 The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.
-Both CEP1 and newsvendor can be written as two-stage stochastic linear programs with recourse. 
-CEP1 was solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}.
+The problems CEP1, DB1 and newsvendor can be written as two-stage stochastic linear programs with recourse.
+CEP1 and DB1 were solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}.
 The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
-In all three cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.
+In all cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.
 
@@
 We also formed 90\% confidence intervals on the optimality gap using ORMP estimators. 
-Results for the newsvendor problem were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs.  
+Results for the newsvendor problem were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.
 Summary of results from these experiments are depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
@@
 	   \includegraphics[width=.32\textwidth]{images/10D_varvar}}
+	\subfloat[][DB1]{
+	   \label{fig:db1_varvar}
+	   \includegraphics[width=.32\textwidth]{images/db1_varvar}}
 		\caption{
@@
 		(b) 10D
+		(c) DB1
 		for various values of $\gamma / m$.
@@
 Empirical results agree with the theoretical values well, with more variability observed in CEP1 and 10D, providing evidence that similar variance reduction can be achieved in stochastic programming by overlapping the batches even with small sample sizes.
+DB1 shows some variance reduction, but less than the asymptotic amount for small sample sizes.
 
@@
 The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \cite{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
-Coverage probability for 10D (not shown) was very high, more than $0.99$.  The bias from solving (\ref{eq:sto_prog_m}) for 10D seems to be much more significant than the variance.
+Coverage probability for 10D and DB1 (not shown) were very high, more than $0.99$.
+The bias from solving (\ref{eq:sto_prog_m}) for these larger problems seems to be much more significant than the variance.
 

### 2013-10-11 omrp.tex
Remove unneeded comments
Rewrite abstract

@@
 \newcommand{\X}{X}
-\newcommand{\x}{x} %% CHANGED THIS NOT TO BE MATHBF 
+\newcommand{\x}{x}
 \newcommand{\xh}{{\hat{\x}}}
 \newcommand{\xs}{\x^*}
-\newcommand{\xit}{\xi}  %% CHANGED THIS TO BE WITHOUT TILDE! 
+\newcommand{\xit}{\xi}
 \newcommand{\xiti}{\xit^i}
@@
 
-% Used only for review of Meketon.  Should probably rewrite these.
-%\newcommand{\xb}{\bar{x}}
-%\newcommand{\xbb}{\bar{\xb}}
-%\newcommand{\sx}{\{X_t, t \geq 0\}}
-%\newcommand{\sxr}{\{X^n\}}
+% Used only for review of Meketon.
 \newcommand{\y}{\mathbf{y}}
@@
 
-% AUTHOR: Enter the authors of the article, see end of the example document for further examples
 \author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 614-292-1695. Fax:+1 614-292-7852}\\[6pt]
@@
       $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA, \texttt{bayraksan.1@osu.edu}}}
-
-%% ONE WAY: JUST NAMES ON TOP, EVERYTHING ELSE AS FOOTNOTE
-%\author{David~Love%
-%\thanks{D.\ Love: Interdisciplinary Graduate Program in Applied Mathematics,
-%University of Arizona, Tucson, AZ 85721, USA. E-mail: \texttt{dlove@math.arizona.edu}}%
-%\ \ and G\"{u}zin~Bayraksan%
-%\thanks{G.\ Bayraksan: (corresponding author) Department of Systems and Industrial Engineering, University of Arizona, Tucson, AZ 85721, USA.
-E-mail: \texttt{guzinb@sie.arizona.edu}.
-Tel.: +1 520-621-2605.
-Fax:+1 520-621-6555}}
-
-%%  ANOTHER WAY: ALL ON TOP, TWO DIFFERENT ONES SIDE BY SIDE
-%\author{David Love \\ [6pt]
-%       \texttt{dlove@math.arizona.edu} \\
-%        Program in Applied Mathematics \\
-%        University of Arizona \\
-%        Tucson, AZ 85721, USA \\
-% Multiple authors are entered as follows.
-% You may also need to adjust the titlevbox size in the preamble - search for titlevboxsize
-%\and
-%        G\"{u}zin Bayraksan \\ [6pt]
-%        \texttt{guzinb@sie.arizona.edu} \\
-%        Department of Systems and Industrial Engineering \\
-%        University of Arizona \\
-%        Tucson, AZ 85721, USA
-%}
 \date{}
@@
 \begin{abstract}
-We investigate the use of overlapping batches for assessing solution quality in stochastic programs. 
-Motivated by the original use of overlapping batches in simulation, we present a variant of the multiple replications procedure that reuses data via variably overlapping batches to obtain alternative variance estimators.
-These estimators have asymptotically lower variances, where the degree of variance reduction depends on the amount of overlap.  
-We provide several desired asymptotic properties and present computational results to examine small-sample behavior.\smallskip
+The method of Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate estimators with asymptotically lower variance.
+In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
+We show conditions under which the resulting optimality gap estimators are strongly consistent, and have the same asymptotically lower variance as the classical results.
+Computational results for several test problems are presented, examining the small-sample behavior of the overlapping batches method.\smallskip
 

### 2013-10-11 omrp.tex
Rewrite large parts of the introduction
1. Include more motivation at the top, especially noting that we're
looking at assessing solution quality.
2. Include a list of contributions

@@
 
-We consider a stochastic program of the form
+We wish to assess the quality of a candidate solution $\xh \in X$, which may have been found in any way, of a stochastic program of the form
 \begin{align} \tag{SP} \label{eq:sto_prog} 
@@
 Even though we will impose a more restrictive moment condition later, we assume that $\e{f(\x,\xit)}$ is well defined and finite for all $\x \in X$ and (\ref{eq:sto_prog}) has a finite optimal solution achieved on $X$.
+
+The quality of the candidate solution $\xh$ is defined by its optimality gap $\e{f(\xh,\xit)} - \zs$.
+Assessing solution quality is important in practice since (\ref{eq:sto_prog}) typically cannot be solved exactly, so one only has an approximate solution $\xh$ without verification of its quality.
+Assessing solution quality is also a critical component of stopping criteria in algorithms.
+In many fields of optimization, it is common to evaluate an upper bound on the optimality gap through relaxations such as integrality or Lagrangian relations.
+In stochastic programming, an approximation of \ref{eq:sto_prog} is often generated by sampling from the distribution of $\xi$.
 Let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (iid) sample from the distribution of $\xit$.
@@
 
-We are interested in assessing the quality of a candidate solution $\xh \in X$, which may have been found in any way, defined by its optimality gap $\e{f(\xh,\xit)} - \zs$.  
-This is important in practice since (\ref{eq:sto_prog}) typically cannot be solved exactly, so one only has an approximate solution $\xh$ without verification of its quality.  
-Assessing solution quality is also a critical component of stopping criteria in algorithms.  
-In many fields of optimization, it is common to evaluate an upper bound on the optimality gap through relaxations such as integrality or Lagrangian relations.  
-In stochastic programming, given a sample size $m$, an upper bound on the optimality gap can be obtained by $\e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}$ due to the inequality $\e{\zs_m} \leq \zs$.
+This motivates estimating the upper bound on the optimality gap by using Monte Carlo sampling.
+Given a sample size $m$, an upper bound on the optimality gap can be obtained by $\e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}$ due to the inequality $\e{\zs_m} \leq \zs$.
 This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$ \cite{Mak1999,norkin_pflug_ruszczynski_98}.  
-For stochastic programs, one way to estimate an upper bound on optimality gaps is through Monte Carlo sampling. 
 A straightforward estimate of $\e{f(\xh,\xit)}$ is the sample mean, $\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti)$. 
@@
 In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \cite{Meketon1984}. 
-Suppose each batch contains $m$ observations and that there are a total of $2m$ observations.  
+As an example, suppose each batch contains $m$ observations and that there are a total of $2m$ observations.
 In the nonoverlapping case, there are only two batches: the first batch contains observations $\xit^1, \xit^2, \dots, \xit^m$ and the second batch contains observations $\xit^{m+1}, \xit^{m+2}, \dots, \xit^{2m}$.
@@
 The idea of overlapping batches can be used for variance estimators of non-means \cite{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \cite{Alexopoulos01012007,Alexopoulos2007}.
-In this paper, we explore its use for assessing solution quality in stochastic programs.  
+
+We explore the use of overlapping batches for assessing solution quality in stochastic programs.
 Similar to Welch \cite{Welch1987} and Song and Schmeiser \cite{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
-We present conditions under which the point estimators are strongly consistent (that is, they converge almost surely (a.s.) as opposed in to in probability; referred to simply as consistent from this point on), the same variance reduction benefits are achieved, and the resulting confidence intervals are asymptotically valid.
-We present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  
+The contributions of this paper are:
+\begin{itemize}
+	\item Formulate the overlapping multiple replications procedure for stochastic programs.
+	\item Give conditions under which the point estimators are strongly consistent (that is, they converge almost surely (a.s.) as opposed in to in probability; referred to simply as consistent from this point on).
+	\item Demonstrate that the classical variance reduction results are achieved for stochastic programs.
+	\item Show the asymptotic validity of the resulting confidence intervals.
+	\item Present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  
 		Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
+\end{itemize}
 

### 2013-10-11 omrp.tex
Rewrite computational results section
1. Include discussion of why the test problems were selected
2. Fix typo from inclusion of DB1

@@
 We empirically tested the effectiveness of OMRP on four problems.
-The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$, the second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations, the third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables, and the final is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
+The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$.
+The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations.
+The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.
+The final problem is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
 Descriptions of CEP1, 10D, and DB1 can be found in \cite{higle1996}, \cite{kleywegt2002sample}, and \cite{donohue1995upper}, respectively.
@@
 In all cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.
+
+We made several considerations in selecting the test problems.
+Newsvendor can be solved very quickly, which allows for solving a large number of independent runs for examining the small sample behavior of OMRP.
+CEP1 is also easy to solve, and obtains the optimal solution $\xs$ with high probability even for small sample sizes.
+This feature shows the behavior $VG$ when the gap size is determined mostly by sampling error, rather than bias.
+10D demonstrates the behavior of OMRP when $|X|$ is finite.
+Furthermore, 10D has a high condition number \cite{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP with the bias of the gap is significant.
+The optimal solutions of both 10D and CEP1 are known, allowing for explicitly checking the computational results.
+In contrast, DB1 is a large scale example, with an unknown optimal solution.
+This final problems allows us to show that OMRP works on more computationally difficult problems.
 
@@
 		Variance Reduction for
-		(a) CEP1 and 
-		(b) 10D
+		(a) CEP1,
+		(b) 10D, and
 		(c) DB1

### 2013-10-22 omrp.tex
formatting changes to enable better editing

@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
+\usepackage{setspace}
+
+\onehalfspacing
 
@@
 {\small
-      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA, \texttt{dlove@math.arizona.edu}} \\
+      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA,}\\
+{\small \ \ \ \ \ \texttt{dlove@math.arizona.edu}} \\
 {\small 
-      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA, \texttt{bayraksan.1@osu.edu}}}
+      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA,}\\
+{\small \ \ \ \  \   \texttt{bayraksan.1@osu.edu}}}
 \date{}
@@
 \begin{abstract}
-The method of Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate estimators with asymptotically lower variance.
+\noindent The method of Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate estimators with asymptotically lower variance.
 In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.

### 2013-10-23 omrp.tex
non Times Roman font
minor changes to abstract and keywords

@@
 \usepackage{enumerate}
-\usepackage{mathptmx}
+%\usepackage{mathptmx}
 \usepackage{amsmath}
@@
 \begin{abstract}
-\noindent The method of Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate estimators with asymptotically lower variance.
+\noindent Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate variance estimators with asymptotically lower variance.
 In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
 We show conditions under which the resulting optimality gap estimators are strongly consistent, and have the same asymptotically lower variance as the classical results.
-Computational results for several test problems are presented, examining the small-sample behavior of the overlapping batches method.\smallskip
+Computational experiments for several test problems are presented, examining the small-sample behavior of the overlapping batches method in this context.\smallskip
 
-\Keywords{Sample average approximation; Optimality gap estimation; Overlapping batches; Stochastic programming}
+\Keywords{Sample average approximation (SAA); Overlapping batch means;   Stochastic programming; Optimality gap estimation}
 \end{abstract}

### 2013-10-23 omrp.tex
attempting a re-write of the introduction
1) pulled the 'contributions' to the opening paragraph

2) streamlining some of the writing in introduction for better flow

NOTE: This will continue.... but committing for now.

@@
 
-We wish to assess the quality of a candidate solution $\xh \in X$, which may have been found in any way, of a stochastic program of the form
+Overlapping Batch Means (OBM) method is widely used in simulation to obtain variance estimators with lower variances. 
+In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.  
+A natural setting where batch means are used in stochastic optimization (esp. in stochastic programming) is for assessing solution quality. 
+Assessing solution quality in stochastic programming typically involves generating point and interval estimators of the optimality gap of a given candidate solution using Monte Carlo simulation. 
+Because the optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonovelapping batches of data to generate a number of optimality gap estimators. 
+These individual estimators are then used to form point and interval estimators using the classical nonoverlapping batches method.
+This is referred to as the Multiple Replications Procedure (MRP).   
+In this paper, we formulate an ovelapping batches version of MRP, allowing for partial overlap, and provide conditions under which the same variance reduction results can be achieved by overlapping like in the classical setting.
+We also show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
+We present computational results to examine small-sample behavior. 
+Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
+
+We consider a stochastic optimization problem of the form 
 \begin{align} \tag{SP} \label{eq:sto_prog} 
@@
 
-The quality of the candidate solution $\xh$ is defined by its optimality gap $\e{f(\xh,\xit)} - \zs$.
+We wish to assess the quality of a candidate solution $\xh \in X$. 
+We define its quality by its optimality gap $\e{f(\xh,\xit)} - \zs$. 
+The lower the optimality gap, the higher the quality of the solution and a zero optimality gap implies that the solution is optimal. 
+Note that the candidate solution $\xh \in X$ may have been found in any way. 
+We assume this solution is given.
+
 Assessing solution quality is important in practice since (\ref{eq:sto_prog}) typically cannot be solved exactly, so one only has an approximate solution $\xh$ without verification of its quality.
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   %    %    %    %    %    %
+
+\bigskip
+
+ We present variants of . .
+
+\bigskip
+
+Batch means have been used in stochastic programming to assess solution quality and we show that. . . 
+\bigskip
+
+What happens when overlapping batches are used in a stochastic optimization setting?
+Can we obtain the same benefits from overlapping batches as we do in a non-optimized setting?
+In this paper, we answer the second question in the affirmative.
+We provide conditions under which the same benefits can be obtained by overlapping for a class of stochastic optimization problems.
+A natural setting where batch means is used in stochastic optimization is solution validation.
+This is referred to as the Multiple Replication Procedure, where each replication is essentially a batch means.
+
+\bigskip
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   %    %    %    %    %    %
 

### 2013-10-24 omrp.tex
Changed the ref style

@@
 %\usepackage{mathptmx}
+\usepackage[square]{natbib}
 \usepackage{amsmath}
@@
 
-Overlapping Batch Means (OBM) method is widely used in simulation to obtain variance estimators with lower variances. 
+Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is widely used in simulation to obtain variance estimators with lower variances. 
 In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.  
@@
 These individual estimators are then used to form point and interval estimators using the classical nonoverlapping batches method.
-This is referred to as the Multiple Replications Procedure (MRP).   
+This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
 In this paper, we formulate an ovelapping batches version of MRP, allowing for partial overlap, and provide conditions under which the same variance reduction results can be achieved by overlapping like in the classical setting.
@@
 Assessing solution quality is also a critical component of stopping criteria in algorithms.
-In many fields of optimization, it is common to evaluate an upper bound on the optimality gap through relaxations such as integrality or Lagrangian relations.
+
 In stochastic programming, an approximation of \ref{eq:sto_prog} is often generated by sampling from the distribution of $\xi$.
@@
 
+In many fields of optimization, it is common to evaluate an upper bound on the optimality gap through relaxations such as integrality or Lagrangian relations.
+
 This motivates estimating the upper bound on the optimality gap by using Monte Carlo sampling.
 Given a sample size $m$, an upper bound on the optimality gap can be obtained by $\e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}$ due to the inequality $\e{\zs_m} \leq \zs$.
-This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$ \cite{Mak1999,norkin_pflug_ruszczynski_98}.  
+This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$ \citep{Mak1999,norkin_pflug_ruszczynski_98}.  
 A straightforward estimate of $\e{f(\xh,\xit)}$ is the sample mean, $\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti)$. 
@@
 Computing $G_m(\xh)$ involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator $\zs_m$, which complicates the statistical analysis. 
-To enable statistical inference, the \emph{Multiple Replications Procedure} (MRP) of Mak et.\ al.\ \cite{Mak1999} generates $k$ independent estimators of $G_m(\xh)$, each using sample size $m$ and averages them to obtain a point estimator.
+To enable statistical inference, the \emph{Multiple Replications Procedure} (MRP) of Mak et.\ al.\ \citep{Mak1999} generates $k$ independent estimators of $G_m(\xh)$, each using sample size $m$ and averages them to obtain a point estimator.
 To form confidence intervals, the sample variance of these estimators is calculated.  
-This is essentially a nonoverlapping batch means type estimator ($k$ batches of size $m$) commonly used in simulation \cite{law_07}. 
+This is essentially a nonoverlapping batch means type estimator ($k$ batches of size $m$) commonly used in simulation \citep{law_07}. 
 We further review MRP estimators in \S \ref{ssec:mrp}.
 
-In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \cite{Meketon1984}. 
+In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \citep{Meketon1984}. 
 As an example, suppose each batch contains $m$ observations and that there are a total of $2m$ observations.
 In the nonoverlapping case, there are only two batches: the first batch contains observations $\xit^1, \xit^2, \dots, \xit^m$ and the second batch contains observations $\xit^{m+1}, \xit^{m+2}, \dots, \xit^{2m}$.
-Meketon and Schmeiser \cite{Meketon1984} overlap the batches so that the first batch is as before, the second batch now consists of $\xit^2, \xit^3, \dots, \xit^{m+1}$, the third batch contains observations $\xit^3, \xit^4, \dots, \xit^{m+2}$ and so on.
+Meketon and Schmeiser \citep{Meketon1984} overlap the batches so that the first batch is as before, the second batch now consists of $\xit^2, \xit^3, \dots, \xit^{m+1}$, the third batch contains observations $\xit^3, \xit^4, \dots, \xit^{m+2}$ and so on.
 As a result, the corresponding batch means are no longer independent. 
 However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual batch means variance estimator but the bias of the two estimators is approximately the same.
-The idea of overlapping batches can be used for variance estimators of non-means \cite{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \cite{Alexopoulos01012007,Alexopoulos2007}.
+The idea of overlapping batches can be used for variance estimators of non-means \citep{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \citep{Alexopoulos01012007,Alexopoulos2007}.
 
 We explore the use of overlapping batches for assessing solution quality in stochastic programs.
-Similar to Welch \cite{Welch1987} and Song and Schmeiser \cite{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
+Similar to Welch \citep{Welch1987} and Song and Schmeiser \citep{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
 The contributions of this paper are:
@@
 However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  
-To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \cite{law_07}.  
+To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citep{law_07}.  
 We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.
@@
 \end{equation}
-Meketon and Schmeiser \cite{Meketon1984} show several attractive properties of the overlapping batches variance estimator, the two most important of which are: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
+Meketon and Schmeiser \citep{Meketon1984} show several attractive properties of the overlapping batches variance estimator, the two most important of which are: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
 That is, 
@@
 in the limit as batch size $m$ and then the number of batches $(n/m)$ tend to infinity.  
-Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \cite{Meketon1984}.  
-The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for iid data for all finite $m$ and $n$ with the same asymptotic benefits \cite{Song1992}.  
+Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
+The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for iid data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
 The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.
 
-Welch \cite{Welch1987} established the relationship between OBM and spectral estimators and also considered partial overlap, see also \cite{Song1992}.  
+Welch \citep{Welch1987} established the relationship between OBM and spectral estimators and also considered partial overlap, see also \citep{Song1992}.  
 In our application to assessment of solution quality, we also consider varying the amount of overlap between neighboring batches.  
@@
 Thus, we can expect that the true probability of the optimality gap residing within the confidence interval to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in Bayraksan and Morton \cite{Bayraksan2006}, which also suggests additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
-See also \cite{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.
+This is shown empirically in Bayraksan and Morton \citep{Bayraksan2006}, which also suggests additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
+See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.
 
@@
 With iid sampling, (\ref{eq:sto_prog}) can be linear or nonlinear, $\X$ can include integrality constraints or not.  
-It is also easy to implement, thus, has been applied to a variety of problems, see e.g., \cite{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  
-Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \cite{wang_ahmed_08} and stochastic dominance \cite{hu2010sample} constraints.
+It is also easy to implement, thus, has been applied to a variety of problems, see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  
+Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
 
@@
 In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
-For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of Meketon and Schmeiser \cite{Meketon1984}.  
+For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of Meketon and Schmeiser \citep{Meketon1984}.  
 The sample mean of each batch estimator is calculated similarly, 
@@
 When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  
-In general, from the spectral analysis given in Welch \cite{Welch1987}, the variance is reduced to
+In general, from the spectral analysis given in Welch \citep{Welch1987}, the variance is reduced to
 \begin{equation} \label{eq:var_reduct_formula}
@@
 
-A $(1-\alpha)$-level approximate CI on the mean can be formed using variably overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \cite{Welch1987}.
+A $(1-\alpha)$-level approximate CI on the mean can be formed using variably overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
 If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$ and for maximally overlapping batches, $d_{\gamma} = \frac{3}{2}$.
@@
 
-The results on overlapping batch means occur in the limit as $n, m, k=n/m \rightarrow \infty$ \cite{damerdji1994strong,damerdji1995mean,Meketon1984,Song1992,Welch1987}.  
+The results on overlapping batch means occur in the limit as $n, m, k=n/m \rightarrow \infty$ \citep{damerdji1994strong,damerdji1995mean,Meketon1984,Song1992,Welch1987}.  
 Let $n_l, m_l$ and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
@@
 Assumption A3 can be satisfied in several ways.  
-Shapiro and Homem-de-Mello \cite{shapiro2000rate} establish rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite and the optimal solution is unique.
-Kleywegt, Shapiro,and Homem-de-Mello \cite{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition of a unique optimal solution $\xs$, and that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $x \in X \backslash \{\xs\}$ is finite valued on $\R$.
+Shapiro and Homem-de-Mello \citep{shapiro2000rate} establish rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite and the optimal solution is unique.
+Kleywegt, Shapiro,and Homem-de-Mello \citep{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition of a unique optimal solution $\xs$, and that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $x \in X \backslash \{\xs\}$ is finite valued on $\R$.
 This class of problems includes stochastic integer programs with recourse.
@@
 
-Strong consistency of the variance estimator $n_l VD_l$ have been studied in \cite{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
+Strong consistency of the variance estimator $n_l VD_l$ have been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
 Under the additional moment assumption
@@
 \end{description}
-for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \cite{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.
+for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \citep{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.
 
@@
 
-Meketon and Schmeiser \cite{Meketon1984} show that $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha = \frac{4}{3}$ for maximally overlapping batches and $\alpha = 2$ for nonoverlapping batches, resulting in the decrease of variance for the maximally overlapping batches estimator.
-Welch \cite{Welch1987} expands this result to variable amounts of overlap, showing that $\alpha$ is twice the value of (\ref{eq:var_reduct_formula}).  
-Damerdji \cite{damerdji1995mean} shows that convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\alpha \sigma^4_{\xh}$, and thus the mean-square consistency of $n_l VD_l$, is guaranteed for $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
+Meketon and Schmeiser \citep{Meketon1984} show that $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha = \frac{4}{3}$ for maximally overlapping batches and $\alpha = 2$ for nonoverlapping batches, resulting in the decrease of variance for the maximally overlapping batches estimator.
+Welch \citep{Welch1987} expands this result to variable amounts of overlap, showing that $\alpha$ is twice the value of (\ref{eq:var_reduct_formula}).  
+Damerdji \citep{damerdji1995mean} shows that convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\alpha \sigma^4_{\xh}$, and thus the mean-square consistency of $n_l VD_l$, is guaranteed for $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
 (With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.)
@@
 The final problem is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
-Descriptions of CEP1, 10D, and DB1 can be found in \cite{higle1996}, \cite{kleywegt2002sample}, and \cite{donohue1995upper}, respectively.
-The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.
+Descriptions of CEP1, 10D, and DB1 can be found in \citep{higle1996}, \citep{kleywegt2002sample}, and \citep{donohue1995upper}, respectively.
+The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \citep{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.
 The problems CEP1, DB1 and newsvendor can be written as two-stage stochastic linear programs with recourse.
-CEP1 and DB1 were solved with the regularized decomposition algorithm of \cite{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}.
+CEP1 and DB1 were solved with the regularized decomposition algorithm of \citep{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
 The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
-In all cases, we used the Mersenne Twister algorithm to generate random samples \cite{wagner_twister_09}.
+In all cases, we used the Mersenne Twister algorithm to generate random samples \citep{wagner_twister_09}.
 
@@
 10D demonstrates the behavior of OMRP when $|X|$ is finite.
-Furthermore, 10D has a high condition number \cite{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP with the bias of the gap is significant.
+Furthermore, 10D has a high condition number \citep{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP with the bias of the gap is significant.
 The optimal solutions of both 10D and CEP1 are known, allowing for explicitly checking the computational results.
@@
 Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
-The solid lines in these figures show the theoretical variance reduction from \cite{Welch1987} given by (\ref{eq:var_reduct_formula}). 
+The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
 Empirical results agree with the theoretical values well, with more variability observed in CEP1 and 10D, providing evidence that similar variance reduction can be achieved in stochastic programming by overlapping the batches even with small sample sizes.
@@
 The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for newsvendor, and we observed the same for CEP1 and 10D.
-The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \cite{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
+The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
 Coverage probability for 10D and DB1 (not shown) were very high, more than $0.99$.
@@
 \section{Conclusion} \label{sec:concl}
-We have extended previous work from simulation analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \cite{Meketon1984,Song1992,Welch1987} for Monte Carlo sampling-based estimators of optimality gaps in stochastic programs \cite{Mak1999}.
+We have extended previous work from simulation analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo sampling-based estimators of optimality gaps in stochastic programs \citep{Mak1999}.
 We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid confidence intervals can be formed.
@@
 The authors thank Andrzej Ruszczy{\'{n}}ski and Artur {\'{S}}wietanowski for
-access to their regularized decomposition code. 
+access to their regularized decomposition code, which was used to solve CEP1 and DB1. 
 This research is supported
@@
 EFRI-0835930.  
-An earlier version of this paper appeared in \cite{love2011overlapping}.
+An earlier version of this paper appeared in \citep{love2011overlapping}.
 
 % Please don't exchange the bibliographystyle style 
-\bibliographystyle{plain}
+\bibliographystyle{abbrvnat}
 % AUTHOR: Include your bib file here

### 2013-10-24 omrp.tex
streamlining the intro - I

@@
 
-We wish to assess the quality of a candidate solution $\xh \in X$. 
-We define its quality by its optimality gap $\e{f(\xh,\xit)} - \zs$. 
-The lower the optimality gap, the higher the quality of the solution and a zero optimality gap implies that the solution is optimal. 
-Note that the candidate solution $\xh \in X$ may have been found in any way. 
-We assume this solution is given.
-
-Assessing solution quality is important in practice since (\ref{eq:sto_prog}) typically cannot be solved exactly, so one only has an approximate solution $\xh$ without verification of its quality.
-Assessing solution quality is also a critical component of stopping criteria in algorithms.
-
-In stochastic programming, an approximation of \ref{eq:sto_prog} is often generated by sampling from the distribution of $\xi$.
-Let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (iid) sample from the distribution of $\xit$.
-A sampling approximation of (\ref{eq:sto_prog}) is given by
+Unless $f$ has a simple structure or the number of realizations of $\xi$ is small, (\ref{eq:sto_prog}) typically cannot be solved exactly. 
+An approximation of (\ref{eq:sto_prog}) is often generated by sampling from the distribution of $\xi$.
+While other sampling schemes are possible, let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (iid) sample from the distribution of $\xit$.
+A sampling approximation of (\ref{eq:sto_prog}), often called the Sample Average Approximation (SAA), is given by
 \begin{align} \tag{SP$_m$} \label{eq:sto_prog_m}
@@
 
-In many fields of optimization, it is common to evaluate an upper bound on the optimality gap through relaxations such as integrality or Lagrangian relations.
+We wish to assess the quality of a candidate solution $\xh \in X$. 
+Assessing solution quality is important in practice because as (\ref{eq:sto_prog}) typically cannot be solved exactly, one only has an approximate solution $\xh$ without verification of its quality.
+Assessing solution quality is also a critical component of stopping criteria in algorithms designed to (approximately) solve (\ref{eq:sto_prog}).
+We define the quality of $\xh$ by its optimality gap, $\e{f(\xh,\xit)} - \zs$. 
+The lower the optimality gap, the higher the quality of the solution and a zero optimality gap implies that the solution is optimal. 
+Note that the candidate solution $\xh \in X$ may have been found in any way. 
+We assume this solution is given throughout this paper.
 
-This motivates estimating the upper bound on the optimality gap by using Monte Carlo sampling.
-Given a sample size $m$, an upper bound on the optimality gap can be obtained by $\e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}$ due to the inequality $\e{\zs_m} \leq \zs$.
+The optimality gap $\e{f(\xh,\xit)} - \zs$ cannot be calculated exactly.
+First,  for a given candidate solution $\xh \in X$, evaluation of $\e{f(\xh,\xit)}$ often involves a difficult multidimensional integral.
+Second, we do not know $\zs$. 
+In many fields of optimization, the second problem is alleviated by obtaining lower bounds on $\zs$ through relaxations such as integrality, Lagrangian or semidefinite relations.
+As a result, it is common to evaluate an upper bound on the optimality gap. 
+This motivates estimating the upper bound on the optimality gap in stochastic programming by using Monte Carlo simulation.
+Given a sample size $m$, an upper bound on the optimality gap can be obtained by $$
+\e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}
+$$ 
+due to the inequality $\e{\zs_m} \leq \zs$.
 This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$ \citep{Mak1999,norkin_pflug_ruszczynski_98}.  
@@
 Instead of $\e{\zs_m}$, simply $\zs_m$ can be used.  
-The resulting point estimator is  $G_m(\xh) = \frac{1}{m} \sum_{i=1}^m f(\xh,\xiti) - \zs_m$.  
+The resulting point estimator of optimality gap is then 
+$$
+G_m(\xh) = \frac{1}{m} \sum_{i=1}^m f(\xh,\xiti) - \zs_m.
+$$ 
 Here, we assume the same observations $\xit^1, \dots, \xit^m$ are used in both terms of $G_m(\xh)$.
 
-Computing $G_m(\xh)$ involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator $\zs_m$, which complicates the statistical analysis. 
-To enable statistical inference, the \emph{Multiple Replications Procedure} (MRP) of Mak et.\ al.\ \citep{Mak1999} generates $k$ independent estimators of $G_m(\xh)$, each using sample size $m$ and averages them to obtain a point estimator.
+Computing $G_m(\xh)$ involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis. 
+As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators of $G_m(\xh)$, each using sample size $m$ ($k$ batches of size $m$) and averages them to obtain a point estimator.
 To form confidence intervals, the sample variance of these estimators is calculated.  
-This is essentially a nonoverlapping batch means type estimator ($k$ batches of size $m$) commonly used in simulation \citep{law_07}. 
-We further review MRP estimators in \S \ref{ssec:mrp}.
+%This is essentially a nonoverlapping batch means type estimator ($k$ batches of size $m$) commonly used in simulation \citep{law_07}. 
+(We further review MRP estimators in \S \ref{ssec:mrp}.)
 

### 2013-10-25 omrp.tex
streamlining the intro - II
1) Added a new reference
2) continuing on with the streamlining

@@
 In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
-We show conditions under which the resulting optimality gap estimators are strongly consistent, and have the same asymptotically lower variance as the classical results.
+We show conditions under which the resulting optimality gap estimators are strongly consistent and have the same asymptotically lower variance as the classical results.
 Computational experiments for several test problems are presented, examining the small-sample behavior of the overlapping batches method in this context.\smallskip
@@
 Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is widely used in simulation to obtain variance estimators with lower variances. 
+While OBM is often used for variance estimators of means, it can also be used for variance estimators of non-means \citep{SAH90} and more recently, it has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) \citep{Alexopoulos01012007,Alexopoulos2007} and their folded versions \citep{Meterelliyoz_etal_12}.
 In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.  
@@
 Because the optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonovelapping batches of data to generate a number of optimality gap estimators. 
-These individual estimators are then used to form point and interval estimators using the classical nonoverlapping batches method.
+These individual estimators are then used to form point and interval estimators using the classical nonoverlapping batch means method.
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
@@
 Unless $f$ has a simple structure or the number of realizations of $\xi$ is small, (\ref{eq:sto_prog}) typically cannot be solved exactly. 
-An approximation of (\ref{eq:sto_prog}) is often generated by sampling from the distribution of $\xi$.
-While other sampling schemes are possible, let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (iid) sample from the distribution of $\xit$.
+An approximation of (\ref{eq:sto_prog}) can be generated by sampling from the distribution of $\xi$.
+While other sampling schemes are possible, let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (i.i.d.) sample from the distribution of $\xit$.
 A sampling approximation of (\ref{eq:sto_prog}), often called the Sample Average Approximation (SAA), is given by
@@
 Note that the candidate solution $\xh \in X$ may have been found in any way. 
-We assume this solution is given throughout this paper.
+We assume that this solution is given as input to our procedures, and hence fixed, throughout this paper.
 
-The optimality gap $\e{f(\xh,\xit)} - \zs$ cannot be calculated exactly.
-First,  for a given candidate solution $\xh \in X$, evaluation of $\e{f(\xh,\xit)}$ often involves a difficult multidimensional integral.
+The optimality gap $\e{f(\xh,\xit)} - \zs$ often cannot be calculated exactly.
+First, for a given candidate solution $\xh \in X$, evaluation of $\e{f(\xh,\xit)}$ typically involves a difficult multidimensional integral.
 Second, we do not know $\zs$. 
@@
 $$ 
-due to the inequality $\e{\zs_m} \leq \zs$.
-This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$ \citep{Mak1999,norkin_pflug_ruszczynski_98}.  
+due to the inequality $\e{\zs_m} \leq \zs$ \citep{Mak1999,norkin_pflug_ruszczynski_98}.
+This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$.  
 A straightforward estimate of $\e{f(\xh,\xit)}$ is the sample mean, $\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti)$. 
@@
 $$
-G_m(\xh) = \frac{1}{m} \sum_{i=1}^m f(\xh,\xiti) - \zs_m.
+\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti) - \zs_m.
 $$ 
-Here, we assume the same observations $\xit^1, \dots, \xit^m$ are used in both terms of $G_m(\xh)$.
+Here, we assume the same observations $\xit^1, \dots, \xit^m$ are used in both terms.
 
@@
 However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual batch means variance estimator but the bias of the two estimators is approximately the same.
-The idea of overlapping batches can be used for variance estimators of non-means \citep{SAH90} and recently, has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) for steady-state simulation output analysis \citep{Alexopoulos01012007,Alexopoulos2007}.
 
@@
 Similar to Welch \citep{Welch1987} and Song and Schmeiser \citep{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
-The contributions of this paper are:
-\begin{itemize}
-	\item Formulate the overlapping multiple replications procedure for stochastic programs.
-	\item Give conditions under which the point estimators are strongly consistent (that is, they converge almost surely (a.s.) as opposed in to in probability; referred to simply as consistent from this point on).
-	\item Demonstrate that the classical variance reduction results are achieved for stochastic programs.
-	\item Show the asymptotic validity of the resulting confidence intervals.
-	\item Present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  
-		Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
-\end{itemize}
+%The contributions of this paper are:
+%\begin{itemize}
+%	\item Formulate the overlapping multiple replications procedure for stochastic programs.
+%	\item Give conditions under which the point estimators are strongly consistent (that is, they converge almost surely (a.s.) as opposed in to in probability; referred to simply as consistent from this point on).
+%	\item Demonstrate that the classical variance reduction results are achieved for stochastic programs.
+%	\item Show the asymptotic validity of the resulting confidence intervals.
+%	\item Present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  
+%		Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
+%\end{itemize}
 
@@
 
- We present variants of . .
+% We present variants of . .
 
@@
 
-Batch means have been used in stochastic programming to assess solution quality and we show that. . . 
+%Batch means have been used in stochastic programming to assess solution quality and we show that. . . 
 \bigskip
 
-What happens when overlapping batches are used in a stochastic optimization setting?
+%What happens when overlapping batches are used in a stochastic optimization setting?
 Can we obtain the same benefits from overlapping batches as we do in a non-optimized setting?
@@
 
-\bigskip
+%\bigskip
 
@@
 Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
-The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for iid data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
+The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
 The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.
@@
 An advantage of MRP is its applicability to a wide range of problems.  
-With iid sampling, (\ref{eq:sto_prog}) can be linear or nonlinear, $\X$ can include integrality constraints or not.  
+With i.i.d.\ sampling, (\ref{eq:sto_prog}) can be linear or nonlinear, $\X$ can include integrality constraints or not.  
 It is also easy to implement, thus, has been applied to a variety of problems, see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  
@@
 \begin{description}
-	\item[A1] Samples of the random variable $\xit$ are iid.
+	\item[A1] Samples of the random variable $\xit$ are i.i.d.
 	\item[A2] $\sup_{\x \in X} \e{f(\x,\xi)^{4}} < \infty$.
@@
 
-First, we restrict our attention to iid sampling by A1.
+First, we restrict our attention to i.i.d.\ sampling by A1.
 The classical variance-reduction results for overlapping batches show that $\var{n_l VG_l}$ is reduced by overlapping, thus requiring at least finite fourth moments. 
@@
 	\end{align*}
-	The expectation term on the right-hand side is bounded by assumption A2 for iid samples.  
+	The expectation term on the right-hand side is bounded by assumption A2 for i.i.d.\ samples.  
         Assumption A3 states $\p{\xs_{m_l} \neq \xs} \rightarrow 0$ exponentially fast.  
@@
         The first and last batch would be identically distributed, as would the second and second-to-last, etc.  
-        We know this because we could reverse the order of the iid sample and perform the batching again to get the exact same batch structure.  
+        We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the exact same batch structure.  
         Rewriting to take this into account, letting $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$, and continuing from (\ref{eq:vvar_conv_pf_1}),

### 2013-10-25 omrp.tex
streamlining the intro - III
I think it reads much better now!!!

1) Editing the intro
2) Pulled the discussion at the beginning of Section 3 to the
introduction, discussing positives and negatives.

@@
 We show conditions under which the resulting optimality gap estimators are strongly consistent and have the same asymptotically lower variance as the classical results.
-Computational experiments for several test problems are presented, examining the small-sample behavior of the overlapping batches method in this context.\smallskip
+Computational experiments for several test problems are presented, examining the small-sample behavior of the overlapping batches method in this context.\medskip
 
@@
 
-Computing $G_m(\xh)$ involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis. 
-As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators of $G_m(\xh)$, each using sample size $m$ ($k$ batches of size $m$) and averages them to obtain a point estimator.
-To form confidence intervals, the sample variance of these estimators is calculated.  
-%This is essentially a nonoverlapping batch means type estimator ($k$ batches of size $m$) commonly used in simulation \citep{law_07}. 
-(We further review MRP estimators in \S \ref{ssec:mrp}.)
+Computing the above optimality gap estimate involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis.
+As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$) and averages them to obtain a point estimator.
+To form confidence intervals, the sample variance of these estimators is calculated (we further review MRP in \S \ref{ssec:mrp}.)
 
-In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \citep{Meketon1984}. 
-As an example, suppose each batch contains $m$ observations and that there are a total of $2m$ observations.
-In the nonoverlapping case, there are only two batches: the first batch contains observations $\xit^1, \xit^2, \dots, \xit^m$ and the second batch contains observations $\xit^{m+1}, \xit^{m+2}, \dots, \xit^{2m}$.
-Meketon and Schmeiser \citep{Meketon1984} overlap the batches so that the first batch is as before, the second batch now consists of $\xit^2, \xit^3, \dots, \xit^{m+1}$, the third batch contains observations $\xit^3, \xit^4, \dots, \xit^{m+2}$ and so on.
-As a result, the corresponding batch means are no longer independent. 
-However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual batch means variance estimator but the bias of the two estimators is approximately the same.
+%When this confidendence interval on the optimality gap is too large, it can be due to three reasons.
+First, $\xh$ can be far from optimal; second, bias can be large; third, the sampling error can be large.
+%We note that for some problems, bias is a more prominent issue and for others, sampling error is the larger issue. 
+%When bias is relatively small, overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
 
-We explore the use of overlapping batches for assessing solution quality in stochastic programs.
-Similar to Welch \citep{Welch1987} and Song and Schmeiser \citep{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
+Our aim is to apply the idea of overlapping batches to MRP.  
+Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
+We note several differences in this setting compared to the classical setting.  
+In simulation output analysis, the point of interest is estimating the variance of the sample mean of a covariance stationary process.  
+We are interested in estimating the variance of an optimality gap estimator.  
+Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
+First, minimization changes the statistical properties of sample means.  
+For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
+Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
+We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
+The nonoptimized counterparts have the desired statistical properties and we establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
+Second, once the data is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
+In this setting, due to the solution of a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
+This can be alleviated in two ways. 
+First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
+Partial overlap results in a fewer number of batches, hence fewer number of optimization problems need to be solved.
+In this paper, we consider partial overlap and show that same asymptotic benefits are obtained and examine the effectiveness of partial overlap with small sample sizes. 
+Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
+
+%In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \citep{Meketon1984}.
+
+%We explore the use of overlapping batches for assessing solution quality in stochastic programs.
+%Similar to Welch \citep{Welch1987} and Song and Schmeiser \citep{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
 %The contributions of this paper are:
@@
 
-\bigskip
+%\bigskip
 
 %Batch means have been used in stochastic programming to assess solution quality and we show that. . . 
-\bigskip
+%\bigskip
 
@@
 %\bigskip 
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   %    %    %    %    %    %
@@
 In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with variable overlap.  
-In \S \ref{sec:theory}, we prove several asymptotic properties of the OMRP estimators and in \S \ref{sec:comp}, we test the performance of OMRP on four problems.  
-We end in \S \ref{sec:concl} with a summary and conclusions.
+In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.
+In \S \ref{sec:comp}, we test the performance of OMRP on four problems and end in \S \ref{sec:concl} with a summary and conclusions.
 
@@
 Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$.
+
+%%%%%%%%%%%%%%
+As an example, suppose each batch contains $m$ observations and that there are a total of $2m$ observations.
+In the nonoverlapping case, there are only two batches: the first batch contains observations $\xit^1, \xit^2, \dots, \xit^m$ and the second batch contains observations $\xit^{m+1}, \xit^{m+2}, \dots, \xit^{2m}$.
+Meketon and Schmeiser \citep{Meketon1984} overlap the batches so that the first batch is as before, the second batch now consists of $\xit^2, \xit^3, \dots, \xit^{m+1}$, the third batch contains observations $\xit^3, \xit^4, \dots, \xit^{m+2}$ and so on.
+As a result, the corresponding batch means are no longer independent. 
+However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual batch means variance estimator but the bias of the two estimators is approximately the same.
+%%%%%%%%%%%%%%%%
 

### 2013-10-25 omrp.tex
Streamlining Sec. 2:  Background
Sec 2.1 OBM:
------------------
(1) Added explanations on OBM that used to be in the intro to this
subsection
(2) minor edits

Sec 2.2 MRP:
------------------
(1) Moved lit review at the end of this section to Intro
(2)  Expanded the discussion on Gbar_j to make the connection with NOBM
clear
(3) Changed the intro of this a bit

@@
 To form confidence intervals, the sample variance of these estimators is calculated (we further review MRP in \S \ref{ssec:mrp}.)  
+An advantage of MRP is its applicability to a wide range of problems.  
+With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
+It is also easy to implement, thus, has been applied to a variety of problems, including finance, supply chain network design, etc.\; see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
+Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
 
@@
 We first discuss the overlapping batch means in \S \ref{ssec:obm} and then briefly go over the multiple replications procedure in \S \ref{ssec:mrp}.  
-In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with variable overlap.  
+In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with partial overlap.  
 In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.
@@
 \subsection{Overlapping Batch Means} \label{ssec:obm}
-Consider a covariance stationary stochastic process which has mean $\mu$ and variance $\sigma^2$.  
+Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
 The task is to estimate $\mu$ given some realization of the stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
-Typically, this involves forming a confidence interval of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$.
+Typically, this involves forming a confidence interval of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.
 The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
@@
 
-%%%%%%%%%%%%%%
+Overlapping batch means modifies this idea by taking batches given by $\yb_j(m) = \frac{1}{m} \sum_{i=1}^{m}$ $y^{(j-1)+i}$, for $j = 1, \dots, n-m+1$.
 As an example, suppose each batch contains $m$ observations and that there are a total of $2m$ observations.
-In the nonoverlapping case, there are only two batches: the first batch contains observations $\xit^1, \xit^2, \dots, \xit^m$ and the second batch contains observations $\xit^{m+1}, \xit^{m+2}, \dots, \xit^{2m}$.
-Meketon and Schmeiser \citep{Meketon1984} overlap the batches so that the first batch is as before, the second batch now consists of $\xit^2, \xit^3, \dots, \xit^{m+1}$, the third batch contains observations $\xit^3, \xit^4, \dots, \xit^{m+2}$ and so on.
-As a result, the corresponding batch means are no longer independent. 
-However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator: a variance estimator that asymptotically has two-thirds of the variance of the usual batch means variance estimator but the bias of the two estimators is approximately the same.
-%%%%%%%%%%%%%%%%
+In the nonoverlapping case, there are only two batches: the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.   
+In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$ and so on.
+This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.
 
-Overlapping batch means modifies this idea by taking batches given by $\yb_j(m) = \frac{1}{m} \sum_{i=1}^{m} y^{(j-1)+i}$, for $j = 1, \dots, n-m+1$.  
-This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
-Given this, the sample variance estimator is updated to
+The sample variance estimator is updated to
 \begin{equation} \label{eq:overlap_variance_def}
@@
 \end{equation}
-Meketon and Schmeiser \citep{Meketon1984} show several attractive properties of the overlapping batches variance estimator, the two most important of which are: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
+Note that the corresponding batch means are no longer independent. 
+However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator. 
+\citet{Meketon1984} show several attractive properties of the overlapping batches variance estimator, the two most important of which are: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
 That is, 
@@
 \end{equation}
-in the limit as batch size $m$ and then the number of batches $(n/m)$ tend to infinity.  
+in the limit as batch size $m$ and the number of batches $(n/m)$ tend to infinity.  
 Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
@@
 
-Welch \citep{Welch1987} established the relationship between OBM and spectral estimators and also considered partial overlap, see also \citep{Song1992}.  
-In our application to assessment of solution quality, we also consider varying the amount of overlap between neighboring batches.  
-We defer this discussion on variable overlap to \S \ref{ssec:overlap} and continue with a brief review of MRP.
+\citet{Welch1987} established the relationship between OBM and spectral estimators and also considered partial overlap, see also \citep{Song1992}.  
+%In our application to assessment of solution quality, we also consider varying the amount of overlap between neighboring batches.  
+We defer this discussion on partial overlap to \S \ref{ssec:overlap} and continue with a brief review of MRP.
 
@@
 
-Given a candidate solution $\xh \in \X$ to (\ref{eq:sto_prog}), the task is to estimate its optimality gap $\e{f(\xh,\xit)} - \zs$.  
-Recall that MRP uses the upper bound on the optimality gap, $\e{f(\xh,\xit)} - \e{\zs_m}$ (for a given sample size $m$), to construct a point estimator and a CI using the nonoverlapping batches method described above.
-Again, taking $n$ observations of the random variables and splitting them into $k$ batches of batch size $m$, define 
-\begin{equation} \label{eq:mrp_gap}
-	\gb_j = \frac{1}{m} \sum_{i = 1}^{m} f(\xh, \xit^{m(j-1)+i}) - \min_{\x \in X} \frac{1}{m} \sum_{i=1}^{m} f(\x, \xit^{m(j-1)+i}), \ \ \ \ j = 1,2, \dots, k.
-\end{equation}
-Since we are assessing the quality of a given solution $\xh \in \X$, we suppress it from the notation. 
-$\gb_j$ is similar to $\yb_j$ except that the second term on the right-hand side of (\ref{eq:mrp_gap}) minimizes a sample mean.  
+%Given a candidate solution $\xh \in \X$ to (\ref{eq:sto_prog}), the task is to estimate its optimality gap $\e{f(\xh,\xit)} - \zs$.  
+%Recall that MRP uses the upper bound on the optimality gap, $\e{f(\xh,\xit)} - \e{\zs_m}$ (for a given sample size $m$), to construct a point estimator and a CI using the nonoverlapping batches method described above.
+
+Taking $n$ observations of the random variables $\xit$ and splitting them into $k$ batches of batch size $m$, define 
+\begin{align} 
+	\gb_j =\  & \frac{1}{m} \sum_{i = 1}^{m} f(\xh, \xit^{m(j-1)+i}) - \min_{\x \in X} \frac{1}{m} \sum_{i=1}^{m} f(\x, \xit^{m(j-1)+i}),& \ \ \ \ j = 1,2, \dots, k \label{eq:mrp_gap}\\
+         =\  & \frac{1}{m} \sum_{i = 1}^{m} \left[ f(\xh, \xit^{m(j-1)+i}) -  f(\xs_j, \xit^{m(j-1)+i}) \right],& \ \ \ \ j = 1,2, \dots, k, \notag
+\end{align}
+where $\xs_j$ denotes an optimal solution to (\ref{eq:sto_prog_m}) of batch $j$ given on the right-hand side of (\ref{eq:mrp_gap}).    
+Since we are assessing the quality of a given solution $\xh \in \X$, we suppress it from the notation $\gb_j$.
+The optimality gap estimator $\gb_j$ is similar to $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
+Notice that, in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is the optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
 As before, after $k$ estimates are obtained, the overall mean of these estimates $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
@@
 Thus, we can expect that the true probability of the optimality gap residing within the confidence interval to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in Bayraksan and Morton \citep{Bayraksan2006}, which also suggests additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
+This is shown empirically in \citep{Bayraksan2006}, which also suggests additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
 See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.
-
-An advantage of MRP is its applicability to a wide range of problems.  
-With i.i.d.\ sampling, (\ref{eq:sto_prog}) can be linear or nonlinear, $\X$ can include integrality constraints or not.  
-It is also easy to implement, thus, has been applied to a variety of problems, see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.  
-Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
 
@@
 \label{sec:omrp}
-
-Our aim is to apply the idea of overlapping batches to MRP.  
-We note several differences in this setting compared to the simulation setting.  
-In simulation, the point of interest is estimating the variance of the sample mean of a covariance stationary process.  
-We are interested in estimating the variance of an optimality gap estimator.  
-Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
-First, minimization changes the statistical properties of sample means.  
-For instance, the central limit theorem may not hold for a minimized sample mean even though it holds for each $\x \in \X$.  
-We overcome this difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
-The nonoptimized counterparts have the desired statistical properties and we establish convergence of the optimality gap estimators to their nonoptimized counterparts. 
-Second, once the data is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
-In our setting, due to the solution of a sampling problem (SP$_m$), the computational effort can increase with data reuse.  
-Fortunately, near-optimal variance reduction can be obtained by partially overlapping the batches.  
-Partial overlap results in a fewer number of batches, hence fewer number of optimization problems need to be solved.  
-Moreover, in many solution methods, warm-starting can be used to solve sampling approximations with overlapping samples, considerably reducing solution time.
 

### 2013-10-25 omrp.tex
Streamlining Sec 3: OMRP
Mostly minor edits to make it read a bit better

@@
 
-Taking $n$ observations of the random variables $\xit$ and splitting them into $k$ batches of batch size $m$, define 
+Taking $n$ observations of the random variables $\xit$ and splitting them into $k$ nonoverlapping batches of size $m$, define 
 \begin{align} 
@@
 In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
-For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of Meketon and Schmeiser \citep{Meketon1984}.  
+For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
 The sample mean of each batch estimator is calculated similarly, 
@@
 When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  
-In general, from the spectral analysis given in Welch \citep{Welch1987}, the variance is reduced to
+In general, from the spectral analysis given in \citep{Welch1987}, the variance is reduced to
 \begin{equation} \label{eq:var_reduct_formula}
-	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right) = -\gammab\left( 1 - 2\gammab\cogb + \gammab^2\cogb^2 \right) + 2\gammab\cogb\left(1-\gammab\cogb\right) + \frac{2}{3}\gammab^3\cogb^3 + \frac{1}{3}\gammab^3\cogb
+	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right) %= -\gammab\left( 1 - 2\gammab\cogb + \gammab^2\cogb^2 \right) + 2\gammab\cogb\left(1-\gammab\cogb\right) + \frac{2}{3}\gammab^3\cogb^3 + \frac{1}{3}\gammab^3\cogb
 \end{equation}
 of the nonoverlapping case.  
-If $\ogb$ is an integer, the terms in parentheses vanish and (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
+If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
 
 A $(1-\alpha)$-level approximate CI on the mean can be formed using variably overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
-If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$ and for maximally overlapping batches, $d_{\gamma} = \frac{3}{2}$.
+If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$.  For maximally overlapping batches, the degrees of freedom is $d_{\gamma} = \frac{3}{2}$.
 
@@
 So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  
-We use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch; $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
+As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch; $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
 

### 2013-10-25 omrp.tex
Streamlining Sec 4.1, 4.2, and 4.3
a number of edits here and more writing to explain things better.

@@
 
-\subsection{Multiple Replications Procedure} \label{ssec:mrp}
+\subsection{Multiple Replications Procedure} 
+\label{ssec:mrp}
 
@@
 \begin{align} 
-	\gb_j =\  & \frac{1}{m} \sum_{i = 1}^{m} f(\xh, \xit^{m(j-1)+i}) - \min_{\x \in X} \frac{1}{m} \sum_{i=1}^{m} f(\x, \xit^{m(j-1)+i}),& \ \ \ \ j = 1,2, \dots, k \label{eq:mrp_gap}\\
-         =\  & \frac{1}{m} \sum_{i = 1}^{m} \left[ f(\xh, \xit^{m(j-1)+i}) -  f(\xs_j, \xit^{m(j-1)+i}) \right],& \ \ \ \ j = 1,2, \dots, k, \notag
+	\gb_j  & = \frac{1}{m} \sum_{i = 1}^{m} f(\xh, \xit^{m(j-1)+i}) - \min_{\x \in X} \frac{1}{m} \sum_{i=1}^{m} f(\x, \xit^{m(j-1)+i}), \ \ \ \ j = 1,2, \dots, k \label{eq:mrp_gap}\\
+         & = \frac{1}{m} \sum_{i = 1}^{m} \left[ f(\xh, \xit^{m(j-1)+i}) -  f(\xs_j, \xit^{m(j-1)+i}) \right], \ \ \ \ j = 1,2, \dots, k, \notag
 \end{align}
@@
 The overall mean, $\gbb_l$, is defined a little differently.  
-Here, $\gbb_l$ still uses each observation $i = 1, 2, \dots, n_l$ but also makes use of all the information collected throughout the batches.  
+Here, $\gbb_l$ still uses each observation $i = 1, 2, \dots, n_l$ but also makes use of {\it all} the information collected throughout the batches.  
 That is, if observation $\xiti$ is used in $|B(i)|$ number of batches, all the optimal solutions $\xs_j$ corresponding to each batch $j \in B(i)$ are used for the lower bound estimator.  
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Theoretical Results} 
@@
 Finally, our proof relies on an exponential rate of convergence of sampled solution to the true solution of the problem.  
-Assumption A3 can be satisfied in several ways.  
-Shapiro and Homem-de-Mello \citep{shapiro2000rate} establish rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite and the optimal solution is unique.
-Kleywegt, Shapiro,and Homem-de-Mello \citep{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition of a unique optimal solution $\xs$, and that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $x \in X \backslash \{\xs\}$ is finite valued on $\R$.
+Assumption A3 can be satisfied for different classes of problems with unique optimal solutions.  
+\citet{shapiro2000rate} establish exponential rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite.
+\citet{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $x \in X \backslash \{\xs\}$ is finite valued on $\R$.
 This class of problems includes stochastic integer programs with recourse.
@@
 To overcome this problem, we introduce the following unbiased optimality gap estimators:
+
 \begin{align}
@@
 
+We begin with two lemmas that establish exponential rates of convergence of certain intermediate quantities.
+
 \begin{lemma} \label{lem:gbb_prob}
@@
 
-\begin{proof}
+\begin{proof} Let $E^C$ denote the complement of event $E$. Note that
 	\begin{align}
@@
 
+We are now ready to show that the resulting point estimators are strongly consistent. 
+We use the abbreviation a.s.\ to denote almost sure convergence. 
+We also use $\mu_{\xh} := \e{\left[f(\xh,\xit) - f(\xs,\xit)\right]}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
+
 \begin{theorem} \label{thm:strong_consistency}
-	Under assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s, and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s. as $l \rightarrow \infty$.  
-        Thus, $\gbb_l$ is a consistent estimator of $\mu_{\xh} = \e{\left[f(\xh,\xit) - f(\xs,\xit)\right]}$, and if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$, then $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$.
+	Under assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s., and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s.\ as $l \rightarrow \infty$.  
+        Therefore, $\gbb_l$ is a consistent estimator of $\mu_{\xh}$, and if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, then $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$.
 \end{theorem}
@@
 \begin{proof}
-	(i) By Lemma \ref{lem:gbb_prob} we saw that $\p{\dbb_l - \gbb_l \neq 0} \rightarrow 0$ exponentially fast.  
+	(i) By Lemma \ref{lem:gbb_prob}, $\p{\dbb_l - \gbb_l \neq 0}$ $\rightarrow 0$ exponentially fast.  
         Thus $\sum_l \p{\dbb_l - \gbb_l \neq 0} < \infty$.  
@@
 	\]
-	and by the proof of Lemma \ref{lem:gbb_prob}, $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast, and thus $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$ if $n_l VD_l$ is, by the Borel-Cantelli Lemma.
+	and by the proof of Lemma \ref{lem:gbb_prob}, $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast, and thus $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$, if $n_l VD_l$ is, by the Borel-Cantelli Lemma.
 \end{proof}
 
-Part (i) of Theorem 1 provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$.
+Part (i) of Theorem \ref{thm:strong_consistency} provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$.
 Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s. 
-
+Similarly, part (ii) of Theorem \ref{thm:strong_consistency} establishes almost sure convergence of $n_l VG_l - n_l VD_l$ to $0$ as $l \rightarrow \infty$. 
+As a result, if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, so is $n_l VG_l$.  
 Strong consistency of the variance estimator $n_l VD_l$ have been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  

### 2013-10-26 omrp.tex
Streamlining Sec 4.4 and 4.5
format changes + a bit more explanations sprinkled here and there

@@
 
-Meketon and Schmeiser \citep{Meketon1984} show that $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha = \frac{4}{3}$ for maximally overlapping batches and $\alpha = 2$ for nonoverlapping batches, resulting in the decrease of variance for the maximally overlapping batches estimator.
-Welch \citep{Welch1987} expands this result to variable amounts of overlap, showing that $\alpha$ is twice the value of (\ref{eq:var_reduct_formula}).  
-Damerdji \citep{damerdji1995mean} shows that convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\alpha \sigma^4_{\xh}$, and thus the mean-square consistency of $n_l VD_l$, is guaranteed for $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
+\citet{Meketon1984} show that $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha = \frac{4}{3}$ for maximally overlapping batches and $\alpha = 2$ for nonoverlapping batches, resulting in the decrease of variance for the maximally overlapping batches estimator.
+\citet{Welch1987} expands this result to variable amounts of overlap, showing that $\alpha$ is twice the value of (\ref{eq:var_reduct_formula}).  
+\citet{damerdji1995mean} shows that convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\alpha \sigma^4_{\xh}$---thus the mean-square consistency of $n_l VD_l$---is guaranteed for $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
 (With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.)
 
-To prove the variance reduction results in our setting, we wish to show that $({n_l}/{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0$, for which it suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.
+To prove the variance reduction results in our setting, we wish to show that 
+$$
+(\tfrac{n_l}{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0,
+$$
+for which it suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.
 
@@
 	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
-        Further, we use abbreviations $n_b = \nbl$ and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$.
+        Further, we use abbreviations $n_b = \nbl$ and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the number of batches and the denominator term in $VG$ and $VD$ in the variably overlapping batches, respectively.
+Note that
 	\begin{align}
@@
         We will separate these into identically distributed ``center'' batches and ``fringe'' batches.  
-        In Figure \ref{fig:overlap_nonint}, only batch 4 is a center batch, while the others are fringe batches.  
-        Notice in Figure \ref{fig:overlap_nonint}, we see $\left\lceil \gammab^{-1} \right\rceil = 3$ sets of nonoverlapping batches, each of which has two fringe batches.  
+        For example, in Figure \ref{fig:overlap_nonint}, only batch 4 is a center batch, while the others are fringe batches.  
+        Notice in Figure \ref{fig:overlap_nonint}, we see $\left\lceil \gammab^{-1} \right\rceil = 3$ sets of nonoverlapping batches $\{1,4,7\}$, $\{2,5\}$, and $\{3,6\}$, each of which has two fringe batches.
         In general, there are $\left\lceil \gammab^{-1} \right\rceil$ sets of nonoverlapping batches, each of which will have two fringe batches, and $n_b - 2\left\lceil \gammab^{-1} \right\rceil$ center batches.
@@
 	\begin{align*}
-		\left( \frac{n}{df} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } & = \left( \frac{n}{df} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
+		& \left( \frac{n}{df} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
+		 =  & \left( \frac{n}{df} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
 		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
@@
 		} \\
-		& = \left( \frac{n}{df} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
-		& = \left( \frac{n}{df} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
+		 = & \left( \frac{n}{df} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
+		 = & \left( \frac{n}{df} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
 		+ \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
@@
 	where equation (\ref{eq:var_reduct_cauchy2}) follows from the Cauchy-Schwartz inequality, and equation (\ref{eq:var_reduct_holder2}) follows from H\"{o}lder's inequality.  
-        Since we can bound both expectation terms by A2, we can demonstrate $\sqrt{\frac{n}{m}}(nVG - nVD) \xrightarrow{L^2} 0$ by focusing on only one of the terms.  
-        Focusing on the first expectation term and returning the $\tfrac{n}{m}$, by H\"{o}lder's inequality,
+        Since we can bound both expectation terms in (\ref{eq:var_reduct_holder2}) by A2, we can demonstrate $\sqrt{\frac{n}{m}}(nVG - nVD) \xrightarrow{L^2} 0$ by focusing on only one of the terms.  
+        Focusing on the first expectation term in (\ref{eq:var_reduct_holder2}) and returning the $\tfrac{n}{m}$, by H\"{o}lder's inequality,
 	\begin{align*}
@@
 
-% END CHANGE
+Theorem \ref{thm:varvar_conv} shows conditions under which the same asymptotic variance reduction results are achieved for the OMRP optimality gap variance estimator. 
+We will empirically examine the variance reduction for small sample sizes in \S \ref{sec:comp}. 
+%We end our theoretical properties in the next section by examining the CIs formed using OMRP.
 

### 2013-10-26 omrp.tex
Streamlining Sec 5: COMPUTATIONAL RESULTS - I
(1)  Created a number of subsections for better organization
(2)  Added a table on problem characteristics  (3) Changed the writing
in the subsections

@@
 \usepackage{enumerate}
+\usepackage{multirow}
+\usepackage{booktabs}
 %\usepackage{mathptmx}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Computational Results}
@@
 
-We empirically tested the effectiveness of OMRP on four problems.
+In the previous section, we proved asymptotic results regarding the OMRP estimators. 
+In this section, we apply OMRP to several test problems and examine its small-sample behavior. 
+We begin our discussion by introducing the test problems used for numerically evaluating OMRP in \S \ref{ssec:test}, followed by experimental setup in \S \ref{ssec:expS}.
+Then, we present and discuss our numerical experiments in \S \ref{ssec:results}.
+
+\subsection{Test Problems}
+\label{ssec:test}
+
+We empirically tested the effectiveness of OMRP on four test problems.
+All test problems are two-stage stochastic programs with recourse and were selected to study the behavior of OMRP under a variety of different situations, as we will shortly discuss below.
+The characteristics of these problems are given in Table \ref{tb:test_problems}. 
 The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$.
-The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations.
-The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables.
-The final problem is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations.
-Descriptions of CEP1, 10D, and DB1 can be found in \citep{higle1996}, \citep{kleywegt2002sample}, and \citep{donohue1995upper}, respectively.
+We denote this problem as NVD.
+The instance of the newsvendor problem can be found in \citep{Bayraksan2006}, except here we used a discrete uniform demand distribution.
+The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations \citep{higle1996}.
+The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables \citep{kleywegt2002sample}.
+The final problem is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations \citep{donohue1995upper}.
+
+\begin{table}[ht]
+\centering
+\scriptsize
+\begin{tabular}{lcccc}
+\hline
+& \# of 1st Stage & \# of 2nd Stage & \# of Stochastic & \multirow{2}{*}{\# of Scenarios} \\
+Problem & Variables & Variables & Parameters & \\
+\cmidrule(r){1-1} \cmidrule(l){2-5}
+NVD 	& 1     	& 1     	& 1   	& $10^5 + 1$ \\
+CEP1 	& 8     	& 15   	& 3   	& $216$ \\
+10D 	& 10     & 1     	& 10   	& $\infty$ \\
+DB1 	& 5   	& 102   	& 46   	& $4.5\times 10^{25}$ \\
+\hline
+\end{tabular}
+\caption{Test problem characteristics}
+\label{tb:test_problems}
+\end{table}
+
 The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \citep{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.
-The problems CEP1, DB1 and newsvendor can be written as two-stage stochastic linear programs with recourse.
-CEP1 and DB1 were solved with the regularized decomposition algorithm of \citep{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
-The newsvendor problem was solved using the quicksort algorithm in C++, and 10D was solved using dynamic programming.  
-In all cases, we used the Mersenne Twister algorithm to generate random samples \citep{wagner_twister_09}.
 
@@
 
-We used a total sample size of $n = 30 m$, with several values of the batch size $m$. 
+\subsection{Experimental Setup}
+\label{ssec:expS}
+
+We used a total sample size of $n = 30 m$, with several values of the batch size $m=100, 200, \ldots$. 
 Then, at each value of $m$, we formed OMRP estimators, with varying amounts of overlap. 
@@
 Results for the newsvendor problem were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.
+
+While NVD can be written as a two-stage stochastic linear program with recourse, it can be solved quickly by sorting the demand values. 
+We solved it using the quicksort algorithm in C++. 
+The problems CEP1 and DB1 are two-stage stochastic linear programs with recourse and were solved with the regularized decomposition algorithm of \citep{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
+10D is a stochastic integer program and was solved using dynamic programming.  
+In all cases, we used the Mersenne Twister algorithm to generate random samples \citep{wagner_twister_09}.
+
+\subsection{Results of Experiments}
+\label{ssec:results}
+
 Summary of results from these experiments are depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.

### 2013-10-26 omrp.tex
Streamlining Sec 5 - II
A whole bunch of edits

@@
 In this section, we apply OMRP to several test problems and examine its small-sample behavior. 
-We begin our discussion by introducing the test problems used for numerically evaluating OMRP in \S \ref{ssec:test}, followed by experimental setup in \S \ref{ssec:expS}.
+We begin our discussion by introducing the test problems used for numerically evaluating OMRP in \S \ref{ssec:test}, followed by our experimental setup in \S \ref{ssec:expS}.
 Then, we present and discuss our numerical experiments in \S \ref{ssec:results}.
@@
 We empirically tested the effectiveness of OMRP on four test problems.
-All test problems are two-stage stochastic programs with recourse and were selected to study the behavior of OMRP under a variety of different situations, as we will shortly discuss below.
+All test problems are two-stage stochastic programs with recourse and were selected to study the behavior of OMRP under a variety of different situations---we will shortly discuss this below.
 The characteristics of these problems are given in Table \ref{tb:test_problems}. 
@@
 The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables \citep{kleywegt2002sample}.
-The final problem is a stochastic vehicle routing problem denoted DB1, with 46 stochastic parameters and a total of $4.5 \cdot 10^{25}$ realizations \citep{donohue1995upper}.
+The final problem is a stochastic vehicle routing problem, denoted DB1, with 46 stochastic parameters and a total of $4.5 \times 10^{25}$ realizations \citep{donohue1995upper}.
 
@@
 
-The instance of the newsvendor problem as well as the candidate solutions used for both problems can be found in \citep{Bayraksan2006}, except here we used a discrete uniform demand distribution for the newsvendor problem.
+We made several considerations in selecting the test problems.
+NVD can be solved very quickly, which allows for solving a large number of independent runs for examining the small-sample behavior of OMRP.
+CEP1 is also easy to solve; the optimal solution $\xs$ can be obtained with high probability even for small sample sizes.
+This feature shows the behavior of $VG$ when the gap size is determined mostly by sampling error, rather than bias.
+10D demonstrates the behavior of OMRP when $|X|$ is finite.
+Furthermore, 10D has a high condition number \citep{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP when the bias of the gap is significant.
+The optimal solutions of NVD, CEP1, and 10D are known, allowing for explicitly checking and verifying the results.
+In contrast, DB1 is a large-scale problem with an unknown optimal solution.
+This final test problem allows us to investigate how OMRP works on large-scale problems.
 
-We made several considerations in selecting the test problems.
-Newsvendor can be solved very quickly, which allows for solving a large number of independent runs for examining the small sample behavior of OMRP.
-CEP1 is also easy to solve, and obtains the optimal solution $\xs$ with high probability even for small sample sizes.
-This feature shows the behavior $VG$ when the gap size is determined mostly by sampling error, rather than bias.
-10D demonstrates the behavior of OMRP when $|X|$ is finite.
-Furthermore, 10D has a high condition number \citep{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP with the bias of the gap is significant.
-The optimal solutions of both 10D and CEP1 are known, allowing for explicitly checking the computational results.
-In contrast, DB1 is a large scale example, with an unknown optimal solution.
-This final problems allows us to show that OMRP works on more computationally difficult problems.
+The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
+We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) with an estimated $\mu_{\xh} = 1.08$ for DB1. 
+Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used to estimate the coverage probability of the OMRP CIs for this test problem below.
 
@@
 
+Our experiments were conducted as follows. 
 We used a total sample size of $n = 30 m$, with several values of the batch size $m=100, 200, \ldots$. 
-Then, at each value of $m$, we formed OMRP estimators, with varying amounts of overlap. 
-We also formed 90\% confidence intervals on the optimality gap using ORMP estimators. 
-Results for the newsvendor problem were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.
+Then, at each value of $m$, we formed the OMRP estimators with varying amounts of overlap. 
+We also set $\alpha=0.10$ formed 90\% confidence intervals on the optimality gap using the ORMP estimators. 
+Results for NVD were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.
 
+We solved the sampling approximations of the test problems as follows.
 While NVD can be written as a two-stage stochastic linear program with recourse, it can be solved quickly by sorting the demand values. 
 We solved it using the quicksort algorithm in C++. 
-The problems CEP1 and DB1 are two-stage stochastic linear programs with recourse and were solved with the regularized decomposition algorithm of \citep{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
-10D is a stochastic integer program and was solved using dynamic programming.  
+The problems CEP1 and DB1 are two-stage stochastic linear programs with recourse and were solved with the regularized decomposition algorithm of \citet{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
+10D is a stochastic knapsack problem and was solved efficiently using dynamic programming.  
 In all cases, we used the Mersenne Twister algorithm to generate random samples \citep{wagner_twister_09}.
@@
 Summary of results from these experiments are depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
+Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
+The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
+Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
+These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
+We note that the variance reduction in DB1 can be less than the asymptotic amount for the small sample sizes used in these experiments. 
+Even with the relatively small sample sizes, compared to the size of this problem, overlapping appears to achieve some variance reduction.
 
@@
 	\caption{
-		Summary of results for the newsvendor problem. 
+		Summary of results for NVD. 
 		(a) Reduction in variance of $nVG$,
@@
 
-Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
-The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
-Empirical results agree with the theoretical values well, with more variability observed in CEP1 and 10D, providing evidence that similar variance reduction can be achieved in stochastic programming by overlapping the batches even with small sample sizes.
-DB1 shows some variance reduction, but less than the asymptotic amount for small sample sizes.
-
 Figure~\ref{fig:nv}(b) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and amount of overlap. 
@@
 Although the estimate of $\e{nVG}$ looks large for $m=100$, the error from $\sigma^2_\xh$ is never more than 1\%.  
-Estimates for $\e{nVG}$ showed a similar pattern for CEP1 and 10D.  Those graphs are omitted for brevity.
+Estimates for $\e{nVG}$ showed a similar pattern for CEP1, 10D, and DB1.  
+Those graphs are omitted for brevity.
 
 Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of confidence intervals generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
-The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for newsvendor, and we observed the same for CEP1 and 10D.
+The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
+We observed the same for CEP1, 10D, and DB1.  
 The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
 Coverage probability for 10D and DB1 (not shown) were very high, more than $0.99$.  
-The bias from solving (\ref{eq:sto_prog_m}) for these larger problems seems to be much more significant than the variance.
+The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.
 
 Because variance reduction drops quickly as $\gammab$ drops below $1$, the authors recommend using an intermediate value of $\gammab$, such as $1/3$ or $1/4$, to gain the majority of the variance reduction, while reducing the number of optimization problems to be solved.
-Warm-starting the algorithm to solve the sampling problems, when such as scheme is available, can significantly reduce the solution times.
+Warm-starting the algorithm to solve the sampling problems, when such as scheme is available, can significantly reduce the computation times.
 
-\section{Conclusion} \label{sec:concl}
+\section{Conclusions} \label{sec:concl}
 We have extended previous work from simulation analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo sampling-based estimators of optimality gaps in stochastic programs \citep{Mak1999}.

### 2013-10-27 omrp.tex
Streamlining Sec 6 & References
(1) Added a new reference, referring to ACM TOMACS paper for Mersenne
Twister
(2) Changed the reference for MT C++ implementation
(3) Other minor edits in Sec 6, etc.

@@
 The problems CEP1 and DB1 are two-stage stochastic linear programs with recourse and were solved with the regularized decomposition algorithm of \citet{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
-10D is a stochastic knapsack problem and was solved efficiently using dynamic programming.  
-In all cases, we used the Mersenne Twister algorithm to generate random samples \citep{wagner_twister_09}.
+10D is a stochastic knapsack problem and was solved using dynamic programming.  
+In all cases, we used the Mersenne Twister algorithm of \citet{matsumoto_nishimura_98} to generate the random samples, using an implementation in C++ \citep{wagner_twister_09}.
 
@@
 
-Because variance reduction drops quickly as $\gammab$ drops below $1$, the authors recommend using an intermediate value of $\gammab$, such as $1/3$ or $1/4$, to gain the majority of the variance reduction, while reducing the number of optimization problems to be solved.
+Because variance reduction drops quickly as $\gammab$ drops below $1$, we recommend using an intermediate value of $\gammab$, such as $1/3$ or $1/4$, to gain the majority of the variance reduction, while reducing the number of optimization problems to be solved.
 Warm-starting the algorithm to solve the sampling problems, when such as scheme is available, can significantly reduce the computation times.
 
-\section{Conclusions} \label{sec:concl}
-We have extended previous work from simulation analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo sampling-based estimators of optimality gaps in stochastic programs \citep{Mak1999}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusions} \vspace*{-0.1in}
+\label{sec:concl}
+
+We have extended previous work from simulation output analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo simulation-based estimators of optimality gaps in stochastic programs \citep{Mak1999}.
 We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid confidence intervals can be formed.
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgments}\vspace*{-0.1in}
 The authors thank Andrzej Ruszczy{\'{n}}ski and Artur {\'{S}}wietanowski for
 access to their regularized decomposition code, which was used to solve CEP1 and DB1. 
-This research is supported
-in part by the National Science Foundation under Grants DMS-0602173 and
-EFRI-0835930.  
+%This research is supported in part by the National Science Foundation under Grants DMS-0602173 and EFRI-0835930.  
 An earlier version of this paper appeared in \citep{love2011overlapping}.

### 2013-10-27 omrp.tex
More Fixes on References
Maybe there is a better way to fix this but when I compile the BibTeX,
it shows doi of the papers, ISSN of the journals, etc.  So, I went
through and cleaned the .bib file
Final Pass
I cannot stop editing, it looks like. BUT... I am stopping.

@@
 
-Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is widely used in simulation to obtain variance estimators with lower variances. 
+Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators with lower variances. 
 While OBM is often used for variance estimators of means, it can also be used for variance estimators of non-means \citep{SAH90} and more recently, it has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) \citep{Alexopoulos01012007,Alexopoulos2007} and their folded versions \citep{Meterelliyoz_etal_12}.
@@
 Because the optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonovelapping batches of data to generate a number of optimality gap estimators. 
-These individual estimators are then used to form point and interval estimators using the classical nonoverlapping batch means method.
+These individual estimators are then used to form point and interval estimators applying the classical nonoverlapping batch means method.
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
@@
 With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
-It is also easy to implement, thus, has been applied to a variety of problems, including finance, supply chain network design, etc.\; see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
+It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
 Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
@@
 Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
-First, minimization changes the statistical properties of sample means.  
+Minimization changes the statistical properties of sample means.  
 For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
@@
 The nonoptimized counterparts have the desired statistical properties and we establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
-Second, once the data is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
+Another difference is, once the data is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
 In this setting, due to the solution of a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
@@
 Partial overlap results in a fewer number of batches, hence fewer number of optimization problems need to be solved.
-In this paper, we consider partial overlap and show that same asymptotic benefits are obtained and examine the effectiveness of partial overlap with small sample sizes. 
+In this paper, we consider variable amounts of overlap and examine this both theoretically and empirically. 
 Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
@@
 We first discuss the overlapping batch means in \S \ref{ssec:obm} and then briefly go over the multiple replications procedure in \S \ref{ssec:mrp}.  
-In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with partial overlap.  
+In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with variable amounts of overlap.  
 In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.
@@
 
-Nonoverlapping batch means takes $n$ observations, $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume for now $n = mk$).
+Nonoverlapping batch means takes $n$ observations, $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume, for now, $n = mk$).
 The sample mean of each batch is then computed as
@@
 Overlapping batch means modifies this idea by taking batches given by $\yb_j(m) = \frac{1}{m} \sum_{i=1}^{m}$ $y^{(j-1)+i}$, for $j = 1, \dots, n-m+1$.
-As an example, suppose each batch contains $m$ observations and that there are a total of $2m$ observations.
+As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
 In the nonoverlapping case, there are only two batches: the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.   
@@
 Note that the corresponding batch means are no longer independent. 
-However, by simply reusing the data in this fashion, and seemingly in a contradictory way that induces dependence, one obtains a better variance estimator. 
-\citet{Meketon1984} show several attractive properties of the overlapping batches variance estimator, the two most important of which are: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
+However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
+\citet{Meketon1984} show that: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
 That is, 
@@
 
-\citet{Welch1987} established the relationship between OBM and spectral estimators and also considered partial overlap, see also \citep{Song1992}.  
+\citet{Welch1987} established the relationship between OBM and spectral estimators and also considered variable amounts of overlap, see also \citep{Song1992}.  
 %In our application to assessment of solution quality, we also consider varying the amount of overlap between neighboring batches.  
-We defer this discussion on partial overlap to \S \ref{ssec:overlap} and continue with a brief review of MRP.
+We defer this discussion on variable overlap to \S \ref{ssec:overlap} and continue with a brief review of MRP.
 
@@
 As before, after $k$ estimates are obtained, the overall mean of these estimates $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
-The sample variance is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in a one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$ that has a level of significance which is approximately $\alpha$.
+The sample variance is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in a one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$ that has a level of significance, which is approximately $\alpha$.
 
@@
 Thus, we can expect that the true probability of the optimality gap residing within the confidence interval to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in \citep{Bayraksan2006}, which also suggests additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
+This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
 See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.
@@
 Now we are ready to define the estimators for OMRP.
-
 \begin{align}
-	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xh,\xit^{\gamma_l(j-1)+i}) - \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xs_j,\xit^{\gamma_l(j-1)+1}),\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
+	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
 	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
@@
 To overcome this problem, we introduce the following unbiased optimality gap estimators:
-
 \begin{align}
-	\db_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xh,\xit^{\gamma_l(j-1)+i}) - \frac{1}{m_l} \sum_{i=1}^{m_l} f(\xs,\xit^{\gamma_l(j-1)+i}),\ \ \ j = 1, 2, \dots, \nbl, \label{eq:dbar} \\
+	\db_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs,\xit^{\gamma_l(j-1)+i}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:dbar} \\
 	\dbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \left[ f(\xh,\xiti) - f(\xs,\xiti) \right], \label{eq:dbb} \\
@@
 	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
-        Further, we use abbreviations $n_b = \nbl$ and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the number of batches and the denominator term in $VG$ and $VD$ in the variably overlapping batches, respectively.
+        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
 Note that
@@
 In the previous section, we proved asymptotic results regarding the OMRP estimators. 
-In this section, we apply OMRP to several test problems and examine its small-sample behavior. 
+In this section, we apply OMRP to several test problems and examine small-sample behavior. 
 We begin our discussion by introducing the test problems used for numerically evaluating OMRP in \S \ref{ssec:test}, followed by our experimental setup in \S \ref{ssec:expS}.
-Then, we present and discuss our numerical experiments in \S \ref{ssec:results}.
+Then, we present and discuss the numerical results in \S \ref{ssec:results}.
 
@@
 The characteristics of these problems are given in Table \ref{tb:test_problems}. 
-The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$.
-We denote this problem as NVD.
+The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$; we denote it as NVD.
 The instance of the newsvendor problem can be found in \citep{Bayraksan2006}, except here we used a discrete uniform demand distribution.
@@
 
-\begin{table}[ht]
+\begin{table}[thb]
 \centering
-\scriptsize
+\footnotesize
 \begin{tabular}{lcccc}
@@
 CEP1 is also easy to solve; the optimal solution $\xs$ can be obtained with high probability even for small sample sizes.
-This feature shows the behavior of $VG$ when the gap size is determined mostly by sampling error, rather than bias.
+This feature shows the behavior of $VG$ when the gap CI width is determined mostly by sampling error, rather than bias.
 10D demonstrates the behavior of OMRP when $|X|$ is finite.
@@
 The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
-We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) with an estimated $\mu_{\xh} = 1.08$ for DB1. 
-Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used to estimate the coverage probability of the OMRP CIs for this test problem below.
+We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an estimated $\mu_{\xh} = 1.08$. 
+Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used below to estimate the coverage probability of the OMRP CIs for this test problem.
 
@@
 Then, at each value of $m$, we formed the OMRP estimators with varying amounts of overlap. 
-We also set $\alpha=0.10$ formed 90\% confidence intervals on the optimality gap using the ORMP estimators. 
+We also set $\alpha=0.10$, forming 90\% confidence intervals on the optimality gap using the ORMP estimators. 
 Results for NVD were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.
@@
 We note that the variance reduction in DB1 can be less than the asymptotic amount for the small sample sizes used in these experiments. 
-Even with the relatively small sample sizes, compared to the size of this problem, overlapping appears to achieve some variance reduction.
+%Even with the relatively small sample sizes, compared to the size of this problem, overlapping appears to achieve some variance reduction.
 
@@
 We observed the same for CEP1, 10D, and DB1.  
-The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with the our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
+The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
 Coverage probability for 10D and DB1 (not shown) were very high, more than $0.99$.  
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions} \vspace*{-0.1in}
+\section{Conclusions}
 \label{sec:concl}
@@
 
-\section*{Acknowledgments}\vspace*{-0.1in}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgments}
 The authors thank Andrzej Ruszczy{\'{n}}ski and Artur {\'{S}}wietanowski for
@@
 
-% Please don't exchange the bibliographystyle style 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{abbrvnat}
-% AUTHOR: Include your bib file here
 \bibliography{omrp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2013-10-28 omrp.tex
A bit more selling + some other minor edits

@@
 While OBM is often used for variance estimators of means, it can also be used for variance estimators of non-means \citep{SAH90} and more recently, it has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) \citep{Alexopoulos01012007,Alexopoulos2007} and their folded versions \citep{Meterelliyoz_etal_12}.
+To the best of our knowledge, OBM has never been studied in a stochastic optimization context before. 
 In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.  
@@
 We present computational results to examine small-sample behavior. 
-Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
+Our experiments indicate that variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
 
@@
 Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
+Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
 We note several differences in this setting compared to the classical setting.  
@@
 In the next section, we review relevant background information.  
-We first discuss the overlapping batch means in \S \ref{ssec:obm} and then briefly go over the multiple replications procedure in \S \ref{ssec:mrp}.  
-In \S \ref{sec:omrp}, we present the overlapping multiple replications procedure (OMRP) with variable amounts of overlap.  
+We first discuss the overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
+In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with variable amounts of overlap.  
 In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.
@@
 These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
-We note that the variance reduction in DB1 can be less than the asymptotic amount for the small sample sizes used in these experiments. 
-%Even with the relatively small sample sizes, compared to the size of this problem, overlapping appears to achieve some variance reduction.
+We note that the variance reduction in DB1 can be less than the asymptotic amount. %for the small sample sizes used in these experiments. 
+Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to achieve some variance reduction.
 

### 2014-05-21 Referee1_Response.tex
Added .tex files for the revision
1. omrp_lb_rev.tex (revised paper)
2. EinC_response.tex
3. AE response
4. Referee1 response
5. Referee2 response
and 6. the .bib file

\documentclass[11pt,notitlepage,onecolumn]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chicago}
\usepackage[singlespacing]{setspace}

\setcounter{MaxMatrixCols}{10}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}

\newcommand{\noi}{\noindent}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\baselineskip0.26in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak

\begin{center}
\textbf{\Large Response to Referee 1} 
\medskip

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
\medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the helpful comments and suggestions. 
We incorporated all of the recommended changes and believe the paper is improved as a result. 
Below, we go through in detail these changes. 
\medskip

\bigskip

%%%%%%%%%%%%%%%%%
%% Need to be careful with the minor changes. Will these be affected?
%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
%%    - GB
%%%%%%%%%%%%%%%%%

\noi  
{\large \bf ``Major'' comments:}
\medskip

\begin{itemize}
\item[\textbf{M1.}] \textit{In the typical simulation setting, the computational effort required to produce the output dominates, and hence one would like to ``make the most'' of the output in terms of analysis. 
Sometimes, a similar motivation can arise in stochastic optimization because there may be a computationally expensive underlying simulation model that must be run to produce the i.i.d.\ realizations that are then used in an SAA approach. 
(While they don't now, the authors could include this as motivation for
their work.)}
\end{itemize}

\noi 
We thank the referee for this suggestion. 
You are right.
There are cases when generating scenarios is expensive in the stochastic optimization setting as well. 
We changed the introduction based on your, the associate editor and the other reviewer's comments. 
We specifically added this as a motivation. 
\medskip

\begin{itemize}
\item[] \textit{However, perhaps more often, sampling the i.i.d. realizations is computationally cheap compared to solving the resulting SAA instances in stochastic optimization. 
In this latter case, we have a choice between simply increasing the number of batches in a non-overlapping method or using the overlapping batch means approach (with some degree of overlap) in order to reduce variance.
Based on the paper's results, perhaps the computational effort required to achieve a level of variance reduction should guide this choice. 
The authors do point to the fact that warm starts in a stochastic
optimization algorithm can be exploited much more easily when using overlapping batch means than when not using overlapping batches. 
Some attempt to explore this tradeoff would be valuable. 
The computational results use sorting (for the news vendor problem), a dynamic programming algorithm (for a stochastic knapsack model), and a decomposition method (for two-stage stochastic linear programs). 
While I am not suggesting that this exploration needs to be made for all three types of algorithms, even exploring it in the case of the sorting algorithm (where some algorithms are well suited for almost-sorted lists) could provide valuable insight.}
\end{itemize}

\noi 
xxx Need to discuss xxx  \medskip 
We performed such an analysis and provide the results of this in the new subsection 7.4... ?? 
Etc.
\medskip

\begin{itemize}
\item[\textbf{M2.}] \textit{The choice of the lower bound that is embedded in equation (8) is interesting. 
(The upper bound in equation (8) is completely natural as the sample mean of the $n_l$ realizations of the function evaluated at $\hat{x}$.) 
It seems that there are also other natural choices that could be made here for the lower bound. 
There is some discussion of this choice in the text that follows equations (7)-(9), but can the authors say more? For example, do the consistency and asymptotic validity results that follow hinge on this choice? Or, do those results also hold for other choices, like forming $\bar\bar{G}$ as a sample
mean of the underlying $\bar{G}$ values. 
We know that the individual gap estimators in (7) are nonnegative, and if we formed $\bar\bar{G}$ as a sample mean of $\bar{G}$ values, it would be nonnegative. 
Is the $\bar\bar{G}$, as specified in (8), nonnegative? 
Have the authors computationally explored other choices here? 
Any insight in this vein would be valuable to the reader in understanding the choice made in equation (8).}
\end{itemize}

\noi
xxxx  Need to discuss. 
I know I changed this but I don't remember why at this point. 
Some theory was incorrect but at that time, we had more relaxed conditions. 
Now we have exponential rates of convergence and it seems to me like anything here should be fine. 
I haven't checked but pretty sure. 
So, yes, why don't we use something else? 
When we did, the results weren't that different at all. 
Right?\ \ \ \ 
xxxxx
\medskip

\bigskip

\noi {\large \bf Minor comments:}

\bigskip

\begin{itemize}
\item[1.] \textit{p1, l49: Suggest: The Overlapping \ldots }
\end{itemize}

\noindent xxx Done. 
\medskip

\begin{itemize}
\item[2.] \textit{p2, l16, l22: overlapping is misspelled twice.}
\end{itemize}

\noindent xxx Corrected. 
\medskip

\begin{itemize}
\item[3.] \textit{p3, l23: Do the authors mean ``relaxations'' rather than ``relations''?}
\end{itemize}

\noindent xxx Corrected. 
\medskip

\begin{itemize}
\item[4.] \textit{p3, l38: Suggest: estimator of the optimality gap \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[5.] \textit{p4, l34: Suggest: once the data are generated through a simulation, they \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[6.] \textit{p4, l42: Suggest: Partial overlap results in fewer batches, hence fewer optimization \ldots}
\end{itemize}

\noindent xxx Changed. xxx MUST CHECK WITH OTHER REFEREE'S COMMENTS.
\medskip

\begin{itemize}
\item[7.] \textit{p6, l32: Suggest: The degrees \ldots make \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[8.] \textit{p7, l18: While a confidence level of $1-\alpha$ may be consistent with a level of significance of $\alpha$, perhaps this could be reworded (as it seemed to distract this reader a bit).}
\end{itemize}

\noindent xxx Changed the wording here. 
Thank you. 
\medskip

\begin{itemize}
\item[9.] \textit{p10, l23: Suggest: convergence of the sampled solution \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[10.] \textit{p12, l53: Suggest: Strong consistency \ldots has been \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[11.] \textit{p14, l13-14: Suggest: The fringe batches come \ldots The first and last batch are identically \ldots}
\end{itemize}

\noindent xxx Changed. 
\medskip

\begin{itemize}
\item[12.] \textit{ p14, l23: Please add $j = 1$ to the sum.}
\end{itemize}

\noindent xxx Added. 
\medskip

\begin{itemize}
\item[13.] \textit{p14, l35: The authors have gone to some length to distinguish different types of $A_j$ terms.
However, this equation has an $\mathbb{E}A_j^2$ term that has been collapsed from a sum, but we don't know ``which $j$''. 
Should there be a $\max_j \mathbb{E}A_j^2$ or some other treatment here?}
\end{itemize}

\noindent xxx NEED TO CHECK AND CORRECT AS NECESSARY. 
\medskip

\begin{itemize}
\item[14.] \textit{p15, Theorem 3: A hypothesis in the theorem is that $\hat{x} \neq x^*$, and yet the proof starts with the case that $\hat{x} = x^*$. 
That hypothesis could be removed if the claim had a ``$\geq$'' or this statement could be removed or modified.}
\end{itemize}

\noindent Thank you for catching this.  
We removed this statement from the proof of Theorem 3 and added it as a remark in the paragraph after the theorem.
\medskip

\begin{itemize}
\item[15.] \textit{p17, l44: Suggest: A summary of results \ldots experiments is depicted \ldots}
\end{itemize}

\noindent Done.
%\ \ \ XXXX CHECK LATER: THIS SECTION MIGHT CHANGE. 
\medskip

\begin{itemize}
\item[16.] \textit{p17, l55: Perhaps add a comment on why DB1 may not experience the asymptotic variance reduction? 
(Is it because it may lack a unique solution?)}
\end{itemize}

\noindent
Done.
% xxx Yes, it is partially because we are not sure if it has a unique optimal solution as DB1 has never been solved before. 
%Even if it has been solved, the variance reduction is shown asymptotically but the computations are only for small sample sizes. 
%We reworded this to reflect these points.
%Thank you for this suggestion. 
\medskip

\begin{itemize}
\item[17.] \textit{p18, figures: The figures are a bit small and hence can be hard to read without enlarging them (but perhaps this will be taken care of at production).}
\end{itemize}

\noindent xxx We enlarged the figures. 
\medskip

\begin{itemize}
\item[18.] \textit{p18, l57: The authors speak of coverage probabilities for DB1, but how can this be done without knowing an optimal solution to DB1?}
\end{itemize}

\noindent 
We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP CIs for this test problem.
We explain this at the end of Section 5.1 (Test Problems). 
We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for the test problem DB1. 
\medskip

\begin{itemize}
\item[19.] \textit{p19: It may be possible to expand on the last paragraph of Section 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
\end{itemize}

\noindent xxx We expanded this paragraph based on our findings. 
xxx Write more---hopefully, we will find good stuff!!!
\medskip

\end{document}

### 2014-05-21 Referee2_Response.tex
Added .tex files for the revision
1. omrp_lb_rev.tex (revised paper)
2. EinC_response.tex
3. AE response
4. Referee1 response
5. Referee2 response
and 6. the .bib file

\documentclass[11pt,notitlepage,onecolumn]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chicago}
\usepackage[singlespacing]{setspace}

\setcounter{MaxMatrixCols}{10}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}

\newcommand{\noi}{\noindent}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\baselineskip0.26in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak

\
\begin{center}
\textbf{\Large Response to Referee 2} 
\medskip

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
\medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the referee for the helpful comments and suggestions. 
We incorporated all of the recommended changes and believe the paper is improved as a result. 
Below, we go through in detail these changes. 
\medskip

\bigskip

%%%%%%%%%%%%%%%%%
%% Need to be careful with the minor changes. Will these be affected?
%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
%%    - GB
%%%%%%%%%%%%%%%%%

\noi  
{\large \bf General Comments:}
\medskip

\begin{itemize}
\item[1.] \textit{The main contributions of the paper need to be stated more clearly and succinctly.}
\end{itemize}

\noindent 
xxx  We agree. 
We changed the introduction to clearly state the contributions of the paper and \ldots 
\medskip

\begin{itemize}
\item[2.] \textit{It is not necessary to go into such detail in the OBM review.}
\end{itemize}

\noindent 
xxx  We shortened the section on OBM review by combining \ldots 
\medskip

\begin{itemize}
\item[3.] \textit{The English needs to be tightened up somewhat.}
\end{itemize}

\noindent  
xxxx
You are right. 
We went through the paper and tightened up the prose. 
We also incorporated all the changes you suggested below and hope the exposition of the paper is improved as a result.
We hope that any remaining English issues could be corrected by the English editor of the journal. (IS THERE ONE????) 
xxxx
\medskip

\bigskip

\noi  
{\large \bf Specific Comments:}
\medskip

\begin{itemize}
\item[] \textit{Page 1, Line 32 (and elsewhere): I believe that you ``apply the OBM method to stochastic programming'' rather than extend it.}
\end{itemize}

\noi
xxx  I actually prefer 'extend' but I am not going to argue over such small stuff. 
So, I will change this sentence and might look for others. 
\medskip

\begin{itemize}
\item[] \textit{1, 35 (and elsewhere): ``We give conditions'' instead of ``We show conditions''}
\end{itemize}

\noi
xxx  Changed
\medskip

\begin{itemize}
\item[] \textit{1, 37: What are the classical results? Reference?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{1, 49: Suggested rewrite to reduce ambiguity: ``The overlapping batch means (OBM) \ldots to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts. 
In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
Schmeiser et al.\ [1990] use overlapping estimators to estimate the
variance of estimators for non-means. 
More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated [Alexopoulos et al., 2007a,b].'' 
In this rewrite, note the use of active and passive referencing formats.}
\end{itemize}

\noi
xxxx  Thank you for this suggestion of rewrite. 
We rewrote this paragraph based on your corrections and paying attention to referencing formats. 
\medskip

\begin{itemize}
\item[] \textit{2, 5: ``never before been studied . . . context.''}
\end{itemize}

\noi
xxx  Changed.
\medskip

\begin{itemize}
\item[] \textit{2, 7: By ``same benefits'', you mean moderate bias and comparatively low variance, right?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 8: Start a new paragraph with ``A natural setting\ldots ''.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 10: ``especially'' instead of ``esp.''. 
Also, ``This'' instead of ``Assessing solution quality in stochastic programming'' (since it's repetitive)}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 13: ``Because optimality gap''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 24: ``under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 24 (and elsewhere): Note: I would be careful about the use of the term ``variance reduction'', which usually refers to the class of techniques such as common random numbers, antithetics, importance sampling, etc. 
I view what you're doing in this paper as simply proposing a new estimator whose variance is lower than that of a competing estimator.}
\end{itemize}

\noi
xxx  You are right. 
Thanks for pointing this out. We corrected the wording throughout the paper. 
\medskip

\begin{itemize}
\item[] \textit{2, 27: ``and that the interval \ldots valid. 
We also present''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 28: ``Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage --- for both small- and large-sample cases.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 34 (and elsewhere): Might want to boldface all vectors.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{2, 42 (and elsewhere): ``more-restrictive moment'' (hyphenate certain non-adverbial compound adjectives)}
\end{itemize}

\noi
xxx  Thank you; we went through the paper and hyphenated all the compound adjectives.
\medskip

\begin{itemize}
\item[] \textit{2, 51: You can delete ``(SAA)'', since the notation isn't used again in the paper.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 11: ``solution; and''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 24 (and elsewhere): ``Lagrangian, or'' (comma after penultimate entry in a conjunctive list)}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 37: ``we can simply use $z_m^*$''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 38: ``estimator of the optimality''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{3, 53: ``The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S 2.2).''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 5 (and elsewhere): ``see, e.g., Bertocchi et al. [2000]; \ldots ''}
\end{itemize}

\noi
xxx  I don't think I agree with this. 
These need to be in parentheses! 
\medskip

\begin{itemize}
\item[] \textit{4, 14: Delete the sentence ``Especially \ldots '' since it doesn't really add anything to the discussion.}
\end{itemize}

\noi
xxx  Deleted.
\medskip

\begin{itemize}
\item[] \textit{4, 17: ``interest is that of estimating''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 20--27: Even though I believe everything, these lines are a bit awkward and confusing.}
\end{itemize}

\noi
xxx   DAVID-- NEED YOUR HELP with this. 
I don't know how to reword it to make it less awkward.
\medskip

\begin{itemize}
\item[] \textit{4, 31: What are the desired statistical properties?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 33: ``Another difference is that''. By the way, what is ``difference'' referring to?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 36: ``due to the need to solve sampling problem"}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 42: ``Partial overlapping results in a smaller number of batches; hence, fewer optimization''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 45: The sentence ``Second, \ldots '' needs some clarification, since it states a conclusion that hasn't so far been justified.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 51: ``discuss overlapping''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 54 (and elsewhere): When you refer to ``variable amounts of overlap'', that is really nothing new. Certainly, any overlapping estimator will have end effects in which the overlap amounts differ from those in the ``middle'' region of the data.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{4, 57 (and elsewhere): ``classical case'' refers to nonoverlapping batch means, right?}
\end{itemize}

\noi
xxx  Yes. 
We reworded this sentence to make it clear.
\medskip

\begin{itemize}
\item[] \textit{5, 12: Does $\sigma^2$ refer to the marginal variance or the ``variance parameter'' (sum of the covariances at all lags)?}
\end{itemize}

\noi
xxx   CHECK -- DON'T REMEMBER
\medskip

\begin{itemize}
\item[] \textit{5, 14: ``realization of the univariate stochastic''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{5, 35 (and elsewhere): Careful! This isn't quite the sample variance! This is actually the sample variance multiplied by $m/n$.}
\end{itemize}

\noi
xxx  Thanks for catching this! We corrected this and others.
\medskip

\begin{itemize}
\item[] \textit{5, 43: You could have introduced the notation ``CI'' earlier.}
\end{itemize}

\noi
xxx  You are right. 
We now do introduce it earlier in the paper -- GIVE PAGE NO.
\medskip

\begin{itemize}
\item[] \textit{5: You can significantly reduce the discussion on OBM here and in \S 3.1. 
Just let the reader know the main results that you'll use.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{6, 13: ``corresponding overlapping batch means''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{6, 29: Note that you use ``Note that'' too often.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{6, 30: Explicitly say what the d.f.\ in (2) is.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{7, 46: Does $\gamma$ need to be an integer? 
You seem to be using it that way, so maybe state the requirement.}
\end{itemize}

\noi
xxx  CHECK THIS
\medskip

\begin{itemize}
\item[] \textit{8, 4 (and elsewhere): Define notations such as floor and ceiling functions.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{8, 11: In addition to the fact that I don't think ``variance reduction'' is quite the right term, the phrase ``variance reduction in this estimator'' is awkward.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{8, 53--57: The various OBM references should have been discussed earlier.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{10, 11 (and elsewhere): ``$E[f(x, \xi)^4]$'' instead of ``$Ef(x, \xi)^4$'' (never hurts to use some brackets to reduce ambiguity)}
\end{itemize}

\noi
xxx Changed. 
\medskip

\begin{itemize}
\item[] \textit{11, 33: It might be helpful to add a step before the first inequality in the proof.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{12, 52: ``$n_l VD_l$' has been studied''}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet? 
In any case, some of the verbiage in this paragraph is a bit repetitive.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 44: Is the expression for d.f. too big?}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 53: The reader might need another step besides C-S to get that inequality.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{15, 25: Do you discuss $t_{d_l,\alpha}$ at all in Theorem 3?}
\end{itemize}

\noi
xxx  CHECK. DON'T RECALL.
\medskip

\begin{itemize}
\item[] \textit{18: Your figures are very difficult to read, even with the pdf file.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{20, 47: ``4th edition''}
\end{itemize}

\noi
Done.
\medskip

\begin{itemize}
\item[] \textit{21, 23: ``\it Jackknife''}
\end{itemize}

\noi
Corrected. Thank you.

\end{document}

### 2014-05-21 AE_Reponse.tex
Added .tex files for the revision
1. omrp_lb_rev.tex (revised paper)
2. EinC_response.tex
3. AE response
4. Referee1 response
5. Referee2 response
and 6. the .bib file

\documentclass[11pt,notitlepage,onecolumn]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chicago}
\usepackage[singlespacing]{setspace}

\setcounter{MaxMatrixCols}{10}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}

\newcommand{\noi}{\noindent}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\baselineskip0.26in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak

\begin{center}
\textbf{\Large Response to the Associate Editor} 
\medskip

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
\medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the Associate Editor for the helpful comments and suggestions. 
We incorporated virtually all of the recommended changes and believe the paper is improved as a result. 
Below, we go through in detail the suggestions of the Associate Editor.
\medskip

\begin{itemize}
\item[]\textit{The paper is not clear in laying out a publishable contribution, and the motivation of the work is not clear.}
\end{itemize}

\noi
We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your comments and the referees.
\medskip

\begin{itemize}
\item[] \textit{The experiments show that the confidence interval average widths and observed coverage probabilities are the same with overlapping batch means; the only difference is in decreased variability of the confidence interval widths. 
That is, the variance of the variance estimator is reduced. 
This second-order benefit should be weighed against the increased computation cost (not to mention complexity and restricted applicability) of the overlapping batch means method.}
\end{itemize}

\noi  
xxx  Hmm We need to be careful addressing this comment but M1 of ref1 could help.
\medskip

\begin{itemize}
\item[] \textit{The issue of computational efficiency is not addressed  in the paper. 
In this setting the efficiency is often defined as the reciprocal of the computation time multiplied by the variance. 
If this quantity were compared (overlapping batch means versus batch means) in the numerical experiments, I am curious if there are any examples where the efficiency is improved.}
\end{itemize}

\noi 
xxxx Need to discuss
\medskip

\begin{itemize}
\item[] \textit{The authors could argue the publishability of the work by establishing improved efficiency for some examples, or providing some other argument for the usefulness of the results.  
A link between less variable confidence interval widths and improved stochastic optimization efficiency would be helpful.}
\end{itemize}

\noi
xxx  Is this really a new comment?  Looks like just continuation of the prev. comment. 
Also, seems like this is what M1 of ref1 is asking us to do. 
Once we have those results, we can argue more.
\medskip

\bigskip

\noi {\large Minor comments:}
\medskip

\begin{itemize}
\item[] \textit{2.38. The meaning of the set $X$ being independent of the random variable $\xi$ is not clear to me.}
\end{itemize}

\noi 
xxx

\begin{itemize}
\item[] \textit{4.24. \ldots data are generated \ldots}
\end{itemize}

\noi 
xxx

\begin{itemize}
\item[] \textit{19.11 \ldots such a scheme \ldots}
\end{itemize}

\noi
xxx

\end{document}

### 2014-05-21 EinC_Reponse.tex
Added .tex files for the revision
1. omrp_lb_rev.tex (revised paper)
2. EinC_response.tex
3. AE response
4. Referee1 response
5. Referee2 response
and 6. the .bib file

\documentclass[11pt,notitlepage,onecolumn]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chicago}
\usepackage[singlespacing]{setspace}

\setcounter{MaxMatrixCols}{10}

\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.0in}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\singlespacing

\baselineskip0.26in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak

\begin{center}
\textbf{\Large Response to the Editor-in-Chief} \medskip

{\large Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs} \medskip

{\footnotesize by D. Love and G. Bayraksan}
\end{center}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the Editor-in-Chief for the helpful comments and suggestions. 
We incorporated all the recommended changes and believe the paper is improved as a result. 
Below, we go through in detail the suggestions of the Editor-in-Chief.\medskip

\begin{itemize}
\item[] \textit{Your paper has a lot of overlap with the 2011 Winter Simulation paper  (which you also state in your paper). 
This refers to research content as well as text. 
If you revise your paper, the word for word copying should be reduced \ldots}
\end{itemize}

\noindent xxx \ \ 
 We incorporated virtually all the recommended changes suggested by you, the associate editor, and the referees. 
We very much appreciate everyone's time and constructive comments. 
We believe the paper is significantly improved and the wording of the paper, compared to the Winter Simulation Conference paper, is changed as a result of the revision.
We also went through the paper and tried to change the text to reduce word for word copying. 
  \medskip

\begin{itemize}
\item[]\textit{Even more important, in clarifying your contribution (as already asked by the reviewers), you should also shortly explain what new research results are presented in the  TOMACS paper in comparison to the WSC paper}
\end{itemize}

\noindent
xxx Do xxx  We added a paragraph (??) in the introduction, detailing what has been done over \ldots

\end{document}

### 2014-05-21 omrp_lb_rev.tex
Added .tex files for the revision
1. omrp_lb_rev.tex (revised paper)
2. EinC_response.tex
3. AE response
4. Referee1 response
5. Referee2 response
and 6. the .bib file

--- 2013-10-28 omrp.tex
@@
 \begin{proof} 
-	Note that for $\xh = \xs$, $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.  
-        With $\xh \neq \xs$, let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.
+%        With $\xh \neq \xs$, 
+			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.
         It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.  
@@
 This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
+Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  For $\xh = \xs$, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.
 
@@
 The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
-We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an estimated $\mu_{\xh} = 1.08$. 
+We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an {\it estimated} $\mu_{\xh} = 1.08$. 
 Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used below to estimate the coverage probability of the OMRP CIs for this test problem.
@@
 
-Summary of results from these experiments are depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
+A summary of results from these experiments is depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
 Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
@@
 We note that the variance reduction in DB1 can be less than the asymptotic amount. %for the small sample sizes used in these experiments. 
+Due its size, DB1 has not yet been solved to optimality, therefore, it may lack a unique optimal solution. 
 Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to achieve some variance reduction.
@@
 The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
-Coverage probability for 10D and DB1 (not shown) were very high, more than $0.99$.  
+Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
 The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.
@@
 
-% \section*{AUTHOR BIOGRAPHIES}
-
-% \noindent {\bf DAVID LOVE} is a graduate student in the Inderdisciplinary Program in Applied Mathematics at the University of Arizona.
-His research focuses on Monte Carlo based quality assessment in stochastic programming.
-His email address is \href{mailto://dlove@email.arizona.edu}{dlove@email.arizona.edu}.\\
-
-% \noindent {\bf G\"{U}Z\.{I}N BAYRAKSAN} is an Assistant Professor in the Department of Systems and Industrial Engineering at the University of Arizona.
-Her research interests include stochastic optimization, particularly Monte Carlo sampling-based methods for stochastic programming, with applications to water resources management.
-Her email address is \href{mailto://guzinb@sie.arizona.edu}{guzinb@sie.arizona.edu} and her web page is \href{http://www.sie.arizona.edu/faculty/guzinb}{www.sie.arizona.edu/faculty/guzinb}.\\
-
 \end{document}

### 2014-06-06 EinC_Reponse.tex
EditorinChief Response: minor changes

@@
 
-\noindent xxx \ \ 
+\noindent  
 We incorporated virtually all the recommended changes suggested by you, the associate editor, and the referees. 
 We very much appreciate everyone's time and constructive comments. 
-We believe the paper is significantly improved and the wording of the paper, compared to the Winter Simulation Conference paper, is changed as a result of the revision.
+We believe the paper is significantly improved as a result. 
+The wording of the paper, compared to the Winter Simulation Conference Proceedings version, is also changed as a result of the revision.
 We also went through the paper and tried to change the text to reduce word for word copying. 

### 2014-06-06 Referee2_Response.tex
Referee 2 specific comments
only some of them regarding 1) the abstract and 2) the first paragraph

@@
 \noi
-xxx  I actually prefer 'extend' but I am not going to argue over such small stuff. 
-So, I will change this sentence and might look for others. 
+Changed.  xxx Also go through to see others! 
 \medskip
@@
 \noi
-xxx  Changed
+Changed. xxx Also go through to see others!
 \medskip
@@
 \noi
-xxx  
+We slightly reworded this sentence and provided references.   
 \medskip
@@
 \noi
-xxxx  Thank you for this suggestion of rewrite. 
-We rewrote this paragraph based on your corrections and paying attention to referencing formats. 
+Thank you for this suggestion of rewrite and for your careful review of the paper. 
+We rewrote this paragraph based on your corrections.
+We also went through the paper and made changes to the language, paying specific attention to active and passive referencing formats. 
 \medskip
@@
 \noi
-xxx  Changed.
+Changed.
 \medskip
@@
 \noi
-xxx  
+Done.
 \medskip
@@
 \noi
-xxx  
+Both done.  
 \medskip

### 2014-06-06 omrp_lb_rev.tex
Referee 2 specific comments
only some of them regarding 1) the abstract and 2) the first paragraph

@@
 \noindent Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate variance estimators with asymptotically lower variance.
-In this paper, we extend the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
-We show conditions under which the resulting optimality gap estimators are strongly consistent and have the same asymptotically lower variance as the classical results.
-Computational experiments for several test problems are presented, examining the small-sample behavior of the overlapping batches method in this context.\medskip
+In this paper, we apply the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
+We give conditions under which the resulting optimality gap estimators are strongly consistent and have the same asymptotically lower variance as the classical OBM estimators \citep{Meketon1984,Welch1987}.
+Computational experiments for several test problems are presented, examining the small-sample behavior and the computational efficiency of the overlapping batches method in this context.\medskip
 
@@
 
-Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators with lower variances. 
-While OBM is often used for variance estimators of means, it can also be used for variance estimators of non-means \citep{SAH90} and more recently, it has been extended to estimators based on standardized time series (e.g., area, Cram\'{e}r-von Mises) \citep{Alexopoulos01012007,Alexopoulos2007} and their folded versions \citep{Meterelliyoz_etal_12}.
-To the best of our knowledge, OBM has never been studied in a stochastic optimization context before. 
+The overlapping batch means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts.
+In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
+\cite{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
+More recently, overlapping estimators based on standardized time series (as opposed to nonoverlapping batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \citep{Meterelliyoz_etal_12}.
+To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
 In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.
-A natural setting where batch means are used in stochastic optimization (esp. in stochastic programming) is for assessing solution quality. 
-Assessing solution quality in stochastic programming typically involves generating point and interval estimators of the optimality gap of a given candidate solution using Monte Carlo simulation. 
-Because the optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonovelapping batches of data to generate a number of optimality gap estimators. 
+
+A natural setting where batch means are used in stochastic optimization (especially in stochastic programming) is for assessing solution quality. 
+This typically involves generating point and interval estimators of the optimality gap of a given candidate solution using Monte Carlo simulation. 
+Because optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonovelapping batches of data to generate a number of optimality gap estimators. 
 These individual estimators are then used to form point and interval estimators applying the classical nonoverlapping batch means method.
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
-In this paper, we formulate an ovelapping batches version of MRP, allowing for partial overlap, and provide conditions under which the same variance reduction results can be achieved by overlapping like in the classical setting.
+In this paper, we formulate an ovelapping batches version of MRP, allowing for partial overlap, and provide conditions under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
 We also show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 

### 2014-06-08 omrp_lb_rev.tex
More Referee 2 and AE comments
minor comments

@@
 \newcommand{\X}{X}
-\newcommand{\x}{x}
+\newcommand{\x}{\mathbf{x}}
 \newcommand{\xh}{{\hat{\x}}}
 \newcommand{\xs}{\x^*}
-\newcommand{\xit}{\xi}
+\newcommand{\xit}{\boldsymbol{\xi}}
 \newcommand{\xiti}{\xit^i}
@@
 
-The overlapping batch means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts.
+The Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts.
 In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
 \cite{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
-More recently, overlapping estimators based on standardized time series (as opposed to nonoverlapping batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \citep{Meterelliyoz_etal_12}.
+More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \citep{Meterelliyoz_etal_12}.
 To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
@@
 We also show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
-We present computational results to examine small-sample behavior. 
-Our experiments indicate that variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
+We also present computational results to examine small-sample behavior. 
+Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.
 
@@
 \end{align}
-where $\x$ is a vector of decision variables, $\xit$ is a vector of random variables, and $X$ is the feasible set, which is assumed to be independent of $\xit$.
+where $\x$ is a vector of decision variables, $\xit$ is a vector of random variables, and $X$ is the feasible set, which consists of only deterministic constraints. 
+There are no stochastic constraints such as probabilistic or expected-value constraints. 
 Further, it is assumed that the distribution of $\xit$ is known and that we can sample from it.
-Even though we will impose a more restrictive moment condition later, we assume that $\e{f(\x,\xit)}$ is well defined and finite for all $\x \in X$ and (\ref{eq:sto_prog}) has a finite optimal solution achieved on $X$.
+Even though we will impose a more-restrictive moment condition later, we assume that $\e{f(\x,\xit)}$ is well defined and finite for all $\x \in X$ and (\ref{eq:sto_prog}) has a finite optimal solution achieved on $X$.
 
 Unless $f$ has a simple structure or the number of realizations of $\xi$ is small, (\ref{eq:sto_prog}) typically cannot be solved exactly. 
-An approximation of (\ref{eq:sto_prog}) can be generated by sampling from the distribution of $\xi$.
+An approximation of (\ref{eq:sto_prog}) can be generated by sampling from the distribution of $\xit$.
 While other sampling schemes are possible, let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (i.i.d.) sample from the distribution of $\xit$.
-A sampling approximation of (\ref{eq:sto_prog}), often called the Sample Average Approximation (SAA), is given by
+A sampling approximation of (\ref{eq:sto_prog}), often called the sample average approximation, is given by
 \begin{align} \tag{SP$_m$} \label{eq:sto_prog_m}
@@
 We define the quality of $\xh$ by its optimality gap, $\e{f(\xh,\xit)} - \zs$. 
-The lower the optimality gap, the higher the quality of the solution and a zero optimality gap implies that the solution is optimal. 
+The lower the optimality gap, the higher the quality of the solution; and a zero optimality gap implies that the solution is optimal. 
 Note that the candidate solution $\xh \in X$ may have been found in any way. 
@@
 Second, we do not know $\zs$. 
-In many fields of optimization, the second problem is alleviated by obtaining lower bounds on $\zs$ through relaxations such as integrality, Lagrangian or semidefinite relations.
+In many fields of optimization, the second problem is alleviated by obtaining lower bounds on $\zs$ through relaxations such as integrality, Lagrangian, or semidefinite relations.
 As a result, it is common to evaluate an upper bound on the optimality gap. 
@@
 A straightforward estimate of $\e{f(\xh,\xit)}$ is the sample mean, $\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti)$. 
-Instead of $\e{\zs_m}$, simply $\zs_m$ can be used.  
-The resulting point estimator of optimality gap is then 
+Instead of $\e{\zs_m}$, we can simply use $\zs_m$.  
+The resulting point estimator of the optimality gap is then 
 $$
@@
 As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$) and averages them to obtain a point estimator.
-To form confidence intervals, the sample variance of these estimators is calculated (we further review MRP in \S \ref{ssec:mrp}.)  
+The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
 An advantage of MRP is its applicability to a wide range of problems.  

### 2014-06-08 Referee2_Response.tex
More Referee 2 and AE comments
minor comments
Minor changes by Referee2 and AE

@@
 \noi
-xxx  
+Done. 
 \medskip
@@
 \noi
-xxx  
+Done.  
 \medskip
@@
 \noi
-xxx  Thank you; we went through the paper and hyphenated all the compound adjectives.
+xxx  Done. But I am not sure if it is correct this way.  
+Thank you; we went through the paper and hyphenated all the compound adjectives.
 \medskip
@@
 \noi
-xxx  I don't think I agree with this. 
-These need to be in parentheses! 
+We put a comma after `see'; however, we still kept the same referencing style `[Bertocchi et al., 2000; \ldots]' as this sentence refers to the papers and not directly to the authors. 
+We also went through to make sure all `see, e.g.,' have the appropriate commas.
 \medskip
@@
 \noi
-xxx  Deleted.
+Deleted.
 \medskip
@@
 \noi
-xxx  
+Thanks for pointing out the ambiguity here. 
+We reworded this sentence and broke it into two sentences to make it clear. 
 \medskip
@@
 \noi
-xxx  
+Done.
+We also changed the sentence to make it clear what the ``difference'' is referring to. 
 \medskip
@@
 \noi
-xxx  
+You are right.
+We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
+We reworded this sentence to reflect this. 
+xxxx  We also \ldots (I think we should write more about our conclusions and our recommendation based on our new findings here) xxxx
 \medskip

### 2014-06-08 omrp_lb_rev.tex
Minor changes by Referee2 and AE

@@
 With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
-It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
+It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
 Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
@@
 Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
-Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
+%Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
 We note several differences in this setting compared to the classical setting.  
-In simulation output analysis, the point of interest is estimating the variance of the sample mean of a covariance stationary process.  
+In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
 We are interested in estimating the variance of an optimality gap estimator.  
@@
 We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
-The nonoptimized counterparts have the desired statistical properties and we establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
-Another difference is, once the data is generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.  
-In this setting, due to the solution of a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
+The nonoptimized counterparts are (regular) overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions.
+We establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
+Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.
+In this setting, due to the need to solve a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
 This can be alleviated in two ways. 
 First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
-Partial overlap results in a fewer number of batches, hence fewer number of optimization problems need to be solved.
+Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
 In this paper, we consider variable amounts of overlap and examine this both theoretically and empirically. 
@@
 In the next section, we review relevant background information.  
-We first discuss the overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
-In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with variable amounts of overlap.  
+We first discuss overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
+In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
 In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.

### 2014-06-09 Referee2_Response.tex
More Referee 2 suggestions
Changes in the response to Referee 2 as well as the paper itself

@@
 \noi
-xxx  Yes. 
+No; by `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to the assessment of solution quality in stochastic programming). 
 We reworded this sentence to make it clear. 
+Please note that based on your earlier comments, we also reworded this sentence to avoid using the term `variance reduction'. 
 \medskip
@@
 \noi
-xxx  Thanks for catching this! We corrected this and others.
+Thanks for catching this. 
+We corrected this sentence. 
+Please note that we broke this sentence into two to avoid long sentences and to improve exposition. 
+We also checked for other occurrences of the term `sample variance' throughout the paper and corrected these terms as well. 
 \medskip
@@
 \noi
-xxx  You are right. 
-We now do introduce it earlier in the paper -- GIVE PAGE NO.
+You are right. 
+We now introduce this abbreviation the first time we use the term `confidence interval' in the introduction. 
+From this point on, we use the abbreviated form `CI' throughout the paper, except for Section 4.5 title (Asymptotic Validity of the Confidence Intervals). 
 \medskip

### 2014-06-09 omrp_lb_rev.tex
More Referee 2 suggestions
Changes in the response to Referee 2 as well as the paper itself

@@
 As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$) and averages them to obtain a point estimator.
-The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
+The sample variance of these estimators is used to form confidence intervals (CIs) for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
 An advantage of MRP is its applicability to a wide range of problems.  
@@
 Our aim is to apply the idea of overlapping batches to MRP.  
-Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
+Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
 %Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
@@
 In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
-In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP confidence intervals, and the variance reduction results as in the classical case.
+In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP CIs, and that the OMRP variance estimators have lower variances than their nonoverlapping counterparts---the MRP estimators.
 In \S \ref{sec:comp}, we test the performance of OMRP on four problems and end in \S \ref{sec:concl} with a summary and conclusions.
@@
 Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
-The task is to estimate $\mu$ given some realization of the stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
-Typically, this involves forming a confidence interval of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.
+The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
+Typically, this involves forming a CI of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.
 The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
@@
 and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  
-The sample variance of the batch means is calculated as
+The variance estimator of the batch means, which is $n/m$ times the sample variance, is calculated as
 \begin{equation} \label{eq:var}
-	\varhat(\ybb) = \frac{m}{n}\frac{1}{k-1} \sum_{j=1}^k \left( \yb_j - \ybb \right)^2,
+	\varhat(\ybb) = \frac{m}{n}\frac{1}{k-1} \sum_{j=1}^k \left( \yb_j - \ybb \right)^2.
 \end{equation}
-and the $(1-\alpha)$-level approximate confidence interval (CI) is formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.
+The $(1-\alpha)$-level approximate CI is then formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.
 Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$.
@@
 \end{equation}
-Note that the corresponding batch means are no longer independent. 
+Note that the corresponding overlapping batch means are no longer independent. 
 However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
@@
 Notice that the minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
-Thus, we can expect that the true probability of the optimality gap residing within the confidence interval to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a confidence interval.
+Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
+This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI.
 See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.
@@
 
-The overlapping variance estimator for stochastic programs displays the same desirable properties as in simulation, but we must still check that it results in a valid confidence interval.  
-Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided confidence interval generated by OMRP. 
+The overlapping variance estimator for stochastic programs displays the same desirable properties as in simulation, but we must still check that it results in a valid CI.  
+Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided CI generated by OMRP. 
 The degrees of freedom $d_l$ is the inverse of (\ref{eq:var_reduct_formula}) using $\frac{\gamma_l}{m_l}$ instead of $\gammab$.
@@
 
-The asymptotic validity of the OMRP confidence interval requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
+The asymptotic validity of the OMRP CI requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
 This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
@@
 Then, at each value of $m$, we formed the OMRP estimators with varying amounts of overlap. 
-We also set $\alpha=0.10$, forming 90\% confidence intervals on the optimality gap using the ORMP estimators. 
+We also set $\alpha=0.10$, forming 90\% CIs on the optimality gap using the ORMP estimators. 
 Results for NVD were compiled over 10,000 independent runs, while the CEP1 and 10D results were taken over 1,000 independent runs, and DB1 results were generated over 500 independent runs.
@@
 		(b) estimates of $\e{nVG}$, and 
-		(c) coverage probability of the confidence intervals for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches).
+		(c) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches).
 	}
@@
 
-Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of confidence intervals generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
+Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of CIs generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
 The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
@@
 We have extended previous work from simulation output analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo simulation-based estimators of optimality gaps in stochastic programs \citep{Mak1999}.
-We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid confidence intervals can be formed.
+We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid CIs can be formed.
 Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.

### 2014-06-10 Referee2_Response.tex
More Referee 2 suggestions

@@
 \noi
-xxx  CHECK THIS
+Yes; we now explicitly state this in a sentence after we introduce $\gamma$. 
 \medskip
@@
 \noi
-xxx  
+Done. 
+We introduced the floor function before its first use and similarly, we introduced the ceiling function before its first use. 
 \medskip
@@
 \noi
-xxx Changed. 
+Changed.
+In fact, we now use brackets for all the expectations in the paper to improve clarity.
+Thank you for this suggestion. 
 \medskip
@@
 \noi
-xxx  
+Instead of adding another step before the first inequality in the proof of Lemma 1, we added explanations at the beginning of the proof to make this inequality clear.   
 \medskip
@@
 \begin{itemize}
-\item[] \textit{12, 52: ``$n_l VD_l$' has been studied''}
+\item[] \textit{12, 52: ``$n_l VD_l$ has been studied''}
 \end{itemize}
@@
 \noi
-xxx  
+We now denote it as `dt' to represent the whole denominator term (d.t.). 
 \medskip
@@
 \noi
-xxx  
+This is a direct application of the Cauchy-Schwartz inequality $\left(\sum_{j=1}^{n}x_j y_j\right)^2 \leq \sum_{j=1}^{n}x_j^2 \sum_{j=1}^{n}y_j^2$, where the $y_j$ are all set to $1$. 
+We added a brief explanation after this inequality to make it clear. 
 \medskip
@@
 \noi
-xxx  CHECK. DON'T RECALL.
+No, we did not.   
+We added explanations in the proof Theorem 3, discussing how $t_{d_l,\alpha}$ factors in the proof. 
 \medskip

### 2014-06-10 omrp_lb_rev.tex
More Referee 2 suggestions

@@
 \newcommand{\p}[1]{\mathbb{P} \left\{ #1 \right\}}
-\newcommand{\e}[1]{\mathbb{E} %\left[ 
-#1 %\right]
+\newcommand{\e}[1]{\mathbb{E} \left[ #1 \right]
 }
@@
 For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
+In general, $\gamma$ can take any integer value between and including $[1,m]$. 
+Let $\lfloor \cdot \rfloor$ be the greatest integer that is less than or equal to its argument. 
 The sample mean of each batch estimator is calculated similarly, 
@@
 When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  
+Let $\lceil \cdot \rceil$ be the smallest integer that is greater than or equal to its argument. 
 In general, from the spectral analysis given in \citep{Welch1987}, the variance is reduced to
@@
 
-\begin{proof} Let $E^C$ denote the complement of event $E$. Note that
+\begin{proof} When the sampling problems used in the calculation of $\gbb$ all have optimal solutions that solve (SP), i.e., when $\xs_{j} = \xs$, for all $j=1,2,\ldots, \nbl$, then $\gbb_l = \dbb_l$.
+Therefore, complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
+Let $E^C$ denote the complement of event $E$. 
+Using this upper bound and continuing on, we obtain
 	\begin{align}
@@
 As a result, if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, so is $n_l VG_l$.  
-Strong consistency of the variance estimator $n_l VD_l$ have been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
+Strong consistency of the variance estimator $n_l VD_l$ has been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
 Under the additional moment assumption
@@
 	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
-        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $df = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
+        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $dt = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
 Note that
 	\begin{align}
-		\e{(nVG - nVD)^2} & = \left( \frac{n}{df} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
-		& \leq \left( \frac{n}{df} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
+		\e{(nVG - nVD)^2} & = \left( \frac{n}{dt} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
+		& \leq \left( \frac{n}{dt} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
 	\end{align}
-	by the Cauchy-Schwartz inequality.  
-        By examining the batch structure in Figure \ref{fig:overlap_nonint} and the definition of $\gbb$ in (\ref{eq:gbb}) one can see that the terms of the expectation are not identically distributed.
+	by the Cauchy-Schwartz inequality, where the second vector in the Cauchy-Schwartz inequality is taken as a vector of ones.  
+        By examining the batch structure in Figure \ref{fig:overlap_nonint} and the definition of $\gbb$ in (\ref{eq:gbb}), one can see that the terms of the expectation in (\ref{eq:vvar_conv_pf_1}) are not identically distributed.
         We will separate these into identically distributed ``center'' batches and ``fringe'' batches.  
@@
 	\begin{align*}
-		& \left( \frac{n}{df} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
-		 =  & \left( \frac{n}{df} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
+		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
+		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
 		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
@@
 		} \\
-		 = & \left( \frac{n}{df} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
-		 = & \left( \frac{n}{df} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
-		+ \left( \frac{n}{df} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
+		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
+		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
+		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
 	\end{align*}	
-	We have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{df}\right)^2n_b^2 < (2m)^2$.  
+	We have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{dt}\right)^2n_b^2 < (2m)^2$.  
         So each expectation can be bounded by
@@
 			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.
+			Also let $z_{\alpha}$ denote the $1-\alpha$ quantile of the standard normal distribution. 
         It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.
+			If $\frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, because $t_{d_l,\alpha} \rightarrow z_{\alpha}$ as $l \rightarrow \infty$, we obtain the desired result by rearranging the terms in $\p{\mu_\xh \leq I^G_l}$ and taking the limit as $l \rightarrow \infty$.
         First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
@@
 This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
-Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  For $\xh = \xs$, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.
+Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  
+For $\xh = \xs$, $\mu_\xh = 0$, and therefore, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.
 

### 2014-06-12 Referee1_Response.tex
Enlarged graphs, changed comp results and relevant referee responses

@@
 
-\noindent xxx We enlarged the figures. 
+\noindent 
+We split these two figures into three and enlarged each graph. 
+All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger than the old graphs. 
 \medskip
@@
 We explain this at the end of Section 5.1 (Test Problems). 
-We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for the test problem DB1. 
+We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for DB1. 
 \medskip
@@
 
-\noindent xxx We expanded this paragraph based on our findings. 
+\noindent 
+Thank you for this suggestion. 
+xxx We expanded this paragraph based on our findings. 
 xxx Write more---hopefully, we will find good stuff!!!

### 2014-06-12 omrp_lb_rev.tex
Enlarged graphs, changed comp results and relevant referee responses

@@
 \begin{proof} When the sampling problems used in the calculation of $\gbb$ all have optimal solutions that solve (SP), i.e., when $\xs_{j} = \xs$, for all $j=1,2,\ldots, \nbl$, then $\gbb_l = \dbb_l$.
-Therefore, complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
+Therefore, probability of the complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
 Let $E^C$ denote the complement of event $E$. 
@@
 
-A summary of results from these experiments is depicted in Figures~\ref{fig:nv} and \ref{fig:varvar}.
-Figures~\ref{fig:nv}(a) and \ref{fig:varvar} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
+A summary of results from these experiments is depicted in Figures~\ref{fig:varvar1}--\ref{fig:nv}.
+Figures~\ref{fig:varvar1} and \ref{fig:varvar2} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
 The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
@@
 	\centering
-	\subfloat[][Variance Reduction]{
+	\subfloat[][NVD]{
 	   \label{fig:nv_varvar}
-	   \includegraphics[width=.32\textwidth]{images/nv_varvar_discrete}}
+	   \includegraphics[width=.5\textwidth]{images/nv_varvar_discrete}}
+	\subfloat[][CEP1]{
+	   \label{fig:cep1_varvar}
+	   \includegraphics[width=.5\textwidth]{images/cep1_varvar}}
+	\caption{
+		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problem
+		(a) NVD, and
+		(b) CEP1
+	}
+\label{fig:varvar1}
+\end{figure}
+
+\begin{figure}[htb!]
+	\centering
+	\subfloat[][10D]{
+	   \label{fig:10d_varvar}
+	   \includegraphics[width=.5\textwidth]{images/10D_varvar}}
+	\subfloat[][DB1]{
+	   \label{fig:db1_varvar}
+	   \includegraphics[width=.5\textwidth]{images/db1_varvar}}
+		\caption{
+		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problem
+		(a) 10D, and
+		(b) DB1
+		}
+\label{fig:varvar2}
+\end{figure}
+
+\begin{figure}[htb!]
+	\centering
 	\subfloat[][Expected Variance]{
 	   \label{fig:nv_avgvar}
-	   \includegraphics[width=.32\textwidth]{images/nv_avgvar_discrete}}
+	   \includegraphics[width=.5\textwidth]{images/nv_avgvar_discrete}}
 	\subfloat[][Coverage Probability]{
 	   \label{fig:nv_cover}
-	   \includegraphics[width=.32\textwidth]{images/nv_cover_discrete}}
+	   \includegraphics[width=.5\textwidth]{images/nv_cover_discrete}}
 	\caption{ 
-		Summary of results for NVD. 
-		(a) Reduction in variance of $nVG$,
-		(b) estimates of $\e{nVG}$, and 
-		(c) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches).
+		Estimates of
+		(a) $\e{nVG}$, and 
+		(c) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches)
+		 for NVD
 	}
@@
 
-\begin{figure}[htb!]
-	\centering
-	\subfloat[][CEP1]{
-	   \label{fig:cep1_varvar}
-	   \includegraphics[width=.32\textwidth]{images/cep1_varvar}}
-	\subfloat[][10D]{
-	   \label{fig:10d_varvar}
-	   \includegraphics[width=.32\textwidth]{images/10D_varvar}}
-	\subfloat[][DB1]{
-	   \label{fig:db1_varvar}
-	   \includegraphics[width=.32\textwidth]{images/db1_varvar}}
-		\caption{
-		Variance Reduction for
-		(a) CEP1,
-		(b) 10D, and
-		(c) DB1
-		for various values of $\gamma / m$.
-		}
-\label{fig:varvar}
-\end{figure}
-
-Figure~\ref{fig:nv}(b) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and amount of overlap. 
+Figure~\ref{fig:nv}(a) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and amount of overlap. 
 We can see that the expectation of the variance estimator is not changed with increasing overlap. 
@@
 
-Finally, Figure~\ref{fig:nv}(c) shows the coverage probability of CIs generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
+Finally, Figure~\ref{fig:nv}(b) shows the coverage probability of CIs generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
 The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
@@
 The bias from solving (\ref{eq:sto_prog_m}) for these problems seems to be much more significant than the variance.
+
+\subsection{Computational Efficiency}
+\label{ssec:compeff}
+
+xxx Add new graphs here \bigskip
+
+xxx Write new text, etc. \bigskip
+
+xxx Revise the recommendations on gammabar \bigskip
 
@@
 access to their regularized decomposition code, which was used to solve CEP1 and DB1. 
-%This research is supported in part by the National Science Foundation under Grants DMS-0602173 and EFRI-0835930.  
+The authors are also grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the paper. 
+%This research has been supported in part by the National Science Foundation under Grant(s)  EFRI-0835930 and CMMI-1345626 ??? 
 An earlier version of this paper appeared in \citep{love2011overlapping}.

### 2014-06-13 Referee1_Response.tex
first pass through the referee minor suggestions
more to be done...

@@
 
-\noindent xxx Done. 
+\noindent 
+Done. 
 \medskip
@@
 
-\noindent xxx Corrected. 
+\noindent 
+Corrected. Thanks for catching these typos.
 \medskip
@@
 
-\noindent xxx Corrected. 
+\noindent 
+Yes. Corrected. 
 \medskip
@@
 
-\noindent xxx Changed. 
+\noindent 
+Done. 
 \medskip
@@
 
-\noindent xxx Changed. 
+\noindent 
+Done. 
+%Please note that this sentence has been changed slightly based on the comments of the other referee. 
 \medskip
@@
 
-\noindent xxx Changed. xxx MUST CHECK WITH OTHER REFEREE'S COMMENTS.
+\noindent 
+We reworded this sentence to read as ``Partial overlapping results in a smaller number of batches; hence, fewer optimization \ldots '' based on the comments of the other referee.
 \medskip
@@
 
-\noindent xxx Changed. 
+\noindent 
+Done. 
+% This sentence might be deleted or changed to the denominator term, etc. CHECK! 
 \medskip
@@
 
-\noindent xxx Changed the wording here. 
-Thank you. 
+\noindent  
+Changed the wording here. Thank you. 
 \medskip
@@
 
-\noindent xxx Added. 
+\noindent 
+Added. Thanks for catching this.
 \medskip
@@
 
-\noindent Thank you for catching this.  
+\noindent Thank you for pointing this out.  
 We removed this statement from the proof of Theorem 3 and added it as a remark in the paragraph after the theorem.
@@
 We split these two figures into three and enlarged each graph. 
-All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger than the old graphs. 
+All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger compared to those in the previous version of the paper. 
 \medskip
@@
 xxx We expanded this paragraph based on our findings. 
-xxx Write more---hopefully, we will find good stuff!!!
-\medskip
+xxx Please note that this paragraph now appears in a new section (\S 5.4 Computational Efficiency).
 

### 2014-06-13 omrp_lb_rev.tex
first pass through the referee minor suggestions
more to be done...

@@
 This typically involves generating point and interval estimators of the optimality gap of a given candidate solution using Monte Carlo simulation. 
-Because optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonovelapping batches of data to generate a number of optimality gap estimators. 
+Because optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonoverlapping batches of data to generate a number of optimality gap estimators. 
 These individual estimators are then used to form point and interval estimators applying the classical nonoverlapping batch means method.
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
-In this paper, we formulate an ovelapping batches version of MRP, allowing for partial overlap, and provide conditions under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
+In this paper, we formulate an overlapping batches version of MRP, allowing for partial overlap, and provide conditions under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
 We also show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
@@
 Second, we do not know $\zs$. 
-In many fields of optimization, the second problem is alleviated by obtaining lower bounds on $\zs$ through relaxations such as integrality, Lagrangian, or semidefinite relations.
+In many fields of optimization, the second problem is alleviated by obtaining lower bounds on $\zs$ through relaxations such as integrality, Lagrangian, or semidefinite relaxations.
 As a result, it is common to evaluate an upper bound on the optimality gap. 
@@
 We establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
-Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, it can be reused without much additional computational effort to obtain the OBM variance estimator.
+Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.
 In this setting, due to the need to solve a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
@@
 Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
-The degrees of freedom in (\ref{eq:overlap_variance_def}) makes $\vart{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
+The degrees of freedom in (\ref{eq:overlap_variance_def}) make $\vart{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
 The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.
@@
 As before, after $k$ estimates are obtained, the overall mean of these estimates $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
-The sample variance is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in a one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$ that has a level of significance, which is approximately $\alpha$.
+The sample variance is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in an approximate $(1-\alpha)$-level one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$.
 
@@
 \subsection{Definition of Estimators for OMRP}
+
 In order to apply overlapping batches to MRP, we need to keep track of solutions to sampling problems (SP$_m$) for each batch of size $m$.  
@@
 The classical variance-reduction results for overlapping batches show that $\var{n_l VG_l}$ is reduced by overlapping, thus requiring at least finite fourth moments. 
-Finally, our proof relies on an exponential rate of convergence of sampled solution to the true solution of the problem.  
+Finally, our proof relies on an exponential rate of convergence of the sampled solution to the true solution of the problem.  
 Assumption A3 can be satisfied for different classes of problems with unique optimal solutions.  
@@
 
-	The fringe batches will come in identically distributed pairs.  
-        The first and last batch would be identically distributed, as would the second and second-to-last, etc.  
+	The fringe batches come in identically distributed pairs.  
+        The first and last batch are identically distributed, as are the second and second-to-last, etc.  
         We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the exact same batch structure.  
@@
 	\begin{align*}
-		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
+		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
 		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
@@
 The asymptotic validity of the OMRP CI requires $n_l VD_l$ to converge in probability to $\sigma^{2}_{\xh}$. 
-This can be achieved either by almost sure or mean-square convergence, which gives a larger range of $r$ in the batching structure.
+This can be achieved either by almost sure or mean-square convergence, where the latter gives a larger range of $r$ in the batching structure.
 Also, a hypothesis of Theorem~\ref{thm:conf_int} is that $\xh \neq \xs$.  
-For $\xh = \xs$, $\mu_\xh = 0$, and therefore, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.
+For $\xh = \xs$, $\mu_\xh = 0$; therefore, in this case, we have $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1$.
 
@@
 These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
-We note that the variance reduction in DB1 can be less than the asymptotic amount. %for the small sample sizes used in these experiments. 
-Due its size, DB1 has not yet been solved to optimality, therefore, it may lack a unique optimal solution. 
+We note that the variance reduction in DB1 can be less than the asymptotic amount %for the small sample sizes used in these experiments. 
+because due its size, DB1 has not yet been solved to optimality; therefore, it may lack a unique optimal solution. 
+%, violating assumption A3. (?)
 Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to achieve some variance reduction.
@@
 Because variance reduction drops quickly as $\gammab$ drops below $1$, we recommend using an intermediate value of $\gammab$, such as $1/3$ or $1/4$, to gain the majority of the variance reduction, while reducing the number of optimization problems to be solved.
-Warm-starting the algorithm to solve the sampling problems, when such as scheme is available, can significantly reduce the computation times.
+Warm-starting the algorithm to solve the sampling problems, when such a scheme is available, can significantly reduce the computation times.
 

### 2014-06-13 Referee2_Response.tex
Enlarged graphs, changed comp results and relevant referee responses
A finer pass through Ref2 comments - PART I

@@
 \noi
-Changed.  xxx Also go through to see others! 
+Changed.  
+We also went through the paper to correct other occurrences. 
+In particular, this was also used in Section 6 (Conclusions). 
+We changed the first sentence of Section 6 (Conclusions) to use the word `apply' instead of `extend'.
+
 \medskip
@@
 \noi
-Changed. xxx Also go through to see others!
+Changed. 
+We also went through the paper and corrected other occurrences. 
+The current version of the paper either has `give conditions' or `provide conditions'. 
 \medskip
@@
 \noi
-We slightly reworded this sentence and provided references.   
+We reworded this sentence to improve clarity and provided references.   
 \medskip
@@
 \noi
-Thank you for this suggestion of rewrite and for your careful review of the paper. 
+Thank you for this suggestion of rewrite and for your careful and detailed review of the paper. 
 We rewrote this paragraph based on your corrections.
@@
 Please note that based on your earlier comments, we also reworded this sentence to avoid using the term `variance reduction'. 
+We also went through the whole paper and removed several uses of the word `classical' to reduce ambiguity (as these were referring to nonoverlapping batches). 
 \medskip
@@
 \noi
-xxx  
+You are right. 
+We split these two figures into three and enlarged each graph. 
+All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger than the old graphs.  
 \medskip

### 2014-06-13 omrp_lb_rev.tex
A finer pass through Ref2 comments - PART I

@@
 Because optimality gap estimators can be difficult to analyze statistically, a common approach is to use nonoverlapping batches of data to generate a number of optimality gap estimators. 
-These individual estimators are then used to form point and interval estimators applying the classical nonoverlapping batch means method.
+These individual estimators are then used to form point and interval estimators applying the nonoverlapping batch means method.
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
@@
 %Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
-We note several differences in this setting compared to the classical setting.  
+We note several differences in this setting compared to the classical simulation setting.  
 In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
@@
 In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
-For instance, $\gamma = m$ corresponds to the classical case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
+For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
 In general, $\gamma$ can take any integer value between and including $[1,m]$. 
@@
 	\item[A1] Samples of the random variable $\xit$ are i.i.d.
-	\item[A2] $\sup_{\x \in X} \e{f(\x,\xi)^{4}} < \infty$.
+	\item[A2] $\sup_{\x \in X} \e{f(\x,\xit)^{4}} < \infty$.
 	\item[A3] (\ref{eq:sto_prog}) has a unique optimal solution $\xs$ and $\p{\xs_m \neq \xs} \rightarrow 0$ exponentially fast as $m \rightarrow \infty$.  
@@
 First, we restrict our attention to i.i.d.\ sampling by A1.
-The classical variance-reduction results for overlapping batches show that $\var{n_l VG_l}$ is reduced by overlapping, thus requiring at least finite fourth moments. 
-Finally, our proof relies on an exponential rate of convergence of the sampled solution to the true solution of the problem.  
+The results for overlapping batches from the simulation output analysis indicate that $\var{n_l VG_l}$ may be reduced by overlapping, thus requiring at least finite fourth moments. 
+We will formally show this result in Section~\ref{ssec:var_reduct}.
+Our proof relies on an exponential rate of convergence of the sampled solution to the true solution of the problem, specified by A3.  
 Assumption A3 can be satisfied for different classes of problems with unique optimal solutions.  
 \citet{shapiro2000rate} establish exponential rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite.
-\citet{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $x \in X \backslash \{\xs\}$ is finite valued on $\R$.
+\citet{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $\x \in X \backslash \{\xs\}$ is finite valued on $\R$.
 This class of problems includes stochastic integer programs with recourse.
@@
 
-Theorem \ref{thm:varvar_conv} shows conditions under which the same asymptotic variance reduction results are achieved for the OMRP optimality gap variance estimator. 
+Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotic variance reduction results are achieved for the OMRP optimality gap variance estimator. 
 We will empirically examine the variance reduction for small sample sizes in \S \ref{sec:comp}. 
@@
 Finally, Figure~\ref{fig:nv}(b) shows the coverage probability of CIs generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
-The results of the classical overlapping batches estimators show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
+The results of the overlapping batches estimators from the simulation literature show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
 We observed the same for CEP1, 10D, and DB1.  
-The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown) remains fairly constant around the desired value of $90\%$.
+The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown for brevity) remains fairly constant around the desired value of $90\%$.
 Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
@@
 
-We have extended previous work from simulation output analysis to assessing solution quality in stochastic programming by means of variably overlapping batches \citep{Meketon1984,Song1992,Welch1987} for Monte Carlo simulation-based estimators of optimality gaps in stochastic programs \citep{Mak1999}.
+We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
 We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid CIs can be formed.

### 2014-06-15 omrp_lb_rev.tex
Review of theoretical efficiency gains and comparison to NV

@@
 
-xxx Add new graphs here \bigskip
+\begin{figure}[htb!]
+	\centering
+	\subfloat[][]{
+	   \label{fig:efficiency_theory}
+	   \includegraphics[width=.5\textwidth]{images/comp_efficiency_theory}}
+	\subfloat[][]{
+	   \label{fig:efficiency_nv}
+	   \includegraphics[width=.5\textwidth]{images/nv_comp_efficiency}}
+		\caption{
+		Theoretical computational efficiency results for overlapping batches (left) and a comparison with measured computational efficiency for the Newsvendor problem using insertion sort (right).
+		Both graphs are scaled so that nonoverlapping batches produces a computational efficiency of 1.
+		}
+\label{fig:efficiency}
+\end{figure}
 
-xxx Write new text, etc. \bigskip
+The increased computational workload from solving overlapping batches raises the question of the computational efficiency of this method to estimate $VG$.
+In this setting, computational efficiency may be defined as $[T(\gammab)\var{VG}]$ where $T(\gammab)$ is the computational time.
+Because variance reduction is known from (\ref{eq:var_reduct_formula}) we need only examine the computational time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$ where $t(\gammab)$ is the average computation time per batch.
+Warm-starting an algorithm may be used to decrease the batch solution time for $\gammab < 1$, leading to a possible increase in computational efficiency.
 
-xxx Revise the recommendations on gammabar \bigskip
+To investigate this, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
+Results for some values of $p$ are shown in Figure \ref{fig:efficiency_theory}.
+Efficiency gains increase with larger exponent $p$, but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
+At $p=1$, i.e., for problems where computational time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches.
 
-Because variance reduction drops quickly as $\gammab$ drops below $1$, we recommend using an intermediate value of $\gammab$, such as $1/3$ or $1/4$, to gain the majority of the variance reduction, while reducing the number of optimization problems to be solved.
-Warm-starting the algorithm to solve the sampling problems, when such a scheme is available, can significantly reduce the computation times.
+We tested this theoretical relationship using the Newsvendor problem solved with insertion sort.
+The average computation time per batch was found empirically to be well approximated by power law with $p = 0.71$.
+The measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}.
+
+In cases where the exponent $p$ can be estimated the above theoretical method may be used to determine a reasonable value for $\gammab$.
+We can see in Figure \ref{fig:efficiency} that for some values of $p$ efficiency gian is nearly flat over a region of $\gammab$.
+In this case we recommend choosing a $\gammab$ near the right side of this region.
+This choice keeps efficiency high while decreasing computation time and preventing large decreases in efficiency in the event that $p$ was overestimated.
 

### 2014-06-16 images/fig2pdf.m
Add fig2pdf.m

@@ -1,0 +1,33 @@
+function fig2pdf( files, fs )
+
+if nargin < 2
+    fs = 16;
+    if nargin < 1
+        files = '*.fig';
+    end
+end
+
+s = dir(files);
+for j = 1:length(s)
+    hf = open(s(j).name);
+    htext = findall(hf,'type','text','-or','type','axes');
+    set(htext,'fontsize',fs)
+    
+    % Make figure boundaries tight
+    %ti = get(gca,'TightInset');
+    %set(gca,'Position',[ti(1) ti(2) 1-ti(3)-ti(1) 1-ti(4)-ti(2)]);
+    
+    % Get rid of pdf boundaries in pdf
+    set(gca,'units','centimeters');
+    pos = get(gca,'Position');
+    ti = get(gca,'TightInset');
+    set(gcf, 'PaperUnits','centimeters');
+    set(gcf, 'PaperSize', [pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+    set(gcf, 'PaperPositionMode', 'manual');
+    set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+    
+    [~,filename,~] = fileparts(s(j).name);
+    % saveas(hf,[filename '.fig'])
+    saveas(hf,[filename '.pdf'])
+    close(hf);
+end

### 2014-06-16 omrp_lb_rev.tex
Remarks on comparing computational work of OMRP to MRP with bigger k
Also cleaned up the plot a little bit

	modified:   images/work_comparison.fig
	modified:   images/work_comparison.pdf
	modified:   omrp_lb_rev.tex

@@
 
+\begin{figure}[htb!]
+	\centering
+	\includegraphics[width=.5\textwidth]{images/work_comparison}
+	\caption{
+		A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
+		}
+\label{fig:comp_work_comparison}
+\end{figure}
+
+A final question on computational efficiency would be whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
+In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$, so decreasing $\var{VG}$ to the level of maximally overlapping batches requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
+Again assuming average time per batch can be represented as $T(\gammab) = \gammab^p$, Figure \ref{fig:comp_work_comparison} compares the increase in computational work for OMRP for several values of $p$ with the work increase for MRP to get an equivalent decrease in variance.
+We again see that OMRP is advantageous for larger values of $p$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-06-16 omrp_lb_rev.tex
and & or

@@
 In the nonoverlapping case, there are only two batches: the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.   
-In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$ and so on.
+In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$, and so on.
 This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.
@@
 $
-where $\nb$ is the number of batches used given $n$, $m$ and $\gamma$.  
+where $\nb$ is the number of batches used given $n$, $m$, and $\gamma$.  
 The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
@@
 Toward this end, let $B(i)$ denote the set of batches $j \in \left\{1, 2, \dots, \nb \right\}$ observation $\xiti$ is used in, $i = 1, 2, \dots, n$.  
-See Figure \ref{fig:overlap_nonint} for an example with $n=18$, $m = 6$ and $\gamma = 2$.  
+See Figure \ref{fig:overlap_nonint} for an example with $n=18$, $m = 6$, and $\gamma = 2$.  
 Here, the first batch uses observations $\xit^1, \xit^2, \xit^3, \xit^4, \xit^5, \xit^6$, the second batch uses $\xit^3, \xit^4, \xit^5, \xit^6, \xit^7, \xit^8$, and so on.  
@@
 	\end{tabular}
-	\caption{Visual representation of overlapping batches with $n = 18$, $m = 6$ and $\gamma = 2$.  
+	\caption{Visual representation of overlapping batches with $n = 18$, $m = 6$, and $\gamma = 2$.  
         The brackets show which observations are used in each batch, and the numbers inside each bracket show the batch number $j$.}
@@
 The results on overlapping batch means occur in the limit as $n, m, k=n/m \rightarrow \infty$ \citep{damerdji1994strong,damerdji1995mean,Meketon1984,Song1992,Welch1987}.  
-Let $n_l, m_l$ and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
-We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$ as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  
+Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
+We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$, as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  
 In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
@@
 Throughout the rest of this section, we assume that the optimality gap estimators (\ref{eq:gbar})--(\ref{eq:vg}) and their nonoptimized counterparts (\ref{eq:dbar})--(\ref{eq:vd}) use identical samples and values of $n_
-l$, 
-$m_l$, and $\gamma_l$.  \smallskip
+l$, $m_l$, and $\gamma_l$.  \smallskip
 
@@
 	\caption{
-		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problem
-		(a) NVD, and
+		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problems
+		(a) NVD and
 		(b) CEP1
@@
 		\caption{
-		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problem
-		(a) 10D, and
+		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problems
+		(a) 10D and
 		(b) DB1
@@
 		Estimates of
-		(a) $\e{nVG}$, and 
-		(c) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches)
+		(a) $\e{nVG}$ and 
+		(b) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches)
 		 for NVD

### 2014-06-17 omrp_lb_rev.tex
Edits on Comp Efficiency Section
Corrected some typos,
Added more explanations

@@
 The increased computational workload from solving overlapping batches raises the question of the computational efficiency of this method to estimate $VG$.
-In this setting, computational efficiency may be defined as $[T(\gammab)\var{VG}]$ where $T(\gammab)$ is the computational time.
-Because variance reduction is known from (\ref{eq:var_reduct_formula}) we need only examine the computational time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$ where $t(\gammab)$ is the average computation time per batch.
-Warm-starting an algorithm may be used to decrease the batch solution time for $\gammab < 1$, leading to a possible increase in computational efficiency.
+In this setting, computational efficiency is defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computational time spent to generate $VG$ for a given value of $\gammab$.
+Because the variance of overlapping estimator relative to the nonoverlapping (MRP) variant is known from (\ref{eq:var_reduct_formula}), we need only examine the computational time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$, where $t(\gammab)$ is the average computation time per batch, multiplied by the number of batches.
+Warm-starting an algorithm may be used to decrease the computation time per batch $t(\gammab)$ for $\gammab < 1$, leading to a possible increase in computational efficiency.
 
-To investigate this, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
+To investigate computational efficiency, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
 Results for some values of $p$ are shown in Figure \ref{fig:efficiency_theory}.
 Efficiency gains increase with larger exponent $p$, but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
-At $p=1$, i.e., for problems where computational time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches.
+At $p=1$, i.e., for problems where computational time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches of \cite{Meketon1984}.
+When $p$ is $0.71$, on the other hand, computational efficiency is observed for values of $\gammab$ from slightly lower than $0.3$ to $1$, and efficiency is maximized at a relatively flat region between $\gammab=0.5$ and $\gammab=0.8$.
 
 We tested this theoretical relationship using the Newsvendor problem solved with insertion sort.
+Insertion sort is an efficient sorting algorithm when the values are already largely sorted. 
+Therefore, as overlapping increases, insertion sort results in a decreased solution time per batch for the NVD problem. 
 The average computation time per batch was found empirically to be well approximated by power law with $p = 0.71$.
-The measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}.
+The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}, where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency_theory}.
+It appears that empirical observations match with the theoretical efficiency calculations well.
 
-In cases where the exponent $p$ can be estimated the above theoretical method may be used to determine a reasonable value for $\gammab$.
-We can see in Figure \ref{fig:efficiency} that for some values of $p$ efficiency gian is nearly flat over a region of $\gammab$.
-In this case we recommend choosing a $\gammab$ near the right side of this region.
+In cases where the exponent $p$ can be estimated, the above theoretical method may be used to determine a reasonable value for $\gammab$.
+When warm-starting can be used to solve the batch sampling problems, we recommend the users to perform preliminary computations to determine how computational time per batch changes as $\gammab$ changes.
+We can see in Figure \ref{fig:efficiency} that for some values of $p$, efficiency gain is nearly flat over a region of $\gammab$.
+In this case, we recommend choosing a $\gammab$ near the right side of this region.
 This choice keeps efficiency high while decreasing computation time and preventing large decreases in efficiency in the event that $p$ was overestimated.
+For example, in the case of NVD, we recommend the use of value $\gammab=0.8$ as this value provides a high computational efficiency with minimal overall computation time across values of $\gammab$ with high efficiency.
 
@@
 A final question on computational efficiency would be whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
+When generating observations is cheap, one could potentially increase the number of batches in MRP to obtain estimators with lower variances. 
 In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$, so decreasing $\var{VG}$ to the level of maximally overlapping batches requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
-Again assuming average time per batch can be represented as $T(\gammab) = \gammab^p$, Figure \ref{fig:comp_work_comparison} compares the increase in computational work for OMRP for several values of $p$ with the work increase for MRP to get an equivalent decrease in variance.
+Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison}. 
+This curve shows the increase in computational effort due to an increased number of batches in MRP in order to obtain the same variance level for OMRP across $\gammab$.
+If the work increase by OMRP is less than this solid black curve, then OMRP is computationally more efficient than increasing the number of batches in MRP. 
+Again, assuming average computation time per batch can be represented as $T(\gammab) \propto \gammab^p$, Figure \ref{fig:comp_work_comparison} compares the increase in computational work for OMRP for several values of $p$ with the work increase for MRP to get an equivalent decrease in variance.
 We again see that OMRP is advantageous for larger values of $p$.
+For small values of $p$, some efficiency gain is observed at $\gammab$ values close to 1.
 

### 2014-06-17 AE_Reponse.tex
More Referee 2 and AE comments
minor comments
Minor changes by Referee2 and AE
first pass through the referee minor suggestions
more to be done...
AE response to comp efficiency

@@
 
-\noi
-We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your comments and the referees.
+\noi xxx 
+We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your and the referees' comments and the new material like computational efficiency added to the paper.
 \medskip
@@
 \begin{itemize}
-\item[] \textit{The experiments show that the confidence interval average widths and observed coverage probabilities are the same with overlapping batch means; the only difference is in decreased variability of the confidence interval widths.
+\item[] \textit{%\ldots
+The experiments show that the confidence interval average widths and observed coverage probabilities are the same with overlapping batch means; the only difference is in decreased variability of the confidence interval widths.
 That is, the variance of the variance estimator is reduced. 
 This second-order benefit should be weighed against the increased computation cost (not to mention complexity and restricted applicability) of the overlapping batch means method.}
-\end{itemize}
 
-\noi  
-xxx  Hmm We need to be careful addressing this comment but M1 of ref1 could help.
-\medskip
-
-\begin{itemize}
-\item[] \textit{The issue of computational efficiency is not addressed  in the paper. 
+\textit{The issue of computational efficiency is not addressed  in the paper. 
 In this setting the efficiency is often defined as the reciprocal of the computation time multiplied by the variance. 
@@
 \noi 
-xxxx Need to discuss
+Thank you for this suggestion. 
+It is indeed important to study computational efficiency in this context. 
+We created a new section, Section 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
+When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
+We discussed efficiency for a given functional form of the solution time per batch. 
+Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
+We illustrated this method on the newsvendor problem using insertion sort. 
+Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping.
+We discussed guidelines on selecting the degree of overlapping (for NVD or for a given generic problem) in Section 5.4 (Computational Efficiency). 
+\medskip
+
+In addition, based on the comments of Referee 1, we also studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances.
+Our results indicate that when warm-starting is effective, overlapping is computationally more efficient than increasing the number of batches of MRP.
+We also illustrated this result on the newsvendor problem. 
+We believe the paper has improved as a result of the study of computational efficiency. 
+Thank you. 
 \medskip
@@
 
-\noi
-xxx  Is this really a new comment?  Looks like just continuation of the prev. comment. 
-Also, seems like this is what M1 of ref1 is asking us to do. 
-Once we have those results, we can argue more.
+\noi xxx 
+Based on your other comments and suggestions of the referees, we provided information on computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming.
+These are detailed in Section 5.4 (Computational Efficiency). 
+(Please see our response to the previous comment.)
+We also changed Section 1 (Introduction) and Section 6 (Conclusions) to clearly motivate the study and usefulness of the results.
+
+%xxx  Is this really a new comment?  Looks like just continuation of the prev. comment. So... combine it with previous comment???
+
 \medskip
@@
 
-\noi {\large Minor comments:}
+\noi {\bf \large Minor comments:}
 \medskip
@@
 \noi 
-xxx
+We meant to say that the feasible region only consists of deterministic constraints and does not have any stochastic constraints such as probabilistic or expected-value constraints. 
+We changed the wording to reflect this. 
+\medskip
 
@@
 \noi 
-xxx
+Done.
+\medskip
 
@@
 \noi
-xxx
+This sentence was removed as a result of the computational efficiency study. 
+Based on the examination of computational efficiency, we provided new guidelines on selecting the degree of overlapping.
 

### 2014-06-19 omrp_lb_rev.tex
corrected brackets after/inside expectations

@@
 
-Unless $f$ has a simple structure or the number of realizations of $\xi$ is small, (\ref{eq:sto_prog}) typically cannot be solved exactly. 
+Unless $f$ has a simple structure or the number of realizations of $\xit$ is small, (\ref{eq:sto_prog}) typically cannot be solved exactly. 
 An approximation of (\ref{eq:sto_prog}) can be generated by sampling from the distribution of $\xit$.
@@
 	\begin{align*}
-		\e{(\db - \gb)^4} & = \e{\left[ \left.(\db - \gb)^4 \right| \db - \gb \neq 0\right]} \p{\db - \gb \neq 0} + 0\\
-		& \leq \e{\left[ \left.(\db - \gb)^4 \right| \db - \gb \neq 0 \right]} \p{ \xs_{m_l}  \neq \xs}.
+		\e{(\db - \gb)^4} & = \e{ \left.(\db - \gb)^4 \right| \db - \gb \neq 0} \p{\db - \gb \neq 0} + 0\\
+		& \leq \e{ \left.(\db - \gb)^4 \right| \db - \gb \neq 0} \p{ \xs_{m_l}  \neq \xs}.
 	\end{align*}
@@
 	\begin{align*}
-		\e{(\dbb - \gbb)^4} & = \e{\left[ \left. (\dbb - \gbb)^4 \right| \dbb - \gbb \neq 0\right]} \p{\dbb - \gbb \neq 0}.
+		\e{(\dbb - \gbb)^4} & = \e{\left. (\dbb - \gbb)^4 \right| \dbb - \gbb \neq 0} \p{\dbb - \gbb \neq 0}.
 	\end{align*}
@@
 We use the abbreviation a.s.\ to denote almost sure convergence. 
-We also use $\mu_{\xh} := \e{\left[f(\xh,\xit) - f(\xs,\xit)\right]}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
+We also use $\mu_{\xh} := \e{f(\xh,\xit) - f(\xs,\xit)}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
 
@@
 		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
-		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\left[ \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
-		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left[ A_j \right]^2 \
-		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left[ A_j \right]^2 \right]\
+		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left( A_j \right)^2 \
+		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left( A_j \right)^2 \
+		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left( A_j \right)^2 
 		} \\
-		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 } \\
-		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left[ A_j \right]^2 }
-		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left[ A_j \right]^2 }.
+		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j \right)^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j \right)^2 } \\
+		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j \right)^2 }
+		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j \right)^2 }.
 	\end{align*}	
@@
 	\begin{align}
-		\left( 2m \right)^2 \e{ \left[ A_j \right]^2 } & = \left( 2m \right)^2 \e{ \left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^2 \left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^2 } \notag \\
-		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{\e{\left[(\gb_j - \gbb) + (\db_j - \dbb)\right]^4 }} \label{eq:var_reduct_cauchy2} \\
-		& \leq \left( 2m \right)^2 \sqrt{\e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}} \sqrt{8 \left(\e{(\gb_j - \gbb)^4} + \e{(\db_j - \dbb)^4} \right)}, \label{eq:var_reduct_holder2}
+		\left( 2m \right)^2 \e{ \left( A_j \right)^2 } & = \left( 2m \right)^2 \e{ \left((\gb_j - \gbb) - (\db_j - \dbb)\right)^2 \left((\gb_j - \gbb) + (\db_j - \dbb)\right)^2 } \notag \\
+		& \leq \left( 2m \right)^2 \sqrt{\e{\left((\gb_j - \gbb) - (\db_j - \dbb)\right)^4}} \sqrt{\e{\left((\gb_j - \gbb) + (\db_j - \dbb)\right)^4 }} \label{eq:var_reduct_cauchy2} \\
+		& \leq \left( 2m \right)^2 \sqrt{\e{\left((\gb_j - \gbb) - (\db_j - \dbb)\right)^4}} \sqrt{8 \left(\e{(\gb_j - \gbb)^4} + \e{(\db_j - \dbb)^4} \right)}, \label{eq:var_reduct_holder2}
 	\end{align}
@@
 	\begin{align*}
-		\frac{n}{m} 4m^2 \e{\left[(\gb_j - \gbb) - (\db_j - \dbb)\right]^4}	& \leq 32 \frac{n}{m} m^2\left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
+		\frac{n}{m} 4m^2 \e{\left((\gb_j - \gbb) - (\db_j - \dbb)\right)^4}	& \leq 32 \frac{n}{m} m^2\left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
 	\end{align*}	

### 2014-06-22 omrp_lb_rev.tex
Update computational efficiency section

@@
 
+All theoretical curves in this section were computed using $m = 1000$, but the results do not change substantially with increasing batch size.
+Newsvendor computations used $m = 1000$ with $10,000$ replications.
+
 We tested this theoretical relationship using the Newsvendor problem solved with insertion sort.
@@
 Therefore, as overlapping increases, insertion sort results in a decreased solution time per batch for the NVD problem. 
-The average computation time per batch was found empirically to be well approximated by power law with $p = 0.71$.
+The average computation time per batch was found empirically to be well approximated ($R^2 = 0.994$) by power law with $p = 0.71$.
 The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}, where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency_theory}.
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{images/work_comparison}
+	\subfloat[][]{
+	   \label{fig:comp_work_comparison_theory}
+	   \includegraphics[width=.5\textwidth]{images/work_comparison}}
+	\subfloat[][]{
+	   \label{fig:comp_work_comparison_nv}
+	   \includegraphics[width=.5\textwidth]{images/nv_work_comparison}}
 		\caption{
-		A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
+		(Left) A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
+		(Right) Measured computational work for NVD compared with the theoretical results.
 		}
@@
 For small values of $p$, some efficiency gain is observed at $\gammab$ values close to 1.
+
+With these considerations, for situations where $p > 0$ but its size cannot be readily measured or estimated, we recommend selecting a large value of $\gammab$ such as $0.9$.
+This allows for some increase in efficiency while remaining robust in the event that $p$ is smaller than expected.
 

### 2014-06-22 omrp_lb_rev.tex
some minor edits to comp efficiency section

@@
 To investigate computational efficiency, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
-Results for some values of $p$ are shown in Figure \ref{fig:efficiency_theory}.
+Results for various values of $p$ are shown in Figure \ref{fig:efficiency_theory}. 
+This figure is constructed using $m = 1000$, but the results do not change substantially with different values of $m$.
 Efficiency gains increase with larger exponent $p$, but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
@@
 
-All theoretical curves in this section were computed using $m = 1000$, but the results do not change substantially with increasing batch size.
-Newsvendor computations used $m = 1000$ with $10,000$ replications.
+%All theoretical curves in this section were computed using $m = 1000$, but the results do not change substantially with increasing batch size.
+%Newsvendor computations used $m = 1000$ with $10,000$ replications.
 
-We tested this theoretical relationship using the Newsvendor problem solved with insertion sort.
-Insertion sort is an efficient sorting algorithm when the values are already largely sorted. 
+We tested this theoretical relationship using the newsvendor problem solved with insertion sort.
+Insertion sort is an efficient sorting algorithm when the values are already almost sorted. 
 Therefore, as overlapping increases, insertion sort results in a decreased solution time per batch for the NVD problem. 
+To test computational efficiency, we used $m = 1000$ with $10,000$ replications.
 The average computation time per batch was found empirically to be well approximated ($R^2 = 0.994$) by power law with $p = 0.71$.
@@
 In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$, so decreasing $\var{VG}$ to the level of maximally overlapping batches requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
-Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison}. 
+Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison} using $m=1000$. 
 This curve shows the increase in computational effort due to an increased number of batches in MRP in order to obtain the same variance level for OMRP across $\gammab$.

### 2014-06-25 Referee1_Response.tex
AE response to comp efficiency
Changes to R1 and AE responses

@@
 
-\noi 
+\noi xxx 
 We thank the referee for this suggestion. 
@@
 \noi 
-xxx Need to discuss xxx  \medskip 
-We performed such an analysis and provide the results of this in the new subsection 7.4... ?? 
-Etc.
+Based on your and the associate editor's comments, we studied the computational efficiency of the OMRP estimators. 
+The results of this study are presented in a new section, Section 5.4 (Computational Efficiency).
+%We studied the computational efficiency of the OMRP estimators, based on your and the associate editor's comments, and provided a summary of our results in a new section, Section 5.4 (Computational Efficiency).
+We first approached efficiency by the reciprocal of variance multiplied by the computation time, per associate editor's suggestion. 
+Maximizing the computational efficiency defined in this manner provided guidelines on selecting the degree of overlap. 
+We then looked at how OMRP compared to increasing the number batches in MRP.
+We examined computational efficiency both theoretically and empirically. 
+For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions. 
+We found that when effective warm-starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
+All these results are presented in Section 5.4 (Computational Efficiency). 
+Thank you for this suggestion. 
+We believe the study of computational efficiency significantly improved the paper. 
 \medskip
@@
 We split these two figures into three and enlarged each graph. 
-All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger compared to those in the previous version of the paper. 
+We also enlarged the legends in these graphs to improve clarity.
+All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger, with legible legends. 
 \medskip
@@
 Thank you for this suggestion. 
-xxx We expanded this paragraph based on our findings. 
-xxx Please note that this paragraph now appears in a new section (\S 5.4 Computational Efficiency).
+Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
+Please note that this guidance appears in the third and last paragraphs of the new section, Section 5.4 (Computational Efficiency).
 

### 2014-06-25 AE_Reponse.tex
Changes to R1 and AE responses

@@
 \noi xxx 
-We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your and the referees' comments and the new material like computational efficiency added to the paper.
+We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your and the referees' comments. 
+The revised introduction also includes several new comments based on the material added to the paper (computational efficiency) and a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).
 \medskip
@@
 Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping.
-We discussed guidelines on selecting the degree of overlapping (for NVD or for a given generic problem) in Section 5.4 (Computational Efficiency). 
+We discussed guidelines on selecting the degree of overlapping. 
 \medskip
 
-In addition, based on the comments of Referee 1, we also studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances.
+In addition, based on the comments of Referee 1, we studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances.
 Our results indicate that when warm-starting is effective, overlapping is computationally more efficient than increasing the number of batches of MRP.
-We also illustrated this result on the newsvendor problem. 
+Even in cases where warm-starting is less effective, computational efficiency can be observed when about 10\% of observations are overlapped.
+We again illustrated this result on the newsvendor problem. 
 We believe the paper has improved as a result of the study of computational efficiency. 

### 2014-06-26 Referee1_Response.tex
Finer pass through Ref2 comments - PART II

@@
 \noindent Thank you for pointing this out.  
-We removed this statement from the proof of Theorem 3 and added it as a remark in the paragraph after the theorem.
+We removed this statement from the proof of Theorem 3 and added it as a remark to the paragraph after the theorem.
 \medskip
@@
 We split these two figures into three and enlarged each graph. 
-We also enlarged the legends in these graphs to improve clarity.
+We also enlarged the legends in these graphs to improve readability.
 All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger, with legible legends. 
@@
 \noindent 
-We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP CIs for this test problem.
+We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP confidence intervals for this test problem.
 We explain this at the end of Section 5.1 (Test Problems). 
@@
 Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
-Please note that this guidance appears in the third and last paragraphs of the new section, Section 5.4 (Computational Efficiency).
+This guidance appears in the third and last paragraphs of the new section, \S 5.4 (Computational Efficiency).
 

### 2014-06-26 Referee2_Response.tex
and & or
Finer pass through Ref2 comments - PART II

@@
 Done.  
+We went through the paper and added commas before `and' and `or' in a list of items with three or more items.
 \medskip
@@
 We put a comma after `see'; however, we still kept the same referencing style `[Bertocchi et al., 2000; \ldots]' as this sentence refers to the papers and not directly to the authors. 
-We also went through to make sure all `see, e.g.,' have the appropriate commas.
+We also went through the paper to make sure all `see, e.g.,' have the appropriate commas.
 \medskip
@@
 We reworded this sentence to make it clear. 
-Please note that based on your earlier comments, we also reworded this sentence to avoid using the term `variance reduction'. 
-We also went through the whole paper and removed several uses of the word `classical' to reduce ambiguity (as these were referring to nonoverlapping batches). 
+Please note that based on your earlier comments, we reworded this sentence to avoid using the term `variance reduction'. 
+We also went through the paper and removed several uses of the word `classical' that referred to nonoverlapping batches to reduce ambiguity.
+%(as these were referring to nonoverlapping batches). 
+%In the current version of the paper, `classical case' is used to only indicate  the use of overlapping batches in simulation output analysis. 
 \medskip
@@
 \noi
-xxx   CHECK -- DON'T REMEMBER
+Variance parameter. 
+xxx We revised this section to clarify this point. 
 \medskip
@@
 Please note that we broke this sentence into two to avoid long sentences and to improve exposition. 
-We also checked for other occurrences of the term `sample variance' throughout the paper and corrected these terms as well. 
+We also checked for other uses of the term `sample variance' throughout the paper and corrected these as needed.
+Thank you.  
 \medskip
@@
 We now introduce this abbreviation the first time we use the term `confidence interval' in the introduction. 
-From this point on, we use the abbreviated form `CI' throughout the paper, except for Section 4.5 title (Asymptotic Validity of the Confidence Intervals). 
+From this point on, we use the abbreviated form `CI' throughout the paper, except for the title of Section 4.5 (Asymptotic Validity of the Confidence Intervals). 
 \medskip
@@
 \noi
-xxx  
+We went through the paper and removed most of the ``note that'' phrases. 
+We decided to leave a couple as is (mainly as ``notice that'') because they highlight important characteristics.  
 \medskip
@@
 \noi
-We now denote it as `dt' to represent the whole denominator term (d.t.). 
+We now denote it as `dt' to represent the whole denominator term. 
 \medskip
@@
 \noi
-You are right. 
 We split these two figures into three and enlarged each graph. 
-All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger than the old graphs.  
+We also enlarged the legends in these graphs to improve readability.
+All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger, with legible legends. 
 \medskip

### 2014-06-26 omrp_lb_rev.tex
Finer pass through Ref2 comments - PART II

@@
 
-We wish to assess the quality of a candidate solution $\xh \in X$. 
+We wish to assess the quality of a candidate solution $\xh \in X$, which may have been found in any way.
 Assessing solution quality is important in practice because as (\ref{eq:sto_prog}) typically cannot be solved exactly, one only has an approximate solution $\xh$ without verification of its quality.
@@
 The lower the optimality gap, the higher the quality of the solution; and a zero optimality gap implies that the solution is optimal. 
-Note that the candidate solution $\xh \in X$ may have been found in any way. 
-We assume that this solution is given as input to our procedures, and hence fixed, throughout this paper.
+We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout this paper.
 
@@
 We are interested in estimating the variance of an optimality gap estimator.  
-Notice that an optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
-Minimization changes the statistical properties of sample means.  
-For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
-Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
+An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
+Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
+%For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
+%Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
 We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
@@
 Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
+Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
 In this paper, we consider variable amounts of overlap and examine this both theoretically and empirically. 
-Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
+% THIS LAST SENTENCE NEEDS TO CHANGE!
 
@@
 and the overall sample mean $\ybb = \frac{1}{k} \sum_{j=1}^k \yb_j = \frac{1}{n} \sum_{i=1}^n y^i$ provides a point estimator of $\mu$.  
-The variance estimator of the batch means, which is $n/m$ times the sample variance, is calculated as
+The variance estimator of the batch means, which is $m/n$ times the sample variance, is calculated as
 \begin{equation} \label{eq:var}
@@
 
-The sample variance estimator is updated to
+The variance estimator is updated to
 \begin{equation} \label{eq:overlap_variance_def}
@@
 \end{equation}
-Note that the corresponding overlapping batch means are no longer independent. 
-However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
+The corresponding overlapping batch means are no longer independent; however, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator.
 \citet{Meketon1984} show that: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
@@
 The optimality gap estimator $\gb_j$ is similar to $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
-Notice that, in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is the optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
+Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is the optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
 As before, after $k$ estimates are obtained, the overall mean of these estimates $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
-The sample variance is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in an approximate $(1-\alpha)$-level one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$.
+The variance estimator is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in an approximate $(1-\alpha)$-level one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$.
 
-Notice that the minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
+The minimization in the second term on the right-hand side of (\ref{eq:mrp_gap}) gives rise to a biased gap estimator (recall the upper bound on the optimality gap).  
 Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
@@
 where $\nb$ is the number of batches used given $n$, $m$, and $\gamma$.  
-The sample variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
+The variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
 \begin{equation} \label{eq:variance_gamma}
@@
 With $\xh$ and $\xs$ fixed, estimators (\ref{eq:dbar})--(\ref{eq:vd}) have the same statistical properties as variably overlapping batches estimators in \S \ref{ssec:overlap}.  
-Note that the optimal solution $\xs$ is not known. 
-However, the estimators (\ref{eq:dbar})--(\ref{eq:vd}) are used only to show convergence of (\ref{eq:gbar})--(\ref{eq:vg}); they are not necessary for carrying out the OMRP algorithm.  
+The optimal solution $\xs$ is not known; however, the estimators (\ref{eq:dbar})--(\ref{eq:vd}) are used only to show convergence of (\ref{eq:gbar})--(\ref{eq:vg}) and not necessary for carrying out the OMRP algorithm.
 Throughout the rest of this section, we assume that the optimality gap estimators (\ref{eq:gbar})--(\ref{eq:vg}) and their nonoptimized counterparts (\ref{eq:dbar})--(\ref{eq:vd}) use identical samples and values of $n_
@@
 
-\begin{proof} When the sampling problems used in the calculation of $\gbb$ all have optimal solutions that solve (SP), i.e., when $\xs_{j} = \xs$, for all $j=1,2,\ldots, \nbl$, then $\gbb_l = \dbb_l$.
+\begin{proof} When all the sampling problems used in the calculation of $\gbb$ have optimal solutions that solve (SP), i.e., when $\xs_{j} = \xs$, for all $j=1,2,\ldots, \nbl$, then $\gbb_l = \dbb_l$.
 Therefore, probability of the complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
@@
 (ii) This proof is nearly identical to above. 
-Note that
+Similar to the proof of Lemma \ref{lem:gbb_prob}, we have
 	\[
-		\p{n_l VD_l -n_l VG_l \neq 0} \leq \p{\left( \bigcap_{j=1}^{\nbl} \{\xs_{j} = \xs\} \right)^C}
+		\p{n_l VD_l -n_l VG_l \neq 0} \leq \p{\left( \bigcap_{j=1}^{\nbl} \{\xs_{j} = \xs\} \right)^C}.
 	\]
-	and by the proof of Lemma \ref{lem:gbb_prob}, $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast, and thus $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$, if $n_l VD_l$ is, by the Borel-Cantelli Lemma.
+	Following the same logic, $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast. 
+Thus, $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$, if $n_l VD_l$ is, by the Borel-Cantelli Lemma.
 \end{proof}
@@
         Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $dt = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
-Note that
+We have
 	\begin{align}
@@
 			If $\frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, because $t_{d_l,\alpha} \rightarrow z_{\alpha}$ as $l \rightarrow \infty$, we obtain the desired result by rearranging the terms in $\p{\mu_\xh \leq I^G_l}$ and taking the limit as $l \rightarrow \infty$.
-        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  Note that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
+        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  
+		  Observe that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
         In the proof of Theorem \ref{thm:strong_consistency} we showed that $\left\{ \dbb_l - \gbb_l \neq 0 \right\}$ happens only finitely many times, so $|X_l - Y_l| \rightarrow 0$, a.s.\ by the Borel-Cantelli Lemma.
@@
 These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
-We note that the variance reduction in DB1 can be less than the asymptotic amount %for the small sample sizes used in these experiments. 
-because due its size, DB1 has not yet been solved to optimality; therefore, it may lack a unique optimal solution. 
+The variance reduction in DB1 can be less than the asymptotic amount %for the small sample sizes used in these experiments. 
+because DB1 has not yet been solved to optimality due its size; therefore, it may lack a unique optimal solution. 
 %, violating assumption A3. (?)
@@
 We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
-We have provided conditions under which the resulting point estimator of the optimality gap and its associated sample variance are consistent, the same variance reduction can be achieved, and asymptotically valid CIs can be formed.
+We have provided conditions under which the resulting point estimator of the optimality gap and its associated variance estimator are consistent, the same variance reduction can be achieved, and asymptotically valid CIs can be formed.
 Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.

### 2014-06-27 omrp_lb_rev.tex
variance parameter (Ref2 comment)

@@
 \subsection{Overlapping Batch Means} \label{ssec:obm}
-Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
+Consider a covariance stationary stochastic process with mean $\mu$ and variance parameter\footnote{For a given process $y^1, y^2, \dots$, the variance parameter is the sum of covariances at all lags, $\sigma^2=\mathrm{Var} \left(y^1 \right)+2\sum_{j=1}^{\infty}\mathrm{Cov} \left(y^1,y^{1+j}\right)$.
+If the variance parameter exists, then  $\sigma^2=\lim_{n\rightarrow \infty}n\mathrm{Var} \left(\ybb\right)$, where $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^{i}$.} $0<\sigma^2<\infty$.
 The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  

### 2014-07-01 Referee2_Response.tex
variance parameter (Ref2 comment)
Major Comment 2 of Referee 2
Removed Section 3.1 and summarized everything in Section 2.1.  Also,
removed some references/text from the later sections to Sec 2.1, as we
use them later on. . .  This way, we have a self-contained background on
overlapping batches that lists the main results we use in the paper.

@@
 \noi
-You are right.
+%You are right.
 We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
 We reworded this sentence to reflect this. 
-xxxx  We also \ldots (I think we should write more about our conclusions and our recommendation based on our new findings here) xxxx
+xxx  We also \ldots avoided using this term and replaced by. . . 
 \medskip
@@
 Variance parameter. 
-xxx We revised this section to clarify this point. 
+We revised this sentence and added a footnote defining the variance parameter for readers who might not be familiar with this term (e.g., readers with more of an optimization background). 
 \medskip

### 2014-07-01 omrp_lb_rev.tex
Major Comment 2 of Referee 2
Removed Section 3.1 and summarized everything in Section 2.1.  Also,
removed some references/text from the later sections to Sec 2.1, as we
use them later on. . .  This way, we have a self-contained background on
overlapping batches that lists the main results we use in the paper.

--- 2014-06-26 omrp_lb_rev.tex
@@
 \newcommand{\vartg}[1]{\widetilde{\mathrm{Var}}_\gamma \left( #1 \right)}
+\newcommand{\vto}[1]{\widetilde{\mathrm{Var}}_{1} \left( #1 \right)}
+\newcommand{\vtm}[1]{\widetilde{\mathrm{Var}}_{m} \left( #1 \right)}
 \newcommand{\varhat}{\widehat{\mathrm{Var}}}
@@
 
-\subsection{Overlapping Batch Means} \label{ssec:obm}
-Consider a covariance stationary stochastic process with mean $\mu$ and variance $\sigma^2$.  
+\subsection{Batch Means} 
+\label{ssec:obm}
+
+Consider a covariance stationary stochastic process with mean $\mu$ and variance parameter\footnote{For a given stochastic process $y^1, y^2, \dots$, the variance parameter is the sum of covariances at all lags, $\sigma^2=\mathrm{Var} \left(y^1 \right)+2\sum_{j=1}^{\infty}\mathrm{Cov} \left(y^1,y^{1+j}\right)$.
+If the variance parameter exists, then  $\sigma^2=\lim_{n\rightarrow \infty}n\mathrm{Var} \left(\ybb\right)$, where $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^{i}$.} $0<\sigma^2<\infty$.
 The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
@@
 
-Nonoverlapping batch means takes $n$ observations, $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume, for now, $n = mk$).
+\subsubsection{Nonoverlapping Batch Means}
+
+Nonoverlapping batch means takes $n$ observations $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume, for now, $n = mk$).
 The sample mean of each batch is then computed as
@@
 
-Overlapping batch means modifies this idea by taking batches given by $\yb_j(m) = \frac{1}{m} \sum_{i=1}^{m}$ $y^{(j-1)+i}$, for $j = 1, \dots, n-m+1$.
+\subsubsection{Overlapping Batch Means}
+\label{ssec:overlap}
+
+Overlapping batch means reuses a subset of the observations from one batch to form the next batch. 
 As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
-In the nonoverlapping case, there are only two batches: the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.   
+In the nonoverlapping case, there are only two batches:
+% the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
+$y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
 In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$, and so on.
 This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
+It is possible to vary the amount of overlap between neighboring batches. 
+This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
+The overlapping batch means 
+%formed using the batch nonoverlap parameter $1 \leq \gamma < m$ 
+are no longer independent. 
+However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
+That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
+%the overlapping estimator has 
+a lower asymptotic variance than its nonoverlapping counterpart.
 
+In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
+For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally-overlapping case of \citet{Meketon1984}.  
+In general, $\gamma$ can take any integer value between and including $[1,m]$. 
+Let $\lfloor \cdot \rfloor$ be the greatest integer that is less than or equal to its argument. 
+The sample mean of each batch is calculated similarly, 
+$
+\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, \nb, 
+$
+now taking into account $\gamma$.  
+Here, $\nb$ batches are formed given $n$, $m$, and $\gamma$.  
 The variance estimator is updated to
-\begin{equation} \label{eq:overlap_variance_def}
-	\vart{\ybb} = \frac{1}{(\tfrac{n}{m}-1)(n - m + 1)}\sum_{j=1}^{n-m+1} (\yb_j(m) - \ybb)^2.
+\begin{equation} \label{eq:variance_gamma}
+	\vartg{\ybb} = \frac{1}{\left( \tfrac{n}{m} - 1 \right) \left( \nb \right)}  \sum_{j=1}^{\nb} (\yb_j - \ybb)^2.
 \end{equation}
-The corresponding overlapping batch means are no longer independent; however, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator.
-\citet{Meketon1984} show that: (i) the overlapping variance estimator has nearly the same bias as the standard nonoverlapping variance estimator, and (ii) the overlapping estimator has only two-thirds of the asymptotic variance of the nonoverlapping one.
-That is, 
-\begin{equation} \label{eq:asym_var}
-	\frac{ \var{\vart{\ybb}} }{ \var{\varhat(\ybb)} } \rightarrow \frac{2}{3}
+With $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).
+With $\gamma=1$ (the maximally-overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \citep{Meketon1984}.
+This slightly different denominator 
+makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.
+
+The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $0\leq \gamma< m$, relative its nonoverlapping counterpart 
+%$\var{\vtm{\ybb}}$ 
+depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$. 
+The maximally-overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
+\cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally-overlapping cases. 
+Under appropriate conditions, these results, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
+\begin{equation}
+\label{eq:varvarred}
+\frac{n}{m}\var{n \vartg{\ybb}} \rightarrow \beta_{\gammab} \sigma^4
 \end{equation}
-in the limit as batch size $m$ and the number of batches $(n/m)$ tend to infinity.  
-Note that the degrees of freedom in (\ref{eq:overlap_variance_def}) is slightly different than in \citep{Meketon1984}.  
-The degrees of freedom in (\ref{eq:overlap_variance_def}) make $\vart{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.  
-The $(1-\alpha)$-level approximate CI is similarly formed by $\ybb \pm t_{3(k-1)/2,\alpha/2} \sqrt{\vart{\ybb}}$, with an adjustment to the degrees of freedom.
+as the batch size $m$ and the number of batches $n/m$ tend to infinity. 
+In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches, $\beta_0 = \frac{4}{3}$ for maximally overlapping batches, and more generally, $\beta_{\gammab}$ is twice the value of 
+\begin{equation} \label{eq:var_reduct_formula}
+	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right).
+\end{equation}
+If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
+This means that the maximally-overlapping variance estimator has a variance that is two-thirds ($66.67\%$) of the nonoverlapping estimator.
+As the amount of overlap decreases, the variance increases. 
+When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/4$), for instance, the variance is 75\% of the nonoverlapping counterpart.
 
-\citet{Welch1987} established the relationship between OBM and spectral estimators and also considered variable amounts of overlap, see also \citep{Song1992}.  
-%In our application to assessment of solution quality, we also consider varying the amount of overlap between neighboring batches.  
-We defer this discussion on variable overlap to \S \ref{ssec:overlap} and continue with a brief review of MRP.
+A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
+If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$.  For the maximally-overlapping batch means, the degrees of freedom is $d_{\gamma} = \frac{3}{2}$.
 
@@
 
-Taking $n$ observations of the random variables $\xit$ and splitting them into $k$ nonoverlapping batches of size $m$, define 
+Taking $n$ observations of the random variables $\xit$ and splitting them into $k$ {\it nonoverlapping} batches of size $m$, define 
 \begin{align} 
@@
 Since we are assessing the quality of a given solution $\xh \in \X$, we suppress it from the notation $\gb_j$.
-The optimality gap estimator $\gb_j$ is similar to $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
+The optimality gap estimator $\gb_j$ is similar to the nonoverlapping $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
 Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is the optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
@@
 \label{sec:omrp}
-
-We begin our discussion with variably overlapping batches and then define the estimators of OMRP.
-
-\subsection{Variably Overlapping Batches} 
-\label{ssec:overlap}
-
-As before, let $m$ denote the batch size, $n$ the total sample size and $k = \lfloor \tfrac{n}{m} \rfloor$ be the number of nonoverlapping batches.  
-In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
-For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
-In general, $\gamma$ can take any integer value between and including $[1,m]$. 
-Let $\lfloor \cdot \rfloor$ be the greatest integer that is less than or equal to its argument. 
-The sample mean of each batch estimator is calculated similarly, 
-$
-\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, \nb, 
-$
-where $\nb$ is the number of batches used given $n$, $m$, and $\gamma$.  
-The variance estimator given in (\ref{eq:overlap_variance_def}) is changed to
-\begin{equation} \label{eq:variance_gamma}
-	\vartg{\ybb} = \frac{1}{\left( \tfrac{n}{m} - 1 \right) \left( \nb \right)}  \sum_{j=1}^{\nb} (\yb_j - \ybb)^2.
-\end{equation}
-Note that with $\gamma=1$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:overlap_variance_def}) and with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).
-
-The amount of asymptotic variance reduction in this estimator depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$.  
-For example, when $\gamma = 1$ (or $\gammab=0$; the maximally overlapping case), the variance is reduced to two-thirds ($66.67\%$) of the original nonoverlapping case, as given in (\ref{eq:asym_var}).
-When 75\% of observations overlap (i.e., when $\gamma = m/4$ or $\gammab = 1/4$), the variance is $33/48$th of the original ($68.75\%$), which is near-optimal.   
-When only half of the observations overlap ($\gammab = 1/2$) the variance is 75\% of original.  
-Let $\lceil \cdot \rceil$ be the smallest integer that is greater than or equal to its argument. 
-In general, from the spectral analysis given in \citep{Welch1987}, the variance is reduced to
-\begin{equation} \label{eq:var_reduct_formula}
-	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right) %= -\gammab\left( 1 - 2\gammab\cogb + \gammab^2\cogb^2 \right) + 2\gammab\cogb\left(1-\gammab\cogb\right) + \frac{2}{3}\gammab^3\cogb^3 + \frac{1}{3}\gammab^3\cogb
-\end{equation}
-of the nonoverlapping case.  
-If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
-
-A $(1-\alpha)$-level approximate CI on the mean can be formed using variably overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
-If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$.  For maximally overlapping batches, the degrees of freedom is $d_{\gamma} = \frac{3}{2}$.
-
-\subsection{Definition of Estimators for OMRP}
 
@@
 
-The results on overlapping batch means occur in the limit as $n, m, k=n/m \rightarrow \infty$ \citep{damerdji1994strong,damerdji1995mean,Meketon1984,Song1992,Welch1987}.  
+The results on overlapping batch means like (\ref{eq:varvarred}) occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
 Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
@@
 
-\subsection{Variance Reduction}
+\subsection{Lower Variances}
 \label{ssec:var_reduct}
 
-\citet{Meketon1984} show that $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha = \frac{4}{3}$ for maximally overlapping batches and $\alpha = 2$ for nonoverlapping batches, resulting in the decrease of variance for the maximally overlapping batches estimator.
-\citet{Welch1987} expands this result to variable amounts of overlap, showing that $\alpha$ is twice the value of (\ref{eq:var_reduct_formula}).  
-\citet{damerdji1995mean} shows that convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\alpha \sigma^4_{\xh}$---thus the mean-square consistency of $n_l VD_l$---is guaranteed for $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
-(With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.)
-
-To prove the variance reduction results in our setting, we wish to show that 
+To prove OMRP estimators have asymptotically lower variances compared to the nonoverlapping MRP estimator, we wish to show that 
 $$
-(\tfrac{n_l}{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0,
+(\tfrac{n_l}{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0;
 $$
-for which it suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.
-
-%To prove the variance reduction results in our setting, we wish to show that $\frac{\frac{n_l}{m_l} \var{n_lVG_l}}{\frac{n_l}{m_l} \var{n_lVD_l}} \rightarrow 1$.
-We do this by showing that $({n_l}/{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0$, for which it suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.
-%
-%\begin{theorem} \label{thm:varvar_conv}
-%	Suppose assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures $nVD_l$ converges in mean-square to $\sigma^2_\xh$.
-Then $\dfrac{\frac{n_l}{m_l}\var{nVG_l}}{\frac{n_l}{m_l}\var{nVD_l}} \rightarrow 1$ as $l \rightarrow \infty$.
-%\end{theorem}
+see, e.g., (\ref{eq:varvarred}).
+It suffices to show $\sqrt{{n_l}/{m_l}} \left( n_l VG_l - n_l VD_l \right) \xrightarrow{L^2} 0$, where $\xrightarrow{L^2}$ denotes mean-square convergence.
 
 \begin{theorem} \label{thm:varvar_conv}
-	Suppose assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures  $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \alpha \sigma^4_{\xh}$ where $\alpha$ is the twice the value of (\ref{eq:var_reduct_formula}).
-        Then, $\frac{n_l}{m_l}\var{n_l VG_l} \rightarrow \alpha \sigma^4_{\xh}$ as $l \rightarrow \infty$ with the same $\alpha$. 
+	Suppose assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures  $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ where $\beta_{\gammab}$ is the twice the value of (\ref{eq:var_reduct_formula}).
+        Then, $\frac{n_l}{m_l}\var{n_l VG_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$ with the same $\beta_{\gammab}$. 
 \end{theorem}
@@
 
-Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotic variance reduction results are achieved for the OMRP optimality gap variance estimator. 
-We will empirically examine the variance reduction for small sample sizes in \S \ref{sec:comp}. 
+Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotic lower variances are achieved for the OMRP optimality gap variance estimator relative to its nonoverlapping counterpart MRP.
+A hypothesis of Theorem \ref{thm:varvar_conv} is a batching structure that ensures convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\beta_{\gammab} \sigma^4_{\xh}$, ensuring the mean-square consistency of $n_l VD_l$.
+\citet{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
+With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.
+
+%We will empirically examine the variance reduction for small sample sizes in \S \ref{sec:comp}.
+
 %We end our theoretical properties in the next section by examining the CIs formed using OMRP.

### 2014-07-03 Referee2_Response.tex
More Ref2 responses

--- 2014-06-26 Referee2_Response.tex
@@
 xxx  We agree. 
-We changed the introduction to clearly state the contributions of the paper and \ldots 
+We changed the introduction to clearly state the contributions of the paper and \ldots  and the presentation of the paper significantly improved.  Thank you.
 \medskip
@@
 
+\smallskip
+
 \noindent 
-xxx  We shortened the section on OBM review by combining \ldots 
-\medskip
+To shorten and streamline the OBM review, and to introduce the main results used in the paper, we combined the previous two sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---with other explanations on OBM found later in the paper.
+The combined review appears in the background section, \S 2.1 (Batch Means). 
+To improve readability, we decided to create two subsections: \S 2.1.1 (Nonoverlapping Batch Means) and \S 2.1.2 (Overlapping Batch Means). 
+While we removed a number of equations and shortened the text, we kept some explanations that are necessary for a reader who is not familiar with OBM (e.g., readers with an optimization focus) to follow the main ideas.
+These basic explanations appear, for instance, in the first paragraph of \S 2.1.2 (Overlapping Batch Means).  
+We hope to be able to reach a broader audience this way. 
+As a result of these changes, 
+\begin{itemize}
+	\item[(i)]  instead of former equations (2) and (5), both on overlapping batch means variance estimator, we have only one equation (2);
+
+	\item[(ii)]  the confidence interval estimation using OBM is discussed only once;
+
+	\item[(iii)] the former equation (3) is removed;
+
+	\item[(iv)] the discussion that appeared at the beginning of \S 4.4 (previously: Variance Reduction, now: Asymptotically Lower Variances) is moved to this review section. 
+\end{itemize}
+
+\noi
+With these changes, the OBM review became more streamlined, focusing on the main results used later in the paper. 
+Thank you.
+\bigskip
 
@@
 \noi
-You are right.
+%You are right.
 We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
 We reworded this sentence to reflect this. 
-xxxx  We also \ldots (I think we should write more about our conclusions and our recommendation based on our new findings here) xxxx
+We also went through the paper, removed other occurrences, and avoided using this term in the new text added. 
 \medskip
@@
 Variance parameter. 
-xxx We revised this section to clarify this point. 
+We revised this sentence and added a footnote defining the variance parameter for readers who might not be familiar with this term (e.g., readers with an optimization focus). 
 \medskip
@@
 \noi
-xxx  
+We removed \S 3.1 (Variably Overlapping Batches) from the paper. 
+We merged this section with \S 2.1.2 (Overlapping Batch Means), focusing on the results used in the paper. 
+We believe the presentation of the paper improved as a result. 
+Thank you for this suggestion. 
 \medskip
@@
 \noi
-xxx  
+We changed this sentence and directly referred to the denominator term.
+We decided to avoid the degrees of freedom here. 
+This is because we wanted to focus on the degrees of freedom for confidence interval construction, which is discussed in both the theoretical and computational results.\smallskip
+
+\noi 
+{\it Note:} This section has been restructured based on your comments. 
+Equation (2) now gives the general overlapping variance estimator with the parametrized amount of overlap. 
 \medskip
@@
 \noi
-Yes; we now explicitly state this in a sentence after we introduce $\gamma$. 
+Yes; we explicitly stated this in a sentence after we introduce $\gamma$.\smallskip
+
+\noi 
+{\it Note:} This sentence now appears in Section 2.1.2 (Overlapping Batch Means). 
 \medskip
@@
 Done. 
-We introduced the floor function before its first use and similarly, we introduced the ceiling function before its first use. 
+%We introduced the floor function before its first use, and we introduced the ceiling function right after its first use.
+\smallskip
+
+\noi 
+{\it Note:} Both definitions appear in Section 2.1.2 (Overlapping Batch Means).
 \medskip
@@
 \noi
-xxx  
+Reworded.\smallskip
+
+\noi 
+{\it Note:} This sentence now appears in Section 2.1.2 (Overlapping Batch Means). 
 \medskip
@@
 \noi
-xxx  
+You are right. 
+We moved these references---in particular, Damerdji (1994, 1995)---to Section 2.1.2 (Overlapping Batch Means) and added a brief discussion.  
 \medskip
@@
 In fact, we now use brackets for all the expectations in the paper to improve clarity. 
-Thank you for this suggestion. 
+Thank you.
 \medskip
@@
 \begin{itemize}
-\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet? 
-In any case, some of the verbiage in this paragraph is a bit repetitive.}
+\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet?}
 \end{itemize}
@@
 xxx 
+This notation was defined before Theorem 1. 
+We moved the definition of $\sigma_{\hat{x}}$ and $\mu_{\hat{x}}$ to \ldots to improve clarity. 
+\medskip
+
+\begin{itemize}
+\item[] \textit{In any case, some of the verbiage in this paragraph is a bit repetitive.}
+\end{itemize}
+
+\noi
+We moved the discussion at the first half of this paragraph to the new, combined OBM review in \S 2.1.2 (Overlapping Batch Means). 
+We referred to equation (3) here to remind the readers the basis of the proof.
+The second half of this paragraph deals with the batching structure, and this discussion is moved to the paragraph after the theorem's proof. 
 \medskip

### 2014-07-03 omrp_lb_rev.tex
More Ref2 responses

@@
 Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
-In this paper, we consider variable amounts of overlap and examine this both theoretically and empirically. 
+In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
 % THIS LAST SENTENCE NEEDS TO CHANGE!
@@
 
-The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $0\leq \gamma< m$, relative its nonoverlapping counterpart 
+The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $0\leq \gamma< m$ relative its nonoverlapping counterpart 
 %$\var{\vtm{\ybb}}$ 
@@
 \begin{equation} \label{eq:var_reduct_formula}
-	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right).
+	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right),
 \end{equation}
+where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument.
 If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
@@
 That is, if observation $\xiti$ is used in $|B(i)|$ number of batches, all the optimal solutions $\xs_j$ corresponding to each batch $j \in B(i)$ are used for the lower bound estimator.  
-Then, $VG_l$ is defined in a similar fashion for the variably overlapping batches variance estimator (\ref{eq:variance_gamma}).
+Then, $VG_l$ is defined in a similar fashion for the overlapping batches variance estimator (\ref{eq:variance_gamma}).
 
@@
 \end{align}
-These are essentially the same as the variably overlapping batches estimators in \S \ref{ssec:overlap} with $y^i = f(\xh,\xiti) - f(\xs,\xiti)$.  
+These are essentially the same as the overlapping batches estimators in \S \ref{ssec:overlap} with $y^i = f(\xh,\xiti) - f(\xs,\xiti)$.  
 These are also defined identically to the original estimators (\ref{eq:gbar})--(\ref{eq:vg}) with the exception that $\xs_j$ from (\ref{eq:gbar}) and (\ref{eq:gbb}) is replaced by an optimal solution $\xs$ in (\ref{eq:dbar}) and (\ref{eq:dbb}).
-With $\xh$ and $\xs$ fixed, estimators (\ref{eq:dbar})--(\ref{eq:vd}) have the same statistical properties as variably overlapping batches estimators in \S \ref{ssec:overlap}.  
+With $\xh$ and $\xs$ fixed, estimators (\ref{eq:dbar})--(\ref{eq:vd}) have the same statistical properties as overlapping batches estimators in \S \ref{ssec:overlap}.  
 The optimal solution $\xs$ is not known; however, the estimators (\ref{eq:dbar})--(\ref{eq:vd}) are used only to show convergence of (\ref{eq:gbar})--(\ref{eq:vg}) and not necessary for carrying out the OMRP algorithm.

### 2014-07-05 Referee1_Response.tex
Various changes
1. Updated the conclusions,
2. Restructured Comp. Efficiency section, and
3. Updated the captions in Comp. Efficiency Section
4. Updated Ref1 and Ref2 responses

@@
 \newcommand{\noi}{\noindent}
+
+% Definitions for overlapping batches
+\newcommand{\gb}{\bar{G}}
+\newcommand{\gbb}{\bar{\gb}}
+\newcommand{\db}{\bar{D}}
+\newcommand{\dbb}{\bar{\db}}
 
@@
 For example, do the consistency and asymptotic validity results that follow hinge on this choice?
-Or, do those results also hold for other choices, like forming $\bar\bar{G}$ as a sample
-mean of the underlying $\bar{G}$ values. 
-We know that the individual gap estimators in (7) are nonnegative, and if we formed $\bar\bar{G}$ as a sample mean of $\bar{G}$ values, it would be nonnegative. 
-Is the $\bar\bar{G}$, as specified in (8), nonnegative? 
+Or, do those results also hold for other choices, like forming $\gbb$ as a sample
+mean of the underlying $\gb$ values. 
+We know that the individual gap estimators in (7) are nonnegative, and if we formed $\gbb$ as a sample mean of $\gb$ values, it would be nonnegative. 
+Is the $\gbb$, as specified in (8), nonnegative? 
 Have the authors computationally explored other choices here? 
@@
 \noi
-xxxx  Need to discuss. 
-I know I changed this but I don't remember why at this point. 
-Some theory was incorrect but at that time, we had more relaxed conditions. 
-Now we have exponential rates of convergence and it seems to me like anything here should be fine. 
-I haven't checked but pretty sure. 
-So, yes, why don't we use something else? 
-When we did, the results weren't that different at all. 
-Right?\ \ \ \ 
-xxxxx
+You are right; we did not clearly motivate this choice of $\gbb$.  
+We added explanations after the definition of the OMRP estimators, motivating this choice and relating it to the theoretical results presented in the paper.\smallskip
+
+\noi 
+As you pointed out for the upper bound in (8), this $\gbb$ was chosen for each observation to have equal weight when the sampling problems yield optimal solutions $x_j^* = x^*, \ \forall j$. 
+This fact is used in Lemmas 1 and 2, which are then used---directly or indirectly---in proving Theorems 1--3. 
+When the alternative $\gbb$, formed as a sample mean of $\gb$ values, is used, theoretical results presented in the paper can be recovered by appropriately adjusting the coefficients of the $\dbb$ terms.
+Notice that these results establish convergence of  $\gbb$, $VG$, etc.\ to their nonoptimized counterparts $\dbb$, $VD$, etc.
+When the coefficients of $\dbb$ are adjusted, however, $\dbb$ and $VD$ are {\it not exactly} the same as the overlapping estimators of simulation output analysis. 
+Because our results depend on the asymptotic properties of the overlapping estimators already established in the simulation literature, we did not want to make any changes. 
+It may be possible to recover the same results but we did not pursue it here. 
+We actually performed computations using $\gbb$ formed as a sample mean of $\gb$ values and the results were essentially the same. 
+However, due to subtle theoretical reasons explained above, we decided not to include or discuss this choice. 
 \medskip
@@
 Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
-This guidance appears in the third and last paragraphs of the new section, \S 5.4 (Computational Efficiency).
+This guidance appears in the last paragraph of \S 5.4 (Computational Efficiency).
 

### 2014-07-05 Referee2_Response.tex
Various changes
1. Updated the conclusions,
2. Restructured Comp. Efficiency section, and
3. Updated the captions in Comp. Efficiency Section
4. Updated Ref1 and Ref2 responses

@@
 \noindent 
-To shorten and streamline the OBM review, and to introduce the main results used in the paper, we combined the previous two sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---with other explanations on OBM found later in the paper.
-The combined review appears in the background section, \S 2.1 (Batch Means). 
-To improve readability, we decided to create two subsections: \S 2.1.1 (Nonoverlapping Batch Means) and \S 2.1.2 (Overlapping Batch Means). 
+We shortened and streamlined the OBM review, introducing the main results used in the paper, by combining the previous two sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---along with other explanations on OBM that appeared later in the paper.
+The combined review is in the background section, \S 2.1 (Batch Means). 
+To improve readability, we created two subsections: \S 2.1.1 (Nonoverlapping Batch Means) and \S 2.1.2 (Overlapping Batch Means). 
 While we removed a number of equations and shortened the text, we kept some explanations that are necessary for a reader who is not familiar with OBM (e.g., readers with an optimization focus) to follow the main ideas.
@@
 
-	\item[(iv)] the discussion that appeared at the beginning of \S 4.4 (previously: Variance Reduction, now: Asymptotically Lower Variances) is moved to this review section. 
+	\item[(iv)] the discussion that appeared at the beginning of \S 4.4 (previously: Variance Reduction, now: Lower Variances) is moved to this review section.\medskip
+
+{\it Note:} While making the changes, we realized that `$\alpha$' was used in the current equation (3) and the statement of Theorem 2 as well as the ($1-\alpha$)-level confidence intervals.  
+Therefore, we changed `$\alpha$' in equation (3) and Theorem 2 to `$\beta_{\bar{\gamma}}$'. 
 \end{itemize}
@@
 With these changes, the OBM review became more streamlined, focusing on the main results used later in the paper. 
-Thank you.
+Thank you for this suggestion.
+
 \bigskip

### 2014-07-05 omrp_lb_rev.tex
Various changes
1. Updated the conclusions,
2. Restructured Comp. Efficiency section, and
3. Updated the captions in Comp. Efficiency Section
4. Updated Ref1 and Ref2 responses

@@
 As the amount of overlap decreases, the variance increases. 
-When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/4$), for instance, the variance is 75\% of the nonoverlapping counterpart.
+When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/2$), for instance, the variance is 75\% of the nonoverlapping counterpart.
 
-A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gamma}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gamma}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
-If $\ogb$ is an integer, $d_{\gamma} = \frac{3}{2+\gammab^2}$.  For the maximally-overlapping batch means, the degrees of freedom is $d_{\gamma} = \frac{3}{2}$.
+A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gammab}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gammab}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
+%If $\ogb$ is an integer, $d_{\gammab} = \frac{3}{2+\gammab^2}$.  
+For the maximally-overlapping batch means, the degrees of freedom is $d_{\gammab} = \frac{3}{2}$.
 
@@
 These are essentially the same as the overlapping batches estimators in \S \ref{ssec:overlap} with $y^i = f(\xh,\xiti) - f(\xs,\xiti)$.  
-These are also defined identically to the original estimators (\ref{eq:gbar})--(\ref{eq:vg}) with the exception that $\xs_j$ from (\ref{eq:gbar}) and (\ref{eq:gbb}) is replaced by an optimal solution $\xs$ in (\ref{eq:dbar}) and (\ref{eq:dbb}).
+These are also defined identically to the original estimators (\ref{eq:gbar})--(\ref{eq:vg}) with the exception that $\xs_j$ from (\ref{eq:gbar}) and (\ref{eq:gbb}) is replaced by the optimal solution $\xs$ in (\ref{eq:dbar}) and (\ref{eq:dbb}).
 With $\xh$ and $\xs$ fixed, estimators (\ref{eq:dbar})--(\ref{eq:vd}) have the same statistical properties as overlapping batches estimators in \S \ref{ssec:overlap}.  
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Computational Efficiency}
@@
 
-\begin{figure}[htb!]
+The increased computational workload from solving overlapping batches raises the question of the computational efficiency of this method to estimate $VG$.
+In this setting, computational efficiency can be defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computational time spent to generate $VG$ for a given value of $\gammab$.
+Because the variance of the overlapping variance estimator relative to the nonoverlapping (MRP) variant is known from (\ref{eq:var_reduct_formula}), we need only examine the computational time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$.
+Here, $t(\gammab)$ is the average computation time per batch, which is multiplied by the number of batches.
+Warm-starting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
+
+To investigate computational efficiency, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
+Results for various values of $p$ are shown in Figure \ref{fig:efficiency}(a). 
+This figure is constructed using $m = 1,000$, but the results do not change substantially with different values of $m$.
+The graph is also scaled so that nonoverlapping batches produces a computational efficiency of 1. 
+Efficiency gains increase with larger exponent $p$ but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
+At $p=1$, i.e., for problems where computational time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches of \cite{Meketon1984}.
+When $p=0.9$, computational efficiency is maximized at around $\gammab=0.3$.
+When $p$ is $0.71$, on the other hand, computational efficiency is observed for values of $\gammab$ from slightly lower than $0.3$ to $1$, and efficiency is maximized at a relatively flat region between $\gammab=0.5$ and $\gammab=0.8$.
+
+\begin{figure}[thb!]
 	\centering
-	\subfloat[][]{
+	\subfloat[][Theoretical]{
 	   \label{fig:efficiency_theory}
 	   \includegraphics[width=.5\textwidth]{images/comp_efficiency_theory}}
-	\subfloat[][]{
+	\subfloat[][Empirical for NVD]{
 	   \label{fig:efficiency_nv}
@@
 		\caption{
-		Theoretical computational efficiency results for overlapping batches (left) and a comparison with measured computational efficiency for the Newsvendor problem using insertion sort (right).
-		Both graphs are scaled so that nonoverlapping batches produces a computational efficiency of 1.
+		Computational efficiency of the OMRP variance estimator relative to the (nonoverlaping) MRP variance estimator measured
+		(a) theoretically and
+		(b) empirically for NVD using insertion sort
+%		(graphs are scaled so that nonoverlapping batches produces a computational efficiency of 1)
 		}
@@
 \end{figure}
-
-The increased computational workload from solving overlapping batches raises the question of the computational efficiency of this method to estimate $VG$.
-In this setting, computational efficiency is defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computational time spent to generate $VG$ for a given value of $\gammab$.
-Because the variance of overlapping estimator relative to the nonoverlapping (MRP) variant is known from (\ref{eq:var_reduct_formula}), we need only examine the computational time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$, where $t(\gammab)$ is the average computation time per batch, multiplied by the number of batches.
-Warm-starting an algorithm may be used to decrease the computation time per batch $t(\gammab)$ for $\gammab < 1$, leading to a possible increase in computational efficiency.
-
-To investigate computational efficiency, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
-Results for various values of $p$ are shown in Figure \ref{fig:efficiency_theory}. 
-This figure is constructed using $m = 1000$, but the results do not change substantially with different values of $m$.
-Efficiency gains increase with larger exponent $p$, but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
-At $p=1$, i.e., for problems where computational time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches of \cite{Meketon1984}.
-When $p$ is $0.71$, on the other hand, computational efficiency is observed for values of $\gammab$ from slightly lower than $0.3$ to $1$, and efficiency is maximized at a relatively flat region between $\gammab=0.5$ and $\gammab=0.8$.
 
@@
 We tested this theoretical relationship using the newsvendor problem solved with insertion sort.
-Insertion sort is an efficient sorting algorithm when the values are already almost sorted. 
+Insertion sort is an efficient algorithm when the values are already largely sorted. 
 Therefore, as overlapping increases, insertion sort results in a decreased solution time per batch for the NVD problem. 
-To test computational efficiency, we used $m = 1000$ with $10,000$ replications.
-The average computation time per batch was found empirically to be well approximated ($R^2 = 0.994$) by power law with $p = 0.71$.
-The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}, where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency_theory}.
+To test computational efficiency, we used $m = 1,000$ with $10,000$ runs.
+The average computation time per batch was found empirically to be well approximated ($R^2 = 0.994$) by the power law with $p = 0.71$.
+The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency}(b), where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency}(a).
 It appears that empirical observations match with the theoretical efficiency calculations well.
+
+Another related question on computational efficiency would be whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
+When generating observations is cheap, one could alternatively increase the number of batches in MRP to obtain estimators with lower variances. 
+In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$; so, decreasing $\var{VG}$ to the level of maximally overlapping batches of \cite{Meketon1984} requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
+Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison}. 
+This curve shows the increase in computational effort due to an increased number of batches in MRP in order to obtain the same variance for OMRP across $\gammab$.
+If the work increase by OMRP is less than this solid black curve, then OMRP is computationally more efficient than increasing the number of batches in MRP. 
+Again, assuming average computation time per batch can be represented as $T(\gammab) \propto \gammab^p$, Figure \ref{fig:comp_work_comparison}(a) compares the increase in computational work for OMRP for several values of $p$ to the work increase for MRP to get an equivalent decrease in variance.
+We again see that OMRP is advantageous for larger values of $p$.
+For small values of $p$, some efficiency gain is observed at $\gammab$ values close to 1.
+We again tested this empirically on NVD using insertion sort with $m=1,000$, average of $10,000$ independent runs. 
+The results, shown in Figure \ref{fig:comp_work_comparison}(b), again appear to match the theory well.
+
+\begin{figure}[htb!]
+	\centering
+	\subfloat[][Theoretical]{
+	   \label{fig:comp_work_comparison_theory}
+	   \includegraphics[width=.5\textwidth]{images/work_comparison}}
+	\subfloat[][Empirical for NVD]{
+	   \label{fig:comp_work_comparison_nv}
+	   \includegraphics[width=.5\textwidth]{images/nv_work_comparison}}
+		\caption{
+		Comparison of computational work required to get equivalent variance between MRP variance estimator with increased number of batches and OMRP variance estimator measured
+		(a) theoretically and 
+		(b) empirically for NVD using insertion sort
+%		(Left) A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
+%		(Right) Measured computational work for NVD compared with the theoretical results.
+		}
+\label{fig:comp_work_comparison}
+\end{figure}
 
@@
 This choice keeps efficiency high while decreasing computation time and preventing large decreases in efficiency in the event that $p$ was overestimated.
-For example, in the case of NVD, we recommend the use of value $\gammab=0.8$ as this value provides a high computational efficiency with minimal overall computation time across values of $\gammab$ with high efficiency.
-
-\begin{figure}[htb!]
-	\centering
-	\subfloat[][]{
-	   \label{fig:comp_work_comparison_theory}
-	   \includegraphics[width=.5\textwidth]{images/work_comparison}}
-	\subfloat[][]{
-	   \label{fig:comp_work_comparison_nv}
-	   \includegraphics[width=.5\textwidth]{images/nv_work_comparison}}
-		\caption{
-		(Left) A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
-		(Right) Measured computational work for NVD compared with the theoretical results.
-		}
-\label{fig:comp_work_comparison}
-\end{figure}
-
-A final question on computational efficiency would be whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
-When generating observations is cheap, one could potentially increase the number of batches in MRP to obtain estimators with lower variances. 
-In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$, so decreasing $\var{VG}$ to the level of maximally overlapping batches requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
-Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison} using $m=1000$. 
-This curve shows the increase in computational effort due to an increased number of batches in MRP in order to obtain the same variance level for OMRP across $\gammab$.
-If the work increase by OMRP is less than this solid black curve, then OMRP is computationally more efficient than increasing the number of batches in MRP. 
-Again, assuming average computation time per batch can be represented as $T(\gammab) \propto \gammab^p$, Figure \ref{fig:comp_work_comparison} compares the increase in computational work for OMRP for several values of $p$ with the work increase for MRP to get an equivalent decrease in variance.
-We again see that OMRP is advantageous for larger values of $p$.
-For small values of $p$, some efficiency gain is observed at $\gammab$ values close to 1.
-
-With these considerations, for situations where $p > 0$ but its size cannot be readily measured or estimated, we recommend selecting a large value of $\gammab$ such as $0.9$.
+For example, in the case of NVD, we recommend the use of value $\gammab=0.8$ as this value provides high computational efficiency with minimal overall computation time across values of $\gammab$ with high efficiency.
+For situations where $p > 0$ but its size cannot be readily measured or estimated, we recommend selecting a large value of $\gammab$ such as $0.9$.
 This allows for some increase in efficiency while remaining robust in the event that $p$ is smaller than expected.
@@
 We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
-We have provided conditions under which the resulting point estimator of the optimality gap and its associated variance estimator are consistent, the same variance reduction can be achieved, and asymptotically valid CIs can be formed.
+We have provided conditions under which the resulting point estimator of the optimality gap and its associated variance estimator are consistent, the same lower variances of OMRP variance estimators relative to the nononverlapping MRP estimator can be achieved, and asymptotically valid CIs can be formed.
 Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.
+We have examined the computational efficiency of OMRP by jointly considering increases in computation time and decreases in variance. 
+Our results indicate that when warm-starting is effective, efficiency can be observed across a wide range of degree of overlap. 
+When warm-starting is less effective, efficiency is observed for small degrees of overlap. 
+We have demonstrated computational efficiency empirically solving the newsvendor problem with insertion sort.
+Finally, we provided guidelines on selecting the degree of overlap based on our study of computational efficiency.
 

### 2014-07-05 Referee1_Response.tex
Referee 1, Minor Comment 13

@@
 
-\noindent xxx NEED TO CHECK AND CORRECT AS NECESSARY. 
+\noindent 
+This is because the center batches are identically distributed. 
+Therefore, $\mathbb{E}A_j^2$ for all the center batches $j=\lceil \bar{\gamma}^{-1} \rceil, \ldots,n_b - \lceil \bar{\gamma}^{-1} \rceil$ are the same. 
+To make this clear, we introduced the notation $A_j^c$ for center batches and $A_j^f$ and $A_j^e$ for the fringe batches that appear at the front and end of each set of nonoverlapping batches, respectively.
+We also emphasized that each front fringe batch has an identically distributed pair at the end fringes, and that all the center batches are identically distributed. 
+%Thanks for catching this. 
+(Please note that we added brackets to expectations to improve readability as suggested by the other referee.)
 \medskip

### 2014-07-05 Referee2_Response.tex
Referee 1, Minor Comment 13

@@
 \noindent 
-We shortened and streamlined the OBM review, introducing the main results used in the paper, by combining the previous two sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---along with other explanations on OBM that appeared later in the paper.
+We shortened and streamlined the OBM review, focusing on the main results used in the paper, by combining the previous two sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---along with other explanations on OBM that appeared later in the paper.
 The combined review is in the background section, \S 2.1 (Batch Means). 

### 2014-07-05 omrp_lb_rev.tex
Referee 1, Minor Comment 13

@@
 \end{equation}
-as the batch size $m$ and the number of batches $n/m$ tend to infinity. 
+as the batch size $m$ and then the number of batches $n/m$ tend to infinity. 
 In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches, $\beta_0 = \frac{4}{3}$ for maximally overlapping batches, and more generally, $\beta_{\gammab}$ is twice the value of 
@@
         We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the exact same batch structure.  
-        Rewriting to take this into account, letting $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$, and continuing from (\ref{eq:vvar_conv_pf_1}),
+		  The center batches are identically distributed.  
+        Let $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$.
+		  Furthermore, let $A_j^f$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$ denote the fringe batches at the front of each set of nonoverlapping batches, $A_j^c$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots n_b - \left\lceil \gammab^{-1} \right\rceil$ denote the center batches, and let $A_j^e$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$ denote the fringe batches at the end of each set of nonoverlapping batches.
+		  Continuing from (\ref{eq:vvar_conv_pf_1}),
 	\begin{align*}
 		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
-		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left( A_j \right)^2 \
-		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left( A_j \right)^2 \
-		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left( A_j \right)^2 
+		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left( A_j^f \right)^2 \
+		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left( A_j^c \right)^2 \
+		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left( A_j^e \right)^2 
 		} \\
-		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j \right)^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j \right)^2 } \\
-		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j \right)^2 }
-		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j \right)^2 }.
+		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^c \right)^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 } \\
+		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j^c \right)^2 }
+		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 }.
 	\end{align*}	
-	We have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{dt}\right)^2n_b^2 < (2m)^2$.  
-        So each expectation can be bounded by
+	These equalities follow because each front fringe batch $\e{(A_j^f)^2}$ has an identical pair in the end fringe batch $\e{(A_j^e)^2}$ and all center batches have identical values of $\e{(A_j^c)^2}$.
+	As a result, we have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{dt}\right)^2n_b^2 < (2m)^2$.  
+        Removing the notation for fringe or center batch for simplicity, each expectation can be bounded by
 	\begin{align}
@@
 	\begin{align*}
-		\frac{n}{m} 4m^2 \e{\left((\gb_j - \gbb) - (\db_j - \dbb)\right)^4}	& \leq 32 \frac{n}{m} m^2\left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
+		\left(\frac{n}{m} 4m^2\right)^2 \e{\left((\gb_j - \gbb) - (\db_j - \dbb)\right)^4}	& \leq 8 \left( \frac{n}{m} 4m^2\right)^2 \left( \e{(\db_j - \gb_j)^4} + \e{(\dbb - \gbb)^4} \right).
 	\end{align*}	
@@
 
-Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotic lower variances are achieved for the OMRP optimality gap variance estimator relative to its nonoverlapping counterpart MRP.
+Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotically lower variances are achieved for the OMRP optimality gap variance estimator relative to its nonoverlapping counterpart MRP.
+We will empirically examine the variance of OMRP estimator for small sample sizes in \S \ref{sec:comp}. 
 A hypothesis of Theorem \ref{thm:varvar_conv} is a batching structure that ensures convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\beta_{\gammab} \sigma^4_{\xh}$, ensuring the mean-square consistency of $n_l VD_l$.
@@
 With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.
-
-%We will empirically examine the variance reduction for small sample sizes in \S \ref{sec:comp}.
 

### 2014-07-07 Referee1_Response.tex
Moving along
1) Major comment 2 of Ref1
2) Response to Major 1,2 of Ref1
3) Edited response to AE

@@
 \noi 
-Based on your and the associate editor's comments, we studied the computational efficiency of the OMRP estimators. 
-The results of this study are presented in a new section, Section 5.4 (Computational Efficiency).
+Based on your and the associate editor's comments, we studied computational efficiency of the OMRP variance estimators. 
+The results of this study are presented in a new section, \S 5.4 (Computational Efficiency).
 %We studied the computational efficiency of the OMRP estimators, based on your and the associate editor's comments, and provided a summary of our results in a new section, Section 5.4 (Computational Efficiency).
-We first approached efficiency by the reciprocal of variance multiplied by the computation time, per associate editor's suggestion. 
-Maximizing the computational efficiency defined in this manner provided guidelines on selecting the degree of overlap. 
-We then looked at how OMRP compared to increasing the number batches in MRP.
-We examined computational efficiency both theoretically and empirically. 
+We first approached efficiency by the reciprocal of variance multiplied by the computation time, per the associate editor's suggestion. 
+Maximizing computational efficiency defined in this manner provided guidelines on selecting the degree of overlap. 
+We then looked at how OMRP compared to increasing the number batches in MRP to reach an equivalent variance level.
+We examined computational efficiency theoretically, assuming a functional form of the solution time per batch, and also empirically. 
 For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions. 
@@
 We believe the study of computational efficiency significantly improved the paper. 
+(Please also see our response to your minor comment 19 below.)
 \medskip
@@
 \noi
-You are right; we did not clearly motivate this choice of $\gbb$.  
+You are right; we did not fully motivate this choice of $\gbb$.  
 We added explanations after the definition of the OMRP estimators, motivating this choice and relating it to the theoretical results presented in the paper.\smallskip
@@
 This fact is used in Lemmas 1 and 2, which are then used---directly or indirectly---in proving Theorems 1--3. 
-When the alternative $\gbb$, formed as a sample mean of $\gb$ values, is used, theoretical results presented in the paper can be recovered by appropriately adjusting the coefficients of the $\dbb$ terms.
-Notice that these results establish convergence of  $\gbb$, $VG$, etc.\ to their nonoptimized counterparts $\dbb$, $VD$, etc.
+When the alternative $\gbb$, formed as a sample mean of $\gb$ values, is used, 
+a subset of the theoretical results can be established (e.g., $\gbb$ converges almost surely to $\mu_{\hat{x}}$). 
+However, we had difficulty establishing the same asymptotically lower variances for the new $VG$. 
+An alternative is to concurrently adjust the coefficients of the $\dbb$ terms to establish convergence of the new $\gbb$, $VG$, etc.\ to their nonoptimized counterparts $\dbb$, $VD$, etc.
 When the coefficients of $\dbb$ are adjusted, however, $\dbb$ and $VD$ are {\it not exactly} the same as the overlapping estimators of simulation output analysis. 
-Because our results depend on the asymptotic properties of the overlapping estimators already established in the simulation literature, we did not want to make any changes. 
-It may be possible to recover the same results but we did not pursue it here. 
-We actually performed computations using $\gbb$ formed as a sample mean of $\gb$ values and the results were essentially the same. 
-However, due to subtle theoretical reasons explained above, we decided not to include or discuss this choice. 
+Because our results depend on the asymptotic properties of the overlapping estimators already established in the simulation literature, we did not want to make any changes to $\dbb$. 
+It may be still be possible to recover the same results using this alternative  $\dbb$ but we did not pursue it here. 
+%We actually performed computations using $\gbb$ formed as a sample mean of $\gb$ values and the results were largely similar. 
+Due to the lack of theoretical results explained above, we decided not to include or discuss $\gbb$ formed as a sample mean of $\gb$ values, even though it appears a natural choice. 
+Instead, we expanded the text motivating the current choice of $\gbb$. 
 \medskip
@@
 This is because the center batches are identically distributed. 
-Therefore, $\mathbb{E}A_j^2$ for all the center batches $j=\lceil \bar{\gamma}^{-1} \rceil, \ldots,n_b - \lceil \bar{\gamma}^{-1} \rceil$ are the same. 
+As a result, $\mathbb{E}A_j^2$ for all the center batches $j=\lceil \bar{\gamma}^{-1} \rceil, \ldots,n_b - \lceil \bar{\gamma}^{-1} \rceil$ are the same. 
 To make this clear, we introduced the notation $A_j^c$ for center batches and $A_j^f$ and $A_j^e$ for the fringe batches that appear at the front and end of each set of nonoverlapping batches, respectively.
@@
 %Thanks for catching this. 
-(Please note that we added brackets to expectations to improve readability as suggested by the other referee.)
+\smallskip
+
+\noi 
+{\it Note:} We added brackets to expectations to improve readability as suggested by the other referee.
 \medskip
@@
 
-\noindent Thank you for pointing this out.  
+\noindent Thank you for pointing this out and for your careful review.  
 We removed this statement from the proof of Theorem 3 and added it as a remark to the paragraph after the theorem.

### 2014-07-07 AE_Reponse.tex
Moving along
1) Major comment 2 of Ref1
2) Response to Major 1,2 of Ref1
3) Edited response to AE

@@
 Thank you for this suggestion. 
-It is indeed important to study computational efficiency in this context. 
-We created a new section, Section 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
+It is important to study computational efficiency in this context. 
+We created a new section, \S 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
 When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
@@
 Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
-We illustrated this method on the newsvendor problem using insertion sort. 
-Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping.
-We discussed guidelines on selecting the degree of overlapping. 
 \medskip
 
-In addition, based on the comments of Referee 1, we studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances.
-Our results indicate that when warm-starting is effective, overlapping is computationally more efficient than increasing the number of batches of MRP.
-Even in cases where warm-starting is less effective, computational efficiency can be observed when about 10\% of observations are overlapped.
-We again illustrated this result on the newsvendor problem. 
+In addition, based on the comments of Referee 1, we studied efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances. 
+Our results indicate that when warm-starting is effective, overlapping is computationally more efficient.
+Even in cases where the effectiveness of warm-starting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\medskip
+
+We illustrated these results on the newsvendor problem using insertion sort. 
+Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping by maximizing efficiency.
+Based on our study, we provided guidelines on selecting the degree of overlapping at the end of \S 5.4 (Computational Efficiency). 
+\medskip
+
 We believe the paper has improved as a result of the study of computational efficiency. 
-Thank you. 
+Thank you for this suggestion. 
 \medskip
@@
 
-\noi xxx 
-Based on your other comments and suggestions of the referees, we provided information on computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming.
-These are detailed in Section 5.4 (Computational Efficiency). 
+\noi 
+We established improved computational efficiency on the newsvendor problem.
+A study of computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming is provided in the new \S 5.4 (Computational Efficiency), based on your and the referee's comments.
 (Please see our response to the previous comment.)
-We also changed Section 1 (Introduction) and Section 6 (Conclusions) to clearly motivate the study and usefulness of the results.
+\medskip
+
+xxx 
+We also changed Section 1 (Introduction) to clearly motivate the study and argue usefulness of the results, paying specific attention to efficiency gains.
+Finally, we updated Section 6 (Conclusions) to summarize these new results, again paying attention to computational efficiency.
 

### 2014-07-07 omrp_lb_rev.tex
Moving along
1) Major comment 2 of Ref1
2) Response to Major 1,2 of Ref1
3) Edited response to AE

@@
 Then, $VG_l$ is defined in a similar fashion for the overlapping batches variance estimator (\ref{eq:variance_gamma}).
+
+The motivation behind forming $\gbb_l$ by taking into account $B(i)$ is to give each observation $\xit^i$ equal weight. 
+This is because we want to be as close to a standard overall mean estimator (e.g., $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^i$) as possible.
+With this definition of $\gbb_l$, when $\xs_j= \xs$ for all $j= 1, 2, \dots, \nbl$, we have $\gbb_l$ equal to its nonoptimized counterpart given in (\ref{eq:dbb}). 
+This fact is key in establishing the theoretical results presented in the next section. 
+We note, however, that this choice of $\gbb_l$ may not be guaranteed to be non-negative.
+In that case, $\max\{\gbb_l,0\}$ can be used in practice. 
+In our computational results, however, we did not observe any negative values of $\gbb_l$.
 

### 2014-07-08 Referee1_Response.tex
Referee 1, Major Comment 2

@@
 Because our results depend on the asymptotic properties of the overlapping estimators already established in the simulation literature, we did not want to make any changes to $\dbb$. 
-It may be still be possible to recover the same results using this alternative  $\dbb$ but we did not pursue it here. 
+It may be still be possible to recover the same results on overlapping using this alternative  $\dbb$ but we did not pursue it here. 
 %We actually performed computations using $\gbb$ formed as a sample mean of $\gb$ values and the results were largely similar. 
-Due to the lack of theoretical results explained above, we decided not to include or discuss $\gbb$ formed as a sample mean of $\gb$ values, even though it appears a natural choice. 
+Due to the lack of theoretical results explained above, we decided not to include or discuss $\gbb$ formed as a sample mean of $\gb$ values, even though it appears as a natural choice. 
 Instead, we expanded the text motivating the current choice of $\gbb$. 
+Based on your comments, we also expanded the text regarding the nonnegativity of $\gbb$. 
+Thank you for your insightful comments. 
 \medskip
@@
 \noindent 
-Thank you for this suggestion. 
 Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
 This guidance appears in the last paragraph of \S 5.4 (Computational Efficiency). 
+Thank you for this suggestion.
 

### 2014-07-08 omrp_lb_rev.tex
Referee 1, Major Comment 2

--- 2014-07-05 omrp_lb_rev.tex
@@
 
-The results on overlapping batch means like (\ref{eq:varvarred}) occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
+The results on overlapping batch means, discussed in Section \ref{ssec:overlap}, occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
 Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
@@
 Then, $VG_l$ is defined in a similar fashion for the overlapping batches variance estimator (\ref{eq:variance_gamma}).
+
+The motivation behind forming $\gbb_l$ by taking into account $B(i)$ is to give each observation $\xit^i$ equal weight. 
+This is because we want to be as close to a standard mean estimator (e.g., $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^i$) as possible.
+With this definition of $\gbb_l$, when $\xs_j= \xs$ for all $j= 1, 2, \dots, \nbl$, we have $\gbb_l$ equal to its nonoptimized counterpart given in (\ref{eq:dbb}), which is the standard mean estimator.
+This fact is key in establishing the theoretical results presented in the next section. 
+We note, however, that this choice of $\gbb_l$ may not be guaranteed to be nonnegative.
+In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping.
+%In our computational results, however, we did not observe any negative values of $\gbb_l$.
 

### 2014-07-09 Referee1_Response.tex
Major rewrite of Introduction
1) Wrote a motivation paragraph
2) Wrote a list of contributions
3) Wrote differences of this paper compared to WSC version
4) Moved a paragraph from Intro to Overlapping Batch Means section and
edited that paragraph
5) Changed Referee 1 response accordingly
6) Added a reference
7) Some other minor minor changes

@@
 
-\noi xxx 
-We thank the referee for this suggestion. 
+\noi
+%We thank the referee for this suggestion. 
+Thank you for this suggestion. 
 You are right.
@@
 We specifically added this as a motivation. 
+The motivation now appears in the first full paragraph on page 4 of the paper. 
 \medskip
@@
 \noi 
-Based on your and the associate editor's comments, we studied computational efficiency of the OMRP variance estimators. 
+We studied computational efficiency of the OMRP variance estimators and demonstrated efficiency on the newsvendor problem using insertion sort. 
 The results of this study are presented in a new section, \S 5.4 (Computational Efficiency).
@@
 We examined computational efficiency theoretically, assuming a functional form of the solution time per batch, and also empirically. 
-For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions. 
+For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions; thank you. 
 We found that when effective warm-starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
-All these results are presented in Section 5.4 (Computational Efficiency). 
-Thank you for this suggestion. 
+%All these results are presented in Section 5.4 (Computational Efficiency). 
+%Thank you for this suggestion. 
 We believe the study of computational efficiency significantly improved the paper. 
-(Please also see our response to your minor comment 19 below.)
+Thank you.\smallskip
+
+\noi
+{\it Note:} Please also see our response to your minor comment 19 below.
 \medskip
@@
 Done. 
-%Please note that this sentence has been changed slightly based on the comments of the other referee. 
+\smallskip
+
+\noi 
+{\it Note:} This sentence now appears in the second paragraph of Section 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
 \medskip
@@
 \noindent 
-We reworded this sentence to read as ``Partial overlapping results in a smaller number of batches; hence, fewer optimization \ldots '' based on the comments of the other referee.
+We removed this sentence and replaced it with a shorter one in order to improve exposition. 
+We used `smaller number of batches' based on the comments of the other referee in the new sentence. 
+\smallskip
+
+\noi 
+{\it Note:} This section now appears in the second paragraph of Section 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
 \medskip
@@
 Done.
-% This sentence might be deleted or changed to the denominator term, etc. CHECK! 
+
+XXXX Denominator term makes!  I think it changed to denominator term. CHECK XXXX
 \medskip

### 2014-07-09 omrp_lb_rev.tex
Major rewrite of Introduction
1) Wrote a motivation paragraph
2) Wrote a list of contributions
3) Wrote differences of this paper compared to WSC version
4) Moved a paragraph from Intro to Overlapping Batch Means section and
edited that paragraph
5) Changed Referee 1 response accordingly
6) Added a reference
7) Some other minor minor changes

@@
 To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
-In this paper we show that the same benefits can be obtained from overlapping batches when used in a stochastic optimization setting.
+In this paper, we show that the same benefits of nearly the same bias and lower variances relative to nonoverlapped counterparts can be obtained from overlapping batches when used in a stochastic optimization setting.
 
@@
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
-In this paper, we formulate an overlapping batches version of MRP, allowing for partial overlap, and provide conditions under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
-We also show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
-We also present computational results to examine small-sample behavior. 
-Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.
+In this paper, we formulate an overlapping batches version of MRP with a parametrized degree of overlap.
+%, and present theoretical and computational results.
 
@@
 where $\x$ is a vector of decision variables, $\xit$ is a vector of random variables, and $X$ is the feasible set, which consists of only deterministic constraints. 
-There are no stochastic constraints such as probabilistic or expected-value constraints. 
+We assume (\ref{eq:sto_prog}) has no stochastic constraints such as probabilistic or expected-value constraints. 
 Further, it is assumed that the distribution of $\xit$ is known and that we can sample from it.
@@
 The lower the optimality gap, the higher the quality of the solution; and a zero optimality gap implies that the solution is optimal. 
-We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout this paper.
+We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout the paper.
 
@@
 Our aim is to apply the idea of overlapping batches to MRP.  
-Overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
+The motivation behind using overlapping in this context is twofolds. 
+First, overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
 %Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
-We note several differences in this setting compared to the classical simulation setting.  
-In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
-We are interested in estimating the variance of an optimality gap estimator.  
-An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
-Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
-%For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
-%Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
-We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{sec:theory}).  
-The nonoptimized counterparts are (regular) overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions.
-We establish convergence of the optimality gap estimators that use overlapping to their nonoptimized counterparts. 
-Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.
-In this setting, due to the need to solve a sampling problem (SP$_m$), the computational effort may increase with data reuse.  
-This can be alleviated in two ways. 
-First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
-Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
-Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
-In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
-% THIS LAST SENTENCE NEEDS TO CHANGE!
+Second, in some cases, generating the realizations $\xit^1, \xit^2, \dots$ to form sampling approximations of (\ref{eq:sto_prog}) can be computationally expensive and overlapping makes the most of the generated observations.
+
+%The following are four specific contributions of this article. 
+The contributions of this article are as follows. 
+\begin{itemize}
+\item[(i)] We formulate an overlapping batch means variant of MRP, where the degree of overlap can be chosen by the user. 
+%This paper applies OBM to assessing solution quality in stochastic optimization. 
+%Specifically, an overlapping batch means variant of MRP is formulated, where the degree of overlap can be chosen by the user. 
+This application of OBM is novel because each batch mean estimator includes an internal minimization, which has not been studied in the literature.
+%\vspace*{-0.1in}
+
+\item[(ii)] We provide conditions under which the resulting optimality gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
+We show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
+These results require new proofs because of the presence of the optimization operator.
+
+\item[(iii)] We  present computational results to examine small-sample behavior. 
+Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.
+
+\item[(iv)] As the degree of overlap increases, the number of batches and optimization problems solved increases because we need to solve a sampling problem per batch. 
+At the same time, variances of the estimators are lowered, and when warm starting is available, solution time per batch can decrease, resulting in efficiency gains. 
+We explore the trade-off between computation time and lower variances.
+% and efficiency gains. 
+%We explore the overall computation time versus lower variances and efficiency gains trade-off. 
+We provide guidelines on selecting the degree of overlap based on computational efficiency and demonstrate efficiency on a newsvendor problem. 
+\end{itemize}
+
+An earlier version of the paper appeared in \citep{love2011overlapping}. 
+This paper contains a number of additional results. 
+% compared to its earlier conference proceedings version. 
+Most of the theoretical results are new, including asymptotically lower variances of the overlapping estimators, asymptotic validity of the interval estimators, and the {\it almost sure} convergence of the variance estimator.
+These results are achieved through an assumption on the fast rate of convergence of the sampling problem's solution to the unique optimal solution, which is satisfied by several classes of (\ref{eq:sto_prog}); see \S \ref{subsec:assumptions}.
+We also present additional computational results, including those from a large-scale problem, and study computational efficiency of the overlapping MRP method.
+
+The rest of the paper is organized as follows.  
+In the next section, we review relevant background information.  
+We first discuss nonoverlapping and overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
+In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
+In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP CIs, and establish that the OMRP variance estimators have lower variances than their nonoverlapping MRP counterparts.
+In \S \ref{sec:comp}, we test the performance of OMRP on four problems and study computational efficiency. 
+We end in \S \ref{sec:concl} with a summary and conclusions.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   %    %    %    %    %    %
-
-The rest of the paper is organized as follows.  
-In the next section, we review relevant background information.  
-We first discuss overlapping batch means in \S \ref{ssec:obm} and then briefly go over MRP in \S \ref{ssec:mrp}.  
-In \S \ref{sec:omrp}, we present the Overlapping Multiple Replications Procedure (OMRP) with a parametrized degree of overlap.  
-In \S \ref{sec:theory}, we show strong consistency of the OMRP point estimators, asymptotic validity of the OMRP CIs, and that the OMRP variance estimators have lower variances than their nonoverlapping counterparts---the MRP estimators.
-In \S \ref{sec:comp}, we test the performance of OMRP on four problems and end in \S \ref{sec:concl} with a summary and conclusions.
 
@@
 This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
+%
 The overlapping batch means 
@@
 are no longer independent. 
-However, by simply reusing the data in this fashion---and seemingly in a contradictory way that induces dependence---one obtains a better variance estimator. 
+However, by simply reusing the data in this fashion one obtains a better variance estimator. 
 That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
@@
 \cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally-overlapping cases. 
-Under appropriate conditions, these results, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
+Under appropriate conditions, the results of \cite{damerdji1995mean}, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
 \begin{equation}
@@
 Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI.
-See also \citep{bayraksan_morton_09,partani2006jackknife,partani_07} for variations of MRP aimed to reduce bias and variance.
+This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI; see also \citep{stockbridge_bayraksan_13}.
+The papers \citep{bayraksan_morton_09,partani2006jackknife,partani_07} discuss variations of MRP aimed to reduce bias and variance.
 
@@
 
-In order to apply overlapping batches to MRP, we need to keep track of solutions to sampling problems (SP$_m$) for each batch of size $m$.  
-Toward this end, let $B(i)$ denote the set of batches $j \in \left\{1, 2, \dots, \nb \right\}$ observation $\xiti$ is used in, $i = 1, 2, \dots, n$.  
-See Figure \ref{fig:overlap_nonint} for an example with $n=18$, $m = 6$, and $\gamma = 2$.  
-Here, the first batch uses observations $\xit^1, \xit^2, \xit^3, \xit^4, \xit^5, \xit^6$, the second batch uses $\xit^3, \xit^4, \xit^5, \xit^6, \xit^7, \xit^8$, and so on.  
-So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  
-As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch; $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
+We wish to apply overlapping batch means to MRP. 
+We begin by discussing several differences in this setting compared to the classical simulation setting.  
+In simulation output analysis, the point of interest is that of estimating the variance of the sample mean of a covariance stationary process.  
+We are interested in estimating the variance of an optimality gap estimator.  
+An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
+Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
+%For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
+%Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
+We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{subsec:nonO}).  
+The nonoptimized counterparts are regular overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions.
+We establish convergence of OMRP estimators to their nonoptimized counterparts (see \S \ref{subsec:conv}--\ref{ssec:validity}); 
+thereby establishing the benefits of overlapping in this context.
 
-\begin{figure}[htb!]
+Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.
+In this setting, the computational effort may increase with data reuse because we need to solve a sampling problem (SP$_m$) for each batch.  
+The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches, and (ii) using warm starting to quickly solve the sampling approximations with overlapping samples.
+%We use the batch nonoverlap parameter $\gamma$ as before to allow for varying degrees of overlap in OMRP. 
+We examine the effect of warm starting and any resulting computational efficiency gains in \S \ref{ssec:compeff}. 
+We are now ready to define the OMRP estimators.
+
+%First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
+%Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
+%Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
+%In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
+% THIS LAST SENTENCE NEEDS TO CHANGE!
+
+\begin{figure}[tb!]
 	\centering
@@
 
-The results on overlapping batch means, discussed in Section \ref{ssec:overlap}, occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
+In order to apply overlapping batches to MRP, we need to keep track of solutions to sampling problems (SP$_m$) for each batch of size $m$.  
+Toward this end, let $B(i)$ denote the set of batches $j \in \left\{1, 2, \dots, \nb \right\}$ observation $\xiti$ is used in, $i = 1, 2, \dots, n$.  
+See Figure \ref{fig:overlap_nonint} for an example with $n=18$, $m = 6$, and $\gamma = 2$.  
+Here, the first batch uses observations $\xit^1, \xit^2, \xit^3, \xit^4, \xit^5, \xit^6$, the second batch uses $\xit^3, \xit^4, \xit^5, \xit^6, \xit^7, \xit^8$, and so on.  
+So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  
+As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch; $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
+
+The results on overlapping batch means discussed in \S \ref{ssec:overlap} occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
 Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
@@
 In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
-Now we are ready to define the estimators for OMRP.
+The OMRP estimators are defined as follows:
 \begin{align}
@@
 This fact is key in establishing the theoretical results presented in the next section. 
-We note, however, that this choice of $\gbb_l$ may not be guaranteed to be nonnegative.
+This choice of $\gbb_l$, however, may not be guaranteed to be nonnegative.
 In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping.
@@
 \subsection{Asymptotic Validity of the Confidence Intervals}
+\label{ssec:validity}
 

### 2014-07-11 Referee2_Response.tex
Major rewrite of Introduction
1) Wrote a motivation paragraph
2) Wrote a list of contributions
3) Wrote differences of this paper compared to WSC version
4) Moved a paragraph from Intro to Overlapping Batch Means section and
edited that paragraph
5) Changed Referee 1 response accordingly
6) Added a reference
7) Some other minor minor changes
Finishing up EinC, AE, Ref1 responses
and a final pass through Ref2 responses and comments -- Still not done.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\noi 
 We thank the referee for the helpful comments and suggestions. 
@@
 \noindent 
-xxx  We agree. 
-We changed the introduction to clearly state the contributions of the paper and \ldots  and the presentation of the paper significantly improved.  Thank you.
+You are right. 
+We changed the introduction to clearly state the main contributions of the paper.  
+Please see page four of the revised manuscript. 
+We also clarified the motivation for the work, included new contributions based on the study computational efficiency added to the paper (contribution (iv)), and provided a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).
+%We believe the presentation of the paper significantly improved.  
+%Thank you.
 \medskip
@@
 Thank you for this suggestion.
-
-\bigskip
+\medskip
 
@@
 \noindent  
-xxxx
-You are right. 
 We went through the paper and tightened up the prose. 
-We also incorporated all the changes you suggested below and hope the exposition of the paper is improved as a result.
-We hope that any remaining English issues could be corrected by the English editor of the journal. (IS THERE ONE????) 
-xxxx
+We also incorporated all the changes you suggested below and believe the exposition of the paper is improved as a result.
+Thank you for your careful review that significantly improved the presentation of the paper. 
 \medskip
@@
 We changed the first sentence of Section 6 (Conclusions) to use the word `apply' instead of `extend'. 
-
 \medskip
@@
 \noi
-xxx  
+Yes; we reworded this sentence. 
+xxx We also went through the paper and made the context clear whenever a phrase like `same benefits', `desired results', etc.\ was used.  
 \medskip
@@
 
+\noi
+{\it Note:}  We moved this sentence from the paragraph on page 2 to later in the introduction to clearly state the contributions of the paper. 
+It now appears as contribution (ii) on page 4 of the revised manuscript.
+\medskip
+
 \begin{itemize}
@@
 \noi
-Done. 
+We made the change to the first sentence above. 
+The first sentence now appears as part of contribution (ii) and the second sentence as part of contribution (iii) on page 4 of the revised manuscript. 
+We decided not to include `also' in the second sentence as it starts a new set of contributions. 
 \medskip
@@
 Done.
+\medskip
+
+\noi
+{\it Note:} We moved this sentence from the paragraph on page 2 to later in the introduction to clearly state the contributions of the paper.
+This sentence now appears as part of contribution (iii) on page 4 of the revised manuscript.
 \medskip
@@
 
+\noi
+{\it Note:}
+ As a result of the revised introduction---aimed to clearly state the contributions of the paper---we moved the technical discussion on the differences between using overlapping batches in simulation output analysis and assessing solution quality in stochastic optimization to \S 3 (Overlapping Multiple Replications Procedure).
+Consequently, this sentence now appears in \S 3. 
+\medskip
+
 \begin{itemize}
@@
 \noi
-xxx   DAVID-- NEED YOUR HELP with this. 
-I don't know how to reword it to make it less awkward.
+We removed the comment on the central limit theorem on the minimized sample means as it is not relevant to the paper. 
+We also reworded these sentences to improve clarity. 
+\medskip
+
+\noi
+{\it Note:}
+As mentioned in the previous comment, this section now appears in  \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 Thanks for pointing out the ambiguity here. 
-We reworded this sentence and broke it into two sentences to make it clear. 
+We reworded this sentence, divided it into two sentences to improve readability, and added further explanations to remove any ambiguities. 
+\medskip
+
+\noi
+{\it Note:}
+This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip

### 2014-07-11 AE_Reponse.tex
Finishing up EinC, AE, Ref1 responses
and a final pass through Ref2 responses and comments -- Still not done.

--- 2014-06-17 AE_Reponse.tex
@@
 
+\noi
 We thank the Associate Editor for the helpful comments and suggestions. 
-We incorporated virtually all of the recommended changes and believe the paper is improved as a result. 
+We incorporated all of the recommended changes and believe the paper is improved as a result. 
 Below, we go through in detail the suggestions of the Associate Editor.
@@
 
-\noi xxx 
-We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work, based on your and the referees' comments and the new material like computational efficiency added to the paper.
-\medskip
+\noi
+We revised the introduction to clearly reflect the contributions of the paper and the motivation for the work. 
+Please see page four of the revised manuscript. 
+This section also includes contributions based on the new material on computational efficiency added to the paper (contribution (iv)) and a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).\medskip
 
 \begin{itemize}
-\item[] \textit{%\ldots
-The experiments show that the confidence interval average widths and observed coverage probabilities are the same with overlapping batch means; the only difference is in decreased variability of the confidence interval widths.
-That is, the variance of the variance estimator is reduced. 
-This second-order benefit should be weighed against the increased computation cost (not to mention complexity and restricted applicability) of the overlapping batch means method.}
-
-\textit{The issue of computational efficiency is not addressed  in the paper. 
+\item[] 
+%\textit{
+%The experiments show that the confidence interval average widths and observed coverage probabilities are the same with overlapping batch means; the only difference is in decreased variability of the confidence interval widths.
+%That is, the variance of the variance estimator is reduced. 
+%This second-order benefit should be weighed against the increased computation cost (not to mention complexity and restricted applicability) of the overlapping batch means method.
+%}
+\textit{\ldots The issue of computational efficiency is not addressed  in the paper. 
 In this setting the efficiency is often defined as the reciprocal of the computation time multiplied by the variance. 
@@
 It is indeed important to study computational efficiency in this context. 
-We created a new section, Section 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
-When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
+We created a new section, \S 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
+%When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
 We discussed efficiency for a given functional form of the solution time per batch. 
-Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
-We illustrated this method on the newsvendor problem using insertion sort. 
-Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping.
-We discussed guidelines on selecting the degree of overlapping (for NVD or for a given generic problem) in Section 5.4 (Computational Efficiency). 
-\medskip
+%Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
+%\medskip 
+In addition, based on the comments of Referee 1, we studied efficiency of overlapping estimators compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with equivalently lower variances.
+Our results indicate that when warm-starting is effective, overlapping is computationally more efficient.
+Even in cases where the effectiveness of warm-starting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\bigskip
 
-In addition, based on the comments of Referee 1, we also studied the efficiency of overlapping compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with lower variances.
-Our results indicate that when warm-starting is effective, overlapping is computationally more efficient than increasing the number of batches of MRP.
-We also illustrated this result on the newsvendor problem. 
+\noi 
+We illustrated these results on the newsvendor problem using insertion sort. 
+Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping by maximizing efficiency.\bigskip
+
+\noi
+Finally, we provided guidelines on selecting the degree of overlap at the end of \S 5.4 (Computational Efficiency) based on our study. 
 We believe the paper has improved as a result of the study of computational efficiency. 
-Thank you. 
+Thank you for this suggestion. 
 \medskip
@@
 
-\noi xxx 
-Based on your other comments and suggestions of the referees, we provided information on computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming.
-These are detailed in Section 5.4 (Computational Efficiency). 
-(Please see our response to the previous comment.)
-We also changed Section 1 (Introduction) and Section 6 (Conclusions) to clearly motivate the study and usefulness of the results.
-
-%xxx  Is this really a new comment?  Looks like just continuation of the prev. comment. So... combine it with previous comment???
-
+\noi 
+We established improved computational efficiency on the newsvendor problem using insertion sort.
+We also (i) changed Section 1 (Introduction) to clearly motivate the study and argue usefulness of the results, paying specific attention to efficiency gains; (ii) updated Section 6 (Conclusions) to summarize these new results, again paying attention to computational efficiency; (iii) provided a study of computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming in the new \S 5.4 (Computational Efficiency); and finally (iv) updated the abstract.
+%(Please see our response to the previous comment.)
 \medskip

### 2014-07-11 EinC_Reponse.tex
Finishing up EinC, AE, Ref1 responses
and a final pass through Ref2 responses and comments -- Still not done.

--- 2014-05-21 EinC_Reponse.tex
@@
 \setlength{\oddsidemargin}{0.0in}
+
+\newcommand{\noi}{\noindent}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\noi
 We thank the Editor-in-Chief for the helpful comments and suggestions. 
@@
 
-\noindent xxx \ \ 
- We incorporated virtually all the recommended changes suggested by you, the associate editor, and the referees. 
+\noindent  
+We incorporated all the recommended changes suggested by you, the associate editor, and the referees and believe the paper is significantly improved as a result.
 We very much appreciate everyone's time and constructive comments. 
-We believe the paper is significantly improved and the wording of the paper, compared to the Winter Simulation Conference paper, is changed as a result of the revision.
-We also went through the paper and tried to change the text to reduce word for word copying. 
+As a result of the revision, the wording and content of the paper, compared to the Winter Simulation Conference Proceedings version, has partly changed.
+We also edited the paper to improve exposition and tried to cut back word for word copying during this process.  
 \medskip
@@
 \begin{itemize}
-\item[]\textit{Even more important, in clarifying your contribution (as already asked by the reviewers), you should also shortly explain what new research results are presented in the  TOMACS paper in comparison to the WSC paper}
+\item[]\textit{Even more important, in clarifying your contribution (as already asked by the reviewers), you should also shortly explain what new research results are presented in the  TOMACS paper in comparison to the WSC paper (please note TOMACS expects about 30\% new research).}
 \end{itemize}
@@
 \noindent
-xxx Do xxx  We added a paragraph (??) in the introduction, detailing what has been done over \ldots
+We added a paragraph in Section 1 (Introduction) detailing what has been done over the WSC proceedings paper. 
+Please see the first paragraph on page 5 of the revised manuscript.\bigskip
+
+\noi 
+Specifically, we now show (i) almost sure consistency of the variance estimator (earlier this was mean-square consistency), (ii) asymptotic validity of the resulting confidence intervals, and (iii) that overlapping MRP variance estimators have asymptotically lower variances compared to (nonoverlapping) MRP variance estimator.
+These new theoretical results are due to a stronger assumption made in the paper submitted to TOMACS, which was not present in the WSC version. 
+We also present a number of new computational results. 
+For instance, we (iv) provide computations on two additional test problems, including a large-scale problem, and (v) study computational efficiency of the proposed method (added as a result of the revision).
 

### 2014-07-11 omrp_lb_rev.tex
Finishing up EinC, AE, Ref1 responses
and a final pass through Ref2 responses and comments -- Still not done.

@@
 \item[(ii)] We provide conditions under which the resulting optimality gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
-We show that the resulting point estimators are strongly consistent and the interval estimators are asymptotically valid. 
+We also show that the resulting point estimators are strongly consistent and that the interval estimators are asymptotically valid. 
 These results require new proofs because of the presence of the optimization operator.
@@
 At the same time, variances of the estimators are lowered, and when warm starting is available, solution time per batch can decrease, resulting in efficiency gains. 
-We explore the trade-off between computation time and lower variances.
+We explore this trade-off between computation time and lower variances.
 % and efficiency gains. 
 %We explore the overall computation time versus lower variances and efficiency gains trade-off. 
+Our results indicate that when warm-starting is effective, overlapping is computationally more efficient relative to estimators formed via nonoverlapping batches.
+%Our results indicate that overlapping can indeed increase computational efficiency, especially when warm-starting is effective. 
 We provide guidelines on selecting the degree of overlap based on computational efficiency and demonstrate efficiency on a newsvendor problem. 
@@
 We are interested in estimating the variance of an optimality gap estimator.  
-An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean $(\zs_m)$.  
+An optimality gap estimator not only has a sample mean $(\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti))$ but also a minimized sample mean; see, e.g., the second term on the right-hand side of (\ref{eq:mrp_gap}).
 Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
@@
 We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{subsec:nonO}).  
-The nonoptimized counterparts are regular overlapping batch means estimators (without any optimization present); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions.
-We establish convergence of OMRP estimators to their nonoptimized counterparts (see \S \ref{subsec:conv}--\ref{ssec:validity}); 
-thereby establishing the benefits of overlapping in this context.
+The nonoptimized counterparts are regular overlapping batch means estimators (without any optimization); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions.
+To show that the same asymptotic properties hold for OMRP estimators, we establish convergence of OMRP estimators to their nonoptimized counterparts (see \S \ref{subsec:conv}--\ref{ssec:validity}).
 

### 2014-07-14 images/fig2pdf.m
Fix right hand side of all images -- some were missing the axis

@@ -22,7 +22,7 @@ for j = 1:length(s)
     pos = get(gca,'Position');
     ti = get(gca,'TightInset');
     set(gcf, 'PaperUnits','centimeters');
-    set(gcf, 'PaperSize', [pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
+    set(gcf, 'PaperSize', [(pos(3)+ti(1)+ti(3))*1.05 (pos(4)+ti(2)+ti(4))*1.05]);
     set(gcf, 'PaperPositionMode', 'manual');
     set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
     

### 2014-07-14 images/fig2pdf.m
figures --gb

@@ -22,7 +22,7 @@ for j = 1:length(s)
     pos = get(gca,'Position');
     ti = get(gca,'TightInset');
     set(gcf, 'PaperUnits','centimeters');
-    set(gcf, 'PaperSize', [(pos(3)+ti(1)+ti(3))*1.05 (pos(4)+ti(2)+ti(4))*1.05]);
+    set(gcf, 'PaperSize', [(pos(3)+ti(1)+ti(3))*1.03 (pos(4)+ti(2)+ti(4))*1.03]);
     set(gcf, 'PaperPositionMode', 'manual');
     set(gcf, 'PaperPosition',[0 0 pos(3)+ti(1)+ti(3) pos(4)+ti(2)+ti(4)]);
     

### 2014-07-15 Referee1_Response.tex
Finishing up EinC, AE, Ref1 responses
and a final pass through Ref2 responses and comments -- Still not done.
Crossing the t's, dotting the i's

@@
 For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions; thank you. 
-We found that when effective warm-starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
+We found that when effective warmstarting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
 %All these results are presented in Section 5.4 (Computational Efficiency). 
@@
 \noi 
-{\it Note:} This sentence now appears in the second paragraph of Section 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
+{\it Note:} This sentence now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
 \medskip
@@
 \noindent 
-We removed this sentence and replaced it with a shorter one in order to improve exposition. 
+We revised this section in order to improve exposition. 
 We used `smaller number of batches' based on the comments of the other referee in the new sentence. 
-\smallskip
+\medskip
 
 \noi 
-{\it Note:} This section now appears in the second paragraph of Section 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
+{\it Note:} This section now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
 \medskip
@@
 \noindent 
-Done.
-
-XXXX Denominator term makes!  I think it changed to denominator term. CHECK XXXX
+We now use denominator instead of degrees of freedom. 
+Therefore, we used `\ldots denominator makes \ldots '
 \medskip
@@
 
-\noindent Done.
-%\ \ \ XXXX CHECK LATER: THIS SECTION MIGHT CHANGE. 
+\noindent 
+Done.
 \medskip
@@
 We also enlarged the legends in these graphs to improve readability.
-All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger, with legible legends. 
+All the new graphs added to the paper in \S 5.4 (Computational Efficiency) are also larger, with legible legends. 
 \medskip
@@
 We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP confidence intervals for this test problem.
-We explain this at the end of Section 5.1 (Test Problems). 
-We also changed the wording in Section 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for DB1. 
+We explain this at the end of \S 5.1 (Test Problems). 
+We also changed the wording in \S 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for DB1. 
 \medskip
@@
 \begin{itemize}
-\item[19.] \textit{p19: It may be possible to expand on the last paragraph of Section 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
+\item[19.] \textit{p19: It may be possible to expand on the last paragraph of \S 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
 \end{itemize}

### 2014-07-15 Referee2_Response.tex
Crossing the t's, dotting the i's

@@
 Please see page four of the revised manuscript. 
-We also clarified the motivation for the work, included new contributions based on the study computational efficiency added to the paper (contribution (iv)), and provided a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).
+We also clarified the motivation for the work, included new contributions based on the study of computational efficiency (contribution (iv)), and provided a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).
 %We believe the presentation of the paper significantly improved.  
@@
 \noindent 
-We shortened and streamlined the OBM review, focusing on the main results used in the paper, by combining the previous two sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---along with other explanations on OBM that appeared later in the paper.
+We shortened and streamlined the OBM review, focusing on the main results used in the paper, by combining two previous sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---along with other explanations on OBM that appeared later in the paper.
 The combined review is in the background section, \S 2.1 (Batch Means). 
@@
 We also went through the paper to correct other occurrences. 
-In particular, this was also used in Section 6 (Conclusions). 
-We changed the first sentence of Section 6 (Conclusions) to use the word `apply' instead of `extend'. 
+In particular, this was also used in \S 6 (Conclusions). 
+We changed the first sentence of \S 6 (Conclusions) to use the word `apply' instead of `extend'. 
 \medskip
@@
 \noi
-Yes; we reworded this sentence. 
-xxx We also went through the paper and made the context clear whenever a phrase like `same benefits', `desired results', etc.\ was used.  
+Yes. We reworded this sentence. 
+We also went through the paper and made the context clear whenever phrases like `same benefits', `desired statistical properties', etc.\ were used.  
 \medskip
@@
 \noi
-xxx  You are right. 
-Thanks for pointing this out. We corrected the wording throughout the paper. 
+You are right. 
+Thanks for pointing this out. 
+We corrected the wording throughout the paper. 
 \medskip
@@
 \noi
-{\it Note:} We moved this sentence from the paragraph on page 2 to later in the introduction to clearly state the contributions of the paper.
+{\it Note:} 
 This sentence now appears as part of contribution (iii) on page 4 of the revised manuscript.
@@
 {\it Note:}
- As a result of the revised introduction---aimed to clearly state the contributions of the paper---we moved the technical discussion on the differences between using overlapping batches in simulation output analysis and assessing solution quality in stochastic optimization to \S 3 (Overlapping Multiple Replications Procedure).
+ As a result of the revised introduction---aimed to clearly state the contributions of the paper---we moved the technical discussion on using overlapping batches in simulation output analysis versus for assessing solution quality in stochastic optimization to \S 3 (Overlapping Multiple Replications Procedure).
 Consequently, this sentence now appears in \S 3. 
@@
 \noi
+You are right. 
 We removed the comment on the central limit theorem on the minimized sample means as it is not relevant to the paper. 
 We also reworded these sentences to improve clarity. 
-\medskip
+\bigskip
 
@@
 {\it Note:}
-As mentioned in the previous comment, this section now appears in  \S 3 (Overlapping Multiple Replications Procedure). 
+As mentioned in the previous comment, the revised sentences now appear in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 We reworded this sentence, divided it into two sentences to improve readability, and added further explanations to remove any ambiguities. 
-\medskip
+\bigskip
 
@@
 {\it Note:}
-This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
+The revised sentences now appear in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 
+\noi
+{\it Note:}
+This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
+\medskip
+
 \begin{itemize}
@@
 \noi
-Done.  
+Changed it to ``\dots because we need to solve \ldots '' to improve readability.  
+\medskip
+
+\noi
+{\it Note:}
+This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 \noi
-Done.  
+We revised this section in order to improve exposition. 
+We used `smaller number of batches' based on your suggestion in the revised version. 
+\medskip
+
+\noi 
+{\it Note:} This sentence now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 \noi
-xxx  
+You are right. 
+While we removed the sentence that started with `Second' in an effort to improve readability, we referred to the computational efficiency study added to the paper to justify this remark.   
+\medskip
+
+\noi
+{\it Note:}
+This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 \noi
-No; by `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to the assessment of solution quality in stochastic programming). 
-We reworded this sentence to make it clear. 
-Please note that based on your earlier comments, we reworded this sentence to avoid using the term `variance reduction'. 
+No. By `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to assessment of solution quality in stochastic programming). 
+We reworded this sentence to remove ambiguity. 
+Based on your earlier comments, we avoided the term `variance reduction' in the revised sentence.
 We also went through the paper and removed several uses of the word `classical' that referred to nonoverlapping batches to reduce ambiguity.
@@
 Variance parameter. 
+Thank you.
 We revised this sentence and added a footnote defining the variance parameter for readers who might not be familiar with this term (e.g., readers with an optimization focus). 
@@
 We corrected this sentence. 
-Please note that we broke this sentence into two to avoid long sentences and to improve exposition. 
+Please note that we split this sentence into two to avoid long sentences and to improve exposition. 
 We also checked for other uses of the term `sample variance' throughout the paper and corrected these as needed.
@@
 We now introduce this abbreviation the first time we use the term `confidence interval' in the introduction. 
-From this point on, we use the abbreviated form `CI' throughout the paper, except for the title of Section 4.5 (Asymptotic Validity of the Confidence Intervals). 
+From this point on, we use the abbreviated form `CI' throughout the paper, except for the title of \S 4.5 (Asymptotic Validity of the Confidence Intervals). 
 \medskip
@@
 Done.  
+We removed the word `corresponding' as part of the rewrite.
 \medskip
@@
 We went through the paper and removed most of the ``note that'' phrases. 
-We decided to leave a couple as is (mainly as ``notice that'') because they highlight important characteristics.  
+We decided to leave a couple as is (as ``notice that'') because they highlight important characteristics.  
 \medskip
@@
 We decided to avoid the degrees of freedom here. 
-This is because we wanted to focus on the degrees of freedom for confidence interval construction, which is discussed in both the theoretical and computational results.\smallskip
+This is because we wanted to focus on the degrees of freedom for confidence interval construction, which is discussed in both the theoretical and computational results.
+\medskip
 
@@
 \noi
-Yes; we explicitly stated this in a sentence after we introduce $\gamma$.\smallskip
+Yes; we explicitly stated this in a sentence after we introduce $\gamma$.
+\medskip
 
 \noi 
-{\it Note:} This sentence now appears in Section 2.1.2 (Overlapping Batch Means). 
+{\it Note:} This sentence now appears in \S 2.1.2 (Overlapping Batch Means). 
 \medskip
@@
 \noi 
-{\it Note:} Both definitions appear in Section 2.1.2 (Overlapping Batch Means).
+{\it Note:} Both definitions appear in \S 2.1.2 (Overlapping Batch Means).
 \medskip
@@
 \noi 
-{\it Note:} This sentence now appears in Section 2.1.2 (Overlapping Batch Means). 
+{\it Note:} This sentence now appears in \S 2.1.2 (Overlapping Batch Means). 
 \medskip
@@
 You are right. 
-We moved these references---in particular, Damerdji (1994, 1995)---to Section 2.1.2 (Overlapping Batch Means) and added a brief discussion.  
+We moved these references---in particular, Damerdji (1994, 1995)---to \S 2.1.2 (Overlapping Batch Means) and added a brief discussion.  
 \medskip
@@
 \noi
-xxx 
 This notation was defined before Theorem 1. 
-We moved the definition of $\sigma_{\hat{x}}$ and $\mu_{\hat{x}}$ to \ldots to improve clarity. 
+We moved the definitions of $\sigma_{\hat{x}}$ and $\mu_{\hat{x}}$ to the end of \S 4.2 (Nonoptimized Counterparts) to improve clarity. 
 \medskip

### 2014-07-15 AE_Reponse.tex
Crossing the t's, dotting the i's

@@
 We created a new section, \S 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
-%When an algorithm has warm-starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
+%When an algorithm has warmstarting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
 We discussed efficiency for a given functional form of the solution time per batch. 
-%Depending on the effectiveness of warm-starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
+%Depending on the effectiveness of warmstarting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
 %\medskip 
 In addition, based on the comments of Referee 1, we studied efficiency of overlapping estimators compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with equivalently lower variances.
-Our results indicate that when warm-starting is effective, overlapping is computationally more efficient.
-Even in cases where the effectiveness of warm-starting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\bigskip
+Our results indicate that when warmstarting is effective, overlapping is computationally more efficient.
+Even in cases where the effectiveness of warmstarting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\bigskip
 
@@
 We established improved computational efficiency on the newsvendor problem using insertion sort.
-We also (i) changed Section 1 (Introduction) to clearly motivate the study and argue usefulness of the results, paying specific attention to efficiency gains; (ii) updated Section 6 (Conclusions) to summarize these new results, again paying attention to computational efficiency; (iii) provided a study of computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming in the new \S 5.4 (Computational Efficiency); and finally (iv) updated the abstract.
+We also (i) changed \S 1 (Introduction) to clearly motivate the study and argue usefulness of the results, paying specific attention to efficiency gains; (ii) updated \S 6 (Conclusions) to summarize these new results, again paying attention to computational efficiency; (iii) provided a study of computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming in the new \S 5.4 (Computational Efficiency); and finally (iv) updated the abstract.
 %(Please see our response to the previous comment.)
@@
 
+\noi
+{\it Note:}
+We moved this sentence from \S 1 (Introduction)---to clearly state the contributions of the paper---to \S 3 (Overlapping Multiple Replications Procedure), where we provided more technical details. 
+\medskip
+
 \begin{itemize}

### 2014-07-15 omrp_lb_rev.tex
figures --gb
Crossing the t's, dotting the i's

@@
 In this paper, we apply the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
-We give conditions under which the resulting optimality gap estimators are strongly consistent and have the same asymptotically lower variance as the classical OBM estimators \citep{Meketon1984,Welch1987}.
+We give conditions under which the resulting optimality gap point estimators are strongly consistent, interval estimators are asymptotically valid, and the variance estimators have the same asymptotically lower variances relative to their nonoverlapping counterparts as the classical OBM estimators \citep{Meketon1984,Welch1987}.
 Computational experiments for several test problems are presented, examining the small-sample behavior and the computational efficiency of the overlapping batches method in this context.\medskip
@@
 This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
-In this paper, we formulate an overlapping batches version of MRP with a parametrized degree of overlap.
-%, and present theoretical and computational results.
+In this paper, we formulate an overlapping batches version of MRP.
 
@@
 \item[(iv)] As the degree of overlap increases, the number of batches and optimization problems solved increases because we need to solve a sampling problem per batch. 
-At the same time, variances of the estimators are lowered, and when warm starting is available, solution time per batch can decrease, resulting in efficiency gains. 
+At the same time, variances of the estimators are lowered, and when warmstarting is available, solution time per batch can decrease, resulting in efficiency gains. 
 We explore this trade-off between computation time and lower variances.
@@
 %We explore the overall computation time versus lower variances and efficiency gains trade-off. 
-Our results indicate that when warm-starting is effective, overlapping is computationally more efficient relative to estimators formed via nonoverlapping batches.
-%Our results indicate that overlapping can indeed increase computational efficiency, especially when warm-starting is effective. 
+Our results indicate that when warmstarting is effective, overlapping is computationally more efficient relative to estimators formed via nonoverlapping batches.
+%Our results indicate that overlapping can indeed increase computational efficiency, especially when warmstarting is effective. 
 We provide guidelines on selecting the degree of overlap based on computational efficiency and demonstrate efficiency on a newsvendor problem. 
@@
 $y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
-In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch contains observations $y^3, y^4, \dots, y^{m+2}$, and so on.
+In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch $y^3, y^4, \dots, y^{m+2}$, and so on.  
 This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
-It is possible to vary the amount of overlap between neighboring batches. 
+It is possible to vary the degree of overlap between neighboring batches. 
 This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
@@
 This slightly different denominator 
-makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits \citep{Song1992}.
+makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits of nearly the same bias and lower variances relative to its counterpart obtained via nonoverlapping batches \citep{Song1992}.
 
@@
 This means that the maximally-overlapping variance estimator has a variance that is two-thirds ($66.67\%$) of the nonoverlapping estimator.
-As the amount of overlap decreases, the variance increases. 
+As the degree of overlap decreases, the variance increases. 
 When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/2$), for instance, the variance is 75\% of the nonoverlapping counterpart.
@@
 In this setting, the computational effort may increase with data reuse because we need to solve a sampling problem (SP$_m$) for each batch.  
-The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches, and (ii) using warm starting to quickly solve the sampling approximations with overlapping samples.
+The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches, and (ii) using warmstarting to quickly solve the sampling approximations with overlapping samples.
 %We use the batch nonoverlap parameter $\gamma$ as before to allow for varying degrees of overlap in OMRP. 
-We examine the effect of warm starting and any resulting computational efficiency gains in \S \ref{ssec:compeff}. 
+We examine the effect of warmstarting and any resulting computational efficiency gains in \S \ref{ssec:compeff}. 
 We are now ready to define the OMRP estimators.
@@
 %Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
-%Second, in many solution methods, warm-starting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
+%Second, in many solution methods, warmstarting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
 %In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
@@
 
-In this section, we provide conditions under which several asymptotic properties hold. 
+In this section, we provide conditions under which several asymptotic properties hold for OMRP estimators. 
 First, we show the consistency of the point estimators of optimality gap, $\gbb_l$, and variance, $n_l VG_l$. 
-Then, we provide conditions under which the same benefits on variance reduction are observed in the stochastic programming setting by overlapping. 
+Then, we provide conditions under which the asymptotically lower variances are observed for the OMRP variance estimator relative to nonoverlapping MRP estimator.  
 Finally, we show the asymptotic validity of the OMRP interval estimator.
@@
 The results for overlapping batches from the simulation output analysis indicate that $\var{n_l VG_l}$ may be reduced by overlapping, thus requiring at least finite fourth moments. 
-We will formally show this result in Section~\ref{ssec:var_reduct}.
+We will formally show this result in \S~\ref{ssec:var_reduct}.
 Our proof relies on an exponential rate of convergence of the sampled solution to the true solution of the problem, specified by A3.  
@@
 l$, $m_l$, and $\gamma_l$.  \smallskip
+
+Before we begin establishing the theoretical results, we introduce the following notation. 
+We use $\mu_{\xh} := \e{f(\xh,\xit) - f(\xs,\xit)}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
+With i.i.d.\ sampling, $\e{\db_{lj}}=\e{\dbb_l}=\mu_{\xh}, \ \forall l,j$ and by (\ref{eq:varvarred}), $\frac{n_l}{m_l} \var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$ under appropriate conditions.
 
@@
 We use the abbreviation a.s.\ to denote almost sure convergence.
-We also use $\mu_{\xh} := \e{f(\xh,\xit) - f(\xs,\xit)}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
 
@@
 
-Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotically lower variances are achieved for the OMRP optimality gap variance estimator relative to its nonoverlapping counterpart MRP.
+Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotically lower variances are achieved for the OMRP optimality gap variance estimator relative to its nonoverlapping counterpart, the MRP variance estimator.
 We will empirically examine the variance of OMRP estimator for small sample sizes in \S \ref{sec:comp}. 
@@
 
-The overlapping variance estimator for stochastic programs displays the same desirable properties as in simulation, but we must still check that it results in a valid CI.  
+The overlapping variance estimator for stochastic programs displays the same desirable properties, detailed in \S \ref{subsec:conv} and \S \ref{ssec:var_reduct}, as in simulation, but we must still check that it results in a valid CI.
 Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided CI generated by OMRP. 
@@
 A summary of results from these experiments is depicted in Figures~\ref{fig:varvar1}--\ref{fig:nv}.
-Figures~\ref{fig:varvar1} and \ref{fig:varvar2} show the reduction of variance, with each term being normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
-The solid lines in these figures show the theoretical variance reduction from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
+Figures~\ref{fig:varvar1} and \ref{fig:varvar2} show the variance of OMRP variance estimators, normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
+The solid lines in these figures show the theoretical relative variance from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
 Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
-These experiments suggest that similar variance reduction can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
-The variance reduction in DB1 can be less than the asymptotic amount %for the small sample sizes used in these experiments. 
-because DB1 has not yet been solved to optimality due its size; therefore, it may lack a unique optimal solution. 
+These experiments suggest that lower variances can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
+The variance of OMRP variance estimators in DB1 can be less than the asymptotic amount established by Theorem \ref{thm:varvar_conv}. %for the small sample sizes used in these experiments. 
+This is because DB1 has not yet been solved to optimality due its size; therefore, it may lack a unique optimal solution. 
 %, violating assumption A3. (?)
-Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to achieve some variance reduction.
+Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to reduce the variances.
 
@@
 
-Figure~\ref{fig:nv}(a) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and amount of overlap. 
+Figure~\ref{fig:nv}(a) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and degree of overlap. 
 We can see that the expectation of the variance estimator is not changed with increasing overlap. 
@@
 Finally, Figure~\ref{fig:nv}(b) shows the coverage probability of CIs generated by OMRP for several values of $m$ across varying values of $\gamma/m$ for the newsvendor problem.  
-The results of the overlapping batches estimators from the simulation literature show that coverage probability does not change with the amount of overlap, which we can  empirically see in this figure for OMRP for NVD.
+The results of the overlapping batches estimators from the simulation literature show that coverage probability does not change with the degree of overlap, which we can  empirically see in this figure for OMRP for NVD.
 We observed the same for CEP1, 10D, and DB1.  
@@
 Here, $t(\gammab)$ is the average computation time per batch, which is multiplied by the number of batches.
-Warm-starting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
+Warmstarting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
 
@@
 	   \label{fig:efficiency_theory}
-	   \includegraphics[width=.5\textwidth]{images/comp_efficiency_theory}}
+	   \includegraphics[width=.49\textwidth]{images/comp_efficiency_theory}}
 	\subfloat[][Empirical for NVD]{
 	   \label{fig:efficiency_nv}
-	   \includegraphics[width=.5\textwidth]{images/nv_comp_efficiency}}
+	   \includegraphics[width=.51\textwidth]{images/nv_comp_efficiency}}
 		\caption{
@@
 
-Another related question on computational efficiency would be whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
+A related question on computational efficiency asks whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
 When generating observations is cheap, one could alternatively increase the number of batches in MRP to obtain estimators with lower variances. 
@@
 Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison}. 
-This curve shows the increase in computational effort due to an increased number of batches in MRP in order to obtain the same variance for OMRP across $\gammab$.
+This curve shows the increased computational effort in MRP due to an increased number of batches to obtain the same variance of OMRP across $\gammab$.
 If the work increase by OMRP is less than this solid black curve, then OMRP is computationally more efficient than increasing the number of batches in MRP. 
@@
 For small values of $p$, some efficiency gain is observed at $\gammab$ values close to 1.
-We again tested this empirically on NVD using insertion sort with $m=1,000$, average of $10,000$ independent runs. 
-The results, shown in Figure \ref{fig:comp_work_comparison}(b), again appear to match the theory well.
+We again tested this empirically on NVD using insertion sort with $m=1,000$, taking an average of $10,000$ independent runs. 
+The results, shown in Figure \ref{fig:comp_work_comparison}(b), appear to match the theory well.
 
@@
 	   \label{fig:comp_work_comparison_theory}
-	   \includegraphics[width=.5\textwidth]{images/work_comparison}}
+	   \includegraphics[width=.51\textwidth]{images/work_comparison}}
 	\subfloat[][Empirical for NVD]{
 	   \label{fig:comp_work_comparison_nv}
-	   \includegraphics[width=.5\textwidth]{images/nv_work_comparison}}
+	   \includegraphics[width=.49\textwidth]{images/nv_work_comparison}}
 		\caption{
@@
 In cases where the exponent $p$ can be estimated, the above theoretical method may be used to determine a reasonable value for $\gammab$.
-When warm-starting can be used to solve the batch sampling problems, we recommend the users to perform preliminary computations to determine how computational time per batch changes as $\gammab$ changes.
+We recommend that users perform preliminary computations to determine how computational time per batch changes as $\gammab$ changes when warmstarting is available. 
 We can see in Figure \ref{fig:efficiency} that for some values of $p$, efficiency gain is nearly flat over a region of $\gammab$.
-In this case, we recommend choosing a $\gammab$ near the right side of this region.
+In this case, we recommend choosing $\gammab$ near the right side of this region.
 This choice keeps efficiency high while decreasing computation time and preventing large decreases in efficiency in the event that $p$ was overestimated.
@@
 We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
-We have provided conditions under which the resulting point estimator of the optimality gap and its associated variance estimator are consistent, the same lower variances of OMRP variance estimators relative to the nononverlapping MRP estimator can be achieved, and asymptotically valid CIs can be formed.
-Empirical results with small sample sizes indicate that the asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP, while bias and coverage probability remain unaffected.
-We have examined the computational efficiency of OMRP by jointly considering increases in computation time and decreases in variance. 
-Our results indicate that when warm-starting is effective, efficiency can be observed across a wide range of degree of overlap. 
-When warm-starting is less effective, efficiency is observed for small degrees of overlap. 
-We have demonstrated computational efficiency empirically solving the newsvendor problem with insertion sort.
-Finally, we provided guidelines on selecting the degree of overlap based on our study of computational efficiency.
+We have provided conditions under which (i) the resulting point estimator of the optimality gap and its associated variance estimator are consistent, (ii) OMRP variance estimators achieve asymptotically lower variances relative to the MRP variance estimator, and (iii) OMRP CIs are asymptotically valid.
+Empirical results indicate that asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP at small sample sizes, while bias and coverage probability remain unaffected.
+Because overlapping may increase computational burden in the stochastic optimization setting, we have examined computational efficiency of OMRP by jointly considering computation time and variance. 
+Our results indicate that when warmstarting is effective, efficiency can be observed across a wide range of overlapping degrees, and when warmstarting is less effective, efficiency increases for only small degrees of overlap.
+We have empirically demonstrated computational efficiency by solving a newsvendor problem using insertion sort.
+Finally, based on our study of computational efficiency, we have provided guidelines on selecting the degree of overlap in OMRP.
 

### 2014-07-17 Referee1_Response.tex
More corrections

@@
 For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions; thank you. 
-We found that when effective warmstarting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
+We found that when effective warm starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
 %All these results are presented in Section 5.4 (Computational Efficiency). 

### 2014-07-17 Referee2_Response.tex
More corrections

@@
 \noi
-xxx  Done. But I am not sure if it is correct this way.  
-Thank you; we went through the paper and hyphenated all the compound adjectives.
+Done.  
+We checked for others and changed them according to the Chicago Manual of Style. 
+For instance, the manual recommends not to hyphenate `adverb ending in ly + participle or adjective' even it appears before a noun (e.g., maximally overlapping batches); therefore we removed the hyphen from these phrases.
 \medskip

### 2014-07-17 AE_Reponse.tex
More corrections

@@
 We created a new section, \S 5.4 (Computational Efficiency), to study the computational efficiency of overlapping estimators in the stochastic optimization setting. 
-%When an algorithm has warmstarting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
+%When an algorithm has warm starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
 We discussed efficiency for a given functional form of the solution time per batch. 
-%Depending on the effectiveness of warmstarting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
+%Depending on the effectiveness of warm starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
 %\medskip 
 In addition, based on the comments of Referee 1, we studied efficiency of overlapping estimators compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with equivalently lower variances.
-Our results indicate that when warmstarting is effective, overlapping is computationally more efficient.
-Even in cases where the effectiveness of warmstarting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\bigskip
+Our results indicate that when warm starting is effective, overlapping is computationally more efficient.
+Even in cases where the effectiveness of warm starting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\bigskip
 

### 2014-07-17 omrp_lb_rev.tex
More corrections

@@
 To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
-In this paper, we show that the same benefits of nearly the same bias and lower variances relative to nonoverlapped counterparts can be obtained from overlapping batches when used in a stochastic optimization setting.
+In this paper, we show that the same benefits of nearly the same bias and lower variances relative to their nonoverlapped counterparts can be obtained from overlapping batches when used in a stochastic optimization setting.
 
@@
 due to the inequality $\e{\zs_m} \leq \zs$ \citep{Mak1999,norkin_pflug_ruszczynski_98}.
-This bound improves as the sample size increases, that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$.  
+This bound improves as the sample size increases; that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$.  
 A straightforward estimate of $\e{f(\xh,\xit)}$ is the sample mean, $\frac{1}{m} \sum_{i=1}^m f(\xh,\xiti)$. 
@@
 Computing the above optimality gap estimate involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis.
-As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$) and averages them to obtain a point estimator.
+As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$), and averages them to obtain a point estimator.
 The sample variance of these estimators is used to form confidence intervals (CIs) for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
@@
 Our aim is to apply the idea of overlapping batches to MRP.  
-The motivation behind using overlapping in this context is twofolds. 
+The motivation behind using overlapping batches in this context is twofold. 
 First, overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
 %Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
-Second, in some cases, generating the realizations $\xit^1, \xit^2, \dots$ to form sampling approximations of (\ref{eq:sto_prog}) can be computationally expensive and overlapping makes the most of the generated observations.
+Second, in some cases, generating the realizations $\xit^1, \xit^2, \dots$ to form sampling approximations of (\ref{eq:sto_prog}) can be computationally expensive, and in these cases, overlapping makes the most of the generated observations by reusing data.
 
 %The following are four specific contributions of this article. 
-The contributions of this article are as follows. 
+The contributions of this article are as follows: 
 \begin{itemize}
 \item[(i)] We formulate an overlapping batch means variant of MRP, where the degree of overlap can be chosen by the user.  
-%This paper applies OBM to assessing solution quality in stochastic optimization. 
-%Specifically, an overlapping batch means variant of MRP is formulated, where the degree of overlap can be chosen by the user. 
 This application of OBM is novel because each batch mean estimator includes an internal minimization, which has not been studied in the literature.
@@
 
-\item[(iii)] We  present computational results to examine small-sample behavior. 
+\item[(iii)] We examine small-sample behavior of the estimators through numerical examples. 
 Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.
 
-\item[(iv)] As the degree of overlap increases, the number of batches and optimization problems solved increases because we need to solve a sampling problem per batch. 
-At the same time, variances of the estimators are lowered, and when warmstarting is available, solution time per batch can decrease, resulting in efficiency gains. 
+\item[(iv)] As the degree of overlap increases, the number of batches---and optimization problems solved---increases because we need to solve a sampling problem per batch. 
+At the same time, variances are lowered, and when warm starting is available, solution time per batch can decrease, yielding efficiency gains. 
 We explore this trade-off between computation time and lower variances.
-% and efficiency gains. 
-%We explore the overall computation time versus lower variances and efficiency gains trade-off. 
-Our results indicate that when warmstarting is effective, overlapping is computationally more efficient relative to estimators formed via nonoverlapping batches.
-%Our results indicate that overlapping can indeed increase computational efficiency, especially when warmstarting is effective. 
-We provide guidelines on selecting the degree of overlap based on computational efficiency and demonstrate efficiency on a newsvendor problem. 
+Our results indicate that when warm starting is effective, overlapping estimators are computationally more efficient than those formed via nonoverlapping batches.
+Based on this study, we provide guidelines on selecting the degree of overlap and demonstrate efficiency on a newsvendor problem. 
 \end{itemize}
@@
 An earlier version of the paper appeared in \citep{love2011overlapping}. 
-This paper contains a number of additional results. 
-% compared to its earlier conference proceedings version. 
-Most of the theoretical results are new, including asymptotically lower variances of the overlapping estimators, asymptotic validity of the interval estimators, and the {\it almost sure} convergence of the variance estimator.
-These results are achieved through an assumption on the fast rate of convergence of the sampling problem's solution to the unique optimal solution, which is satisfied by several classes of (\ref{eq:sto_prog}); see \S \ref{subsec:assumptions}.
+Most of the theoretical results in the current version of the paper are new, including {\it almost sure} convergence and asymptotically lower variances of the overlapping variance estimators, and asymptotic validity of the interval estimators.
+These results are achieved through a stronger assumption on the rate of convergence of the sampling problem's solution to the unique optimal solution, which is satisfied by several classes of (\ref{eq:sto_prog}); see \S \ref{subsec:assumptions}.
 We also present additional computational results, including those from a large-scale problem, and study computational efficiency of the overlapping MRP method.
@@
 We end in \S \ref{sec:concl} with a summary and conclusions.
-
-%In this paper, we extend MRP by overlapping the batches similar to the overlapping batch means (OBM) introduced by Meketon and Schmeiser \citep{Meketon1984}.
-
-%We explore the use of overlapping batches for assessing solution quality in stochastic programs.
-%Similar to Welch \citep{Welch1987} and Song and Schmeiser \citep{Song1992}, we consider partial overlap between batches to reduce computational effort in our setting.
-%The contributions of this paper are:
-%\begin{itemize}
-%	\item Formulate the overlapping multiple replications procedure for stochastic programs.
-%	\item Give conditions under which the point estimators are strongly consistent (that is, they converge almost surely (a.s.) as opposed in to in probability; referred to simply as consistent from this point on).
-%	\item Demonstrate that the classical variance reduction results are achieved for stochastic programs.
-%	\item Show the asymptotic validity of the resulting confidence intervals.
-%	\item Present computational results on two-stage stochastic linear and integer programs with recourse to examine small sample behavior.  
-%		Our experiments indicate that the asymptotic variance reduction is achieved with small sample sizes, while bias and coverage probability are unaffected.
-%\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   %    %    %    %    %    %
-
-%\bigskip
-
-% We present variants of . .
-
-%\bigskip
-
-%Batch means have been used in stochastic programming to assess solution quality and we show that. . . 
-%\bigskip
-
-%What happens when overlapping batches are used in a stochastic optimization setting?
-Can we obtain the same benefits from overlapping batches as we do in a non-optimized setting?
-In this paper, we answer the second question in the affirmative.
-We provide conditions under which the same benefits can be obtained by overlapping for a class of stochastic optimization problems.
-A natural setting where batch means is used in stochastic optimization is solution validation.
-This is referred to as the Multiple Replication Procedure, where each replication is essentially a batch means.
-
-%\bigskip 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   %    %    %    %    %    %
 
@@
 
-Overlapping batch means reuses a subset of the observations from one batch to form the next batch. 
-As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
-In the nonoverlapping case, there are only two batches:
-% the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
-$y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
-In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch $y^3, y^4, \dots, y^{m+2}$, and so on.  
-This is what we call the \emph{maximally-overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
-It is possible to vary the degree of overlap between neighboring batches. 
-This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
-%
-The overlapping batch means 
-%formed using the batch nonoverlap parameter $1 \leq \gamma < m$ 
-are no longer independent. 
-However, by simply reusing the data in this fashion one obtains a better variance estimator. 
-That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
-%the overlapping estimator has 
-a lower asymptotic variance than its nonoverlapping counterpart.
-
+Overlapping batch means modifies nonoverlapping batch means by reusing a subset of observations from one batch to form the next batch. 
+%As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
+%In the nonoverlapping case, there are only two batches:
+%% the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
+%$y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
+%In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch $y^3, y^4, \dots, y^{m+2}$, and so on.  
+%This is what we call the \emph{maximally overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
+%It is possible to vary the degree of overlap between neighboring batches. 
+%This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
+%%
 In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
-For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally-overlapping case of \citet{Meketon1984}.  
+For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
 In general, $\gamma$ can take any integer value between and including $[1,m]$. 
@@
 \end{equation}
-With $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).
-With $\gamma=1$ (the maximally-overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \citep{Meketon1984}.
+
+The overlapping batch means 
+formed using $1 \leq \gamma < m$ 
+are no longer independent. 
+However, by simply reusing the data in this fashion one obtains a better variance estimator. 
+That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
+%the overlapping estimator has 
+a lower asymptotic variance than its nonoverlapping counterpart. 
+Observe that with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).
+With $\gamma=1$ (the maximally overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \citep{Meketon1984}.
 This slightly different denominator 
-makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits of nearly the same bias and lower variances relative to its counterpart obtained via nonoverlapping batches \citep{Song1992}.
+makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits of nearly the same bias and lower variance relative to its counterpart obtained via nonoverlapping batches \citep{Song1992}.
 
-The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $0\leq \gamma< m$ relative its nonoverlapping counterpart 
+The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $1\leq \gamma< m$ relative its nonoverlapping counterpart 
 %$\var{\vtm{\ybb}}$ 
 depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$. 
-The maximally-overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
-\cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally-overlapping cases. 
+The maximally overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
+\cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally overlapping cases. 
 Under appropriate conditions, the results of \cite{damerdji1995mean}, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
@@
 as the batch size $m$ and then the number of batches $n/m$ tend to infinity. 
-In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches, $\beta_0 = \frac{4}{3}$ for maximally overlapping batches, and more generally, $\beta_{\gammab}$ is twice the value of 
+In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches and $\beta_0 = \frac{4}{3}$ for maximally overlapping batches.  
+More generally, $\beta_{\gammab}$ is twice the value of 
 \begin{equation} \label{eq:var_reduct_formula}
@@
 \end{equation}
-where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument.
+where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument \citep{Welch1987}.
 If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
-This means that the maximally-overlapping variance estimator has a variance that is two-thirds ($66.67\%$) of the nonoverlapping estimator.
+This means that the maximally overlapping variance estimator has a variance that is two-thirds ($66.67\%$) of the nonoverlapping estimator.
 As the degree of overlap decreases, the variance increases. 
-When only half of the observations overlap ($\gammab = 1/2$ or $\gamma=m/2$), for instance, the variance is 75\% of the nonoverlapping counterpart.
+When only half of the observations overlap 
+($\gammab = 1/2$),
+%($\gammab = 1/2$ or $\gamma=m/2$),
+for instance, the variance is 75\% of the nonoverlapping counterpart.
 
-A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gammab}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gammab}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) \citep{Welch1987}.
+A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gammab}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gammab}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}).
+%\citep{Welch1987}.
 %If $\ogb$ is an integer, $d_{\gammab} = \frac{3}{2+\gammab^2}$.  
-For the maximally-overlapping batch means, the degrees of freedom is $d_{\gammab} = \frac{3}{2}$.
+For the maximally overlapping batch means, the degrees of freedom is $d_{\gammab} = \frac{3}{2}$.
 
@@
 
-%Given a candidate solution $\xh \in \X$ to (\ref{eq:sto_prog}), the task is to estimate its optimality gap $\e{f(\xh,\xit)} - \zs$.  
-%Recall that MRP uses the upper bound on the optimality gap, $\e{f(\xh,\xit)} - \e{\zs_m}$ (for a given sample size $m$), to construct a point estimator and a CI using the nonoverlapping batches method described above.
-
-Taking $n$ observations of the random variables $\xit$ and splitting them into $k$ {\it nonoverlapping} batches of size $m$, define 
+Taking $n$ observations of $\xit$ and splitting them into $k$ {\it nonoverlapping} batches of size $m$, define
 \begin{align} 
@@
 The optimality gap estimator $\gb_j$ is similar to the nonoverlapping $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
-Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is the optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
-As before, after $k$ estimates are obtained, the overall mean of these estimates $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
+Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is an optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
+As before, after $k$ batch-means estimators are obtained, the overall mean of these estimators $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
 The variance estimator is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in an approximate $(1-\alpha)$-level one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$.
@@
 In this setting, the computational effort may increase with data reuse because we need to solve a sampling problem (SP$_m$) for each batch.  
-The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches, and (ii) using warmstarting to quickly solve the sampling approximations with overlapping samples.
+The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches (but a higher variance), and (ii) using warm starting to quickly solve the sampling approximations with overlapping observations.
 %We use the batch nonoverlap parameter $\gamma$ as before to allow for varying degrees of overlap in OMRP. 
-We examine the effect of warmstarting and any resulting computational efficiency gains in \S \ref{ssec:compeff}. 
+We investigate the balance of computational efficiency gains from warm starting versus variability of the estimators in \S \ref{ssec:compeff}. 
 We are now ready to define the OMRP estimators.
-
-%First, near-optimal variance reduction can be obtained by partially overlapping the batches \citep{Welch1987,Song1992}.  
-%Partial overlapping results in a smaller number of batches; hence, fewer optimization problems need to be solved.
-%Second, in many solution methods, warmstarting can be used to quickly solve the sampling approximations with overlapping samples, considerably reducing solution time.
-%In this paper, we consider a parametrized degree of overlap, where the degree of overlap is at the user's discretion, and examine this both theoretically and empirically. 
-% THIS LAST SENTENCE NEEDS TO CHANGE!
 
@@
 \begin{align}
-	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} \\
+	\gb_{lj} & = \frac{1}{m_l} \sum_{i=1}^{m_l} \left[ f(\xh,\xit^{\gamma_l(j-1)+i}) - f(\xs_j,\xit^{\gamma_l(j-1)+1}) \right],\ \ \ j = 1, 2, \dots, \nbl, \label{eq:gbar} 
+\end{align}
+\begin{align}
 	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
@@
 First, we show the consistency of the point estimators of optimality gap, $\gbb_l$, and variance, $n_l VG_l$. 
-Then, we provide conditions under which the asymptotically lower variances are observed for the OMRP variance estimator relative to nonoverlapping MRP estimator.  
+Then, we provide conditions under which the OMRP variance estimator achieves asymptotically lower variances relative to the MRP estimator.  
 Finally, we show the asymptotic validity of the OMRP interval estimator.
@@
 We use $\mu_{\xh} := \e{f(\xh,\xit) - f(\xs,\xit)}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
-With i.i.d.\ sampling, $\e{\db_{lj}}=\e{\dbb_l}=\mu_{\xh}, \ \forall l,j$ and by (\ref{eq:varvarred}), $\frac{n_l}{m_l} \var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$ under appropriate conditions.
+With i.i.d.\ sampling, $\e{\db_{lj}}=\e{\dbb_l}=\mu_{\xh}, \ \forall l,j$, $\var{\dbb_l}=\sigma^2_{\xh}/n_l, \ \forall l$, and under appropriate conditions, $\frac{n_l}{m_l} \var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$  by (\ref{eq:varvarred}).
 
@@
 
-To prove OMRP estimators have asymptotically lower variances compared to the nonoverlapping MRP estimator, we wish to show that 
+To prove OMRP variance estimators have asymptotically lower variances when compared to the MRP variance estimator, we wish to show that 
 $$
@@
         Let $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$.
-		  Furthermore, let $A_j^f$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$ denote the fringe batches at the front of each set of nonoverlapping batches, $A_j^c$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots n_b - \left\lceil \gammab^{-1} \right\rceil$ denote the center batches, and let $A_j^e$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$ denote the fringe batches at the end of each set of nonoverlapping batches.
+		  Furthermore, let $A_j^c$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, n_b - \left\lceil \gammab^{-1} \right\rceil$ denote the center batches, and let $A_j^f$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$ and $A_j^e$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$ denote the fringe batches at the front and end of each set of nonoverlapping batches, respectively.
 		  Continuing from (\ref{eq:vvar_conv_pf_1}),
@@
 		} \\
-		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^c \right)^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 } \\
+%		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^c \right)^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 } \\
 		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j^c \right)^2 }
@@
 	\end{align*}	
-	These equalities follow because each front fringe batch $\e{(A_j^f)^2}$ has an identical pair in the end fringe batch $\e{(A_j^e)^2}$ and all center batches have identical values of $\e{(A_j^c)^2}$.
+	The last equality follows because each front-fringe batch's $\e{(A_j^f)^2}$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$  has an identical pair in an end-fringe batch's $\e{(A_j^e)^2}$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$, and all center batches have identical values of $\e{(A_j^c)^2}$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, n_b - \left\lceil \gammab^{-1} \right\rceil$.
 	As a result, we have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{dt}\right)^2n_b^2 < (2m)^2$.  
@@
 A hypothesis of Theorem \ref{thm:varvar_conv} is a batching structure that ensures convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\beta_{\gammab} \sigma^4_{\xh}$, ensuring the mean-square consistency of $n_l VD_l$.
-\citet{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $4+\epsilon$ finite moments assumption A2$^\prime$.
+\citet{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $(4+\epsilon)$th-finite-moments assumption A2$^\prime$.
 With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.
-
-%We end our theoretical properties in the next section by examining the CIs formed using OMRP.
 
@@
 
-The overlapping variance estimator for stochastic programs displays the same desirable properties, detailed in \S \ref{subsec:conv} and \S \ref{ssec:var_reduct}, as in simulation, but we must still check that it results in a valid CI.
-Let $I^G_l = \gbb_l + t_{d_l,\alpha} \sqrt{VG_l}$ be the width of the one-sided CI generated by OMRP. 
-The degrees of freedom $d_l$ is the inverse of (\ref{eq:var_reduct_formula}) using $\frac{\gamma_l}{m_l}$ instead of $\gammab$.
+The overlapping variance estimator for stochastic programs displays the same desirable properties, such as consistency and reduced variability, as in simulation, but we must still check that it results in a valid CI.
+Let $I^G_l = \gbb_l + t_{d_l \left( k_l-1\right),\alpha} \sqrt{VG_l}$ be the width of the one-sided CI generated by OMRP. 
+Here, $k_l= \left\lfloor\frac{n_l}{m_l}\right\rfloor $ is the number of batches formed in the nonoverlapping counterpart, and the degrees of freedom increase $d_l$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}) using $\frac{\gamma_l}{m_l}$ instead of $\gammab$.
 
@@
         It is suffices to show $Y_lZ_l = \frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, where $\Rightarrow$ denotes convergence in distribution.
-			If $\frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, because $t_{d_l,\alpha} \rightarrow z_{\alpha}$ as $l \rightarrow \infty$, we obtain the desired result by rearranging the terms in $\p{\mu_\xh \leq I^G_l}$ and taking the limit as $l \rightarrow \infty$.
+			If $\frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, we obtain the theorem's result by rearranging the terms in $\p{\mu_\xh \leq I^G_l}$ and taking the limit as $l \rightarrow \infty$ because $t_{d_l(k_l -1),\alpha} \rightarrow z_{\alpha}$ as $l \rightarrow \infty$.
         First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  
@@
 Here, $t(\gammab)$ is the average computation time per batch, which is multiplied by the number of batches.
-Warmstarting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
+warm starting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
 
@@
 In cases where the exponent $p$ can be estimated, the above theoretical method may be used to determine a reasonable value for $\gammab$.
-We recommend that users perform preliminary computations to determine how computational time per batch changes as $\gammab$ changes when warmstarting is available. 
+We recommend that users perform preliminary computations to determine how computational time per batch changes as $\gammab$ changes when warm starting is available. 
 We can see in Figure \ref{fig:efficiency} that for some values of $p$, efficiency gain is nearly flat over a region of $\gammab$.
@@
 Because overlapping may increase computational burden in the stochastic optimization setting, we have examined computational efficiency of OMRP by jointly considering computation time and variance. 
-Our results indicate that when warmstarting is effective, efficiency can be observed across a wide range of overlapping degrees, and when warmstarting is less effective, efficiency increases for only small degrees of overlap.
+Our results indicate that when warm starting is effective, efficiency can be observed across a wide range of overlapping degrees, and when warm starting is less effective, efficiency increases for only small degrees of overlap.
 We have empirically demonstrated computational efficiency by solving a newsvendor problem using insertion sort.

### 2014-07-18 omrp_lb_rev.tex
Some more...
Mainly final pass through the paper to polish up

@@
 
-\subsection{Lower Variances}
+\subsection{Asymptotically Lower Variances}
 \label{ssec:var_reduct}
@@
 			If $\frac{\gbb_l - \mu_\xh}{\sqrt{VG_l}} \Rightarrow N(0,1)$, we obtain the theorem's result by rearranging the terms in $\p{\mu_\xh \leq I^G_l}$ and taking the limit as $l \rightarrow \infty$ because $t_{d_l(k_l -1),\alpha} \rightarrow z_{\alpha}$ as $l \rightarrow \infty$.
-        First, we show that $|X_l - Y_l| \rightarrow 0$, a.s.  
+        Toward this end, we first show that $|X_l - Y_l| \rightarrow 0$, a.s.  
 		  Observe that $|X_l - Y_l| > 0$ if and only if $|\dbb_l - \gbb_l| > 0$.  
@@
 
-In the previous section, we proved asymptotic results regarding the OMRP estimators. 
+In the previous section, we proved various asymptotic results regarding the OMRP estimators. 
 In this section, we apply OMRP to several test problems and examine small-sample behavior. 
@@
 Then, we present and discuss the numerical results in \S \ref{ssec:results}.
+The trade-off between overall computational effort and variability of the estimators is investigated last, in \S \ref{ssec:compeff}, where we also provide guidelines on selecting the degree of overlap.
 
@@
 The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
-We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an {\it estimated} $\mu_{\xh} = 1.08$. 
-Because the optimal solution of DB1 is unknown, a Latin hypercube sample of size 50,000 was used to estimate $\mu_{\xh}$, which was then used below to estimate the coverage probability of the OMRP CIs for this test problem.
+We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an estimated $\mu_{\xh} = 1.08$. 
+Because the optimal solution of DB1 is unknown, we used a Latin hypercube sample of size 50,000 to estimate $\mu_{\xh}$.
+We then used this value of $\mu_{\xh}$ to estimate the coverage probability of the OMRP CIs for DB1.
 
@@
 We used a total sample size of $n = 30 m$, with several values of the batch size $m=100, 200, \ldots$. 
-Then, at each value of $m$, we formed the OMRP estimators with varying amounts of overlap. 
+Then, at each value of $m$, we formed the OMRP estimators with varying degrees of overlap. 
 We also set $\alpha=0.10$, forming 90\% CIs on the optimality gap using the ORMP estimators. 
@@
 Figures~\ref{fig:varvar1} and \ref{fig:varvar2} show the variance of OMRP variance estimators, normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
-The solid lines in these figures show the theoretical relative variance from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
+The solid lines in these figures show the theoretical relative decreases in variance from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
 Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
 These experiments suggest that lower variances can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
-The variance of OMRP variance estimators in DB1 can be less than the asymptotic amount established by Theorem \ref{thm:varvar_conv}. %for the small sample sizes used in these experiments. 
+The variance of OMRP variance estimators for DB1 can be less than the asymptotic amount established in Theorem \ref{thm:varvar_conv}. %for the small sample sizes used in these experiments. 
 This is because DB1 has not yet been solved to optimality due its size; therefore, it may lack a unique optimal solution. 
 %, violating assumption A3. (?)
-Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to reduce the variances.
+Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to lower the variances.
 
@@
 The increased computational workload from solving overlapping batches raises the question of the computational efficiency of this method to estimate $VG$.
-In this setting, computational efficiency can be defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computational time spent to generate $VG$ for a given value of $\gammab$.
-Because the variance of the overlapping variance estimator relative to the nonoverlapping (MRP) variant is known from (\ref{eq:var_reduct_formula}), we need only examine the computational time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$.
+In this setting, computational efficiency can be defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computation time spent to generate $VG$ for a given value of $\gammab$.
+Because the variance of the overlapping variance estimator relative to the nonoverlapping (MRP) variant is known from (\ref{eq:var_reduct_formula}), we need only examine the computation time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$.
 Here, $t(\gammab)$ is the average computation time per batch, which is multiplied by the number of batches.
-warm starting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
+Warm starting an algorithm may be used to decrease the computation time per batch for $\gammab < 1$, leading to a possible increase in computational efficiency.
 
 To investigate computational efficiency, we assumed that computation time per batch can be approximated as $t(\gammab) \propto \gammab^p$ for some $p \geq 0$.
-Results for various values of $p$ are shown in Figure \ref{fig:efficiency}(a). 
+The results for various values of $p$ are shown in Figure \ref{fig:efficiency}(a). 
 This figure is constructed using $m = 1,000$, but the results do not change substantially with different values of $m$.
@@
 Efficiency gains increase with larger exponent $p$ but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
-At $p=1$, i.e., for problems where computational time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches of \cite{Meketon1984}.
+At $p=1$, i.e., for problems where computation time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches of \cite{Meketon1984}.
 When $p=0.9$, computational efficiency is maximized at around $\gammab=0.3$.
-When $p$ is $0.71$, on the other hand, computational efficiency is observed for values of $\gammab$ from slightly lower than $0.3$ to $1$, and efficiency is maximized at a relatively flat region between $\gammab=0.5$ and $\gammab=0.8$.
+When $p$ is $0.71$, on the other hand, computational efficiency is observed for values of $\gammab$ ranging from slightly lower than $0.3$ to $1$, and efficiency is maximized at a relatively flat region between $\gammab=0.5$ and $\gammab=0.8$.
 
@@
 The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency}(b), where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency}(a).
-It appears that empirical observations match with the theoretical efficiency calculations well.
+It appears that empirical observations match the theoretical efficiency calculations well.
 
@@
 Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison}. 
-This curve shows the increased computational effort in MRP due to an increased number of batches to obtain the same variance of OMRP across $\gammab$.
+This curve shows the increased computational effort in MRP because of an increased number of batches to obtain the same variance as OMRP across $\gammab$.
 If the work increase by OMRP is less than this solid black curve, then OMRP is computationally more efficient than increasing the number of batches in MRP. 
@@
 In cases where the exponent $p$ can be estimated, the above theoretical method may be used to determine a reasonable value for $\gammab$.
-We recommend that users perform preliminary computations to determine how computational time per batch changes as $\gammab$ changes when warm starting is available. 
+We recommend that users perform preliminary computations to determine how computation time per batch changes as $\gammab$ changes when warm starting is available. 
 We can see in Figure \ref{fig:efficiency} that for some values of $p$, efficiency gain is nearly flat over a region of $\gammab$.
@@
 This choice keeps efficiency high while decreasing computation time and preventing large decreases in efficiency in the event that $p$ was overestimated.
-For example, in the case of NVD, we recommend the use of value $\gammab=0.8$ as this value provides high computational efficiency with minimal overall computation time across values of $\gammab$ with high efficiency.
+For example, in the case of NVD, we recommend the use of $\gammab=0.8$ 
+because this value provides minimal overall computation time across all values of $\gammab$ with the highest efficiency level for this problem.  
 For situations where $p > 0$ but its size cannot be readily measured or estimated, we recommend selecting a large value of $\gammab$ such as $0.9$.
@@
 The authors are also grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the paper. 
-%This research has been supported in part by the National Science Foundation under Grant(s)  EFRI-0835930 and CMMI-1345626 ??? 
+%This research has been supported in part by the National Science Foundation under Grant(s) DMS-0602173  EFRI-0835930 and CMMI-1345626 ??? 
 An earlier version of this paper appeared in \citep{love2011overlapping}.

### 2014-07-19 AE_Reponse.tex
FINAL PASS THROUGH ALL DOCUMENTS

@@
 %When an algorithm has warm starting capability, as the degree of overlapping increases,  solution time per batch could decrease; as a result, computational efficiency gains could be observed.  
-We discussed efficiency for a given functional form of the solution time per batch. 
+We analyzed efficiency for a given functional form of the solution time per batch. 
 %Depending on the effectiveness of warm starting, maximizing computational efficiency provides guidelines on selecting the degree of overlapping. 
 %\medskip 
-In addition, based on the comments of Referee 1, we studied efficiency of overlapping estimators compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with equivalently lower variances.
+In addition, based on the comments of Referee 1, we studied the efficiency of OMRP compared to increasing the number of batches in MRP to obtain (nonoverlapping) estimators with equivalently lower variances.
 Our results indicate that when warm starting is effective, overlapping is computationally more efficient.
-Even in cases where the effectiveness of warm starting is quite low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\bigskip
+Even in cases where the effectiveness of warm starting is low, computational efficiency can be observed with a low degree of overlap (e.g., when approximately 10\% of observations are overlapped).\medskip
 
@@
 We illustrated these results on the newsvendor problem using insertion sort. 
-Our experiments show that (i) the functional form used provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping levels, and (iii) this analysis provides a way to select the degree of overlapping by maximizing efficiency.\bigskip
+Our experiments show that (i) the functional form used to express solution time per batch provides a good representation, (ii) increased computational efficiency over the nonoverlapping counterpart is indeed observed over a range of overlapping degrees, and (iii) this analysis provides a way to select the degree of overlap by maximizing efficiency and then minimizing overall computation time.\bigskip
 
 \noi
-Finally, we provided guidelines on selecting the degree of overlap at the end of \S 5.4 (Computational Efficiency) based on our study. 
-We believe the paper has improved as a result of the study of computational efficiency. 
+As a result of this study, we provided guidelines on selecting the degree of overlap in OMRP at the end of \S 5.4 (Computational Efficiency).  
+We believe the paper has substantially improved as a result of the study of computational efficiency. 
 Thank you for this suggestion. 
@@
 We established improved computational efficiency on the newsvendor problem using insertion sort.
-We also (i) changed \S 1 (Introduction) to clearly motivate the study and argue usefulness of the results, paying specific attention to efficiency gains; (ii) updated \S 6 (Conclusions) to summarize these new results, again paying attention to computational efficiency; (iii) provided a study of computational efficiency gains of overlapping in the context of assessing solution quality in stochastic programming in the new \S 5.4 (Computational Efficiency); and finally (iv) updated the abstract.
+We also studied the computational efficiency of overlapping for assessment of solution quality in stochastic programming in the new \S 5.4 (Computational Efficiency), based on your earlier comments. 
+In addition, we (i) changed \S 1 (Introduction) to clearly motivate the study and argue usefulness of the results, (ii) updated \S 6 (Conclusions) to summarize these new results, paying specific attention to computational efficiency, and finally (iv) updated the abstract.
 %(Please see our response to the previous comment.)
@@
 This sentence was removed as a result of the computational efficiency study. 
-Based on the examination of computational efficiency, we provided new guidelines on selecting the degree of overlapping.
+Based on the examination of computational efficiency, we provided new guidelines on selecting the degree of overlap.
 

### 2014-07-19 EinC_Reponse.tex
FINAL PASS THROUGH ALL DOCUMENTS

@@
 We very much appreciate everyone's time and constructive comments. 
-As a result of the revision, the wording and content of the paper, compared to the Winter Simulation Conference Proceedings version, has partly changed.
+As a result of the revision, the wording and content of the paper, compared to the Winter Simulation Conference Proceedings version, has changed.
 We also edited the paper to improve exposition and tried to cut back word for word copying during this process.  
@@
 \noindent
-We added a paragraph in Section 1 (Introduction) detailing what has been done over the WSC proceedings paper. 
-Please see the first paragraph on page 5 of the revised manuscript.\bigskip
+We added a paragraph in \S 1 (Introduction) detailing what has been done over the WSC proceedings paper. 
+Please see the first paragraph on page five of the revised manuscript.\bigskip
 

### 2014-07-19 omrp_lb_rev.tex
FINAL PASS THROUGH ALL DOCUMENTS

@@
 		\caption{
-		Computational efficiency of the OMRP variance estimator relative to the (nonoverlaping) MRP variance estimator measured
+		Computational efficiency of the OMRP variance estimator relative to the (nonoverlapping) MRP variance estimator measured
 		(a) theoretically and
@@
 Empirical results indicate that asymptotic reductions in variance of the variance estimator show a similar decrease in OMRP at small sample sizes, while bias and coverage probability remain unaffected.
-Because overlapping may increase computational burden in the stochastic optimization setting, we have examined computational efficiency of OMRP by jointly considering computation time and variance. 
-Our results indicate that when warm starting is effective, efficiency can be observed across a wide range of overlapping degrees, and when warm starting is less effective, efficiency increases for only small degrees of overlap.
-We have empirically demonstrated computational efficiency by solving a newsvendor problem using insertion sort.
-Finally, based on our study of computational efficiency, we have provided guidelines on selecting the degree of overlap in OMRP.
+
+Overlapping may increase the computational burden in the stochastic optimization setting.
+By jointly considering computation time and variance, we have examined the computational efficiency of OMRP, and we have empirically demonstrated  efficiency by solving a newsvendor problem using insertion sort.
+Our analysis illustrates that when warm starting is effective, computational efficiency gains can be observed across a wide range of overlapping degrees.
+Even when warm starting is less effective, efficiency slightly increases for low degrees of overlap. 
+Maximizing efficiency and then minimizing total computation time suggests selecting the lowest degree of overlap across all the degrees with the highest efficiency for a given problem and solution method (with warm starting) combination.
+
+%Finally, based on our study of computational efficiency, we have provided guidelines on selecting the degree of overlap in OMRP.
+
+Overall, the results in this paper suggest that OMRP could be an efficient method to estimate optimality gaps for a class of stochastic programs when warm starting is available and/or when generating the observations is costly.
 
@@
 access to their regularized decomposition code, which was used to solve CEP1 and DB1. 
-The authors are also grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the paper. 
-%This research has been supported in part by the National Science Foundation under Grant(s) DMS-0602173  EFRI-0835930 and CMMI-1345626 ??? 
+The authors are grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the paper. 
+%This research has been supported in part by the National Science Foundation under Grants DMS-0602173 and CMMI-1345626.
+%EFRI-0835930
 An earlier version of this paper appeared in \citep{love2011overlapping}.

### 2014-12-19 Referee1_Response_fl.tex
CHANGED THE FILES
For the first look revision...

--- 2014-07-17 Referee1_Response.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\noi
 We thank the referee for the helpful comments and suggestions. 
@@
 \bigskip
-
-%%%%%%%%%%%%%%%%%
-%% Need to be careful with the minor changes. Will these be affected?
-%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
-%%    - GB
-%%%%%%%%%%%%%%%%%
 
@@
 \noi 
-%We thank the referee for this suggestion. 
 Thank you for this suggestion. 
@@
 There are cases when generating scenarios is expensive in the stochastic optimization setting as well. 
-We changed the introduction based on your, the associate editor and the other reviewer's comments. 
-We specifically added this as a motivation. 
-The motivation now appears in the first full paragraph on page 4 of the paper. 
+We changed the introduction based on your, the associate editor, and the other reviewer's comments. 
+We specifically added this as a motivation in the first full paragraph on page four of the revised paper. 
 \medskip
@@
 The results of this study are presented in a new section, \S 5.4 (Computational Efficiency).
-%We studied the computational efficiency of the OMRP estimators, based on your and the associate editor's comments, and provided a summary of our results in a new section, Section 5.4 (Computational Efficiency).
 We first approached efficiency by the reciprocal of variance multiplied by the computation time, per the associate editor's suggestion. 
@@
 We then looked at how OMRP compared to increasing the number batches in MRP to reach an equivalent variance level.
-We examined computational efficiency theoretically, assuming a functional form of the solution time per batch, and also empirically. 
+We examined computational efficiency theoretically---assuming a functional form of the solution time per batch---and also empirically. 
 For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions; thank you. 
 We found that when effective warm starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
-%All these results are presented in Section 5.4 (Computational Efficiency). 
-%Thank you for this suggestion. 
 We believe the study of computational efficiency significantly improved the paper. 
@@
 It may be still be possible to recover the same results on overlapping using this alternative  $\dbb$ but we did not pursue it here. 
-%We actually performed computations using $\gbb$ formed as a sample mean of $\gb$ values and the results were largely similar. 
 Due to the lack of theoretical results explained above, we decided not to include or discuss $\gbb$ formed as a sample mean of $\gb$ values, even though it appears as a natural choice. 
@@
 \noindent 
-We revised this section in order to improve exposition. 
+We revised this paragraph in order to improve exposition. 
 We used `smaller number of batches' based on the comments of the other referee in the new sentence. 
@@
 \noi 
-{\it Note:} This section now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
+{\it Note:} The revised sentence now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
 \medskip
@@
 We also emphasized that each front fringe batch has an identically distributed pair at the end fringes, and that all the center batches are identically distributed. 
-%Thanks for catching this. 
-\smallskip
+\medskip
 
@@
 {\it Note:} We added brackets to expectations to improve readability as suggested by the other referee.
+We also removed the second equality to save some space because this equality's result was also equally expressed in the last inequality. 
 \medskip
@@
 Done.
-% xxx Yes, it is partially because we are not sure if it has a unique optimal solution as DB1 has never been solved before. 
-%Even if it has been solved, the variance reduction is shown asymptotically but the computations are only for small sample sizes. 
-%We reworded this to reflect these points.
-%Thank you for this suggestion. 
 \medskip

### 2014-12-19 Referee2_Response_fl.tex
CHANGED THE FILES
For the first look revision...

--- 2014-07-15 Referee2_Response.tex
@@
 
-%%%%%%%%%%%%%%%%%
-%% Need to be careful with the minor changes. Will these be affected?
-%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
-%%    - GB
-%%%%%%%%%%%%%%%%%
-
 \noi  
@@
 We also clarified the motivation for the work, included new contributions based on the study of computational efficiency (contribution (iv)), and provided a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).
-%We believe the presentation of the paper significantly improved.  
-%Thank you.
+\medskip
+
+\noi 
+As a result of the revised introduction---aimed to clearly state the contributions of the paper---we decided to move the technical discussion on using overlapping batches in simulation output analysis versus assessing solution quality in stochastic optimization to \S 3 (Overlapping Multiple Replications Procedure).
+We provided `{\it Note:}'s whenever a sentence was moved when addressing your minor comments below. 
+We believe the presentation of the paper significantly improved.  
+Thank you.
 \medskip
@@
 While we removed a number of equations and shortened the text, we kept some explanations that are necessary for a reader who is not familiar with OBM (e.g., readers with an optimization focus) to follow the main ideas.
-These basic explanations appear, for instance, in the first paragraph of \S 2.1.2 (Overlapping Batch Means).  
-We hope to be able to reach a broader audience this way. 
-As a result of these changes, 
+We hope to reach a broader audience this way. 
+As a result of these changes: 
 \begin{itemize}
@@
 
-	\item[(iv)] the discussion that appeared at the beginning of \S 4.4 (previously: Variance Reduction, now: Lower Variances) is moved to this review section.\medskip
+	\item[(iv)] the discussion that appeared at the beginning of \S 4.4 (previously: Variance Reduction, now: Asymptotically Lower Variances) is moved to this review section.\medskip
 
-{\it Note:} While making the changes, we realized that `$\alpha$' was used in the current equation (3) and the statement of Theorem 2 as well as the ($1-\alpha$)-level confidence intervals.  
-Therefore, we changed `$\alpha$' in equation (3) and Theorem 2 to `$\beta_{\bar{\gamma}}$'. 
+{\it Note:} While making the changes, we realized that notation `$\alpha$' was overloaded. 
+It was used in the current equation (3) and the statement of Theorem 2 to represent the relative variances, and it was used as the level of significance in confidence intervals.  
+To remedy this issue, we changed `$\alpha$' in equation (3) and Theorem 2 to `$\beta_{\bar{\gamma}}$'. 
 \end{itemize}
@@
 \noi
-Changed.  
+Yes. Done.  
 We also went through the paper to correct other occurrences. 
@@
 \noi
-Changed. 
+Done. 
 We also went through the paper and corrected other occurrences. 
@@
 \noi
-Changed.
+Done.
 \medskip
@@
 \noi
-{\it Note:}  We moved this sentence from the paragraph on page 2 to later in the introduction to clearly state the contributions of the paper. 
-It now appears as contribution (ii) on page 4 of the revised manuscript.
+{\it Note:}  We moved this sentence from the paragraph on page two to later in the introduction to clearly and succinctly state the contributions of the paper. 
+It now appears as contribution (ii) on page four of the revised manuscript.
 \medskip
@@
 Thanks for pointing this out. 
-We corrected the wording throughout the paper. 
+We corrected the wording throughout the paper, avoiding the use of the term `variance reduction'. 
 \medskip
@@
 We made the change to the first sentence above. 
-The first sentence now appears as part of contribution (ii) and the second sentence as part of contribution (iii) on page 4 of the revised manuscript. 
-We decided not to include `also' in the second sentence as it starts a new set of contributions. 
+We reworded the second sentence because it starts a new set of contributions in the revised paper. 
+\medskip
+
+\noi
+{\it Note:}
+The first sentence now appears as part of contribution (ii) and the second sentence as part of contribution (iii) on page four of the revised manuscript. 
 \medskip
@@
 \noi
-xxx  Done. But I am not sure if it is correct this way.  
-Thank you; we went through the paper and hyphenated all the compound adjectives.
+Done.  
+We checked for other compound adjectives and changed them according to the Chicago Manual of Style. 
+For instance, the manual recommends not to hyphenate `adverb ending in ly + participle or adjective' even it appears before a noun (e.g., maximally overlapping batches); therefore we removed the hyphen from this phrase.
 \medskip
@@
 {\it Note:}
- As a result of the revised introduction---aimed to clearly state the contributions of the paper---we moved the technical discussion on using overlapping batches in simulation output analysis versus for assessing solution quality in stochastic optimization to \S 3 (Overlapping Multiple Replications Procedure).
-Consequently, this sentence now appears in \S 3. 
+This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 We also reworded these sentences to improve clarity. 
-\bigskip
+\medskip
 
@@
 {\it Note:}
-As mentioned in the previous comment, the revised sentences now appear in \S 3 (Overlapping Multiple Replications Procedure). 
+The revised sentences now appear in \S 3 (Overlapping Multiple Replications Procedure). 
 \medskip
@@
 Thanks for pointing out the ambiguity here. 
-We reworded this sentence, divided it into two sentences to improve readability, and added further explanations to remove any ambiguities. 
-\bigskip
+We reworded this sentence, divided it into two sentences to improve readability, and added further explanations to remove any remaining ambiguities. 
+\medskip
 
@@
 We revised this section in order to improve exposition. 
-We used `smaller number of batches' based on your suggestion in the revised version. 
+We used `smaller number of batches' based on your suggestion in the revised sentence. 
 \medskip
@@
 \noi
-%You are right.
 We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
 We reworded this sentence to reflect this. 
-We also went through the paper, removed other occurrences, and avoided using this term in the new text added. 
+We went through the paper and removed other occurrences of phrases like `variable amounts of overlap', `variably overlapping batches', etc.
+We also avoided using these terms in the newly added text. 
 \medskip
@@
 No. By `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to assessment of solution quality in stochastic programming). 
-We reworded this sentence to remove ambiguity. 
-Based on your earlier comments, we avoided the term `variance reduction' in the revised sentence.
-We also went through the paper and removed several uses of the word `classical' that referred to nonoverlapping batches to reduce ambiguity.
-%(as these were referring to nonoverlapping batches). 
+We reworded this sentence. 
+%Based on your earlier comments, we avoided the term `variance reduction' in the revised sentence.
+We also went through the paper and removed several uses of the word `classical' that referred to nonoverlapping batches.
+Any remaining sentences with the word `classical' only refer to the use of overlapping batches in simulation output analysis. 
 %In the current version of the paper, `classical case' is used to only indicate  the use of overlapping batches in simulation output analysis. 
@@
 Done.  
-We removed the word `corresponding' as part of the rewrite.
+We removed the word `corresponding' as part of the rewrite but added the word `overlapping' based on your suggestion.
 \medskip
@@
 We went through the paper and removed most of the ``note that'' phrases. 
-We decided to leave a couple as is (as ``notice that'') because they highlight important characteristics.  
+We decided to leave some as is (as ``notice that'') because they highlight important characteristics.  
 \medskip
@@
 \noi
-We changed this sentence and directly referred to the denominator term.
-We decided to avoid the degrees of freedom here. 
-This is because we wanted to focus on the degrees of freedom for confidence interval construction, which is discussed in both the theoretical and computational results.
-\medskip
+We changed this sentence and directly referred to the denominator.
+We decided to avoid the `degrees of freedom' here. 
+This is because we wanted to focus on the degrees of freedom for confidence interval construction, which is an important component of both our theoretical and computational results.\medskip
 
@@
 \noi
-Yes; we explicitly stated this in a sentence after we introduce $\gamma$.
+Yes. We explicitly stated this in a sentence after we introduce $\gamma$.
 \medskip
@@
 Done. 
-%We introduced the floor function before its first use, and we introduced the ceiling function right after its first use.
 \smallskip
@@
 This notation was defined before Theorem 1. 
-We moved the definitions of $\sigma_{\hat{x}}$ and $\mu_{\hat{x}}$ to the end of \S 4.2 (Nonoptimized Counterparts) to improve clarity. 
+We moved the definitions of $\sigma_{\hat{x}}$ and $\mu_{\hat{x}}$ to the end of \S 4.2 (Nonoptimized Counterparts) to improve clarity and added explanations to provide context. 
 \medskip
@@
 \noi
-We moved the discussion at the first half of this paragraph to the new, combined OBM review in \S 2.1.2 (Overlapping Batch Means). 
+We moved the discussion in the first half of this paragraph to the new, combined OBM review in \S 2.1.2 (Overlapping Batch Means). 
 We referred to equation (3) here to remind the readers the basis of the proof.
@@
 \noi
-No, we did not.   
-We added explanations in the proof Theorem 3, discussing how $t_{d_l,\alpha}$ factors in the proof. 
+No, we had not.   
+We added explanations in the proof Theorem 3, discussing how $t_{d_l(k_l - 1),\alpha}$ factors in the proof. 
 \medskip
 
+\noi 
+{\it Note:}
+While making this revision we noticed a typo. 
+We changed $t_{d_l,\alpha}$ to $t_{d_l(k_l - 1),\alpha}$, where $k_l=\left\lfloor \frac{n_l}{m_l} \right\rfloor$ is the number of batches used in the nonoverlapping counterpart. 
+\medskip
+
+\newpage
 \begin{itemize}

### 2014-12-19 omrp_lb_fl.tex
CHANGED THE FILES
For the first look revision...

--- 2014-07-19 omrp_lb_rev.tex
@@
 We give conditions under which the resulting optimality gap point estimators are strongly consistent, interval estimators are asymptotically valid, and the variance estimators have the same asymptotically lower variances relative to their nonoverlapping counterparts as the classical OBM estimators \citep{Meketon1984,Welch1987}.
-Computational experiments for several test problems are presented, examining the small-sample behavior and the computational efficiency of the overlapping batches method in this context.\medskip
+We investigate computational efficiency, a combined measure of variance and computation time, providing guidelines on the degree of overlap.  
+Numerical experiments on several test problems are presented, examining the small-sample behavior and the empirical computational efficiency of the overlapping batches method in this context.  
+\medskip
 
@@
 While other sampling schemes are possible, let $\xit^1, \xit^2, \dots, \xit^m$ be an independent and identically distributed (i.i.d.) sample from the distribution of $\xit$.
-A sampling approximation of (\ref{eq:sto_prog}), often called the sample average approximation, is given by
+A sampling approximation of (\ref{eq:sto_prog}), often called the sample average approximation, is given by\vspace*{-0.07in}
 \begin{align} \tag{SP$_m$} \label{eq:sto_prog_m}
@@
 Even when warm starting is less effective, efficiency slightly increases for low degrees of overlap. 
-Maximizing efficiency and then minimizing total computation time suggests selecting the lowest degree of overlap across all the degrees with the highest efficiency for a given problem and solution method (with warm starting) combination.
+Maximizing efficiency and then minimizing total computation time, we recommend  selecting the lowest degree of overlap across all the degrees with the highest efficiency for a given problem and solution method (with warm starting) combination.
 
@@
 
-Overall, the results in this paper suggest that OMRP could be an efficient method to estimate optimality gaps for a class of stochastic programs when warm starting is available and/or when generating the observations is costly.
+Overall, the results in this paper suggest that OMRP could be an efficient method to estimate optimality gaps for a class of stochastic programs when warm starting is available and/or generating the observations is costly.
 

### 2014-12-19 omrp_lb_fl.tex
R2 minor edits
thru end of p.5

@@
 In this paper, we apply the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
-We give conditions under which the resulting optimality gap point estimators are strongly consistent, interval estimators are asymptotically valid, and the variance estimators have the same asymptotically lower variances relative to their nonoverlapping counterparts as the classical OBM estimators \citep{Meketon1984,Welch1987}.
+We give conditions under which the resulting optimality gap point estimators are strongly consistent, the optimality gap interval estimators are asymptotically valid, and the OBM variance estimators of optimality gap have asymptotically lower variances relative to their nonoverlapping counterparts \citep{Meketon1984,Welch1987}.
 We investigate computational efficiency, a combined measure of variance and computation time, providing guidelines on the degree of overlap.  
@@
 \cite{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
-More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \citep{Meterelliyoz_etal_12}.
+More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \cite{Meterelliyoz_etal_12}.
 To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
-In this paper, we show that the same benefits of nearly the same bias and lower variances relative to their nonoverlapped counterparts can be obtained from overlapping batches when used in a stochastic optimization setting.
+In this paper, we show that the overlapping batches achieve nearly the same bias and lower variances relative to their nonoverlapped counterparts when used in a stochastic optimization setting.
 
@@
 
-Computing the above optimality gap estimate involves solving an optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis.
+Computing the above optimality gap estimate involves solving the optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis.
 As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$), and averages them to obtain a point estimator.
@@
 With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
-It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \citep{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
+It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \cite{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
 Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
-
-%When this confidendence interval on the optimality gap is too large, it can be due to three reasons.
-First, $\xh$ can be far from optimal; second, bias can be large; third, the sampling error can be large.
-%We note that for some problems, bias is a more prominent issue and for others, sampling error is the larger issue. 
-%When bias is relatively small, overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved confidence intervals.
 
@@
 First, overlapping could help to obtain better variance estimators with simple data reuse, resulting in improved CIs.
-%Especially for problems where sampling error is dominant, this simple data reuse method could yield better estimators.
 Second, in some cases, generating the realizations $\xit^1, \xit^2, \dots$ to form sampling approximations of (\ref{eq:sto_prog}) can be computationally expensive, and in these cases, overlapping makes the most of the generated observations by reusing data.
 
-%The following are four specific contributions of this article. 
 The contributions of this article are as follows: 
@@
 
-An earlier version of the paper appeared in \citep{love2011overlapping}. 
-Most of the theoretical results in the current version of the paper are new, including {\it almost sure} convergence and asymptotically lower variances of the overlapping variance estimators, and asymptotic validity of the interval estimators.
+An earlier version of the paper appeared in \cite{love2011overlapping}. 
+Most of the theoretical results in the current version of the paper are new, including almost sure convergence and asymptotically lower variances of the overlapping variance estimators, and asymptotic validity of the interval estimators.
 These results are achieved through a stronger assumption on the rate of convergence of the sampling problem's solution to the unique optimal solution, which is satisfied by several classes of (\ref{eq:sto_prog}); see \S \ref{subsec:assumptions}.
@@
 
-Consider a covariance stationary stochastic process with mean $\mu$ and variance parameter\footnote{For a given stochastic process $y^1, y^2, \dots$, the variance parameter is the sum of covariances at all lags, $\sigma^2=\mathrm{Var} \left(y^1 \right)+2\sum_{j=1}^{\infty}\mathrm{Cov} \left(y^1,y^{1+j}\right)$.
-If the variance parameter exists, then  $\sigma^2=\lim_{n\rightarrow \infty}n\mathrm{Var} \left(\ybb\right)$, where $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^{i}$.} $0<\sigma^2<\infty$.
+Consider a covariance stationary stochastic process $y^1, y^2, \dots$ with mean $\mu$ and variance parameter $0<\sigma^2<\infty$.  
+The variance parameter is the sum of covariances at all lags, $\sigma^2=\mathrm{Var} \left(y^1 \right)+2\sum_{j=1}^{\infty}\mathrm{Cov} \left(y^1,y^{1+j}\right)$. 
+If the variance parameter exists, then  $\sigma^2=\lim_{n\rightarrow \infty}n\mathrm{Var} \left(\ybb\right)$, where $\ybb=\frac{1}{n}\sum_{i=1}^{n} y^{i}$.
 The task is to estimate $\mu$ given some realization of the univariate stochastic process $\y = (y^1, y^2, \dots, y^n)$.  
 Typically, this involves forming a CI of the form $[L_\alpha(\y), U_\alpha(\y)]$ for a given level of significance $\alpha$ such that $\p{L_\alpha(\y) \leq \mu \leq U_\alpha(\y)} = 1 - \alpha$ or that this probability is approximately $1 - \alpha$ for large enough sample sizes.
-The usual estimator for $\mu$ is the sample mean $\ybb = \frac{1}{n} \sum_{i=1}^n y^i$, which is an unbiased estimator even in the presence of correlated data.  
-However, the usual variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.  
-To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citep{law_07}.  
+The usual estimator for $\mu$ is the sample mean $\ybb$, which is an unbiased estimator even in the presence of correlated data.  
+However, the usual (sample) variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.
+To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \cite{law_07}.  
 We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.

### 2014-12-20 omrp_lb_fl.tex
R2 minor edits continued
thru end of p 9

@@
 Overlapping batch means modifies nonoverlapping batch means by reusing a subset of observations from one batch to form the next batch. 
-%As an example, suppose each batch contains $m$ observations and that there are a total of $n=2m$ observations.
-%In the nonoverlapping case, there are only two batches:
-%% the first batch contains observations $y^1, y^2, \dots, y^m$ and the second batch contains observations $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
-%$y^1, y^2, \dots, y^m$ and $y^{m+1}, y^{m+2}, \dots, y^{2m}$.  
-%In the overlapping batches of \citet{Meketon1984}, the first batch is as before, the second batch now consists of $y^2, y^3, \dots, y^{m+1}$, the third batch $y^3, y^4, \dots, y^{m+2}$, and so on.  
-%This is what we call the \emph{maximally overlapping} batch means method, because $m-1$ observations are common to---and only one observation changes between---adjacent batches.  
-%It is possible to vary the degree of overlap between neighboring batches. 
-%This generalization was first studied by \citet{Welch1987}, who also established the relationship between OBM and spectral estimators; see also \citep{Song1992}.
-%%
 In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
@@
 Let $\lfloor \cdot \rfloor$ be the greatest integer that is less than or equal to its argument. 
-The sample mean of each batch is calculated similarly, 
+The sample mean of each overlapping batch is calculated similarly, 
 $
@@
 
-The overlapping batch means 
-formed using $1 \leq \gamma < m$ 
-are no longer independent. 
-However, by simply reusing the data in this fashion one obtains a better variance estimator. 
-That is, the overlapping variance estimator has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii)
-%the overlapping estimator has 
-a lower asymptotic variance than its nonoverlapping counterpart. 
+The overlapping variance estimator using $1 \leq \gamma < m$ has (i) nearly the same bias as the standard nonoverlapping variance estimator, and it has (ii) a lower asymptotic variance than its nonoverlapping counterpart.
+Therefore, by simply reusing the data in this fashion one obtains a better variance estimator. 
 Observe that with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).
-With $\gamma=1$ (the maximally overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \citep{Meketon1984}.
-This slightly different denominator 
-makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$ with the same asymptotic benefits of nearly the same bias and lower variance relative to its counterpart obtained via nonoverlapping batches \citep{Song1992}.
+With $\gamma=1$ (the maximally overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \cite{Meketon1984}.
+This slightly different denominator makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$, with the same asymptotic benefits of nearly the same bias and lower variance relative to its counterpart obtained via nonoverlapping batches \citep{Song1992}.
 
-The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $1\leq \gamma< m$ relative its nonoverlapping counterpart 
-%$\var{\vtm{\ybb}}$ 
-depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$. 
+The amount of asymptotic reduction in $\var{\vartg{\ybb}}$ for a given $1\leq \gamma< m$ relative to its nonoverlapping counterpart depends on the asymptotic ratio of $\gamma/m$, which we denote by $\gammab$.
 The maximally overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
@@
 \end{equation}
-as the batch size $m$ and then the number of batches $n/m$ tend to infinity. 
+as the batch size $m$ and then the number of batches $n/m$ tend to infinity; see also \cite{Alexopoulos2007}. 
 In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches and $\beta_0 = \frac{4}{3}$ for maximally overlapping batches.  
@@
 When only half of the observations overlap 
-($\gammab = 1/2$),
-%($\gammab = 1/2$ or $\gamma=m/2$),
-for instance, the variance is 75\% of the nonoverlapping counterpart.
+($\gammab = 1/2$), for instance, the variance is 75\% of the nonoverlapping counterpart.
 
 A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gammab}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gammab}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}).
-%\citep{Welch1987}.
-%If $\ogb$ is an integer, $d_{\gammab} = \frac{3}{2+\gammab^2}$.  
-For the maximally overlapping batch means, the degrees of freedom is $d_{\gammab} = \frac{3}{2}$.
+For the maximally overlapping batch means, the degrees of freedom factor is $d_{\gammab} = \frac{3}{2}$.
 
@@
 where $\xs_j$ denotes an optimal solution to (\ref{eq:sto_prog_m}) of batch $j$ given on the right-hand side of (\ref{eq:mrp_gap}).    
-Since we are assessing the quality of a given solution $\xh \in \X$, we suppress it from the notation $\gb_j$.
+Since we are assessing the quality of a given solution $\xh \in \X$, we suppress $\xh$ from the notation $\gb_j$.
 The optimality gap estimator $\gb_j$ is similar to the nonoverlapping $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
-Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but all the observations in that batch $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{m(j-1)+m}$ because $\xs_j$ is an optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
+Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but on all the observations in that batch,  $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{mj}$ because $\xs_j$ is an optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
 As before, after $k$ batch-means estimators are obtained, the overall mean of these estimators $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
-The variance estimator is obtained as in (\ref{eq:var}) by $\varh{\gbb} = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in an approximate $(1-\alpha)$-level one-sided CI $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varh{\gbb}} \right]$.
+The variance estimator is obtained as in (\ref{eq:var}) by $\varhat(\gbb) = \frac{1}{k} \frac{1}{k-1} \sum_{j=1}^k (\gb_j - \gbb)^2$, which results in an approximate $(1-\alpha)$-level one-sided CI, $\left[0, \gbb + t_{k-1,\alpha} \sqrt{\varhat(\gbb)} \right]$.
 
@@
 Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in \citep{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI; see also \citep{stockbridge_bayraksan_13}.
-The papers \citep{bayraksan_morton_09,partani2006jackknife,partani_07} discuss variations of MRP aimed to reduce bias and variance.
+This is shown empirically in \cite{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI; see also \cite{stockbridge_bayraksan_13}.
+\cite{bayraksan_morton_09}, \cite{partani2006jackknife}, and \cite{partani_07} discuss variations of MRP aimed to reduce bias and variance.
 
@@
 Minimization changes the statistical properties of sample means, complicating the asymptotic analysis.  
-%For instance, the central limit theorem may not hold for a minimized sample mean, even though it holds for each $\x \in \X$.  
-%Therefore, analysis of the asymptotic benefits of overlapping becomes more complicated.
 We overcome this technical difficulty by approximating the optimality gap estimators by their nonoptimized counterparts (see \S \ref{subsec:nonO}).  
 The nonoptimized counterparts are regular overlapping batch means estimators (without any optimization); therefore, they have the desired statistical properties of approximately the same bias and lower variances compared to their nonoverlapping versions.
-To show that the same asymptotic properties hold for OMRP estimators, we establish convergence of OMRP estimators to their nonoptimized counterparts (see \S \ref{subsec:conv}--\ref{ssec:validity}).
+To show that the same asymptotic properties hold for OMRP estimators, we establish convergence of OMRP estimators to their nonoptimized counterparts (see \S\S \ref{subsec:conv}--\ref{ssec:validity}).
 
-Another difference between our setting and simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.
-In this setting, the computational effort may increase with data reuse because we need to solve a sampling problem (SP$_m$) for each batch.  
+Another difference between our setting and typical simulation output analysis is that once the data are generated through a simulation, they can be reused without much additional computational effort to obtain the OBM variance estimator.
+In our setting, the computational effort may increase with data reuse because we need to solve a sampling problem (SP$_m$) for each batch.  
 The increase in computation time can be alleviated in two ways: (i) by increasing $\gamma$ to partially overlap the batches, resulting in a smaller number of batches (but a higher variance), and (ii) using warm starting to quickly solve the sampling approximations with overlapping observations.
-%We use the batch nonoverlap parameter $\gamma$ as before to allow for varying degrees of overlap in OMRP. 
 We investigate the balance of computational efficiency gains from warm starting versus variability of the estimators in \S \ref{ssec:compeff}. 
@@
 So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  
-As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch; $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
+As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch. 
+The sampling problem (SP$_m$) formed using the $j$th batch might have multiple optimal solutions. 
+We use $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$ to denote one optimal solution.
+
+The set of optimal solutions to The sampling problem (SP$_m$) formed using the $j$th batch might not be a singleton; there might be multiple optimal solutions.
 
 The results on overlapping batch means discussed in \S \ref{ssec:overlap} occur in the limit as $n, m, k=n/m \rightarrow \infty$.  
-Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, then the limits will be taken as $l \rightarrow \infty$.  
+Let $n_l, m_l$, and $k_l$ be sequences of numbers satisfying these requirements, so that the limits will be taken as $l \rightarrow \infty$.  
 We assume a batching structure where $m_l = \lfloor n_l ^r \rfloor$ for some $0<r<1$, as is typical in simulation, and $n_l$ tends to infinity as $l \rightarrow \infty$.  

### 2014-12-22 omrp_lb_fl.tex
R2 minor edits, cont'd thru p. 19

@@
 So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  
-As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch. 
-The sampling problem (SP$_m$) formed using the $j$th batch might have multiple optimal solutions. 
-We use $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$ to denote one optimal solution.
+As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch, which may not be unique; so we set $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
 
@@
 The optimality gap estimator for each batch $\gb_{lj}$ is defined like (\ref{eq:mrp_gap}) for general values of the nonoverlap parameter $\gamma_l$.  
-We just removed the minimization in (\ref{eq:mrp_gap}) and used directly an optimal solution of $\xs_j$ of batch $j$.  
+We simply removed the minimization in (\ref{eq:mrp_gap}) and directly used an optimal solution of $\xs_j$ of batch $j$.  
 The overall mean, $\gbb_l$, is defined a little differently.  
@@
 This choice of $\gbb_l$, however, may not be guaranteed to be nonnegative.
-In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping.
-%In our computational results, however, we did not observe any negative values of $\gbb_l$.
+In practice, $\max\{\gbb_l,0\}$ can be used as the point estimator of the optimality gap to ensure nonnegativity, and $VG_l$ can be calculated the same way given in (\ref{eq:vg}), using $\gbb_l$, to obtain improved interval estimators via overlapping.
 
@@
 In this section, we provide conditions under which several asymptotic properties hold for OMRP estimators. 
-First, we show the consistency of the point estimators of optimality gap, $\gbb_l$, and variance, $n_l VG_l$. 
+First, we show the consistency of the point estimators of the optimality gap, $\gbb_l$, and variance, $n_l VG_l$. 
 Then, we provide conditions under which the OMRP variance estimator achieves asymptotically lower variances relative to the MRP estimator.  
@@
 	\item[A3] (\ref{eq:sto_prog}) has a unique optimal solution $\xs$ and $\p{\xs_m \neq \xs} \rightarrow 0$ exponentially fast as $m \rightarrow \infty$.  
-           That is, there exists constants $M > 0$ and $c > 0$ such that $\log(\p{\xs_m \neq \xs}) \leq -cm$ for all $m > M$.
+           That is, there exist constants $M > 0$ and $c > 0$ such that $\log(\p{\xs_m \neq \xs}) \leq -cm$ for all $m > M$.
 \end{description}
@@
 First, we restrict our attention to i.i.d.\ sampling by A1.
-The results for overlapping batches from the simulation output analysis indicate that $\var{n_l VG_l}$ may be reduced by overlapping, thus requiring at least finite fourth moments. 
-We will formally show this result in \S~\ref{ssec:var_reduct}.
+The results for overlapping batches from simulation output analysis indicate that $\var{n_l VG_l}$ may be reduced by overlapping, thus requiring at least finite fourth moments. 
+We will formally show this result in \S\ref{ssec:var_reduct}.
 Our proof relies on an exponential rate of convergence of the sampled solution to the true solution of the problem, specified by A3.  
@@
 \citet{shapiro2000rate} establish exponential rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite.
-\citet{kleywegt2002sample} show that assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $\x \in X \backslash \{\xs\}$ is finite valued on $\R$.
+\citet{kleywegt2002sample} show that Assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $\x \in X \backslash \{\xs\}$ is finite valued on $\R$.
 This class of problems includes stochastic integer programs with recourse.
   We present computational results on both stochastic linear and integer programs with recourse in \S \ref{sec:comp}.
-
-% \begin{description}
-% 	\item[A'1] (\ref{eq:sto_prog}) has a unique and sharp optimal solution, i.e., there is a constant $C$ such that $\e{f(\x,\xi)} \geq \e{f(\xs,\xi)} + C\Vert \x - \xs\Vert$ for all $\x \in X$
-% 	\item[A'2] (\ref{eq:sto_prog}) is Lipschitz continuous almost surely, i.e., there is a constant $K$ such that $|f(\x_1,\xit) - f(\x_2,\xit)| \leq K \Vert \x_1 - \x_2 \Vert$ for all $\x_1,\x_2 \in X$.
-
-% Some results require an additional assumption:
-% \begin{description}
-% 	\item[A4] (\ref{eq:sto_prog}) has a unique optimal solution.
-% \end{description}
 
@@
 Before we begin establishing the theoretical results, we introduce the following notation. 
-We use $\mu_{\xh} := \e{f(\xh,\xit) - f(\xs,\xit)}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} := \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
-With i.i.d.\ sampling, $\e{\db_{lj}}=\e{\dbb_l}=\mu_{\xh}, \ \forall l,j$, $\var{\dbb_l}=\sigma^2_{\xh}/n_l, \ \forall l$, and under appropriate conditions, $\frac{n_l}{m_l} \var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$  by (\ref{eq:varvarred}).
+We use $\mu_{\xh} = \e{f(\xh,\xit) - f(\xs,\xit)}$ to denote the optimality gap of $\xh$ and $\sigma^2_{\xh} = \var{f(\xh,\xit) - f(\xs,\xit)}$ to denote the associated variance term.
+With i.i.d.\ sampling, $\e{\db_{lj}}=\e{\dbb_l}=\mu_{\xh}, \ \forall l,j$, $\mathrm{Var}(\dbb_l)=\sigma^2_{\xh}/n_l, \ \forall l$, and under appropriate conditions, $\frac{n_l}{m_l} \var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$  by (\ref{eq:varvarred}).
 
@@
 \begin{lemma} \label{lem:gbb_prob}
-	Under assumptions A1 and A3, $\p{\dbb_l - \gbb_l \neq 0} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
+	Under Assumptions A1 and A3, $\p{\dbb_l - \gbb_l \neq 0} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
 \end{lemma}
@@
 \begin{proof} When all the sampling problems used in the calculation of $\gbb$ have optimal solutions that solve (SP), i.e., when $\xs_{j} = \xs$, for all $j=1,2,\ldots, \nbl$, then $\gbb_l = \dbb_l$.
-Therefore, probability of the complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
+Therefore, the probability of the complement of this event provides an upper bound on the probability that $\dbb_l - \gbb_l \neq 0$. 
 Let $E^C$ denote the complement of event $E$. 
@@
 		& = \p{ \bigcup_{j=1}^{\nbl} \{\xs_{j} \neq \xs\}} \notag \\
-% 		& \leq \sum_{j=1}^{\nbl} \p{ \xs_j \neq \xs } \notag \\
 		& \leq \left( \nbl\right) \p{ \xs_{m_l} \neq \xs }. \notag
@@
 \begin{lemma} \label{lem:gb_gbb_l4}
-	Under assumptions A1--A3, both (i) $\e{(\db_{lj} - \gb_{lj})^4} \rightarrow 0$ and (ii) $\e{(\dbb_l - \gbb_l)^4} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
+	Under Assumptions A1--A3, both (i) $\e{(\db_{lj} - \gb_{lj})^4} \rightarrow 0$ and (ii) $\e{(\dbb_l - \gbb_l)^4} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
 \end{lemma}
@@
 	\end{align*}
-	The expectation term on the right-hand side is bounded by assumption A2 for i.i.d.\ samples.  
+	The expectation term on the right-hand side is bounded by Assumption A2 for i.i.d.\ samples.  
         Assumption A3 states $\p{\xs_{m_l} \neq \xs} \rightarrow 0$ exponentially fast.  
         Thus $\e{(\db - \gb)^4} \rightarrow 0$ exponentially fast.
-(ii) This expectation term can be decomposed in the same manner
-	\begin{align*}
-		\e{(\dbb - \gbb)^4} & = \e{\left. (\dbb - \gbb)^4 \right| \dbb - \gbb \neq 0} \p{\dbb - \gbb \neq 0}.
-	\end{align*}
-	With the expectation term on the right-hand side again bounded by A2, and the probability term converges to zero exponentially fast by Lemma \ref{lem:gbb_prob}.
+(ii) This expectation term can be decomposed in the same manner as
+$
+		\e{(\dbb - \gbb)^4}  = \e{\left. (\dbb - \gbb)^4 \right| \dbb - \gbb \neq 0} \p{\dbb - \gbb \neq 0}.
+$ 
+	The proof follows using similar arguments as proof of part (i) and Lemma \ref{lem:gbb_prob}.
 \end{proof}
@@
 \begin{theorem} \label{thm:strong_consistency}
-	Under assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s., and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s.\ as $l \rightarrow \infty$.  
+	Under Assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s., and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s.\ as $l \rightarrow \infty$.  
         Therefore, $\gbb_l$ is a consistent estimator of $\mu_{\xh}$, and if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, then $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$.
@@
 %
-(ii) This proof is nearly identical to above. 
-Similar to the proof of Lemma \ref{lem:gbb_prob}, we have
+(ii) Similar to the proof of Lemma \ref{lem:gbb_prob}, we have
 	\[
@@
 	\]
-	Following the same logic, $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast. 
+	Following the same logic as in (i), $\p{n_l VD_l -n_l VG_l \neq 0} \rightarrow 0$ exponentially fast. 
 Thus, $n_l VG_l$ is a consistent estimator of $\sigma^2_{\xh}$, if $n_l VD_l$ is, by the Borel-Cantelli Lemma.
@@
 Part (i) of Theorem \ref{thm:strong_consistency} provides conditions under which the point estimator $\gbb$ of OMRP is a consistent estimator of the optimality gap, by establishing almost sure convergence of $\gbb_l - \dbb_l$ to $0$ as $l \rightarrow \infty$.
-Notice that under assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s. 
+Notice that under Assumption A1, $\dbb_l \rightarrow \mu_\xh$, a.s. by the strong law of large numbers; as a result, $\gbb \rightarrow \mu_\xh$, a.s. 
 Similarly, part (ii) of Theorem \ref{thm:strong_consistency} establishes almost sure convergence of $n_l VG_l - n_l VD_l$ to $0$ as $l \rightarrow \infty$. 
 As a result, if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, so is $n_l VG_l$.  
-Strong consistency of the variance estimator $n_l VD_l$ has been studied in \citep{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
+Strong consistency of the variance estimator $n_l VD_l$ has been studied in \cite{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
 Under the additional moment assumption
@@
 \end{description}
-for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \citep{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.
+for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \cite{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.
 
@@
 \begin{theorem} \label{thm:varvar_conv}
-	Suppose assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures  $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ where $\beta_{\gammab}$ is the twice the value of (\ref{eq:var_reduct_formula}).
+	Suppose Assumptions A1--A3 hold, $\gammab = \frac{\gamma_l}{m_l}$ is constant for all $l$, and the batching structure ensures  $\frac{n_l}{m_l}\var{n_l VD_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ where $\beta_{\gammab}$ is the twice the value of (\ref{eq:var_reduct_formula}).
         Then, $\frac{n_l}{m_l}\var{n_l VG_l} \rightarrow \beta_{\gammab} \sigma^4_{\xh}$ as $l \rightarrow \infty$ with the same $\beta_{\gammab}$. 
@@
         The first and last batch are identically distributed, as are the second and second-to-last, etc.  
-        We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the exact same batch structure.  
+        We know this because we could reverse the order of the i.i.d.\ sample and perform the batching again to get the same batch structure.  
 		  The center batches are identically distributed.  
@@
 		} \\
-%		 = & \left( \frac{n}{dt} \right)^2 n_b \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^c \right)^2 } + \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 } \\
 		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j^c \right)^2 }
-		+ \left( \frac{n}{dt} \right)^2 (n_b) 2\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 }.
+		+ \left( \frac{n}{dt} \right)^2  2 n_b \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 }.
 	\end{align*}	
@@
 	\end{align}
-	where equation (\ref{eq:var_reduct_cauchy2}) follows from the Cauchy-Schwartz inequality, and equation (\ref{eq:var_reduct_holder2}) follows from H\"{o}lder's inequality.  
+	where (\ref{eq:var_reduct_cauchy2}) follows from the Cauchy-Schwartz inequality, and (\ref{eq:var_reduct_holder2}) follows from H\"{o}lder's inequality.  
         Since we can bound both expectation terms in (\ref{eq:var_reduct_holder2}) by A2, we can demonstrate $\sqrt{\frac{n}{m}}(nVG - nVD) \xrightarrow{L^2} 0$ by focusing on only one of the terms.  
@@
 	\end{align*}	
-	By Lemma \ref{lem:gb_gbb_l4}, both expectation terms above converge to zero with exponential rates.  
+	By Lemma \ref{lem:gb_gbb_l4}, both expectation terms converge to zero with exponential rates.  
         With a batching structure $m_l = \lfloor n_l^r \rfloor$ for some $0<r<1$, we see that $\frac{n_l}{m_l} \e{(n_l VG_l - n_l VD_l)^2} \rightarrow 0$.
@@
 Theorem \ref{thm:varvar_conv} gives conditions under which the same asymptotically lower variances are achieved for the OMRP optimality gap variance estimator relative to its nonoverlapping counterpart, the MRP variance estimator.
-We will empirically examine the variance of OMRP estimator for small sample sizes in \S \ref{sec:comp}. 
+We will empirically examine the variance of the OMRP estimator for small sample sizes in \S \ref{sec:comp}. 
 A hypothesis of Theorem \ref{thm:varvar_conv} is a batching structure that ensures convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\beta_{\gammab} \sigma^4_{\xh}$, ensuring the mean-square consistency of $n_l VD_l$.
-\citet{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $(4+\epsilon)$th-finite-moments assumption A2$^\prime$.
+\citet{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $(4+\epsilon)$th-finite-moments Assumption A2$^\prime$.
 With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.
@@
 
-The overlapping variance estimator for stochastic programs displays the same desirable properties, such as consistency and reduced variability, as in simulation, but we must still check that it results in a valid CI.
+The overlapping variance estimator for stochastic programs displays the same desirable properties, such as consistency and reduced variability, as the original OBM estimators, but we must still check that it results in a valid CI.
 Let $I^G_l = \gbb_l + t_{d_l \left( k_l-1\right),\alpha} \sqrt{VG_l}$ be the width of the one-sided CI generated by OMRP. 
@@
 \begin{theorem} \label{thm:conf_int}
-	Suppose assumptions A1--A3 hold and the batching structure ensures $n_l VD_l$ converges in probability to $\sigma^2_\xh$.  
+	Suppose Assumptions A1--A3 hold and the batching structure ensures $n_l VD_l$ converges in probability to $\sigma^2_\xh$.  
         Then, for $\xh \neq \xs$, $\lim_{l\rightarrow\infty} \p{\mu_\xh \leq I^G_l} = 1 - \alpha$.
@@
 %        With $\xh \neq \xs$, 
-			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVD_l}} \frac{\sqrt{n_lVD_l}}{\sqrt{n_lVG_l}}$.
+			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVG_l}}$. 
 			Also let $z_{\alpha}$ denote the $1-\alpha$ quantile of the standard normal distribution. 
@@
 In this section, we apply OMRP to several test problems and examine small-sample behavior. 
-We begin our discussion by introducing the test problems used for numerically evaluating OMRP in \S \ref{ssec:test}, followed by our experimental setup in \S \ref{ssec:expS}. 
+We begin our discussion by introducing in \S \ref{ssec:test} the test problems used for numerically evaluating OMRP, followed by our experimental setup in \S \ref{ssec:expS}. 
 Then, we present and discuss the numerical results in \S \ref{ssec:results}.
@@
 We empirically tested the effectiveness of OMRP on four test problems.
-All test problems are two-stage stochastic programs with recourse and were selected to study the behavior of OMRP under a variety of different situations---we will shortly discuss this below.
+All test problems are two-stage stochastic programs with recourse and were selected to study the behavior of OMRP under a variety of different situations---we will discuss this below.
 The characteristics of these problems are given in Table \ref{tb:test_problems}. 
@@
 We made several considerations in selecting the test problems.
-NVD can be solved very quickly, which allows for solving a large number of independent runs for examining the small-sample behavior of OMRP.
+NVD can be solved very quickly, which allows for a large number of independent runs for examining the small-sample behavior of OMRP.
 CEP1 is also easy to solve; the optimal solution $\xs$ can be obtained with high probability even for small sample sizes.
@@
 These experiments suggest that lower variances can be achieved in stochastic programming by overlapping the batches, even with small sample sizes.
-The variance of OMRP variance estimators for DB1 can be less than the asymptotic amount established in Theorem \ref{thm:varvar_conv}. %for the small sample sizes used in these experiments. 
+The variance of OMRP variance estimators for DB1 can be less than the asymptotic result established in Theorem \ref{thm:varvar_conv}.
 This is because DB1 has not yet been solved to optimality due its size; therefore, it may lack a unique optimal solution. 
-%, violating assumption A3. (?)
 Even with the relatively small sample sizes compared to the size of this problem, however, overlapping appears to lower the variances.
@@
 	\caption{
-		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problems
+		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the case of nonoverlapping batches) for test problems
 		(a) NVD and
@@
 		(a) $\e{nVG}$ and 
-		(b) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches)
+		(b) coverage probability of the CIs for various values of $\gamma/m$ ($\gamma/m=1$ denotes the case of nonoverlapping batches)
 		 for NVD
@@
 Figure~\ref{fig:nv}(a) shows estimates of $\e{nVG}$ in the newsvendor problem for changing batch size and degree of overlap. 
-We can see that the expectation of the variance estimator is not changed with increasing overlap. 
+We see that the expectation of the variance estimator does not change with increasing overlap. 
 Although the estimate of $\e{nVG}$ looks large for $m=100$, the error from $\sigma^2_\xh$ is never more than 1\%.  
@@
 The authors are grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the paper. 
-%This research has been supported in part by the National Science Foundation under Grants DMS-0602173 and CMMI-1345626.
+This research has been supported in part by the National Science Foundation under Grants DMS-0602173 and CMMI-1345626.
 %EFRI-0835930

### 2014-12-23 omrp_lb_fl.tex
All R1 and R2 edits, except for one comment

@@
 In this paper, we apply the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
-We give conditions under which the resulting optimality gap point estimators are strongly consistent, the optimality gap interval estimators are asymptotically valid, and the OBM variance estimators of optimality gap have asymptotically lower variances relative to their nonoverlapping counterparts \citep{Meketon1984,Welch1987}.
+We give conditions under which the resulting optimality gap point estimators are strongly consistent, the optimality gap interval estimators are asymptotically valid, and the OBM variance estimators for optimality gap have asymptotically lower variances relative to their nonoverlapping counterparts \citep{Meketon1984,Welch1987}.
 We investigate computational efficiency, a combined measure of variance and computation time, providing guidelines on the degree of overlap.  
@@
 These individual estimators are then used to form point and interval estimators applying the nonoverlapping batch means method.
-This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citep{Mak1999}.   
+This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \cite{Mak1999}.   
 In this paper, we formulate an overlapping batches version of MRP.
@@
 However, the usual (sample) variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.
-To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \cite{law_07}.  
+To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \cite{law_15}.  
 We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.
@@
 Nonoverlapping batch means takes $n$ observations $y^1, \dots, y^n$ of the stochastic process and splits them into $k$ batches of size $m$, where $k = \frac{n}{m}$ (for simplicity, assume, for now, $n = mk$).
-The sample mean of each batch is then computed as
+In the application under consideration in this article, the observations {\it within} a batch are correlated due to the optimization in each batch; see \S \ref{ssec:mrp} for details. 
+The sample mean of each batch is computed as
 $
@@
 The $(1-\alpha)$-level approximate CI is then formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.
-Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$.
+Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$ \citep{alexo_enc_06}.
 
@@
 A $(1-\alpha)$-level approximate CI on the mean can be formed using overlapping batches by $\ybb \pm t_{d_{\gammab}(k-1),\alpha/2}$ $\sqrt{\vartg{\ybb}}$, where the degrees of freedom increase $d_{\gammab}$ is the multiplicative inverse of (\ref{eq:var_reduct_formula}).
-For the maximally overlapping batch means, the degrees of freedom factor is $d_{\gammab} = \frac{3}{2}$.
+For the maximally overlapping batch means, the degrees of freedom increase is $d_{\gammab} = \frac{3}{2}$.
 
@@
 The optimality gap estimator $\gb_j$ is similar to the nonoverlapping $\yb_j$ with individual observations $y^{m(j-1)+i} = f(\xh,\xit^{m(j-1)+i}) - f(\xs_j,\xit^{m(j-1)+i})$, for $i=1,\ldots,m$ and $j=1,\ldots, k$.
-Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but on all the observations in that batch,  $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{mj}$ because $\xs_j$ is an optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
+Notice that in this case, $y^i$ not only depends on observation $i$ of batch $j$, $\xit^{m(j-1)+i}$, but on all the observations in that batch,  $\xit^{m(j-1)+1},\xit^{m(j-1)+2},\ldots,\xit^{mj}$, because $\xs_j$ is an optimal solution to (\ref{eq:sto_prog_m}) given in (\ref{eq:mrp_gap}).
 As before, after $k$ batch-means estimators are obtained, the overall mean of these estimators $\gbb = \frac{1}{k} \sum_{j=1}^k \gb_j$ provides a point estimator of the optimality gap.  
@@
 	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
-        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $dt = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
+        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $\tau = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
 We have
 	\begin{align}
-		\e{(nVG - nVD)^2} & = \left( \frac{n}{dt} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
-		& \leq \left( \frac{n}{dt} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
+		\e{(nVG - nVD)^2} & = \left( \frac{n}{\tau} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
+		& \leq \left( \frac{n}{\tau} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
 	\end{align}
@@
 	\begin{align*}
-		& \left( \frac{n}{dt} \right)^2 n_b \e{ \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
-		 =  & \left( \frac{n}{dt} \right)^2 n_b \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left( A_j^f \right)^2 \
+		& \left( \frac{n}{\tau} \right)^2 n_b \e{ \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
+		 =  & \left( \frac{n}{\tau} \right)^2 n_b \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left( A_j^f \right)^2 \
 		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left( A_j^c \right)^2 \
@@
 		} \\
-		 = & \left( \frac{n}{dt} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j^c \right)^2 }
-		+ \left( \frac{n}{dt} \right)^2  2 n_b \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 }.
+		 = & \left( \frac{n}{\tau} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j^c \right)^2 }
+		+ \left( \frac{n}{\tau} \right)^2  2 n_b \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 }.
 	\end{align*}	
 	The last equality follows because each front-fringe batch's $\e{(A_j^f)^2}$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$  has an identical pair in an end-fringe batch's $\e{(A_j^e)^2}$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$, and all center batches have identical values of $\e{(A_j^c)^2}$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, n_b - \left\lceil \gammab^{-1} \right\rceil$.
-	As a result, we have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{dt}\right)^2n_b^2 < (2m)^2$.  
+	As a result, we have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{\tau}\right)^2n_b^2 < (2m)^2$.  
         Removing the notation for fringe or center batch for simplicity, each expectation can be bounded by
@@
 The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$; we denote it as NVD.
-The instance of the newsvendor problem can be found in \citep{Bayraksan2006}, except here we used a discrete uniform demand distribution.
+The instance of the newsvendor problem can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution.
 The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations \citep{higle1996}.
@@
 
-The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citep{Bayraksan2006}.
+The candidate solutions used for NVD and CEP1 and their characteristics can be found in \cite{Bayraksan2006}.
 We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an estimated $\mu_{\xh} = 1.08$. 
@@
 
-A summary of results from these experiments is depicted in Figures~\ref{fig:varvar1}--\ref{fig:nv}.
-Figures~\ref{fig:varvar1} and \ref{fig:varvar2} show the variance of OMRP variance estimators, normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
-The solid lines in these figures show the theoretical relative decreases in variance from \citep{Welch1987} given by (\ref{eq:var_reduct_formula}). 
+A summary of results from these experiments is depicted in Figures~\ref{fig:varvar1} and \ref{fig:nv}.
+Figure~\ref{fig:varvar1} shows the variance of OMRP variance estimators, normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
+The solid lines in these figures show the theoretical relative decreases in variance from \cite{Welch1987} given by (\ref{eq:var_reduct_formula}). 
 Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
@@
 	   \includegraphics[width=.5\textwidth]{images/cep1_varvar}}
-	\caption{
-		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the case of nonoverlapping batches) for test problems
-		(a) NVD and
-		(b) CEP1
-	}
-\label{fig:varvar1}
-\end{figure}
-
-\begin{figure}[htb!]
-	\centering
+	\\
 	\subfloat[][10D]{
@@
 	\caption{
-		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the nonoverlapping batches) for test problems
-		(a) 10D and
-		(b) DB1
+		$\var{n VG}$ relative to the nonoverlapping counterpart across various values of $\gamma/m$ ($\gamma/m=1$ denotes the case of nonoverlapping batches) for test problems
+		(a) NVD,
+		(b) CEP1,
+		(c) 10D, and
+		(d) DB1
 	}
-\label{fig:varvar2}
+\label{fig:varvar1}
 \end{figure}
@@
 We observed the same for CEP1, 10D, and DB1.  
-The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citep{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown for brevity) remains fairly constant around the desired value of $90\%$.
+The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \cite{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown for brevity) remains fairly constant around the desired value of $90\%$.
 Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
@@
 
-The increased computational workload from solving overlapping batches raises the question of the computational efficiency of this method to estimate $VG$.
-In this setting, computational efficiency can be defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computation time spent to generate $VG$ for a given value of $\gammab$.
+The increased computational workload from applying overlapping batches to assessing solution quality raises the question of computational efficiency to estimate $VG$ in this context.
+Computational efficiency can be defined as $[T(\gammab)\var{VG}]^{-1}$, where $T(\gammab)$ is the computation time spent to generate $VG$ for a given value of $\gammab$.
 Because the variance of the overlapping variance estimator relative to the nonoverlapping (MRP) variant is known from (\ref{eq:var_reduct_formula}), we need only examine the computation time, which can be decomposed as $T(\gammab) = t(\gammab)\left(\nb\right)$.
@@
 Efficiency gains increase with larger exponent $p$ but are positive even for small values of $p$ when $\gammab$ is sufficiently close to 1.
-At $p=1$, i.e., for problems where computation time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches of \cite{Meketon1984}.
+At $p=1$, i.e., for problems where computation time is proportional to the number of samples replaced in the batch, computational efficiency is maximized with maximally overlapping batches.
 When $p=0.9$, computational efficiency is maximized at around $\gammab=0.3$.
@@
 		(b) empirically for NVD using insertion sort
-%		(graphs are scaled so that nonoverlapping batches produces a computational efficiency of 1)
 		}
@@
 \end{figure}
-
-%All theoretical curves in this section were computed using $m = 1000$, but the results do not change substantially with increasing batch size.
-%Newsvendor computations used $m = 1000$ with $10,000$ replications.
 
@@
 The average computation time per batch was found empirically to be well approximated ($R^2 = 0.994$) by the power law with $p = 0.71$.
-The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency}(b), where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency}(a).
-It appears that empirical observations match the theoretical efficiency calculations well.
+The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency}(b), where the theoretical computational efficiency, shown by a solid line, is repeated from Figure \ref{fig:efficiency}(a).
+It appears that the empirical observations match the theoretical efficiency calculations well.
 
@@
 When generating observations is cheap, one could alternatively increase the number of batches in MRP to obtain estimators with lower variances. 
-In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$; so, decreasing $\var{VG}$ to the level of maximally overlapping batches of \cite{Meketon1984} requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
+In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$; so, decreasing $\var{VG}$ to the level of maximally overlapping batches requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
 Continuing on in this way for various values of $\gammab$, we obtain the solid black curve in Figure \ref{fig:comp_work_comparison}. 
-This curve shows the increased computational effort in MRP because of an increased number of batches to obtain the same variance as OMRP across $\gammab$.
+This curve shows the increased computational effort for MRP because of an increased number of batches to obtain the same variance as OMRP across $\gammab$.
 If the work increase by OMRP is less than this solid black curve, then OMRP is computationally more efficient than increasing the number of batches in MRP. 
@@
 For small values of $p$, some efficiency gain is observed at $\gammab$ values close to 1.
-We again tested this empirically on NVD using insertion sort with $m=1,000$, taking an average of $10,000$ independent runs. 
+We tested this assertion empirically on NVD using insertion sort with $m=1,000$, taking an average of $10,000$ independent runs. 
 The results, shown in Figure \ref{fig:comp_work_comparison}(b), appear to match the theory well.
@@
 	   \label{fig:comp_work_comparison_nv}
-	   \includegraphics[width=.49\textwidth]{images/nv_work_comparison}}
+	   \includegraphics[width=.48\textwidth]{images/nv_work_comparison2}}
 		\caption{
-		Comparison of computational work required to get equivalent variance between MRP variance estimator with increased number of batches and OMRP variance estimator measured
+		Comparison of computational work required to obtain equivalent variance between the MRP variance estimator with increased number of batches and the OMRP variance estimator measured
 		(a) theoretically and 
 		(b) empirically for NVD using insertion sort
-%		(Left) A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
-%		(Right) Measured computational work for NVD compared with the theoretical results.
 		}
@@
 We recommend that users perform preliminary computations to determine how computation time per batch changes as $\gammab$ changes when warm starting is available. 
-We can see in Figure \ref{fig:efficiency} that for some values of $p$, efficiency gain is nearly flat over a region of $\gammab$.
+We can see in Figure \ref{fig:efficiency} that for some values of $p$, the efficiency gain is nearly flat over a region of $\gammab$.
 In this case, we recommend choosing $\gammab$ near the right side of this region.
@@
 
-We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
+We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to the problem of assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
 We have provided conditions under which (i) the resulting point estimator of the optimality gap and its associated variance estimator are consistent, (ii) OMRP variance estimators achieve asymptotically lower variances relative to the MRP variance estimator, and (iii) OMRP CIs are asymptotically valid.
@@
 Even when warm starting is less effective, efficiency slightly increases for low degrees of overlap. 
-Maximizing efficiency and then minimizing total computation time, we recommend  selecting the lowest degree of overlap across all the degrees with the highest efficiency for a given problem and solution method (with warm starting) combination.
-
-%Finally, based on our study of computational efficiency, we have provided guidelines on selecting the degree of overlap in OMRP.
+Maximizing efficiency and then minimizing total computation time, we recommend  selecting the lowest degree of overlap across all the degrees with the highest efficiency for a given problem and solution method (with warm starting).
 
@@
 This research has been supported in part by the National Science Foundation under Grants DMS-0602173 and CMMI-1345626.
-%EFRI-0835930
-An earlier version of this paper appeared in \citep{love2011overlapping}.
 

### 2014-12-28 omrp_lb_fl.tex
All edits of R1 and R2 DONE

@@
 \newcommand{\nb}{\left\lfloor\tfrac{n-m}{\gamma}\right\rfloor+1}
-\newcommand{\nbl}{\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1}
+%\newcommand{\nbl}{\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1}
+\newcommand{\nbl}{b_l}
 \newcommand{\gammab}{\bar{\gamma}}
@@
 Let $\lfloor \cdot \rfloor$ be the greatest integer that is less than or equal to its argument. 
+Here, $b=\nb$ batches are formed given $n$, $m$, and $\gamma$. 
 The sample mean of each overlapping batch is calculated similarly, 
 $
-\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, \nb, 
+\yb_j = \frac{1}{m} \sum_{i=1}^m y^{\gamma(j-1) + i},\ \  j = 1, 2, \dots, b, 
 $
 now taking into account $\gamma$.   
-Here, $\nb$ batches are formed given $n$, $m$, and $\gamma$.  
 The variance estimator is updated to
 \begin{equation} \label{eq:variance_gamma}
-	\vartg{\ybb} = \frac{1}{\left( \tfrac{n}{m} - 1 \right) \left( \nb \right)}  \sum_{j=1}^{\nb} (\yb_j - \ybb)^2.
+	\vartg{\ybb} = \frac{1}{b \left( \tfrac{n}{m} - 1 \right) }  \sum_{j=1}^{b} (\yb_j - \ybb)^2.
 \end{equation}
@@
 In order to apply overlapping batches to MRP, we need to keep track of solutions to sampling problems (SP$_m$) for each batch of size $m$.  
-Toward this end, let $B(i)$ denote the set of batches $j \in \left\{1, 2, \dots, \nb \right\}$ observation $\xiti$ is used in, $i = 1, 2, \dots, n$.  
+Toward this end, let $B(i)$ denote the set of batches $j \in \left\{1, 2, \dots, b \right\}$ observation $\xiti$ is used in, $i = 1, 2, \dots, n$.  
 See Figure \ref{fig:overlap_nonint} for an example with $n=18$, $m = 6$, and $\gamma = 2$.  
@@
 So, $B(1) = \{1\}$, $B(3) = \{1,2\}$, and $B(7)=\{2,3,4\}$.  
-As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch, which may not be unique; so we set $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, \nb$.
-
-The set of optimal solutions to The sampling problem (SP$_m$) formed using the $j$th batch might not be a singleton; there might be multiple optimal solutions.
+As before, we use $\xs_j$ to denote an optimal solution to sampling problem (SP$_m$) formed using the $j$th batch, which may not be unique; so we set $\xs_j \in \argmin_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xit^{\gamma(j-1) + i})$, $j = 1, 2, \dots, b$.
 
@@
 In addition, we may desire that the batch nonoverlap parameter change with $l$, to ensure that $\gamma_l / m_l = \gammab_l$ converges to the constant $\gammab$.  
+The notation for the number of batches is updated to $b_l = \left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1$.
 The OMRP estimators are defined as follows:
@@
 	\gbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \frac{1}{|B(i)|} \sum_{j \in B(i)} \left[ f(\xh,\xiti) - f(\xs_j,\xiti) \right], \label{eq:gbb} \\
-	VG_l & = \dfrac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
+	VG_l & = \dfrac{1}{ \nbl \left( \tfrac{n_l}{m_l} - 1 \right)} \sum_{j=1}^{\nbl} (\gb_{lj} - \gbb_l)^2. \label{eq:vg}
 \end{align}
@@
 	\dbb_l & = \frac{1}{n_l} \sum_{i=1}^{n_l} \left[ f(\xh,\xiti) - f(\xs,\xiti) \right], \label{eq:dbb} \\
-	VD_l & = \frac{1}{\left( \tfrac{n_l}{m_l} - 1 \right) \left(\nbl\right)} \sum_{j=1}^{\nbl} (\db_{lj} - \dbb_l)^2. \label{eq:vd}
+	VD_l & = \frac{1}{\nbl \left( \tfrac{n_l}{m_l} - 1 \right)} \sum_{j=1}^{\nbl} (\db_{lj} - \dbb_l)^2. \label{eq:vd}
 \end{align}
@@
 		& = \p{ \bigcup_{j=1}^{\nbl} \{\xs_{j} \neq \xs\}} \notag \\
-		& \leq \left( \nbl\right) \p{ \xs_{m_l} \neq \xs }. \notag
+		& \leq \nbl \, \p{ \xs_{m_l} \neq \xs }. \notag
 	\end{align}
@@
 	For simplicity of exposition, we drop the subscript $l$ and the $\frac{n_l}{m_l}$ for now and add them in later.  
-        Further, we use abbreviations $n_b = \nbl$ to denote the number of batches and $\tau = \left(\tfrac{n_l}{m_l} - 1\right) \left(\nbl\right)$ to denote the denominator term in $VG_l$ and $VD_l$.
-We have
+        Further, we use abbreviation $\tau = \nbl \left(\tfrac{n_l}{m_l} - 1\right)$ to denote the denominator term in $VG_l$ and $VD_l$. We have
 	\begin{align}
-		\e{(nVG - nVD)^2} & = \left( \frac{n}{\tau} \right)^2 \e{ \left( \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
-		& \leq \left( \frac{n}{\tau} \right)^2 \e{ n_b \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
+		\e{(nVG - nVD)^2} & = \left( \frac{n}{\tau} \right)^2 \e{ \left( \sum_{j=1}^{b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right] \right)^2 } \notag \\
+		& \leq \left( \frac{n}{\tau} \right)^2 \e{ b \sum_{j=1}^{b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \label{eq:vvar_conv_pf_1}
 	\end{align}
@@
         Notice in Figure \ref{fig:overlap_nonint}, we see $\left\lceil \gammab^{-1} \right\rceil = 3$ sets of nonoverlapping batches $\{1,4,7\}$, $\{2,5\}$, and $\{3,6\}$, each of which has two fringe batches.
-        In general, there are $\left\lceil \gammab^{-1} \right\rceil$ sets of nonoverlapping batches, each of which will have two fringe batches, and $n_b - 2\left\lceil \gammab^{-1} \right\rceil$ center batches.
+        In general, there are $\left\lceil \gammab^{-1} \right\rceil$ sets of nonoverlapping batches, each of which will have two fringe batches, and $b - 2\left\lceil \gammab^{-1} \right\rceil$ center batches.
 
@@
         Let $A_j = (\gb_j - \gbb)^2 - (\db_j - \dbb)^2$.
-		  Furthermore, let $A_j^c$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, n_b - \left\lceil \gammab^{-1} \right\rceil$ denote the center batches, and let $A_j^f$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$ and $A_j^e$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$ denote the fringe batches at the front and end of each set of nonoverlapping batches, respectively.
+		  Furthermore, let $A_j^c$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, b - \left\lceil \gammab^{-1} \right\rceil$ denote the center batches, and let $A_j^f$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$ and $A_j^e$, $j=b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,b$ denote the fringe batches at the front and end of each set of nonoverlapping batches, respectively.
 		  Continuing from (\ref{eq:vvar_conv_pf_1}),
 	\begin{align*}
-		& \left( \frac{n}{\tau} \right)^2 n_b \e{ \sum_{j=1}^{n_b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
-		 =  & \left( \frac{n}{\tau} \right)^2 n_b \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \left( A_j^f \right)^2 \
-		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{n_b-\left\lceil \gammab^{-1} \right\rceil} \left( A_j^c \right)^2 \
-		 + \sum_{j=n_b-\left\lceil \gammab^{-1} \right\rceil+1}^{n_b} \left( A_j^e \right)^2 
+		& \left( \frac{n}{\tau} \right)^2 b \, \e{ \sum_{j=1}^{b} \left[ (\gb_j - \gbb)^2 - (\db_j - \dbb)^2 \right]^2 } \\
+		 =  & \left( \frac{n}{\tau} \right)^2 b \, \e{\sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \big( A_j^f \big)^2 \
+		 + \sum_{j=\left\lceil \gammab^{-1} \right\rceil+1}^{b-\left\lceil \gammab^{-1} \right\rceil} \big( A_j^c \big)^2 \
+		 + \sum_{j=b-\left\lceil \gammab^{-1} \right\rceil+1}^{b} \big( A_j^e \big)^2 
 		} \\
-		 = & \left( \frac{n}{\tau} \right)^2 n_b \left(n_b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \left( A_j^c \right)^2 }
-		+ \left( \frac{n}{\tau} \right)^2  2 n_b \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \left( A_j^f \right)^2 }.
+		 = & \left( \frac{n}{\tau} \right)^2 b \left(b - 2\left\lceil \gammab^{-1} \right\rceil \right) \e{ \big( A_j^c \big)^2 }
+		+ \left( \frac{n}{\tau} \right)^2  2 b \sum_{j=1}^{\left\lceil \gammab^{-1} \right\rceil} \e{ \big( A_j^f \big)^2 }.
 	\end{align*}	
-	The last equality follows because each front-fringe batch's $\e{(A_j^f)^2}$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$  has an identical pair in an end-fringe batch's $\e{(A_j^e)^2}$, $j=n_b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,n_b$, and all center batches have identical values of $\e{(A_j^c)^2}$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, n_b - \left\lceil \gammab^{-1} \right\rceil$.
-	As a result, we have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{\tau}\right)^2n_b^2 < (2m)^2$.  
+	The last equality follows because each front-fringe batch's $\e{\big(A_j^f\big)^2}$, $j=1,\ldots,\left\lceil \gammab^{-1} \right\rceil$  has an identical pair in an end-fringe batch's $\e{\big(A_j^e\big)^2}$, $j=b - \left\lceil \gammab^{-1} \right\rceil+1,\ldots,b$, and all center batches have identical values of $\e{\big(A_j^c\big)^2}$, $j=\left\lceil \gammab^{-1} \right\rceil+1, \ldots, b - \left\lceil \gammab^{-1} \right\rceil$.
+	As a result, we have $\left\lceil \gammab^{-1} \right\rceil + 1$ expectation terms, each of which has a coefficient that is less than $\left(\frac{n}{\tau}\right)^2b^2 < (2m)^2$.  
         Removing the notation for fringe or center batch for simplicity, each expectation can be bounded by

### 2014-12-29 formatted/omrp_lb_acmtomacs.tex
Formatted According to ACM TOMACS
All the files, images, etc. are in the new subfolder 'formatted'

--- 2014-12-28 omrp_lb_fl.tex
@@
-\documentclass[12pt]{article}
+% v2-acmsmall-sample.tex, dated March 6 2012
+% This is a sample file for ACM small trim journals
+%
+% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
+% (c) 2010 Association for Computing Machinery (ACM)
+%
+% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
+% Users can also go through the FAQs available on the journal's submission webpage.
+%
+% Steps to compile: latex, bibtex, latex latex
+%
+% For tracking purposes => this is v1.3 - March 2012
 
+\documentclass[prodmode,acmtomacs]{acmsmall} % Aptara syntax
+
+% Package to generate and customize Algorithm as per ACM style
+\usepackage[ruled]{algorithm2e}
+\renewcommand{\algorithmcfname}{ALGORITHM}
+\SetAlFnt{\small}
+\SetAlCapFnt{\small}
+\SetAlCapNameFnt{\small}
+\SetAlCapHSkip{0pt}
+\IncMargin{-\parindent}
+
+% Metadata Information   %%% TO BE UPDATED!
+\acmVolume{9}
+\acmNumber{4}
+\acmArticle{39}
+\acmYear{2010}
+\acmMonth{3}
+
+% User added packages
 \usepackage{latexsym}
-\usepackage[margin=1in]{geometry}
-\usepackage{graphicx}
-\usepackage{subfig}
-\usepackage{enumerate}
+\usepackage{amsmath}
 \usepackage{multirow}
 \usepackage{booktabs}
-%\usepackage{mathptmx}
-\usepackage[square]{natbib}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsbsy}
-\usepackage{amsthm}
-\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
-\usepackage{setspace}
+\usepackage{subfig}
 
-\onehalfspacing
-
-\newtheorem{theorem}{Theorem}
-\renewcommand{\thetheorem}{ \arabic{theorem}}
-\newtheorem{corollary}[theorem]{Corollary}
-\renewcommand{\thecorollary}{\arabic{corollary}}
-\newtheorem{definition}{Definition}
-\renewcommand{\thedefinition}{\arabic{definition}}
-\newtheorem{lemma}{Lemma}
-\renewcommand{\thelemma}{ \arabic{lemma}}
-\newtheorem{proposition}{Proposition}
-\renewcommand{\theproposition}{ \arabic{proposition}}
-\newtheorem{remark}{Remark}
-\renewcommand{\theremark}{ \arabic{remark}}
-
+% User added commands
 % Frequently used general mathematics
@@
 
-\newcommand{\Keywords}[1]{\par\noindent 
-{\small{\em Keywords\/}: #1}}
-
-%#########################################################
-%*
-%*  The Document.
-%*
+% Document starts
 \begin{document}
 
+% Page heads
+\markboth{D. Love and G. Bayraksan}{Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
+
+% Title portion
 \title{Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs}
+\author{DAVID LOVE
+\affil{University of Arizona}
+G\"{U}Z\.{I}N BAYRAKSAN
+\affil{The Ohio State University}
+}
 
-\author{David~Love$^{a}$\ \ and G\"{u}zin~Bayraksan$^{b}$\thanks{Corresponding author. Tel.: +1 614-292-1695. Fax:+1 614-292-7852}\\[6pt]
-{\small
-      $^{a}$ Program in Applied Mathematics, University of Arizona, Tucson, AZ 85721, USA,}\\
-{\small \ \ \ \ \ \texttt{dlove@math.arizona.edu}} \\
-{\small 
-      $^{b}$ Integrated Systems Engineering, The Ohio State University, Columbus, OH 43210, USA,}\\
-{\small \ \ \ \  \   \texttt{bayraksan.1@osu.edu}}}
-\date{}
+\begin{abstract}
+Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate variance estimators with asymptotically lower variance.
+In this article, we apply the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
+We give conditions under which the resulting optimality gap point estimators are strongly consistent, the optimality gap interval estimators are asymptotically valid, and the OBM variance estimators for optimality gap have asymptotically lower variances relative to their nonoverlapping counterparts \cite{Meketon1984,Welch1987}.
+We investigate computational efficiency, a combined measure of variance and computation time, providing guidelines on the degree of overlap.  
+Numerical experiments on several test problems are presented, examining the small-sample behavior and the empirical computational efficiency of the overlapping batches method in this context.  
+\end{abstract}
+
+\category{G.1.6}{Numerical Analysis}{Optimization}[Stochastic Programming]
+\category{I.6.8}{Simulation and Modeling}{Types of Simulation}[Monte Carlo]
+\category{I.6.1}{Simulation and Modeling}{Simulation Theory}
+
+\terms{Theory, Algorithms, Measurement}
+
+\keywords{Sample average approximation (SAA); Overlapping batch means;   Stochastic programming; Optimality gap estimation}
+
+\acmformat{David Love and G\"{u}zin Bayraksan, 2014. Overlapping batches for the assessment of solution quality in stochastic programs.}
+% At a minimum you need to supply the author names, year and a title.
+% IMPORTANT:
+% Full first names whenever they are known, surname last, followed by a period.
+% In the case of two authors, 'and' is placed between them.
+% In the case of three or more authors, the serial comma is used, that is, all author names
+% except the last one but including the penultimate author's name are followed by a comma,
+% and then 'and' is placed before the final author's name.
+% If only first and middle initials are known, then each initial
+% is followed by a period and they are separated by a space.
+% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
+
+\begin{bottomstuff}
+This work is supported in part by the National Science Foundation, under
+grant CMMI-1345626 and grant DMS-0602173.
+
+Author's addresses: D. Love, (Current address) American Express, New York, NY;
+G. Bayraksan, Department of Integrated Systems Engineering, the Ohio State University, Columbus, OH; email: bayraksan.1@osu.edu.
+\end{bottomstuff}
 
 \maketitle
-
-\begin{abstract}
-\noindent Overlapping Batch Means (OBM) has long been used in simulation as a method of reusing data to generate variance estimators with asymptotically lower variance.
-In this paper, we apply the OBM method to stochastic programming by formulating a variant of the multiple replications procedure used for assessing solution quality.
-We give conditions under which the resulting optimality gap point estimators are strongly consistent, the optimality gap interval estimators are asymptotically valid, and the OBM variance estimators for optimality gap have asymptotically lower variances relative to their nonoverlapping counterparts \citep{Meketon1984,Welch1987}.
-We investigate computational efficiency, a combined measure of variance and computation time, providing guidelines on the degree of overlap.  
-Numerical experiments on several test problems are presented, examining the small-sample behavior and the empirical computational efficiency of the overlapping batches method in this context.  
-\medskip
-
-\Keywords{Sample average approximation (SAA); Overlapping batch means;   Stochastic programming; Optimality gap estimation}
-\end{abstract}
 
@@
 
-The Overlapping Batch Means (OBM) method, proposed by \citet{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts.
+The Overlapping Batch Means (OBM) method, proposed by \citeN{Meketon1984}, is commonly used in simulation to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts.
 In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
-\cite{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
-More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated \citep{Alexopoulos01012007,Alexopoulos2007}; see also \cite{Meterelliyoz_etal_12}.
+\citeN{SAH90} use overlapping estimators to estimate the variance of estimators for non-means. 
+More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated [\citeNP{Alexopoulos01012007};\citeyearNP{Alexopoulos2007}]; see also \citeN{Meterelliyoz_etal_12}.
 To the best of our knowledge, OBM has never before been studied in a stochastic optimization context. 
-In this paper, we show that the overlapping batches achieve nearly the same bias and lower variances relative to their nonoverlapped counterparts when used in a stochastic optimization setting.
+In this article, we show that the overlapping batches achieve nearly the same bias and lower variances relative to their nonoverlapped counterparts when used in a stochastic optimization setting.
 
@@
 These individual estimators are then used to form point and interval estimators applying the nonoverlapping batch means method.
-This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \cite{Mak1999}.   
-In this paper, we formulate an overlapping batches version of MRP.
+This is referred to as the Multiple Replications Procedure (MRP) and was initially discussed in \citeN{Mak1999}.   
+In this article, we formulate an overlapping batches version of MRP.
 
 We consider a stochastic optimization problem of the form 
-\begin{align} \tag{SP} \label{eq:sto_prog} 
+\begin{align} 
+	\tag{SP} 
+	\label{eq:sto_prog} 
 	z^* & = \min_{\x \in X} \e{f(\x,\xit)},
@@
 A sampling approximation of (\ref{eq:sto_prog}), often called the sample average approximation, is given by\vspace*{-0.07in}
-\begin{align} \tag{SP$_m$} \label{eq:sto_prog_m}
+\begin{align} 
+	\tag{SP$_m$} 
+	\label{eq:sto_prog_m}
 	z_m^* & = \min_{\x \in X} \frac{1}{m} \sum_{i=1}^m f(\x,\xiti).
@@
 The lower the optimality gap, the higher the quality of the solution; and a zero optimality gap implies that the solution is optimal. 
-We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout the paper.
+We assume that the candidate solution $\xh$ is given as input to our procedures, and hence fixed, throughout the article.
 
@@
 This motivates estimating the upper bound on the optimality gap in stochastic programming by using Monte Carlo simulation.
-Given a sample size $m$, an upper bound on the optimality gap can be obtained by $$
+Given a sample size $m$, an upper bound on the optimality gap can be obtained by \[
 \e{f(\xh,\xit)} - \zs \leq \e{f(\xh,\xit)} - \e{\zs_m}
-$$ 
-due to the inequality $\e{\zs_m} \leq \zs$ \citep{Mak1999,norkin_pflug_ruszczynski_98}.
+\]
+due to the inequality $\e{\zs_m} \leq \zs$ \cite{Mak1999,norkin_pflug_ruszczynski_98}.
 This bound improves as the sample size increases; that is, $\e{\zs_m} \leq \e{\zs_{m+1}} \leq \zs$.  
@@
 The resulting point estimator of the optimality gap is then 
-$$
+\[
 \frac{1}{m} \sum_{i=1}^m f(\xh,\xiti) - \zs_m.
-$$ 
+\]
 Here, we assume the same observations $\xit^1, \dots, \xit^m$ are used in both terms.
@@
 Computing the above optimality gap estimate involves solving the optimization problem (\ref{eq:sto_prog_m}) to obtain a lower bound estimator of $\zs$, $\zs_m$, which complicates the statistical analysis.
-As mentioned above, to enable statistical inference, the MRP of \citet{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$), and averages them to obtain a point estimator.
+As mentioned above, to enable statistical inference, the MRP of \citeN{Mak1999} generates $k$ independent estimators, each using sample size $m$ ($k$ nonoverlapping batches of size $m$), and averages them to obtain a point estimator.
 The sample variance of these estimators is used to form confidence intervals (CIs) for the optimality gap (we further review MRP in \S \ref{ssec:mrp}).  
@@
 With i.i.d.\ sampling, $f$ can be linear or nonlinear, $\X$ can include integrality constraints or not.  
-It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \cite{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
-Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \citep{wang_ahmed_08} and stochastic dominance \citep{hu2010sample} constraints.
+It is also easy to implement; thus, MRP has been applied to a wide variety of problems, including finance, supply chain network design, etc.; see, e.g., \citeN{bertocchi_etal_99,janjarassuk_linderoth_08,santoso_ahmed_etal_05}.
+Recently, the approach of (nonoverlapping) batching has been used for assessing solution quality of stochastic programs with finitely many expected value \cite{wang_ahmed_08} and stochastic dominance \cite{hu2010sample} constraints.
 
@@
 The contributions of this article are as follows: 
-\begin{itemize}
-\item[(i)] We formulate an overlapping batch means variant of MRP, where the degree of overlap can be chosen by the user.  
+\begin{enumerate}
+\item We formulate an overlapping batch means variant of MRP, where the degree of overlap can be chosen by the user.  
 This application of OBM is novel because each batch mean estimator includes an internal minimization, which has not been studied in the literature.
-%\vspace*{-0.1in}
 
-\item[(ii)] We provide conditions under which the resulting optimality gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
+\item We provide conditions under which the resulting optimality gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.
 We also show that the resulting point estimators are strongly consistent and that the interval estimators are asymptotically valid. 
@@
 
-\item[(iii)] We examine small-sample behavior of the estimators through numerical examples. 
+\item We examine small-sample behavior of the estimators through numerical examples. 
 Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage---for both small- and large-sample cases.
 
-\item[(iv)] As the degree of overlap increases, the number of batches---and optimization problems solved---increases because we need to solve a sampling problem per batch. 
+\item As the degree of overlap increases, the number of batches---and optimization problems solved---increases because we need to solve a sampling problem per batch. 
 At the same time, variances are lowered, and when warm starting is available, solution time per batch can decrease, yielding efficiency gains. 
@@
 Based on this study, we provide guidelines on selecting the degree of overlap and demonstrate efficiency on a newsvendor problem. 
-\end{itemize}
+\end{enumerate}
 
-An earlier version of the paper appeared in \cite{love2011overlapping}. 
-Most of the theoretical results in the current version of the paper are new, including almost sure convergence and asymptotically lower variances of the overlapping variance estimators, and asymptotic validity of the interval estimators.
+An earlier version of the article appeared in \citeN{love2011overlapping}. 
+Most of the theoretical results in the current version of the article are new, including almost sure convergence and asymptotically lower variances of the overlapping variance estimators, and asymptotic validity of the interval estimators.
 These results are achieved through a stronger assumption on the rate of convergence of the sampling problem's solution to the unique optimal solution, which is satisfied by several classes of (\ref{eq:sto_prog}); see \S \ref{subsec:assumptions}.
@@
 
-The rest of the paper is organized as follows.  
+The rest of the article is organized as follows.  
 In the next section, we review relevant background information.  
@@
 However, the usual (sample) variance estimator $\frac{1}{n-1} \sum_{i=1}^n (y^i - \ybb)^2$ can be inappropriate to use in the presence of correlated data, resulting in inaccurate interval estimators.
-To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \cite{law_15}.  
+To overcome this difficulty, various variance estimators have been proposed in the simulation literature; see, e.g., \citeN{law_15}.  
 We briefly review two of these variance estimators: nonoverlapping and overlapping batch means.
@@
 The variance estimator of the batch means, which is $m/n$ times the sample variance, is calculated as
-\begin{equation} \label{eq:var}
+\begin{equation} 
+	\label{eq:var}
 	\varhat(\ybb) = \frac{m}{n}\frac{1}{k-1} \sum_{j=1}^k \left( \yb_j - \ybb \right)^2.
@@
 The $(1-\alpha)$-level approximate CI is then formed by $\ybb \pm t_{k-1,\alpha/2} \sqrt{\varhat(\ybb)}$, where $t_{k-1,\alpha/2}$ denotes the $1-\alpha/2$ quantile of the Student's t distribution with $k-1$ degrees of freedom.
-Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$ \citep{alexo_enc_06}.
+Under appropriate conditions, $n\varhat(\ybb)$ is a consistent estimator of $\sigma^2$ \cite{alexo_enc_06}.
 
@@
 Overlapping batch means modifies nonoverlapping batch means by reusing a subset of observations from one batch to form the next batch. 
-In this paper, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
-For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citet{Meketon1984}.  
+In this article, we use the {\it batch nonoverlap parameter} $1 \leq \gamma \leq m$ to denote how much neighboring batches do {\it not} overlap.  
+For instance, $\gamma = m$ corresponds to the case of nonoverlapping batches and $\gamma = 1$ corresponds to the maximally overlapping case of \citeN{Meketon1984}.  
 In general, $\gamma$ can take any integer value between and including $[1,m]$. 
@@
 The variance estimator is updated to
-\begin{equation} \label{eq:variance_gamma}
+\begin{equation} 
+	\label{eq:variance_gamma}
 	\vartg{\ybb} = \frac{1}{b \left( \tfrac{n}{m} - 1 \right) }  \sum_{j=1}^{b} (\yb_j - \ybb)^2.
@@
 Observe that with $\gamma=m$ and $n=mk$, (\ref{eq:variance_gamma}) reduces to (\ref{eq:var}).
-With $\gamma=1$ (the maximally overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \cite{Meketon1984}.
-This slightly different denominator makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$, with the same asymptotic benefits of nearly the same bias and lower variance relative to its counterpart obtained via nonoverlapping batches \citep{Song1992}.
+With $\gamma=1$ (the maximally overlapping case), the denominator in (\ref{eq:variance_gamma}) is slightly different than the one in  \citeN{Meketon1984}.
+This slightly different denominator makes $\vto{\ybb}$ an unbiased estimator for i.i.d.\ data for all finite $m$ and $n$, with the same asymptotic benefits of nearly the same bias and lower variance relative to its counterpart obtained via nonoverlapping batches \cite{Song1992}.
 
@@
 The maximally overlapping case ($\gamma = 1$) corresponds to $\gammab=0$, and the nonoverlapping case corresponds to $\gammab=1$. 
-\cite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally overlapping cases. 
-Under appropriate conditions, the results of \cite{damerdji1995mean}, along with those of \cite{Meketon1984} and \cite{Welch1987}, establish that 
+Damerdji~\shortcite{damerdji1994strong,damerdji1995mean} studied batching structures that guarantee almost sure and mean-square consistency of $\vartg{\ybb}$ in the nonoverlapping and maximally overlapping cases.
+Under appropriate conditions, the results of \citeN{damerdji1995mean}, along with those of \citeN{Meketon1984} and \citeN{Welch1987}, establish that 
 \begin{equation}
@@
 \end{equation}
-as the batch size $m$ and then the number of batches $n/m$ tend to infinity; see also \cite{Alexopoulos2007}. 
+as the batch size $m$ and then the number of batches $n/m$ tend to infinity; see also \citeN{Alexopoulos2007}. 
 In (\ref{eq:varvarred}), $\beta_1 = 2$ for nonoverlapping batches and $\beta_0 = \frac{4}{3}$ for maximally overlapping batches.  
 More generally, $\beta_{\gammab}$ is twice the value of 
-\begin{equation} \label{eq:var_reduct_formula}
+\begin{equation} 
+	\label{eq:var_reduct_formula}
 	\gammab \left( 1 + 2 \sum_{j=1}^{\cogb-1} (1-j\gammab)^2 \right),
 \end{equation}
-where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument \citep{Welch1987}.
+where $\lceil \cdot \rceil$ denotes the smallest integer that is greater than or equal to its argument \cite{Welch1987}.
 If $\ogb$ is an integer, (\ref{eq:var_reduct_formula}) simplifies to $\frac{2+\gammab^2}{3}$.
@@
 Thus, we can expect that the true probability of the optimality gap residing within the CI to be greater than the $1 - \alpha$ suggested by the above calculation.  
-This is shown empirically in \cite{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI; see also \cite{stockbridge_bayraksan_13}.
-\cite{bayraksan_morton_09}, \cite{partani2006jackknife}, and \cite{partani_07} discuss variations of MRP aimed to reduce bias and variance.
+This is shown empirically in \citeN{Bayraksan2006}, which also investigates additional methods for using a smaller number of replications (e.g., 1 or 2) with an alternative variance estimator to compute a CI; see also \citeN{stockbridge_bayraksan_13}.
+\citeN{bayraksan_morton_09}, \citeN{partani2006jackknife}, and \citeN{partani_07} discuss variations of MRP aimed to reduce bias and variance.
 
@@
 
-\begin{description}
+\begin{describe}{{\bf A2$^\prime$\/}}
 	\item[A1] Samples of the random variable $\xit$ are i.i.d.
@@
            That is, there exist constants $M > 0$ and $c > 0$ such that $\log(\p{\xs_m \neq \xs}) \leq -cm$ for all $m > M$.
-\end{description}
+\end{describe}
 
@@
 Assumption A3 can be satisfied for different classes of problems with unique optimal solutions.  
-\citet{shapiro2000rate} establish exponential rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite.
-\citet{kleywegt2002sample} show that Assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $\x \in X \backslash \{\xs\}$ is finite valued on $\R$.
+\citeN{shapiro2000rate} establish exponential rates of convergence for a class of (\ref{eq:sto_prog}), which include two-stage stochastic linear programs with recourse when the support of $\xit$ is finite.
+\citeN{kleywegt2002sample} show that Assumption A3 can be satisfied for discrete stochastic programs (i.e., when $X$ is a finite set) under the condition that the moment generating function of $f(\xs,\xit) - f(\x,\xit)$ for $\x \in X \backslash \{\xs\}$ is finite valued on $\R$.
 This class of problems includes stochastic integer programs with recourse.
@@
 
-\begin{lemma} \label{lem:gbb_prob}
+\begin{lemma} 
+	\label{lem:gbb_prob}
 	Under Assumptions A1 and A3, $\p{\dbb_l - \gbb_l \neq 0} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
@@
 
-\begin{lemma} \label{lem:gb_gbb_l4}
+\begin{lemma} 
+	\label{lem:gb_gbb_l4}
 	Under Assumptions A1--A3, both (i) $\e{(\db_{lj} - \gb_{lj})^4} \rightarrow 0$ and (ii) $\e{(\dbb_l - \gbb_l)^4} \rightarrow 0$ exponentially fast as $l \rightarrow \infty$.
@@
 
-\begin{theorem} \label{thm:strong_consistency}
+\begin{theorem} 
+	\label{thm:strong_consistency}
 	Under Assumptions A1--A3, (i) $\gbb_l - \dbb_l \rightarrow 0$, a.s., and (ii) $n_l VG_l - n_l VD_l \rightarrow 0$, a.s.\ as $l \rightarrow \infty$.  
@@
 As a result, if $n_l VD_l$ is a consistent estimator of $\sigma^2_{\xh}$, so is $n_l VG_l$.  
-Strong consistency of the variance estimator $n_l VD_l$ has been studied in \cite{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
+Strong consistency of the variance estimator $n_l VD_l$ has been studied in \citeN{damerdji1994strong} for the cases of nonoverlapping and maximally overlapping batches.  
 Under the additional moment assumption
-\begin{description}
+\begin{describe}{{\bf A2$^\prime$\/}}
 	\item[A2$^\prime$]  $\exists \epsilon > 0$ such that $\sup_{\x \in X} \e{f(\x,\xi)^{4+\epsilon}} < \infty$,
-\end{description}
-for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \cite{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.
+\end{describe}
+for a sampling scheme of $m_l = \lfloor n_l^r \rfloor$, Corollaries 3.4 and 4.2 of \citeN{damerdji1994strong} show that $n_l VD_l$ is consistent if $\tfrac{2}{4+\epsilon} < r < 1$ for nonoverlapping batches and $\tfrac{2}{4+\epsilon} < r < \tfrac{1}{2}$ for maximally overlapping batches.
 
@@
 To prove OMRP variance estimators have asymptotically lower variances when compared to the MRP variance estimator, we wish to show that 
-$$
+\[
 (\tfrac{n_l}{m_l}) \left( \var{n_l VG_l} - \var{n_l VD_l} \right) \rightarrow 0;
-$$
+\]
 see, e.g., (\ref{eq:varvarred}).
@@
 A hypothesis of Theorem \ref{thm:varvar_conv} is a batching structure that ensures convergence of $\frac{n_l}{m_l}\var{n_l VD_l}$ to the appropriate $\beta_{\gammab} \sigma^4_{\xh}$, ensuring the mean-square consistency of $n_l VD_l$.
-\citet{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $(4+\epsilon)$th-finite-moments Assumption A2$^\prime$.
+\citeN{damerdji1995mean} shows that mean-square convergence is guaranteed by $\tfrac{1}{2} + \tfrac{1}{4+\epsilon} < r < 1$ for both nonoverlapping and maximally overlapping batches under the batching structure $m_l = \lfloor n_l^r \rfloor$ and $(4+\epsilon)$th-finite-moments Assumption A2$^\prime$.
 With A2, the range of $r$ that ensures mean-square consistency can be found by setting $\epsilon=0$.
@@
 
-\begin{theorem} \label{thm:conf_int}
+\begin{theorem} 
+	\label{thm:conf_int}
 	Suppose Assumptions A1--A3 hold and the batching structure ensures $n_l VD_l$ converges in probability to $\sigma^2_\xh$.  
@@
 \begin{proof} 
-%        With $\xh \neq \xs$, 
 			Let $X_l = \frac{\dbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, $Y_l = \frac{\gbb_l - \mu_\xh}{\sigma^2_\xh/\sqrt{n_l}}$, and $Z_l = \frac{\sigma^2_\xh}{\sqrt{n_lVG_l}}$. 
@@
 The first test problem is a newsvendor problem with demand distributed uniformly on $\{0, 0.0001, 0.0002, \dots, 10\}$; we denote it as NVD.
-The instance of the newsvendor problem can be found in \cite{Bayraksan2006}, except here we used a discrete uniform demand distribution.
-The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations \citep{higle1996}.
-The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables \citep{kleywegt2002sample}.
-The final problem is a stochastic vehicle routing problem, denoted DB1, with 46 stochastic parameters and a total of $4.5 \times 10^{25}$ realizations \citep{donohue1995upper}.
+The instance of the newsvendor problem can be found in \citeN{Bayraksan2006}, except here we used a discrete uniform demand distribution.
+The second is a capacity expansion planning problem, denoted CEP1, with random demand vector $\xit$ of dimension 3, with 216 total realizations \cite{higle1996}.
+The third is a stochastic knapsack problem denoted 10D, with 10 stochastic parameters and 10 binary decision variables \cite{kleywegt2002sample}.
+The final problem is a stochastic vehicle routing problem, denoted DB1, with 46 stochastic parameters and a total of $4.5 \times 10^{25}$ realizations \cite{donohue1995upper}.
 
-\begin{table}[thb]
-\centering
-\footnotesize
+\begin{table}
+\tbl{Test problem characteristics\label{tb:test_problems}}{
 \begin{tabular}{lcccc}
@@
 \hline
-\end{tabular}
-\caption{Test problem characteristics}
-\label{tb:test_problems}
+\end{tabular}}
 \end{table}
@@
 10D demonstrates the behavior of OMRP when $|X|$ is finite.
-Furthermore, 10D has a high condition number \citep{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP when the bias of the gap is significant.
+Furthermore, 10D has a high condition number \cite{kleywegt2002sample}, making it unlikely that the optimal solution $\xs$ is found when using a sampling solution, thus demonstrating the behavior of OMRP when the bias of the gap is significant.
 The optimal solutions of NVD, CEP1, and 10D are known, allowing for explicitly checking and verifying the results.
@@
 
-The candidate solutions used for NVD and CEP1 and their characteristics can be found in \cite{Bayraksan2006}.
+The candidate solutions used for NVD and CEP1 and their characteristics can be found in \citeN{Bayraksan2006}.
 We used the candidate solution (0, 0, 1, 1, 1, 0, 1, 1, 0, 1) for 10D with $\mu_{\xh} = 158.579$ and the candidate solution (11, 14, 8, 11, 7) for DB1 with an estimated $\mu_{\xh} = 1.08$. 
@@
 We solved it using the quicksort algorithm in C++. 
-The problems CEP1 and DB1 are two-stage stochastic linear programs with recourse and were solved with the regularized decomposition algorithm of \citet{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \citep{ruszczynski1997accelerating}.
+The problems CEP1 and DB1 are two-stage stochastic linear programs with recourse and were solved with the regularized decomposition algorithm of \citeN{ruszczynski1986regularized}, using the accelerated version of the algorithm implemented in C++ \cite{ruszczynski1997accelerating}.
 10D is a stochastic knapsack problem and was solved using dynamic programming.  
-In all cases, we used the Mersenne Twister algorithm of \citet{matsumoto_nishimura_98} to generate the random samples, using an implementation in C++ \citep{wagner_twister_09}.
+In all cases, we used the Mersenne Twister algorithm of \citeN{matsumoto_nishimura_98} to generate the random samples, using an implementation in C++ \cite{wagner_twister_09}.
 
@@
 Figure~\ref{fig:varvar1} shows the variance of OMRP variance estimators, normalized with respect to $\var{nVG}$ of the nonoverlapping case (MRP). 
-The solid lines in these figures show the theoretical relative decreases in variance from \cite{Welch1987} given by (\ref{eq:var_reduct_formula}). 
+The solid lines in these figures show the theoretical relative decreases in variance from \citeN{Welch1987} given by (\ref{eq:var_reduct_formula}). 
 Empirical results agree with the theoretical values well, with more variability observed in CEP1, 10D, and DB1. 
@@
 	   \label{fig:nv_varvar}
-	   \includegraphics[width=.5\textwidth]{images/nv_varvar_discrete}}
+	   \includegraphics[width=.5\textwidth]{nv_varvar_discrete}}
 	\subfloat[][CEP1]{
 	   \label{fig:cep1_varvar}
-	   \includegraphics[width=.5\textwidth]{images/cep1_varvar}}
+	   \includegraphics[width=.5\textwidth]{cep1_varvar}}
 	\\
@@
 	   \label{fig:10d_varvar}
-	   \includegraphics[width=.5\textwidth]{images/10D_varvar}}
+	   \includegraphics[width=.5\textwidth]{10D_varvar}}
 	\subfloat[][DB1]{
 	   \label{fig:db1_varvar}
-	   \includegraphics[width=.5\textwidth]{images/db1_varvar}}
+	   \includegraphics[width=.5\textwidth]{db1_varvar}}
 	\caption{
@@
 	   \label{fig:nv_avgvar}
-	   \includegraphics[width=.5\textwidth]{images/nv_avgvar_discrete}}
+	   \includegraphics[width=.5\textwidth]{nv_avgvar_discrete}}
 	\subfloat[][Coverage Probability]{
 	   \label{fig:nv_cover}
-	   \includegraphics[width=.5\textwidth]{images/nv_cover_discrete}}
+	   \includegraphics[width=.5\textwidth]{nv_cover_discrete}}
 	\caption{ 
@@
 We observed the same for CEP1, 10D, and DB1.  
-The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \cite{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown for brevity) remains fairly constant around the desired value of $90\%$.
+The coverage probabilities from applying the (nonoverlapping) MRP algorithm to these problems presented in \citeN{Bayraksan2006} agree with our results: for the newsvendor problem, coverage probability drops as $m$ increases and the coverage probability of CEP1 (not shown for brevity) remains fairly constant around the desired value of $90\%$.
 Coverage probability for 10D (not shown) and {\it estimated} coverage probability for DB1 (also not shown) were very high, more than $0.99$.  
@@
 	   \label{fig:efficiency_theory}
-	   \includegraphics[width=.49\textwidth]{images/comp_efficiency_theory}}
+	   \includegraphics[width=.49\textwidth]{comp_efficiency_theory}}
 	\subfloat[][Empirical for NVD]{
 	   \label{fig:efficiency_nv}
-	   \includegraphics[width=.51\textwidth]{images/nv_comp_efficiency}}
+	   \includegraphics[width=.51\textwidth]{nv_comp_efficiency}}
 		\caption{
@@
 	   \label{fig:comp_work_comparison_theory}
-	   \includegraphics[width=.51\textwidth]{images/work_comparison}}
+	   \includegraphics[width=.51\textwidth]{work_comparison}}
 	\subfloat[][Empirical for NVD]{
 	   \label{fig:comp_work_comparison_nv}
-	   \includegraphics[width=.48\textwidth]{images/nv_work_comparison2}}
+	   \includegraphics[width=.48\textwidth]{nv_work_comparison2}}
 		\caption{
@@
 
-We have applied the overlapping batch means method from simulation output analysis \citep{Meketon1984,Song1992,Welch1987} to the problem of assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \citep{Mak1999}.
+We have applied the overlapping batch means method from simulation output analysis \cite{Meketon1984,Song1992,Welch1987} to the problem of assessing solution quality in stochastic programming, in particular, to Monte Carlo simulation-based estimators of optimality gaps \cite{Mak1999}.
 We have provided conditions under which (i) the resulting point estimator of the optimality gap and its associated variance estimator are consistent, (ii) OMRP variance estimators achieve asymptotically lower variances relative to the MRP variance estimator, and (iii) OMRP CIs are asymptotically valid.
@@
 
-Overall, the results in this paper suggest that OMRP could be an efficient method to estimate optimality gaps for a class of stochastic programs when warm starting is available and/or generating the observations is costly.
+Overall, the results in this article suggest that OMRP could be an efficient method to estimate optimality gaps for a class of stochastic programs when warm starting is available and/or generating the observations is costly.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgments}
+\begin{acks}
 The authors thank Andrzej Ruszczy{\'{n}}ski and Artur {\'{S}}wietanowski for
 access to their regularized decomposition code, which was used to solve CEP1 and DB1. 
-The authors are grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the paper. 
-This research has been supported in part by the National Science Foundation under Grants DMS-0602173 and CMMI-1345626.
+The authors are grateful to the associate editor and two anonymous referees for valuable suggestions that significantly improved both the content and the presentation of the article. 
+%This research has been supported in part by the National Science Foundation under Grants DMS-0602173 and CMMI-1345626.
+\end{acks}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{abbrvnat}
+\bibliographystyle{ACM-Reference-Format-Journals}
 \bibliography{omrp}
@@
 
+% History dates
+\received{October 2013}{July 2014}{December 2014}
+
 \end{document}

### 2014-12-29 Referee1_Response_fl.tex
Responses for the minor comments

@@
 \begin{center}
-\textbf{\Large Response to Referee 1} 
+\textbf{\Large Response to Reviewer 1} 
 \medskip
+
+on the revision of\\
 
@@
 
-\bigskip
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \noi
-We thank the referee for the helpful comments and suggestions. 
-We incorporated all of the recommended changes and believe the paper is improved as a result. 
+We thank the Reviewer for the careful read and the helpful suggestions. 
+We incorporated all of the recommended changes. 
 Below, we go through in detail these changes. 
@@
 
+\begin{itemize}
+\item \textit{p6, l47: The sentence with ``are no longer independent'' doesn't quite make sense, given the context introduced so far in which the observations of y can be dependent.}
+\end{itemize}
+
 \noi 
-{\large \bf ``Major'' comments:}
+Deleted this sentence. 
+Thank you; good catch! 
+We revised and rearranged the beginning of this paragraph for better flow.  
 \medskip
@@
 \begin{itemize}
-\item[\textbf{M1.}] \textit{In the typical simulation setting, the computational effort required to produce the output dominates, and hence one would like to ``make the most'' of the output in terms of analysis.
-Sometimes, a similar motivation can arise in stochastic optimization because there may be a computationally expensive underlying simulation model that must be run to produce the i.i.d.\ realizations that are then used in an SAA approach.
-(While they don't now, the authors could include this as motivation for
-their work.)}
+\item \textit{p11, l16: Delete extra space in \S4.4.}
 \end{itemize}
@@
 \noi 
-Thank you for this suggestion. 
-You are right.
-There are cases when generating scenarios is expensive in the stochastic optimization setting as well. 
-We changed the introduction based on your, the associate editor, and the other reviewer's comments. 
-We specifically added this as a motivation in the first full paragraph on page four of the revised paper. 
+Done. 
 \medskip
@@
 \begin{itemize}
-\item[] \textit{However, perhaps more often, sampling the i.i.d. realizations is computationally cheap compared to solving the resulting SAA instances in stochastic optimization. 
-In this latter case, we have a choice between simply increasing the number of batches in a non-overlapping method or using the overlapping batch means approach (with some degree of overlap) in order to reduce variance.
-Based on the paper's results, perhaps the computational effort required to achieve a level of variance reduction should guide this choice. 
-The authors do point to the fact that warm starts in a stochastic
-optimization algorithm can be exploited much more easily when using overlapping batch means than when not using overlapping batches. 
-Some attempt to explore this tradeoff would be valuable. 
-The computational results use sorting (for the news vendor problem), a dynamic programming algorithm (for a stochastic knapsack model), and a decomposition method (for two-stage stochastic linear programs).
-While I am not suggesting that this exploration needs to be made for all three types of algorithms, even exploring it in the case of the sorting algorithm (where some algorithms are well suited for almost-sorted lists) could provide valuable insight.}
+\item \textit{p13, l21-22: I know what the authors mean, but I can't quite parse the last sentence of the proof of Lemma 2.}
 \end{itemize}
@@
 \noi
-We studied computational efficiency of the OMRP variance estimators and demonstrated efficiency on the newsvendor problem using insertion sort. 
-The results of this study are presented in a new section, \S 5.4 (Computational Efficiency).
-We first approached efficiency by the reciprocal of variance multiplied by the computation time, per the associate editor's suggestion. 
-Maximizing computational efficiency defined in this manner provided guidelines on selecting the degree of overlap. 
-We then looked at how OMRP compared to increasing the number batches in MRP to reach an equivalent variance level.
-We examined computational efficiency theoretically---assuming a functional form of the solution time per batch---and also empirically. 
-For empirical evaluation, we used the newsvendor problem with insertion sort, based on your suggestions; thank you. 
-We found that when effective warm starting is available, overlapping can lead to more efficient estimators than (nonverlapping) MRP, both when the direct nonoverlapping counterpart is used or when the number of batches in MRP is increased to match the variance of the overlapping counterpart.
-We believe the study of computational efficiency significantly improved the paper. 
-Thank you.\smallskip
-
-\noi
-{\it Note:} Please also see our response to your minor comment 19 below.
+Deleted this sentence. Shortened the paragraph as suggested by Reviewer 2. 
 \medskip
@@
 \begin{itemize}
-\item[\textbf{M2.}] \textit{The choice of the lower bound that is embedded in equation (8) is interesting. 
-(The upper bound in equation (8) is completely natural as the sample mean of the $n_l$ realizations of the function evaluated at $\hat{x}$.) 
-It seems that there are also other natural choices that could be made here for the lower bound. 
-There is some discussion of this choice in the text that follows equations (7)-(9), but can the authors say more?
-For example, do the consistency and asymptotic validity results that follow hinge on this choice?
-Or, do those results also hold for other choices, like forming $\gbb$ as a sample
-mean of the underlying $\gb$ values. 
-We know that the individual gap estimators in (7) are nonnegative, and if we formed $\gbb$ as a sample mean of $\gb$ values, it would be nonnegative. 
-Is the $\gbb$, as specified in (8), nonnegative? 
-Have the authors computationally explored other choices here? 
-Any insight in this vein would be valuable to the reader in understanding the choice made in equation (8).}
+\item \textit{p13, l37: Suggest: is nearly identical to that above.}
 \end{itemize}
 
-\noi
-You are right; we did not fully motivate this choice of $\gbb$.  
-We added explanations after the definition of the OMRP estimators, motivating this choice and relating it to the theoretical results presented in the paper.\smallskip
-
-\noi 
-As you pointed out for the upper bound in (8), this $\gbb$ was chosen for each observation to have equal weight when the sampling problems yield optimal solutions $x_j^* = x^*, \ \forall j$. 
-This fact is used in Lemmas 1 and 2, which are then used---directly or indirectly---in proving Theorems 1--3. 
-When the alternative $\gbb$, formed as a sample mean of $\gb$ values, is used, 
-a subset of the theoretical results can be established (e.g., $\gbb$ converges almost surely to $\mu_{\hat{x}}$). 
-However, we had difficulty establishing the same asymptotically lower variances for the new $VG$. 
-An alternative is to concurrently adjust the coefficients of the $\dbb$ terms to establish convergence of the new $\gbb$, $VG$, etc.\ to their nonoptimized counterparts $\dbb$, $VD$, etc.
-When the coefficients of $\dbb$ are adjusted, however, $\dbb$ and $VD$ are {\it not exactly} the same as the overlapping estimators of simulation output analysis. 
-Because our results depend on the asymptotic properties of the overlapping estimators already established in the simulation literature, we did not want to make any changes to $\dbb$. 
-It may be still be possible to recover the same results on overlapping using this alternative  $\dbb$ but we did not pursue it here. 
-Due to the lack of theoretical results explained above, we decided not to include or discuss $\gbb$ formed as a sample mean of $\gb$ values, even though it appears as a natural choice. 
-Instead, we expanded the text motivating the current choice of $\gbb$. 
-Based on your comments, we also expanded the text regarding the nonnegativity of $\gbb$. 
-Thank you for your insightful comments. 
+\noindent 
+Deleted this sentence as suggested by Reviewer 2. 
 \medskip
 
-\bigskip
-
-\noi {\large \bf Minor comments:}
-
-\bigskip
-
 \begin{itemize}
-\item[1.] \textit{p1, l49: Suggest: The Overlapping \ldots }
+\item \textit{p17, l58: ``solving'' could be deleted so we don't have the notion of ``solving ... runs''; this may appear elsewhere, too.}
 \end{itemize}
@@
 
-\begin{itemize}
-\item[2.] \textit{p2, l16, l22: overlapping is misspelled twice.}
-\end{itemize}
-
-\noindent 
-Corrected. Thanks for catching these typos.
-\medskip
-
-\begin{itemize}
-\item[3.] \textit{p3, l23: Do the authors mean ``relaxations'' rather than ``relations''?}
-\end{itemize}
-
-\noindent 
-Yes. Corrected. 
-\medskip
-
-\begin{itemize}
-\item[4.] \textit{p3, l38: Suggest: estimator of the optimality gap \ldots}
-\end{itemize}
-
-\noindent 
-Done.
-\medskip
-
-\begin{itemize}
-\item[5.] \textit{p4, l34: Suggest: once the data are generated through a simulation, they \ldots}
-\end{itemize}
-
-\noindent 
-Done. 
-\smallskip
-
-\noi 
-{\it Note:} This sentence now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
-\medskip
-
-\begin{itemize}
-\item[6.] \textit{p4, l42: Suggest: Partial overlap results in fewer batches, hence fewer optimization \ldots}
-\end{itemize}
-
-\noindent 
-We revised this paragraph in order to improve exposition. 
-We used `smaller number of batches' based on the comments of the other referee in the new sentence. 
-\medskip
-
-\noi 
-{\it Note:} The revised sentence now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure) as a result of restructuring the introduction based on the comments of the associate editor and the other referee.
-\medskip
-
-\begin{itemize}
-\item[7.] \textit{p6, l32: Suggest: The degrees \ldots make \ldots}
-\end{itemize}
-
-\noindent 
-We now use denominator instead of degrees of freedom. 
-Therefore, we used `\ldots denominator makes \ldots '
-\medskip
-
-\begin{itemize}
-\item[8.] \textit{p7, l18: While a confidence level of $1-\alpha$ may be consistent with a level of significance of $\alpha$, perhaps this could be reworded (as it seemed to distract this reader a bit).}
-\end{itemize}
-
-\noindent  
-Changed the wording here. Thank you. 
-\medskip
-
-\begin{itemize}
-\item[9.] \textit{p10, l23: Suggest: convergence of the sampled solution \ldots}
-\end{itemize}
-
-\noindent 
-Done. 
-\medskip
-
-\begin{itemize}
-\item[10.] \textit{p12, l53: Suggest: Strong consistency \ldots has been \ldots}
-\end{itemize}
-
-\noindent 
-Done. 
-\medskip
-
-\begin{itemize}
-\item[11.] \textit{p14, l13-14: Suggest: The fringe batches come \ldots The first and last batch are identically \ldots}
-\end{itemize}
-
-\noindent 
-Done. 
-\medskip
-
-\begin{itemize}
-\item[12.] \textit{ p14, l23: Please add $j = 1$ to the sum.}
-\end{itemize}
-
-\noindent 
-Added. Thanks for catching this.
-\medskip
-
-\begin{itemize}
-\item[13.] \textit{p14, l35: The authors have gone to some length to distinguish different types of $A_j$ terms.
-However, this equation has an $\mathbb{E}A_j^2$ term that has been collapsed from a sum, but we don't know ``which $j$''. 
-Should there be a $\max_j \mathbb{E}A_j^2$ or some other treatment here?}
-\end{itemize}
-
-\noindent 
-This is because the center batches are identically distributed. 
-As a result, $\mathbb{E}A_j^2$ for all the center batches $j=\lceil \bar{\gamma}^{-1} \rceil, \ldots,n_b - \lceil \bar{\gamma}^{-1} \rceil$ are the same. 
-To make this clear, we introduced the notation $A_j^c$ for center batches and $A_j^f$ and $A_j^e$ for the fringe batches that appear at the front and end of each set of nonoverlapping batches, respectively.
-We also emphasized that each front fringe batch has an identically distributed pair at the end fringes, and that all the center batches are identically distributed. 
-\medskip
-
-\noi 
-{\it Note:} We added brackets to expectations to improve readability as suggested by the other referee.
-We also removed the second equality to save some space because this equality's result was also equally expressed in the last inequality. 
-\medskip
-
-\begin{itemize}
-\item[14.] \textit{p15, Theorem 3: A hypothesis in the theorem is that $\hat{x} \neq x^*$, and yet the proof starts with the case that $\hat{x} = x^*$. 
-That hypothesis could be removed if the claim had a ``$\geq$'' or this statement could be removed or modified.}
-\end{itemize}
-
-\noindent Thank you for pointing this out and for your careful review.  
-We removed this statement from the proof of Theorem 3 and added it as a remark to the paragraph after the theorem.
-\medskip
-
-\begin{itemize}
-\item[15.] \textit{p17, l44: Suggest: A summary of results \ldots experiments is depicted \ldots}
-\end{itemize}
-
-\noindent 
-Done.
-\medskip
-
-\begin{itemize}
-\item[16.] \textit{p17, l55: Perhaps add a comment on why DB1 may not experience the asymptotic variance reduction? 
-(Is it because it may lack a unique solution?)}
-\end{itemize}
-
-\noindent
-Done.
-\medskip
-
-\begin{itemize}
-\item[17.] \textit{p18, figures: The figures are a bit small and hence can be hard to read without enlarging them (but perhaps this will be taken care of at production).}
-\end{itemize}
-
-\noindent 
-We split these two figures into three and enlarged each graph. 
-We also enlarged the legends in these graphs to improve readability.
-All the new graphs added to the paper in \S 5.4 (Computational Efficiency) are also larger, with legible legends. 
-\medskip
-
-\begin{itemize}
-\item[18.] \textit{p18, l57: The authors speak of coverage probabilities for DB1, but how can this be done without knowing an optimal solution to DB1?}
-\end{itemize}
-
-\noindent 
-We used a Latin hypercube sample of size 50,000 estimate $\mu_{\hat{x}}$ for DB1, which was then used to estimate the coverage probability of the OMRP confidence intervals for this test problem.
-We explain this at the end of \S 5.1 (Test Problems). 
-We also changed the wording in \S 5.3 (Results of Experiments) to make it clear that the coverage probability is estimated for DB1. 
-\medskip
-
-\begin{itemize}
-\item[19.] \textit{p19: It may be possible to expand on the last paragraph of \S 5, in giving guidance on selecting the degree of overlap, depending on the authors' response to comment M1 above.}
-\end{itemize}
-
-\noindent 
-Based on our study of computational efficiency of the OMRP estimators, we  provided an updated and expanded guidance on selecting the degree of overlap. 
-This guidance appears in the last paragraph of \S 5.4 (Computational Efficiency). 
-Thank you for this suggestion.
-
 \end{document}

### 2014-12-29 Referee2_Response_fl.tex
Responses for the minor comments

--- 2014-07-15 Referee2_Response.tex
@@
 
-\
 \begin{center}
-\textbf{\Large Response to Referee 2} 
+\textbf{\Large Response to Reviewer 2} 
 \medskip
+
+on the revision of\\
 
@@
 \noi
-We thank the referee for the helpful comments and suggestions. 
-We incorporated all of the recommended changes and believe the paper is improved as a result. 
+We thank the Reviewer for the careful read and the helpful suggestions. 
+We incorporated all of the recommended changes. 
 Below, we go through in detail these changes. 
@@
 
-%%%%%%%%%%%%%%%%%
-%% Need to be careful with the minor changes. Will these be affected?
-%% Need to CHECK AT THE VERY END... FOR ANY CHANGES on TOP OF these...
-%%    - GB
-%%%%%%%%%%%%%%%%%
-
-\noi  
-{\large \bf General Comments:}
-\medskip
-
 \begin{itemize}
-\item[1.] \textit{The main contributions of the paper need to be stated more clearly and succinctly.}
-\end{itemize}
-
-\noindent 
-You are right. 
-We changed the introduction to clearly state the main contributions of the paper.  
-Please see page four of the revised manuscript. 
-We also clarified the motivation for the work, included new contributions based on the study of computational efficiency (contribution (iv)), and provided a comparison with the proceedings version of the paper (based on the editor-in-chief's suggestion).
-%We believe the presentation of the paper significantly improved.  
-%Thank you.
-\medskip
-
-\begin{itemize}
-\item[2.] \textit{It is not necessary to go into such detail in the OBM review.}
-\end{itemize}
-
-\smallskip
-
-\noindent 
-We shortened and streamlined the OBM review, focusing on the main results used in the paper, by combining two previous sections---\S 2.1 (Overlapping Batch Means) and \S 3.1 (Variably Overlapping Batches)---along with other explanations on OBM that appeared later in the paper.
-The combined review is in the background section, \S 2.1 (Batch Means). 
-To improve readability, we created two subsections: \S 2.1.1 (Nonoverlapping Batch Means) and \S 2.1.2 (Overlapping Batch Means). 
-While we removed a number of equations and shortened the text, we kept some explanations that are necessary for a reader who is not familiar with OBM (e.g., readers with an optimization focus) to follow the main ideas.
-These basic explanations appear, for instance, in the first paragraph of \S 2.1.2 (Overlapping Batch Means).  
-We hope to be able to reach a broader audience this way. 
-As a result of these changes, 
-\begin{itemize}
-	\item[(i)]  instead of former equations (2) and (5), both on overlapping batch means variance estimator, we have only one equation (2);
-
-	\item[(ii)]  the confidence interval estimation using OBM is discussed only once;
-
-	\item[(iii)] the former equation (3) is removed;
-
-	\item[(iv)] the discussion that appeared at the beginning of \S 4.4 (previously: Variance Reduction, now: Lower Variances) is moved to this review section.\medskip
-
-{\it Note:} While making the changes, we realized that `$\alpha$' was used in the current equation (3) and the statement of Theorem 2 as well as the ($1-\alpha$)-level confidence intervals.  
-Therefore, we changed `$\alpha$' in equation (3) and Theorem 2 to `$\beta_{\bar{\gamma}}$'. 
-\end{itemize}
-
-\noi
-With these changes, the OBM review became more streamlined, focusing on the main results used later in the paper. 
-Thank you for this suggestion.
-\medskip
-
-\begin{itemize}
-\item[3.] \textit{The English needs to be tightened up somewhat.}
-\end{itemize}
-
-\noindent  
-We went through the paper and tightened up the prose. 
-We also incorporated all the changes you suggested below and believe the exposition of the paper is improved as a result.
-Thank you for your careful review that significantly improved the presentation of the paper. 
-\medskip
-
-\bigskip
-
-\noi  
-{\large \bf Specific Comments:}
-\medskip
-
-\begin{itemize}
-\item[] \textit{Page 1, Line 32 (and elsewhere): I believe that you ``apply the OBM method to stochastic programming'' rather than extend it.}
-\end{itemize}
-
-\noi
-Changed.  
-We also went through the paper to correct other occurrences. 
-In particular, this was also used in \S 6 (Conclusions). 
-We changed the first sentence of \S 6 (Conclusions) to use the word `apply' instead of `extend'. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{1, 35 (and elsewhere): ``We give conditions'' instead of ``We show conditions''}
-\end{itemize}
-
-\noi
-Changed. 
-We also went through the paper and corrected other occurrences. 
-The current version of the paper either has `give conditions' or `provide conditions'. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{1, 37: What are the classical results? Reference?}
-\end{itemize}
-
-\noi
-We reworded this sentence to improve clarity and provided references.   
-\medskip
-
-\begin{itemize}
-\item[] \textit{1, 49: Suggested rewrite to reduce ambiguity: ``The overlapping batch means (OBM) \ldots to obtain variance estimators having variances that are comparatively lower than their nonoverlapped counterparts.
-In the context of steady-state simulation, OBM is often used to estimate the variance of the sample mean, which is itself an estimator for the mean. 
-Schmeiser et al.\ [1990] use overlapping estimators to estimate the
-variance of estimators for non-means. 
-More recently, overlapping estimators based on standardized time series (as opposed to batch means) have been evaluated [Alexopoulos et al., 2007a,b].'' 
-In this rewrite, note the use of active and passive referencing formats.}
-\end{itemize}
-
-\noi
-Thank you for this suggestion of rewrite and for your careful and detailed review of the paper. 
-We rewrote this paragraph based on your corrections.
-We also went through the paper and made changes to the language, paying specific attention to active and passive referencing formats. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 5: ``never before been studied . . . context.''}
-\end{itemize}
-
-\noi
-Changed.
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 7: By ``same benefits'', you mean moderate bias and comparatively low variance, right?}
-\end{itemize}
-
-\noi
-Yes. We reworded this sentence. 
-We also went through the paper and made the context clear whenever phrases like `same benefits', `desired statistical properties', etc.\ were used.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 8: Start a new paragraph with ``A natural setting\ldots ''.}
+\item \textit{Page 1, Abstract: Minor suggested changes as mentioned on annotated copy.}
 \end{itemize}
@@
 \begin{itemize}
-\item[] \textit{2, 10: ``especially'' instead of ``esp.''. 
-Also, ``This'' instead of ``Assessing solution quality in stochastic programming'' (since it's repetitive)}
+\item \textit{2, 6 (and elsewhere): ``Active'' citations should be of the form ``Smith [2013]'', while ``passive'' (``parenthetical'') cites should be of the form ``[Smith, 2013]''.}
 \end{itemize}
@@
 \noi 
-Both done.  
+Checked all and corrected as needed. 
 \medskip
@@
 \begin{itemize}
-\item[] \textit{2, 13: ``Because optimality gap''}
+\item \textit{2, 8: Minor wording suggestions as on annotated copy.}
+\end{itemize}
+
+\noindent 
+Done. 
+\medskip
+
+\begin{itemize}
+\item \textit{5, -3: Footnote can go in main text. Also, $\bar{\bar{y}}$ was already defined.}
+\end{itemize}
+
+\noindent  
+Done. 
+\medskip
+
+\begin{itemize}
+\item \textit{6, 2: Naive question: Are the $y_i$'s independent or possibly correlated in your specific problem application?}
+\end{itemize}
+
+\noi
+Correlated in a particular way. 
+Added a comment on this in Section 2.1.1.
+\medskip
+
+\begin{itemize}
+\item \textit{7: Suggest that you include a couple of references where indicated in annotated copy.}
 \end{itemize}
@@
 \begin{itemize}
-\item[] \textit{2, 24: ``under which the resulting gap estimators exhibit reduced variance when compared to their counterparts obtained via nonoverlapping batches.''}
-\end{itemize}
-
-\noi
-Done.
-\medskip
-
-\noi
-{\it Note:}  We moved this sentence from the paragraph on page 2 to later in the introduction to clearly state the contributions of the paper. 
-It now appears as contribution (ii) on page 4 of the revised manuscript.
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 24 (and elsewhere): Note: I would be careful about the use of the term ``variance reduction'', which usually refers to the class of techniques such as common random numbers, antithetics, importance sampling, etc.
-I view what you're doing in this paper as simply proposing a new estimator whose variance is lower than that of a competing estimator.}
-\end{itemize}
-
-\noi
-You are right. 
-Thanks for pointing this out. 
-We corrected the wording throughout the paper. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 27: ``and that the interval \ldots valid. 
-We also present''}
-\end{itemize}
-
-\noi
-We made the change to the first sentence above. 
-The first sentence now appears as part of contribution (ii) and the second sentence as part of contribution (iii) on page 4 of the revised manuscript. 
-We decided not to include `also' in the second sentence as it starts a new set of contributions. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 28: ``Our experiments indicate that the use of overlapping estimators results in gap estimators achieving lower variance than their nonoverlapping counterparts, along with comparable bias and interval coverage --- for both small- and large-sample cases.}
-\end{itemize}
-
-\noi
-Done.
-\medskip
-
-\noi
-{\it Note:} 
-This sentence now appears as part of contribution (iii) on page 4 of the revised manuscript.
-\medskip
-
-\begin{itemize}
-\item[] \textit{2, 34 (and elsewhere): Might want to boldface all vectors.}
+\item \textit{9, -9: Maybe mention that $x_j^*$ may not be unique.}
 \end{itemize}
@@
 \begin{itemize}
-\item[] \textit{2, 42 (and elsewhere): ``more-restrictive moment'' (hyphenate certain non-adverbial compound adjectives)}
+\item \textit{10, 2 (and elsewhere): Save time and space by defining $n_b =\left\lfloor\tfrac{n_l-m_l}{\gamma_l}\right\rfloor+1$.}
 \end{itemize}
@@
 \noi
-xxx  Done. But I am not sure if it is correct this way.  
-Thank you; we went through the paper and hyphenated all the compound adjectives.
+Done.
+We used the notation $b$ (instead of $n_b$) to denote the number of batches in the general case (Section 2), and we used $b_l$ to denote the above quantity to make the dependence on $l$ explicit.  
 \medskip
@@
 \begin{itemize}
-\item[] \textit{2, 51: You can delete ``(SAA)'', since the notation isn't used again in the paper.}
+\item \textit{13, 7: Not necessary to give all of the details for (ii) (since they're so similar to (i)).}
 \end{itemize}
@@
 \begin{itemize}
-\item[] \textit{3, 11: ``solution; and''}
+\item \textit{14, -9: Pick other notation for ``$dt$'' looks too much like an integrator.}
+\end{itemize}
+
+\noi
+Changed it to $\tau$.
+\medskip
+
+\begin{itemize}
+\item \textit{16, -5: Why the ``complicated'' expression for $Z_l$?}
+\end{itemize}
+
+\noi
+Simplified.
+\medskip
+
+\begin{itemize}
+\item \textit{19--20: Can you combined Figs. 2 and 3?}
 \end{itemize}
@@
 \begin{itemize}
-\item[] \textit{3, 24 (and elsewhere): ``Lagrangian, or'' (comma after penultimate entry in a conjunctive list)}
+\item \textit{21, 9: ``solving overlapping batches'' sounds funny.}
 \end{itemize}
@@
 \noi
-Done.  
-We went through the paper and added commas before `and' and `or' in a list of items with three or more items.
+Reworded.
 \medskip
 
-\begin{itemize}
-\item[] \textit{3, 37: ``we can simply use $z_m^*$''}
-\end{itemize}
-
-\noi
-Done. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{3, 38: ``estimator of the optimality''}
-\end{itemize}
-
-\noi
-Done.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{3, 53: ``The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S 2.2).''}
-\end{itemize}
-
-\noi
-Done. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 5 (and elsewhere): ``see, e.g., Bertocchi et al. [2000]; \ldots ''}
-\end{itemize}
-
-\noi
-We put a comma after `see'; however, we still kept the same referencing style `[Bertocchi et al., 2000; \ldots]' as this sentence refers to the papers and not directly to the authors. 
-We also went through the paper to make sure all `see, e.g.,' have the appropriate commas.
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 14: Delete the sentence ``Especially \ldots '' since it doesn't really add anything to the discussion.}
-\end{itemize}
-
-\noi
-Deleted.
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 17: ``interest is that of estimating''}
-\end{itemize}
-
-\noi
-Done.  
-\medskip
-
-\noi
-{\it Note:}
- As a result of the revised introduction---aimed to clearly state the contributions of the paper---we moved the technical discussion on using overlapping batches in simulation output analysis versus for assessing solution quality in stochastic optimization to \S 3 (Overlapping Multiple Replications Procedure).
-Consequently, this sentence now appears in \S 3. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 20--27: Even though I believe everything, these lines are a bit awkward and confusing.}
-\end{itemize}
-
-\noi
-You are right. 
-We removed the comment on the central limit theorem on the minimized sample means as it is not relevant to the paper. 
-We also reworded these sentences to improve clarity. 
-\bigskip
-
-\noi
-{\it Note:}
-As mentioned in the previous comment, the revised sentences now appear in \S 3 (Overlapping Multiple Replications Procedure). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 31: What are the desired statistical properties?}
-\end{itemize}
-
-\noi
-Thanks for pointing out the ambiguity here. 
-We reworded this sentence, divided it into two sentences to improve readability, and added further explanations to remove any ambiguities. 
-\bigskip
-
-\noi
-{\it Note:}
-The revised sentences now appear in \S 3 (Overlapping Multiple Replications Procedure). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 33: ``Another difference is that''. By the way, what is ``difference'' referring to?}
-\end{itemize}
-
-\noi
-Done.
-We also changed the sentence to make it clear what the ``difference'' is referring to. 
-\medskip
-
-\noi
-{\it Note:}
-This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 36: ``due to the need to solve sampling problem"}
-\end{itemize}
-
-\noi
-Changed it to ``\dots because we need to solve \ldots '' to improve readability.  
-\medskip
-
-\noi
-{\it Note:}
-This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 42: ``Partial overlapping results in a smaller number of batches; hence, fewer optimization''}
-\end{itemize}
-
-\noi
-We revised this section in order to improve exposition. 
-We used `smaller number of batches' based on your suggestion in the revised version. 
-\medskip
-
-\noi 
-{\it Note:} This sentence now appears in the second paragraph of \S 3 (Overlapping Multiple Replications Procedure). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 45: The sentence ``Second, \ldots '' needs some clarification, since it states a conclusion that hasn't so far been justified.}
-\end{itemize}
-
-\noi
-You are right. 
-While we removed the sentence that started with `Second' in an effort to improve readability, we referred to the computational efficiency study added to the paper to justify this remark.   
-\medskip
-
-\noi
-{\it Note:}
-This sentence now appears in \S 3 (Overlapping Multiple Replications Procedure). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 51: ``discuss overlapping''}
-\end{itemize}
-
-\noi
-Done.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 54 (and elsewhere): When you refer to ``variable amounts of overlap'', that is really nothing new.
-Certainly, any overlapping estimator will have end effects in which the overlap amounts differ from those in the ``middle'' region of the data.}
-\end{itemize}
-
-\noi
-%You are right.
-We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
-We reworded this sentence to reflect this. 
-We also went through the paper, removed other occurrences, and avoided using this term in the new text added. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{4, 57 (and elsewhere): ``classical case'' refers to nonoverlapping batch means, right?}
-\end{itemize}
-
-\noi
-No. By `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to assessment of solution quality in stochastic programming). 
-We reworded this sentence to remove ambiguity. 
-Based on your earlier comments, we avoided the term `variance reduction' in the revised sentence.
-We also went through the paper and removed several uses of the word `classical' that referred to nonoverlapping batches to reduce ambiguity.
-%(as these were referring to nonoverlapping batches). 
-%In the current version of the paper, `classical case' is used to only indicate  the use of overlapping batches in simulation output analysis. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{5, 12: Does $\sigma^2$ refer to the marginal variance or the ``variance parameter'' (sum of the covariances at all lags)?}
-\end{itemize}
-
-\noi
-Variance parameter. 
-Thank you.
-We revised this sentence and added a footnote defining the variance parameter for readers who might not be familiar with this term (e.g., readers with an optimization focus). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{5, 14: ``realization of the univariate stochastic''}
-\end{itemize}
-
-\noi
-Done.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{5, 35 (and elsewhere): Careful! This isn't quite the sample variance! This is actually the sample variance multiplied by $m/n$.}
-\end{itemize}
-
-\noi
-Thanks for catching this. 
-We corrected this sentence. 
-Please note that we split this sentence into two to avoid long sentences and to improve exposition. 
-We also checked for other uses of the term `sample variance' throughout the paper and corrected these as needed.
-Thank you.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{5, 43: You could have introduced the notation ``CI'' earlier.}
-\end{itemize}
-
-\noi
-You are right. 
-We now introduce this abbreviation the first time we use the term `confidence interval' in the introduction. 
-From this point on, we use the abbreviated form `CI' throughout the paper, except for the title of \S 4.5 (Asymptotic Validity of the Confidence Intervals). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{5: You can significantly reduce the discussion on OBM here and in \S 3.1. 
-Just let the reader know the main results that you'll use.}
-\end{itemize}
-
-\noi
-We removed \S 3.1 (Variably Overlapping Batches) from the paper. 
-We merged this section with \S 2.1.2 (Overlapping Batch Means), focusing on the results used in the paper. 
-We believe the presentation of the paper improved as a result. 
-Thank you for this suggestion. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{6, 13: ``corresponding overlapping batch means''}
-\end{itemize}
-
-\noi
-Done.  
-We removed the word `corresponding' as part of the rewrite.
-\medskip
-
-\begin{itemize}
-\item[] \textit{6, 29: Note that you use ``Note that'' too often.}
-\end{itemize}
-
-\noi
-We went through the paper and removed most of the ``note that'' phrases. 
-We decided to leave a couple as is (as ``notice that'') because they highlight important characteristics.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{6, 30: Explicitly say what the d.f.\ in (2) is.}
-\end{itemize}
-
-\noi
-We changed this sentence and directly referred to the denominator term.
-We decided to avoid the degrees of freedom here. 
-This is because we wanted to focus on the degrees of freedom for confidence interval construction, which is discussed in both the theoretical and computational results.
-\medskip
-
-\noi 
-{\it Note:} This section has been restructured based on your comments. 
-Equation (2) now gives the general overlapping variance estimator with the parametrized amount of overlap. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{7, 46: Does $\gamma$ need to be an integer? 
-You seem to be using it that way, so maybe state the requirement.}
-\end{itemize}
-
-\noi
-Yes; we explicitly stated this in a sentence after we introduce $\gamma$.
-\medskip
-
-\noi 
-{\it Note:} This sentence now appears in \S 2.1.2 (Overlapping Batch Means). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{8, 4 (and elsewhere): Define notations such as floor and ceiling functions.}
-\end{itemize}
-
-\noi
-Done. 
-%We introduced the floor function before its first use, and we introduced the ceiling function right after its first use.
-\smallskip
-
-\noi 
-{\it Note:} Both definitions appear in \S 2.1.2 (Overlapping Batch Means).
-\medskip
-
-\begin{itemize}
-\item[] \textit{8, 11: In addition to the fact that I don't think ``variance reduction'' is quite the right term, the phrase ``variance reduction in this estimator'' is awkward.}
-\end{itemize}
-
-\noi
-Reworded.\smallskip
-
-\noi 
-{\it Note:} This sentence now appears in \S 2.1.2 (Overlapping Batch Means). 
-\medskip
-
-\begin{itemize}
-\item[] \textit{8, 53--57: The various OBM references should have been discussed earlier.}
-\end{itemize}
-
-\noi
-You are right. 
-We moved these references---in particular, Damerdji (1994, 1995)---to \S 2.1.2 (Overlapping Batch Means) and added a brief discussion.  
-\medskip
-
-\begin{itemize}
-\item[] \textit{10, 11 (and elsewhere): ``$E[f(x, \xi)^4]$'' instead of ``$Ef(x, \xi)^4$'' (never hurts to use some brackets to reduce ambiguity)}
-\end{itemize}
-
-\noi
-Changed.
-In fact, we now use brackets for all the expectations in the paper to improve clarity. 
-Thank you.
-\medskip
-
-\begin{itemize}
-\item[] \textit{11, 33: It might be helpful to add a step before the first inequality in the proof.}
-\end{itemize}
-
-\noi
-Instead of adding another step before the first inequality in the proof of Lemma 1, we added explanations at the beginning of the proof to make this inequality clear.   
-\medskip
-
-\begin{itemize}
-\item[] \textit{12, 52: ``$n_l VD_l$ has been studied''}
-\end{itemize}
-
-\noi
-Done.
-\medskip
-
-\begin{itemize}
-\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet?}
-\end{itemize}
-
-\noi
-This notation was defined before Theorem 1. 
-We moved the definitions of $\sigma_{\hat{x}}$ and $\mu_{\hat{x}}$ to the end of \S 4.2 (Nonoptimized Counterparts) to improve clarity. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{In any case, some of the verbiage in this paragraph is a bit repetitive.}
-\end{itemize}
-
-\noi
-We moved the discussion at the first half of this paragraph to the new, combined OBM review in \S 2.1.2 (Overlapping Batch Means). 
-We referred to equation (3) here to remind the readers the basis of the proof.
-The second half of this paragraph deals with the batching structure, and this discussion is moved to the paragraph after the theorem's proof. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{13, 44: Is the expression for d.f. too big?}
-\end{itemize}
-
-\noi
-We now denote it as `dt' to represent the whole denominator term. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{13, 53: The reader might need another step besides C-S to get that inequality.}
-\end{itemize}
-
-\noi
-This is a direct application of the Cauchy-Schwartz inequality $\left(\sum_{j=1}^{n}x_j y_j\right)^2 \leq \sum_{j=1}^{n}x_j^2 \sum_{j=1}^{n}y_j^2$, where the $y_j$ are all set to $1$. 
-We added a brief explanation after this inequality to make it clear. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{15, 25: Do you discuss $t_{d_l,\alpha}$ at all in Theorem 3?}
-\end{itemize}
-
-\noi
-No, we did not.   
-We added explanations in the proof Theorem 3, discussing how $t_{d_l,\alpha}$ factors in the proof. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{18: Your figures are very difficult to read, even with the pdf file.}
-\end{itemize}
-
-\noi
-We split these two figures into three and enlarged each graph. 
-We also enlarged the legends in these graphs to improve readability.
-All the new graphs added to the paper in \S 5.4 (Computational Efficiency) are also larger, with legible legends. 
-\medskip
-
-\begin{itemize}
-\item[] \textit{20, 47: ``4th edition''}
-\end{itemize}
-
-\noi
-Done.
-\medskip
-
-\begin{itemize}
-\item[] \textit{21, 23: ``\it Jackknife''}
-\end{itemize}
-
-\noi
-Corrected. Thank you.
-
 \end{document}
